---
title: "Figures Used In the Main Document of the Manuscript"
author: "E.T"
format:
  docx:
    toc: true
    fontsize: 10pt
    fig-cap-location: bottom
    fig-numbering: false  
  html:
    toc: true
  pdf:
    toc: true
    knitr:
      opts_chunk:
        dev: "cairo_png"
        dev.args:
        bg: "white" 
editor: visual
---

> This file contains all plots for publication in sequence.

```{r, echo=FALSE, message=FALSE, warning=FALSE}

# setwd("/mnt/pixstor/kingeg-lab/etb68/evogen-sims/FluctSelectionModels.dir/WritingFigures.dir/CodeFigures.dir")

#| label: setup

#| include: false

# Setting the directory containing the document to be the home directory and destination 

document_dir <- Sys.getenv("QUARTO_DOCUMENT_PATH", unset = "")

if (!nzchar(document_dir)) {

  if (requireNamespace("rstudioapi", quietly = TRUE) && rstudioapi::isAvailable()) {
    active_file <- rstudioapi::getActiveDocumentContext()$path
    document_dir <- if (nzchar(active_file)) {
      dirname(active_file)
      } else {
        getwd()
        }
    } else {
      document_dir <- getwd()
    }
  }

document_dir <- normalizePath(
  document_dir, winslash = "/", mustWork = TRUE
)
library(forcats)
library(stringi)
library(tidyr)
library(dplyr)
library(stringr)
library(ggplot2)
library(patchwork)
library(cowplot)
library(purrr)
library(doParallel)

theme_set(theme_cowplot())
mythemes <- function(){
  theme(axis.title = element_text(face = "bold"),
        axis.text = element_text(face = "italic"),
        plot.title = element_text(hjust = 0.5),
        legend.position = "none")
}
```


## 1. Selection Model Setting

### 1.0. Infinitessimal model

```{r, echo=FALSE, fig.width=8, fig.height=4, dpi = 300, warning=FALSE}
#| label: Exponential_Model
########### Infinitisimal Model #################
a = 5
b = 25
x = seq(1:100)
y <- function(x){
  Y = a*exp(-x/b)
}
Y <- y(x)
z = data.frame(Y, x)

Inf_ModPlot <- z %>% ggplot(aes(x,Y))+
  geom_line(linewidth = 2)+
  annotate("text", x = 55, y = max(Y)/1.5, label = "Exponential Effects", fontface = "bold", size = 10) +  #  Add this line
  labs(title = "A", x = "Loci", y = "Effect")+
  theme_set(theme_bw())+
  theme(text = element_text(family = "sans"), 
        legend.position = "none",
        axis.text = element_text(size = 20, face = "bold"),
        axis.line = element_line(size = 3),
        strip.text = element_text(size = 17, face = "bold"),
        plot.title = element_text(hjust = 0.01, face = "bold", size = 40),
        axis.title.x = element_text(margin = margin(t = 20), size = 20, face = "bold"),
        axis.title.y = element_text(margin = margin(r = 25), size = 20, face = "bold"),
        panel.spacing = unit(4, "lines"))

ggsave("Exponential_Model.jpg", plot = Inf_ModPlot, dpi = 300, width = 7, height = 4, units = "in", path = "../OutputFigures.dir")

Inf_ModPlot
```

### 1.1 Constant model

```{r, echo=FALSE, fig.width=8, fig.height=4, dpi = 300, warning=FALSE}
# Generation sequence from 1 to 2000
Generation <- c(1:2000)


# Initialize Optimum vector
Optimum = rep(0, length(Generation))

Optimum <- seq(-4, 4, length.out = 2000)
df <- data.frame(Generation, Optimum) %>% filter(Generation <= 100)

Const_ModPlot <- ggplot(df) + 
  geom_blank(aes(Generation, Optimum, ymax = 4)) +
 # geom_hline(yintercept = 0, color = "darkred", size = 3)+
 #annotate("text", x = 100, y = 0, 
  #         label = "Mean Phenotype", 
  #         size = 10, vjust = -.5, col = "darkred")+
  geom_hline(yintercept = 2, size = 3)+
#annotate("text", x = 100, y = 2.1, label = "Optium", size = 10, vjust = -.5, col = "black")+
  labs(title = "A", x = "Generation", y = "Optimum")+
  theme(text = element_text(family = "sans"), 
        legend.position = "none",
        axis.text = element_text(size = 20, face = "bold"),
        axis.line = element_line(size = 3),
        strip.text = element_text(size = 17, face = "bold"),
        plot.title = element_text(hjust = 0.01, face = "bold", size = 40),
        axis.title.x = element_text(margin = margin(t = 20), size = 30, face = "bold"),
        axis.title.y = element_text(margin = margin(r = 25), size = 30, face = "bold"),
        panel.spacing = unit(4, "lines"))
 
 ggsave("Constant_Model.jpg", plot = Const_ModPlot, dpi = 300, width = 7, height = 4, units = "in", path = "../OutputFigures.dir")
 Const_ModPlot

```

### 1.2 Instantaneous Selection model

```{r, echo=FALSE, fig.width=8, fig.height=4, dpi = 300, warning=FALSE}
#| label: Instant_Model
Opti_Gen <- tibble(Generation = seq(1:100),
                   Optimum1 = rep(c(rep(110, 10), rep(90, 10)), 5),
                   Optimum2 = rep(c(rep(105, 10), rep(95, 10)), 5))

mu_pheno = mean(Opti_Gen$Optimum1)

Opt_Data <- Opti_Gen %>% 
  filter(Generation == 0 | Generation %% 25 != 0)

Instant_Model <- ggplot()+
  geom_line(data = Opt_Data, aes(x = Generation, y = (Optimum1 - 100)/2.5), size = 1)+
  labs(title = "B", x = "Generation", y = "Optimum")+
  theme_set(theme_bw())+ 
  theme(text = element_text(family = "sans"), 
        legend.position = "none",
        axis.text = element_text(size = 20, face = "bold"),
        axis.line = element_line(size = 3),
        strip.text = element_text(size = 17, face = "bold"),
        plot.title = element_text(hjust = 0.01, face = "bold", size = 40),
        axis.title.x = element_text(margin = margin(t = 20), size = 30, face = "bold"),
        axis.title.y = element_text(margin = margin(r = 25), size = 30, face = "bold"),
        panel.spacing = unit(4, "lines"))


ggsave("Instant_Model.jpg", plot = Instant_Model, dpi = 300, width = 7, height = 4, units = "in", path = "../OutputFigures.dir")
 
Instant_Model
```

### 1.3 Gradual Two Season Selection model

```{r, echo=FALSE, fig.width=8, fig.height=4, dpi = 300, warning=FALSE}
#| label: Gradual_Two_Season_Model
Generation <- seq(1, 100, length.out = 400) 
phenotypes <- rnorm(10000, 0, 1)
Optimum <- 10 *sin( pi* Generation / 25) /2.5
df <- data.frame(Generation, Optimum) 

GradI <- ggplot(df) + 
  geom_line(aes(Generation, Optimum), size = 3) + 
  theme_set(theme_bw())+
  labs(title = "C", x = "Generation", y = "Optimum")+
  theme_set(theme_bw())+ 
  theme(text = element_text(family = "sans"), 
        legend.position = "none",
        axis.text = element_text(size = 20, face = "bold"),
        axis.line = element_line(size = 3),
        strip.text = element_text(size = 17, face = "bold"),
        plot.title = element_text(hjust = 0.01, face = "bold", size = 40),
        axis.title.x = element_text(margin = margin(t = 20), size = 30, face = "bold"),
        axis.title.y = element_text(margin = margin(r = 25), size = 30, face = "bold"),
        panel.spacing = unit(4, "lines"))


ggsave("Gradual_Two_Season_Model.jpg", plot = GradI, dpi = 300, width = 7, height = 4, units = "in", path = "../OutputFigures.dir")
 
GradI
```


> A model with four different selection strength

```{r, echo=FALSE, fig.width=8, fig.height=4, dpi = 300, warning=FALSE}
#| label: Gradual_Four_Season_Model_NEW
set.seed(3564);
seasons = c(12,22,10,16);
year = sum(seasons);
sd_values = c(3,1,4,2);
pheno = rnorm(10000);
mu_p = mean(pheno);
sd_p = sd(pheno);

current_time = 1;
year_counter = 1;
season_counter = 1;

total_time = 500;
n_opt = numeric(total_time);

while(current_time <= total_time){
  for(i in seq_along(seasons)){
    if(current_time > total_time) break;
    season_length = seasons[i];
    sd_val = sd_values[i];
    remain_time = total_time - current_time + 1;
    act_length = min(season_length, remain_time);
    
    time_pt = 1:act_length;
    opt = mu_p + sd_val * sd_p * sin(2*pi*time_pt/season_length);
    end_time = current_time + act_length - 1;
    n_opt[current_time:end_time] = opt;
    current_time = current_time + act_length;
    season_counter = current_time + 1;
  }
}

df <- data.frame(Generation = seq(1,total_time), Optimum =  n_opt)

# Plot the Optimum over the first 120 generations marking a two cycles

ggplot(df[1:100,]) + 
    geom_line(aes(Generation, Optimum), size = 3) + 
  ylim(-4, 4) +  
  labs(title = "D", x = "Generation", y = "Optimum")+
  theme_set(theme_bw())+ 
  theme(text = element_text(family = "sans"), 
        legend.position = "none",
        axis.text = element_text(size = 20, face = "bold"),
        axis.line = element_line(size = 3),
        strip.text = element_text(size = 17, face = "bold"),
        plot.title = element_text(hjust = 0.01, face = "bold", size = 40),
        axis.title.x = element_text(margin = margin(t = 20), size = 30, face = "bold"),
        axis.title.y = element_text(margin = margin(r = 25), size = 30, face = "bold"),
        panel.spacing = unit(4, "lines"))
```

> A model with same selection strength

```{r, echo=FALSE, fig.width=8, fig.height=4, dpi = 300, warning=FALSE}
#| label: Gradual_Four_Season_Model_NEW_sameSD
set.seed(3564);
seasons = c(12,22,10,16);
year = sum(seasons);
#sd_values = c(3,1,4,2);
sd_values = c(4,4,4,4);
pheno = rnorm(10000);
mu_p = mean(pheno);
sd_p = sd(pheno);

current_time = 1;
year_counter = 1;
season_counter = 1;

total_time = 500;
n_opt = numeric(total_time);

while(current_time <= total_time){
  for(i in seq_along(seasons)){
    if(current_time > total_time) break;
    season_length = seasons[i];
    sd_val = sd_values[i];
    remain_time = total_time - current_time + 1;
    act_length = min(season_length, remain_time);
    
    time_pt = 1:act_length;
    opt = mu_p + sd_val * sd_p * sin(2*pi*time_pt/season_length);
    end_time = current_time + act_length - 1;
    n_opt[current_time:end_time] = opt;
    current_time = current_time + act_length;
    season_counter = current_time + 1;
  }
}

df <- data.frame(Generation = seq(1,total_time), Optimum =  n_opt)
# 
# # df <- read.csv("~/Mylab/evogen-sims/FluctSelectionModels.dir/Output.dir/SinFSGen.dir/MeanPhenotypes1_n300_H0.8SD4.csv") %>%
# #   dplyr::select(c(Generation, Optimum))
# 
#  df <- read.csv("~/Mylab/evogen-sims/FluctSelectionModels.dir/Output.dir/SinFS.dir/MeanPhenotypes13_n300_H0.5SD1Gen30.csv") %>% 
#    dplyr::select(c(Generation, Optimum))

# Plot the Optimum over the first 120 generations marking a two cycles

ggplot(df[1:100,]) + 
    geom_line(aes(Generation, Optimum), size = 3) +  
  labs(title = "D", x = "Generation", y = "Optimum")+
  theme_set(theme_bw())+ 
  theme(text = element_text(family = "sans"), 
        legend.position = "none",
        axis.text = element_text(size = 20, face = "bold"),
        axis.line = element_line(size = 3),
        strip.text = element_text(size = 17, face = "bold"),
        plot.title = element_text(hjust = 0.01, face = "bold", size = 40),
        axis.title.x = element_text(margin = margin(t = 20), size = 30, face = "bold"),
        axis.title.y = element_text(margin = margin(r = 25), size = 30, face = "bold"),
        panel.spacing = unit(4, "lines"))
```

## 2. Null and Constant Models Comparison
```{r, message=FALSE, echo=FALSE, warning=FALSE}
###############################################################################
# Required Libraries
###############################################################################
library(parallel)
library(doParallel)
library(foreach)
library(dplyr)
library(ggplot2)
library(future)
library(purrr)
library(furrr)
library(cowplot)  
#library(stringr)
###############################################################################
# Custom Theme
###############################################################################
mythemes <- theme_bw() +
  theme(
    plot.title.position = "plot", 
    plot.title = element_text(hjust = 0, vjust = 1, size = 70, face = "bold", margin = margin(b = 10)),
    plot.margin = margin(t = 5, r = 5, b = 5, l = 0),
    text = element_text(family = "sans"), 
    legend.position = "none",
    axis.text.x = element_text(face = "bold", size = 50, angle =25, margin = margin(t = 20), hjust = 1),
    axis.text.y = element_text(face = "bold", size = 50, angle = 15, margin = margin(r = 10)),
    axis.line = element_line(size = 3),
    # plot.title = element_text(hjust = 0, vjust = 1, face = "bold", margin = margin(b = 1, unit = "lines")),
    axis.title.x = element_text(size = 50, face = "bold", margin = margin(t = 30)),
    axis.title.y = element_text(size = 50, face = "bold", margin = margin(r = 35)),
    strip.text = element_text(size = 50, face = "bold"),
    panel.spacing = unit(5, "lines"),
    panel.grid = element_blank()
  )

```

### 2.1. Allele Frequency

```{r, warning=FALSE, fig.width=40, fig.height=20, dpi=300, echo=FALSE, message=FALSE}
#| label: AF_CSNS_model_comparison

first_existing_file <- function(candidates, model_name) {

  existing_files <- candidates[file.exists(candidates)]

  if (length(existing_files) == 0) {
    stop(
      "No file was found for ", model_name, ". Tried:\n",
      paste(candidates, collapse = "\n")
    )
  }

  existing_files[[1]]
}

null_file <- first_existing_file(
  candidates = c(
    "../../Output.dir/NS.dir/genome10_n100_H0.1.csv"
  ),
  model_name = "Null model"
)

constant_low_file <- first_existing_file(
  candidates = c(
    "../../Output.dir/CS.dir/genome10_n100_H0.1SD1Gen10.csv",
    "../../Output.dir/CS.dir/genome10_n100_H0.1SD1.csv"
  ),
  model_name = "Constant model low"
)

constant_high_file <- first_existing_file(
  candidates = c(
    "../../Output.dir/CS.dir/genome10_n100_H0.8SD4Gen30.csv",
    "../../Output.dir/CS.dir/genome10_n100_H0.8SD4.csv"
  ),
  model_name = "Constant model high"
)

###############################################################################
# Read only the columns required for the plot
###############################################################################

read_af_model <- function(file, selection_label) {

  required_columns <- c(
    "Position",
    "Generation",
    "Frequency"
  )

  model_data <- read.csv(
    file,
    stringsAsFactors = FALSE
  )

  missing_columns <- setdiff(
    required_columns,
    names(model_data)
  )

  if (length(missing_columns) > 0) {
    stop(
      basename(file),
      " is missing: ",
      paste(missing_columns, collapse = ", ")
    )
  }

  model_data %>%
    transmute(
      Position = Position,
      Generation = as.numeric(Generation),
      Frequency = as.numeric(Frequency),
      Selection = selection_label
    ) %>%
    filter(
      !is.na(Position),
      is.finite(Generation),
      is.finite(Frequency)
    )
}

null_data <- read_af_model(
  null_file,
  "Null model"
)

constant_low_data <- read_af_model(
  constant_low_file,
  "Constant model low"
)

constant_high_data <- read_af_model(
  constant_high_file,
  "Constant model high"
)

###############################################################################
# Select the same 30 loci in all three models
###############################################################################

common_positions <- Reduce(
  intersect,
  list(
    unique(null_data$Position),
    unique(constant_low_data$Position),
    unique(constant_high_data$Position)
  )
)

if (length(common_positions) == 0) {
  stop(
    "There are no Position values shared by all three model files."
  )
}

###############################################################################
# Effect sizes for highlighted positions
###############################################################################

pos_meta <- tibble::tribble(
  ~Position, ~effect_size,
  982341,     0.000008,
  811499,     3.562828
) %>%
  mutate(
    beta_lab = sprintf(
      "\u03B2=%s",
      signif(effect_size, 3)
    )
  )

missing_highlight_positions <- setdiff(
  pos_meta$Position,
  common_positions
)

if (length(missing_highlight_positions) > 0) {
  warning(
    "The following highlighted positions are not shared by all models: ",
    paste(missing_highlight_positions, collapse = ", ")
  )
}

###############################################################################
# Always retain shared highlighted loci, then sample the remaining loci
###############################################################################

set.seed(12345)

number_of_positions <- min(
  30L,
  length(common_positions)
)

highlight_positions <- intersect(
  pos_meta$Position,
  common_positions
)

if (length(highlight_positions) > number_of_positions) {
  highlight_positions <- highlight_positions[
    seq_len(number_of_positions)
  ]
}

number_random <- number_of_positions -
  length(highlight_positions)

random_pool <- setdiff(
  common_positions,
  highlight_positions
)

random_positions <- if (number_random > 0) {
  sample(
    random_pool,
    size = number_random,
    replace = FALSE
  )
} else {
  numeric(0)
}

selected_positions <- c(
  highlight_positions,
  random_positions
)

###############################################################################
# Combine the three models
###############################################################################

Genome_dataset <- bind_rows(
  null_data,
  constant_low_data,
  constant_high_data
) %>%
  filter(
    Position %in% selected_positions,
    Generation <= 1000
  ) %>%
  mutate(
    Selection = factor(
      Selection,
      levels = c(
        "Null model",
        "Constant model low",
        "Constant model high"
      )
    )
  ) %>%
  left_join(
    pos_meta,
    by = "Position"
  ) %>%
  mutate(
    is_highlight = !is.na(effect_size)
  )

###############################################################################
# Highlight colors
###############################################################################

col_vals <- setNames(
  c(
    "#0072B2",
    "darkred"
  ),
  pos_meta$beta_lab
)


###############################################################################
# Allele-frequency plot
###############################################################################

AF_CSNS_model_comparison <- ggplot(
  Genome_dataset,
  aes(
    x = Generation,
    y = Frequency,
    group = interaction(
      Selection,
      Position
    )
  )
) +
  geom_line(
    data = filter(
      Genome_dataset,
      !is_highlight
    ),
    color = "grey70",
    linewidth = 0.5,
    alpha = 0.6
  ) +
  geom_line(
    data = filter(
      Genome_dataset,
      is_highlight
    ),
    aes(
      color = beta_lab
    ),
    linewidth = 1.1,
    alpha = 0.95
  ) +
  scale_color_manual(
    name = "Effect size",
    values = col_vals,
    drop = FALSE
  ) +
  facet_wrap(
    ~ Selection,
    nrow = 1
  ) +
  labs(
    title = "A) Allele Frequency Dynamics",
    x = "Generation",
    y = "Allele Frequency"
  ) +
  mythemes

###############################################################################
# Save using the new descriptive filename
###############################################################################

output_dir <- "../OutputFigures.dir"

dir.create(
  output_dir,
  recursive = TRUE,
  showWarnings = FALSE
)

jpeg_device <- if (
  requireNamespace(
    "ragg",
    quietly = TRUE
  )
) {
  ragg::agg_jpeg
} else {
  "jpeg"
}

ggsave(
  filename = file.path(
    output_dir,
    "AF_CSNS_model_comparison.jpg"
  ),
  plot = AF_CSNS_model_comparison,
  device = jpeg_device,
  dpi = 300,
  width = 22,
  height = 10,
  units = "in",
  bg = "white",
  limitsize = FALSE
)

print(AF_CSNS_model_comparison)

```

### 2.2. Spectral Analysis Comparison

```{r, warning=FALSE, fig.width=40, fig.height=10, dpi=600, echo=FALSE, message=FALSE}
#| label: Spectral_CSNS_model_comparison

find_preferred_files <- function(
    folder,
    patterns,
    selection_label
) {

  if (!dir.exists(folder)) {
    stop(
      "Directory does not exist: ",
      folder
    )
  }

  for (current_pattern in patterns) {

    files <- list.files(
      path = folder,
      pattern = current_pattern,
      full.names = TRUE
    )

    if (length(files) > 0) {

      return(
        tibble(
          file_path = sort(files),
          Selection = selection_label,
          matched_pattern = current_pattern
        )
      )
    }
  }

  stop(
    "No files found for ",
    selection_label,
    " in ",
    folder,
    ". Patterns tried:\n",
    paste(patterns, collapse = "\n")
  )
}

###############################################################################
# Define the three requested groups
###############################################################################

model_specs <- list(
  list(
    Selection = "Null model",
    folder = "../../Output.dir/NS.dir",
    patterns = c(
      "^genome[0-9]+_n100_H0\\.1\\.csv$"
    )
  ),

  list(
    Selection = "Constant model low",
    folder = "../../Output.dir/CS.dir",
    patterns = c(
      "^genome[0-9]+_n100_H0\\.1SD1Gen10\\.csv$",
      "^genome[0-9]+_n100_H0\\.1SD1\\.csv$"
    )
  ),

  list(
    Selection = "Constant model high",
    folder = "../../Output.dir/CS.dir",
    patterns = c(
      "^genome[0-9]+_n100_H0\\.8SD4Gen30\\.csv$",
      "^genome[0-9]+_n100_H0\\.8SD4\\.csv$"
    )
  )
)

###############################################################################
# Build the file table
###############################################################################

files_df <- bind_rows(
  lapply(
    model_specs,
    function(model_spec) {

      find_preferred_files(
        folder = model_spec$folder,
        patterns = model_spec$patterns,
        selection_label = model_spec$Selection
      )
    }
  )
) %>%
  mutate(
    base_name = basename(file_path),

    replicate = as.integer(
      sub(
        "^genome([0-9]+)_.*$",
        "\\1",
        base_name
      )
    )
  )

if (anyNA(files_df$replicate)) {
  stop(
    "Replicate numbers could not be extracted from all filenames."
  )
}

duplicate_replicates <- files_df %>%
  count(
    Selection,
    replicate,
    name = "number_of_files"
  ) %>%
  filter(
    number_of_files > 1
  )

if (nrow(duplicate_replicates) > 0) {
  print(duplicate_replicates)

  stop(
    "More than one file was selected for at least one model/replicate."
  )
}

###############################################################################
# Calculate the spectrum for one replicate file
###############################################################################

calculate_file_spectrum <- function(
    file_path,
    selection_label,
    replicate_value,
    spectrum_span = 2,
    max_period = 80
) {

  allele_data <- readr::read_csv(
    file_path,
    col_types = readr::cols_only(
      Generation = readr::col_double(),
      Frequency = readr::col_double()
    ),
    progress = FALSE,
    show_col_types = FALSE
  ) %>%
    filter(
      is.finite(Generation),
      is.finite(Frequency)
    )

  if (nrow(allele_data) == 0) {
    stop(
      "No valid observations in: ",
      basename(file_path)
    )
  }

  mean_series <- allele_data %>%
    group_by(
      Generation
    ) %>%
    summarise(
      mean_allele_frequency = mean(
        Frequency,
        na.rm = TRUE
      ),
      .groups = "drop"
    ) %>%
    arrange(
      Generation
    )

  if (nrow(mean_series) < 4) {
    stop(
      "At least four generations are required in: ",
      basename(file_path)
    )
  }

  generation_steps <- diff(
    mean_series$Generation
  )

  if (
    length(generation_steps) == 0 ||
    length(unique(generation_steps)) != 1
  ) {
    stop(
      "Generation intervals are not regular in: ",
      basename(file_path)
    )
  }

  generation_interval <- unique(
    generation_steps
  )

  spectrum_result <- stats::spectrum(
    stats::ts(
      mean_series$mean_allele_frequency,
      frequency = 1
    ),
    spans = spectrum_span,
    plot = FALSE
  )

  spectrum_table <- tibble(
    Period =
      (1 / spectrum_result$freq) *
      generation_interval,

    Spectrum = as.numeric(
      spectrum_result$spec
    ),

    Selection = selection_label,
    replicate = replicate_value
  ) %>%
    filter(
      Period <= max_period
    )

  rm(
    allele_data,
    mean_series,
    spectrum_result
  )

  invisible(gc())

  spectrum_table
}

###############################################################################
# Process each file sequentially, which I did intentionally here. It avoids loading the same large
# CSV files into many parallel worker processes at the same time.
###############################################################################

plot_df <- bind_rows(
  lapply(
    seq_len(nrow(files_df)),
    function(file_index) {

      calculate_file_spectrum(
        file_path =
          files_df$file_path[file_index],

        selection_label =
          files_df$Selection[file_index],

        replicate_value =
          files_df$replicate[file_index],

        spectrum_span = 2,
        max_period = 80
      )
    }
  )
) %>%
  mutate(
    Selection = factor(
      Selection,
      levels = c(
        "Null model",
        "Constant model low",
        "Constant model high"
      )
    ),

    replicate = factor(
      replicate
    )
  )

###############################################################################
# Spectral-density plot
###############################################################################

spec_plot <- ggplot(
  plot_df,
  aes(
    x = Period,
    y = Spectrum,
    color = replicate,
    group = replicate
  )
) +
  geom_line(
    linewidth = 1,
    alpha = 0.9
  ) +
  scale_y_continuous(
    labels = scales::scientific_format()
  ) +
  facet_wrap(
    ~ Selection,
    scales = "free_y",
    ncol = 3
  ) +
  labs(
    title = "B) Spectral Density",
    x = "Period (Generations)",
    y = "Spectral Density",
    color = "Replicate"
  ) +
  mythemes

###############################################################################
# Save the standalone spectral plot
###############################################################################

output_dir <- "../OutputFigures.dir"

dir.create(
  output_dir,
  recursive = TRUE,
  showWarnings = FALSE
)

jpeg_device <- if (
  requireNamespace(
    "ragg",
    quietly = TRUE
  )
) {
  ragg::agg_jpeg
} else {
  "jpeg"
}

ggsave(
  filename = file.path(
    output_dir,
    "Spectral_CSNS_model_comparison.jpg"
  ),
  plot = spec_plot,
  device = jpeg_device,
  dpi = 300,
  width = 30,
  height = 10,
  units = "in",
  bg = "white",
  limitsize = FALSE
)

print(spec_plot)

```


### 2.3 Combined Models comparison

```{r, warning=FALSE, fig.width=58, fig.height=40, dpi=300, echo=FALSE, message=FALSE}
#| label: AF_Spectral_CSNS_model_comparison

###############################################################################
# Prepare the upper allele-frequency panel
###############################################################################

af_panel <- AF_CSNS_model_comparison +
  theme(
    axis.title = element_blank(),

    plot.margin = margin(
      t = 1,
      r = 2,
      b = 1,
      l = 1,
      unit = "lines"
    )
  )

###############################################################################
# Prepare the lower spectral-density panel
###############################################################################

spectral_panel <- spec_plot +
  theme(
    axis.title = element_blank(),

    plot.margin = margin(
      t = 1,
      r = 1,
      b = 1,
      l = 2,
      unit = "lines"
    )
  )

###############################################################################
# Stack the two panels vertically
###############################################################################

AF_Spectral_CSNS_model_comparison <- cowplot::plot_grid(
  af_panel,
  spectral_panel,
  ncol = 1,
  rel_heights = c(
    1,
    1.2
  ),
  align = "v"
)

###############################################################################
# Save the combined figure
###############################################################################

output_dir <- "../OutputFigures.dir"

dir.create(
  output_dir,
  recursive = TRUE,
  showWarnings = FALSE
)

# jpeg_device <- if (
#   requireNamespace(
#     "ragg",
#     quietly = TRUE
#   )
# ) {
#   ragg::agg_jpeg
# } else {
#   "jpeg"
# }

ggsave(
  filename = file.path(
    output_dir,
    "Figure2.jpg" #"AF_Spectral_CSNS_model_comparison.jpg"
  ),
  plot = AF_Spectral_CSNS_model_comparison,
  device = jpeg_device,
  dpi = 300,
  width = 58,
  height = 36,
  units = "in",
  bg = "white",
  limitsize = FALSE
)

print(AF_Spectral_CSNS_model_comparison)

```


## 3. Instantaneous Selection for Polygenic Traits

### 3.1. Polygenic Instantaneous AF

```{r, warning=FALSE, fig.width = 30, fig.height = 30, dpi = 300, echo=FALSE}
###############################################################################
# Function to extract H, SD, and Gen values from filename
###############################################################################
extract_params <- function(filename) {
  base <- basename(filename)
  
  h_value <- as.numeric(sub(".*_H(0\\.[0-9]+).*", "\\1", base))
  sd_value <- as.numeric(sub(".*SD([0-9]+).*", "\\1", base))
  gen_value <- as.numeric(sub(".*Gen([0-9]+).*", "\\1", base))
  
  list(H = h_value, SD = sd_value, Gen = gen_value)
}

###############################################################################
# Main function to read files, process data, and create the plot
###############################################################################
create_plot <- function(path, pattern) {
  file_list <- list.files(path = path, pattern = pattern, full.names = TRUE)
  
  combined_dataset <- map_df(file_list, function(file) {
    data   <- read.csv(file, header = TRUE) %>% 
                filter(Generation <= 1000)
    params <- extract_params(file)
    
    data %>% 
      mutate(
        H = params$H,
        SD = params$SD,
        Gen = params$Gen
      )
  })
  
  # Randomly select at most 15 positions for visibility
  set.seed(12345)
  unique_positions   <- unique(combined_dataset$Position)
  selected_positions <- sample(unique_positions, size = min(30, length(unique_positions)))
  
  filtered_dataset <- combined_dataset %>% 
    filter(Position %in% selected_positions)
  
  # Positions with high and small effect
  
  highlight_colors <- c(
  `982341`  = "#0072B2",
 # `1067762` = "#D55E00",
  #`811499`  = "#009E73",
  #`323379`  = "#CC79A7",
 `811499`  = "darkred",
  other     = "grey70"
)

Freq_Instant_Poly <- filtered_dataset %>%
  mutate(
    H_SD_Gen = paste0("h\u00B2 = ", H, " Δ = ", SD, " Gen = ", Gen),
    pos_key  = dplyr::case_when(
      Position == 982341  ~ "982341",
    #  Position == 1067762 ~ "1067762",
      Position == 811499  ~ "811499",
     # Position == 323379  ~ "323379",
      TRUE ~ "other"
    ),
    line_size = ifelse(pos_key == "other", 0.5, 1.2)
  ) %>% 
  ggplot(aes(x = Generation, y = Frequency,
             group = factor(Position),
             color = pos_key, size = line_size)) +
  geom_line() +
  scale_color_manual(values = highlight_colors) +
  scale_size_identity() +
  facet_wrap(~ H_SD_Gen, scales = "free", ncol = 2, dir = "v") +
  theme_bw() +
  labs(
    title = "A) Allele Frequency",
    x     = "Generation",
    y     = "Frequency"
  ) +
  mythemes
  
  Freq_Instant_Poly
}

path    <- "../../Output.dir/LinFS.dir"
pattern <- "^genome10_n100_H(0\\.1|0\\.8)SD(1|4)Gen(10|30)\\.csv$"
Freq_Instant_Poly <- create_plot(path, pattern)

# Save to file
ggsave(
  filename = "Instant_Poly_AF.jpg",
  plot = Freq_Instant_Poly,
  dpi  = 600,
  width = 30,
  height = 25,
  units  = "in",
  path = "../OutputFigures.dir"
)

# print(Freq_Instant_Poly)

```

### 3.2. Polygenic Instantaneous Phenotypes

```{r, warning=FALSE, fig.width = 25, fig.height = 20, dpi = 300, echo=FALSE}
#| label: Instant_Poly_Pheno
extract_params <- function(filename) {
  h_value <- as.numeric(sub(".*_H(0\\.\\d+).*", "\\1", basename(filename)))
  sd_value <- as.numeric(sub(".*SD(\\d+).*", "\\1", basename(filename)))
  gen_value <- as.numeric(sub(".*Gen(\\d+).*", "\\1", basename(filename)))
  replicate_value <- as.numeric(sub(".*MeanPhenotypes(\\d+)_.*", "\\1", basename(filename)))
  
  list(
    H = h_value,
    SD = sd_value,
    Gen = gen_value,
    Replicate = replicate_value
  )
}

file_list <- list.files(
  path = "../../Output.dir/LinFS.dir",
  pattern = "MeanPhenotypes\\d+_n100_H(0\\.1|0\\.8)SD(1|4)Gen(10|30)\\.csv",
  full.names = TRUE
)

combined_dataset <- map_df(file_list, function(file) {
  data   <- read.csv(file, header = TRUE)
  params <- extract_params(file)
  
  data %>%
    mutate(
      H = params$H,
      SD = params$SD,
      Gen = params$Gen,
      Replicate = params$Replicate,
      Optimum = ifelse(Optimum == max(Optimum, na.rm = TRUE), "High", "Low")
    ) %>%
    filter(
      Generation <= 1000,
      (H == 0.1 & SD == 1 & Gen == 10) |
      (H == 0.8 & SD == 4 & Gen == 30)
    )
})

Pheno_Instant_Poly <- combined_dataset %>% 
  mutate(
    SD_Gen = paste0("Δ = ", SD, " Gen = ", Gen),
    H_SD_Gen = paste0("h\u00B2 = ", H, " Δ = ", SD, " Gen = ", Gen),
    H_SD = paste0("h\u00B2 = ", H, " Δ = ", SD),
    H_label = paste0("h\u00B2 = ", H)
  ) %>% 
  ggplot(aes(x = Generation, y = Phenotype)) +          
    geom_line(aes(group = Replicate), color = "gray50", alpha = 0.5, size = 1) +
    # stat_summary(
    #   fun = mean, aes(group = 1), geom = "line", alpha = 1,     size = 3
    # ) + #  color = "red", 
    facet_wrap(~ H_SD_Gen, scales = "free", ncol = 1, dir = "v") +
    theme_bw() +
    labs(title = "B) Phenotypes", x = "Generation", y = "Phenotype") +
    mythemes

ggsave(
  filename = "Instant_Poly_Pheno.jpg",
  plot = Pheno_Instant_Poly,
  dpi = 300,
  width = 25, 
  height = 15, 
  units = "in", 
  path = "../OutputFigures.dir"
)

# print(Pheno_Instant_Poly)
```

### 3.3. Polygenic Instantaneous Spec Analysis

```{r, warning=FALSE, fig.width = 20, fig.height = 15, echo=FALSE, dpi = 300}
#| label: Instant_Poly_SpecAnalysis

###############################################################################
################## Function for spectral analysis ############################
###############################################################################

run_fft_analysis <- function(folder_path, pattern, spectrum_span = 2) {
  
  # Create the directory to save images if it doesn't exist
  last_dir <- basename(normalizePath(folder_path))
  
  #### Function for AF files
  file_list <- list.files(
    path = folder_path,
    pattern = pattern,
    full.names = TRUE
  )
  
###########################################
######## DataFrame for all replicates #####
###########################################
  
  files_df <- data.frame(file_name = file_list) %>%
    mutate(
  base_name = basename(file_name),
  genome = ifelse(
    grepl("genome\\d+", base_name),
    as.numeric(sub(".*genome(\\d+).*", "\\1", base_name)),
    NA_real_
  ),
  n = ifelse(
    grepl("_n\\d+", base_name),
    as.numeric(sub(".*_n(\\d+).*", "\\1", base_name)),
    NA_real_
  ),
  H = ifelse(
    grepl("_H[0-9]+\\.?[0-9]*", base_name),
    as.numeric(sub(".*_H([0-9]+\\.?[0-9]*).*", "\\1", base_name)),
    NA_real_
  ),
 SD = ifelse(
    grepl("SD[0-9]+(\\.[0-9]+)?", base_name),
    as.numeric(sub(".*SD([0-9]+(?:\\.[0-9]+)?).*", "\\1", base_name)),
    NA_real_
  ),
 Gen = ifelse(
    grepl("Gen\\d+", base_name),
    as.numeric(sub(".*Gen(\\d+).*", "\\1", base_name)),
    NA_real_
  )
)%>%
    mutate(
      param_combination = paste0(
        "n_", n, "_H", H,
        ifelse(!is.na(SD),  paste0("_SD", SD),  ""),
        ifelse(!is.na(Gen), paste0("_Gen", Gen), "")
      )
    )

###...................................#######
### parallelization for files reading #######
###...................................#######
  
  num_cores_to_use <- min(detectCores() - 16, 64) # check the cores before
  cluster_type   <- if (.Platform$OS.type == "windows") "PSOCK" else "FORK"
  cl <- makeCluster(num_cores_to_use, type = cluster_type)
  registerDoParallel(cl)
  
  combined_data_list <- foreach(i = seq_along(files_df$file_name),
                                .packages = c("dplyr")) %dopar% {
    file   <- files_df$file_name[i]
    params <- files_df[i, ]
    df     <- read.csv(file)
    df %>%
      mutate(
        allele_id = as.factor(Position),
        generation  = as.numeric(Generation),
        allele_frequency = Frequency,
        sample_size = 10000,
        file = params$base_name,
        genome = params$genome,
        n = params$n,
        H = params$H,
        SD = params$SD,
        Gen = params$Gen,
        param_combination= params$param_combination
      ) %>%
      dplyr::select(
        allele_id, generation, allele_frequency, sample_size, file,
        genome, n, H, SD, Gen, param_combination
      )
  }
  
  combined_data <- bind_rows(combined_data_list)
  
  stopCluster(cl)
  
  mean_allele_data <- combined_data %>%
    group_by(generation, n, genome, H, SD, Gen, param_combination) %>%
    summarize(mean_allele_frequency = mean(allele_frequency), .groups = "drop")

####'''''''''''''''''''''''#####
#### Convert to time series ####
####'''''''''''''''''''''''#####

  ts_data_list <- mean_allele_data %>%
    group_by(n, genome, H, SD, Gen, param_combination) %>%
    summarize(
      ts_data = list(ts(mean_allele_frequency,
                        start = min(generation),
                        frequency = 1)), #frequency = 1
      .groups = 'drop'
    )
  
### Compute spectral density ####
  
  spec_results_list <- lapply(ts_data_list$ts_data, function(ts_data) {
    spectrum(ts_data, spans = spectrum_span, plot = FALSE)
  })
  
#### Prepare data for plotting
  plot_data_list <- list()
  for (i in seq_along(spec_results_list)) {
    spec_result <- spec_results_list[[i]]
    params      <- ts_data_list[i, ]
    # compute period
    period      <- 1 / spec_result$freq
    
    df_spec <- data.frame(
      Period = period,
      Spectrum = spec_result$spec,
      n = params$n,
      genome = params$genome,
      H = params$H,
      SD = params$SD,
      Gen = params$Gen,
      param_combination = params$param_combination
    ) 
    
    plot_data_list[[i]] <- df_spec
  }
  
  # Combine spectral data
  plot_data <- bind_rows(plot_data_list)
  
  # Limit Period by threshold for each param_combination 
  plot_data <- plot_data %>%
    group_by(param_combination) %>%
    mutate(
      threshold = case_when(
        Gen == 10 ~ 40,  # keep period < 40 if Gen=10
        Gen == 30 ~ 80,  # keep period < 80 if Gen=30
        TRUE      ~ max(Period)
      )
    ) %>%
    ungroup() %>%
    # Keep only the two combos: (H=0.1,SD=1,Gen=10) or (H=0.8,SD=4,Gen=30)
    filter(
      Period < threshold &
      (
        (H == 0.1 & SD == 1 & Gen == 10) | 
        (H == 0.8 & SD == 4 & Gen == 30)
      )
    )
  
  # Creating labels 
  plot_data <- plot_data %>%
    mutate(
      H_label  = paste0("H = ", H),
      SD_label = ifelse(!is.na(SD),  paste0("Δ = ", SD),  "No Δ"),
      Gen_label= ifelse(!is.na(Gen), paste0("Gen = ", Gen), "No Gen"),
      H_SD_Gen = paste0("h\u00B2 = ", H, " Δ=", SD, " Gen=", Gen)
    )
  
  spec_plot_comb1 <- ggplot( plot_data, 
                            aes(x = Period, y = Spectrum, 
                                color = factor(genome), group = factor(genome))) +
    geom_line(linewidth = 3) +
    facet_wrap(~ H_SD_Gen, scales = "free", ncol = 1) +
    scale_y_continuous(labels = scales::label_number())+
    #scale_y_continuous(labels = scales::label_scientific())+
    labs(
      title = "C) Spectral Density", x = "Period (Generations)", y = "Spectral Density") +
    mythemes
  
  return(spec_plot_comb1)
}

###############################################################################
################## Run The Function for Spectral Analysis ####################
###############################################################################

dirpath   <- "../../Output.dir/LinFS.dir/"
my_pattern<- "^genome\\d+_n100_H0\\.(1|8)(SD(1|4))?(Gen(10|30))?\\.csv$"


final_plot <- run_fft_analysis(dirpath, my_pattern)

ggsave("Instant_Poly_SpecAnalysis_Combined.jpg",
       plot = final_plot,
       dpi = 300, width = 25, height = 15, units = "in",
       path = "../OutputFigures.dir")


# final_plot
```

### 3.4. Combined Polygenic Instantaneous for AF, Pheno, and Spec Analysis

```{r, warning=FALSE, fig.width = 55, fig.height = 40, dpi = 300, echo=FALSE}
#| label: Instant_Poly_AF_Pheno_SpecAnalysis_comb

top_row <- plot_grid(
  Pheno_Instant_Poly, 
  final_plot,
  ncol = 1, 
  rel_heights = c(1, 1)
)

combined_plot <- plot_grid(
  Freq_Instant_Poly, 
  top_row, 
  ncol = 2,
  rel_widths = c(2, 1)
)

ggsave(
  filename = "Figure3.jpg", 
  plot = combined_plot,
  dpi = 600,
  width = 49,
  height = 32,
  units = "in",
  path = "../OutputFigures.dir"
)
combined_plot  

```


## 4. Genetic Architecture: Instantaneous models

### 4.1. AF monogenic, oligogenic, and Polygenic

```{r, warning=FALSE, fig.width = 25, fig.height = 22, dpi = 300, echo=FALSE}
#| label: AF_Mono_Ologo_Poly_Instant
read_files <- function() {
  file_list <- list.files(path = "../../Output.dir/LinFS.dir/", pattern = "genome10_n(1|10)_H0\\.(1|5|8)(SD(1|2|4))?Gen(10|20|30)\\.csv$", full.names = TRUE)
  
  datasets <- lapply(file_list, function(file) {
    data <- read.csv(file)
    matches <- regmatches(file, regexec("genome10_n([0-9]+)_H([0-9\\.]+)SD([0-9]+)Gen([0-9]+)", file))[[1]]
    selection_type <- as.numeric(matches[2])
    selection_label <- ifelse(selection_type == 1, "1 Locus",
                              ifelse(selection_type == 10, "10 Loci", "100 Loci"))
    
    data <- data %>% 
      mutate(Selection = selection_label,
             H = as.numeric(matches[3]),
             SD = as.numeric(matches[4]),
             Gen = as.numeric(matches[5]))
    return(data)
  })
  
  return(bind_rows(datasets))
}

#########################
### Read in the data ####
##########################

Genome_dataset <- read_files() %>% 
  filter(Generation <= 1000) %>% 
  mutate(Selection = fct_relevel(Selection, 
                                 "1 Locus",  
                                 "10 Loci", 
                                 "100 Loci"))

# select up to 15 unique positions for each group
set.seed(123)
selected_positions <- Genome_dataset %>%
  group_by(Selection) %>%
  group_map(~ {
    positions <- unique(.x$Position)
    if (length(positions) > 30) {
      sample(positions, 30)
    } else {
      positions
    }
  }) %>%
  unlist()

filtered_dataset <- Genome_dataset %>%
  filter(Position %in% selected_positions)

filtered_dataset <- filtered_dataset %>%
  filter((H == 0.1 & SD == 1 & Gen == 10) |
         (H == 0.5 & SD == 2 & Gen == 20) |
          (H == 0.8 & SD == 4 & Gen == 30))

filtered_dataset <- filtered_dataset %>%
  mutate(Color = case_when(
    Selection == "1 Locus" ~ "magenta",
    Selection == "10 Loci" & Position == "427101" ~ "magenta", #1037246
    Selection == "100 Loci" & Position == "323379" ~ "magenta", # 201349
    TRUE ~ "black"
  ),
  LineSize = case_when(
    Color == "magenta" ~ 2,
    TRUE ~ 0.5
  ))


AF_Mono_Ologo_Poly_Instant <- filtered_dataset %>%
  filter(Generation <= 1000) %>%
  mutate(H_SD_Gen = paste0("H = ", H, " SD =  ", SD, " Gen = ", Gen)) %>% 
  mutate(
    H_SD_Gen_short = case_when(
      H == 0.1 & SD == 1 & Gen == 10 ~ "Min combo",
      H == 0.5 & SD == 2 & Gen == 20 ~ "Med combo",
      H == 0.8 & SD == 4 & Gen == 30 ~ "High combo"
    )) %>%
  mutate(
    H_SD_Gen_short = fct_relevel(H_SD_Gen_short, "Min combo", "Med combo", "High combo")
  ) %>%
  ggplot(aes(x = Generation, y = Frequency, group = factor(Position), 
              size = LineSize)) + #color = Color,
  geom_line(alpha = 0.7) + 
 # scale_color_identity() +
  scale_size_identity() +
  facet_grid(H_SD_Gen_short ~ Selection) +
  labs(title = "A) Allele Frequency", x = "Generation", y = "Frequency") +
  theme_bw() +
  mythemes

ggsave(
  filename = "AF_Mono_Ologo_Poly_Instant.jpg",
  plot     = AF_Mono_Ologo_Poly_Instant,
  dpi      = 600,
  width    = 49,
  height   = 30,
  units    = "in",
  path     = "../OutputFigures.dir"
)

# AF_Mono_Ologo_Poly_Instant
```

### 4.2. Pheno monogenic, oligogenic, and Polygenic

```{r, warning=FALSE, fig.width = 25, fig.height = 20, dpi = 300, echo=FALSE}
#| label: Pheno_Mono_Oligo_Poly_Instant

dirpath <- "../../Output.dir/LinFS.dir/"
pattern <- "^MeanPhenotypes\\d+_n(1|10)_H0\\.(1|5|8)(SD(1|2|4))?(Gen(10|20|30))?\\.csv$"

process_files <- function(dirpath, pattern) {
  
  # List matching files
  files <- list.files(dirpath, pattern = pattern, full.names = TRUE)
  
  dataframes <- list()
  
  for (file in files) {
    replicate <- as.numeric( sub(".*MeanPhenotypes(\\d+)_.*", "\\1", basename(file)))
    H <- as.numeric( sub(".*_H(0\\.\\d+).*", "\\1", basename(file)))
    loci <- as.numeric( sub(".*_n(\\d+)_.*", "\\1", basename(file)))
    SD <- as.numeric( sub(".*SD(\\d+).*", "\\1", basename(file)))
    Gen <- as.numeric( sub(".*Gen(\\d+).*", "\\1", basename(file)))
    
    
    selection_label <- ifelse(loci == 1, "1 Locus",
                       ifelse(loci == 10, "10 Loci", "100 Loci"))
    
    data <- read.csv(file, header = TRUE) %>%
      mutate(
        H = H,
        loci = loci,
        SD = SD,
        Gen = Gen,
        replicate = as.factor(replicate),
        Selection = selection_label,
        
        h2_sd = paste0("h2 = ", H, " sd = ", SD),
        loci_gen = paste0("loci = ", loci, " gen = ", Gen),
        Fitness = exp(-(1/125) * (Phenotype - Optimum)^2)) %>%
      filter(
        Generation <= 1000
      )
    
    dataframes[[file]] <- data
  }
  
  combined_data <- bind_rows(dataframes)
  
 #combined_data <- combined_data %>%
  #  filter(!replicate %in% c("1", "13", "28"))
  
  return(combined_data)
}

combined_data <- process_files(dirpath, pattern)

Pheno_Mono_Oligo_Poly <- combined_data %>%
  filter(
    (H == 0.1 & SD == 1 & Gen == 10) |
    (H == 0.8 & SD == 4 & Gen == 30)
  ) %>%
  mutate(
    H_SD_Gen_short = case_when(
      H == 0.1 & SD == 1 & Gen == 10 ~ "Min combo",
      H == 0.8 & SD == 4 & Gen == 30 ~ "High combo"
    )
  ) %>%
  mutate(
    H_SD_Gen_short = fct_relevel(H_SD_Gen_short, "Min combo", "High combo")
  ) %>%
  ggplot(aes(x = Generation, y = Phenotype)) +
  geom_line(aes(group = replicate),
            color = "gray50", alpha = 0.7, size = 0.5) +
  # stat_summary(
  #   fun = mean, aes(group = 1), geom = "line",
  #   color = "red", alpha = 0.7, size = 3
  # ) +
  facet_grid(H_SD_Gen_short ~ Selection, scales = "free") +
  labs(
    title = "B) Phenotypes",
    x = "Generation",
    y = "Phenotypes"
  ) +
  theme_bw() +
  mythemes

ggsave(
  filename = "Pheno_Mono_Oligo_Poly.jpg",
  plot     = Pheno_Mono_Oligo_Poly,
  dpi      = 600,
  width    = 49,
  height   = 30,
  units    = "in",
  path     = "../OutputFigures.dir"
)

# Pheno_Mono_Oligo_Poly

```

### 4.3. Spec_Analysis monogenic, oligogenic, and Polygenic

```{r, warning=FALSE, fig.width = 20, fig.height = 20, dpi = 300, echo=FALSE}
#| label: Spec_Analysis_Mono_Oligo_Poly_Instant

run_fft_analysis <- function(folder_path, pattern, spectrum_span = 2) {
  
  # 1) Find all files
  file_list <- list.files(path = folder_path, pattern = pattern, full.names = TRUE)
  
  files_df <- data.frame(file_name = file_list) %>%
    mutate(
      base_name = basename(file_name),
      replicate <- as.numeric( sub(".*genome(\\d+)_.*", "\\1", base_name)),
      genome = ifelse(
        grepl("genome\\d+", base_name),
        as.numeric(sub(".*genome(\\d+).*", "\\1", base_name)),
        NA_real_),
      loci = ifelse(
        grepl("_n\\d+", base_name),
        as.numeric(sub(".*_n(\\d+).*", "\\1", base_name)),
        NA_real_),
      H = ifelse(
        grepl("_H[0-9]+\\.?[0-9]*", base_name),
        as.numeric(sub(".*_H([0-9]+\\.?[0-9]*).*", "\\1", base_name)),
        NA_real_),
      SD = ifelse(
        grepl("SD[0-9]+(\\.[0-9]+)?", base_name),
        as.numeric(sub(".*SD([0-9]+(?:\\.[0-9]+)?).*", "\\1", base_name)),
        NA_real_),
      Gen = ifelse(
        grepl("Gen\\d+", base_name),
        as.numeric(sub(".*Gen(\\d+).*", "\\1", base_name)),
        NA_real_),
     Selection = case_when(
        loci == 1 ~ "1 Locus",
        loci == 10 ~ "10 Loci",
        TRUE ~ "Unknown"
      ),
      
      param_combination = paste0(
        "loci_", loci, "_H", H, 
        ifelse(!is.na(SD), paste0("_SD", SD), ""), 
        ifelse(!is.na(Gen), paste0("_Gen", Gen), "")
      )
    )

  num_cores_to_use <- min(detectCores() - 16, 64) # check the cores before
  cluster_type   <- if (.Platform$OS.type == "windows") "PSOCK" else "FORK"
  cl <- makeCluster(num_cores_to_use, type = cluster_type)
  registerDoParallel(cl)

  combined_data_list <- foreach(i = seq_along(files_df$file_name), 
                                .packages = c("dplyr")) %dopar% {
    file  <- files_df$file_name[i]
    params <- files_df[i, ]
    
    df <- read.csv(file) 
    data <- df %>%
      mutate(
        allele_id       = as.factor(Position),
        generation      = as.numeric(Generation),
        allele_frequency= Frequency,
        file            = params$base_name,
        replicate       = params$replicate,
        loci            = params$loci,
        H               = params$H,
        SD              = params$SD,
        Gen             = params$Gen,
        Selection       = params$Selection,
        param_combination = params$param_combination
      ) %>%
      dplyr::select(
        allele_id, generation, allele_frequency, replicate, 
        loci, H, SD, Gen, Selection, param_combination
      )
    data
  }
  combined_data <- bind_rows(combined_data_list)
  
  filtered_data <- combined_data %>%
    filter(
      (Selection == "1 Locus"  & H == 0.1 & SD == 1 & Gen == 10) |
      (Selection == "1 Locus"  & H == 0.8 & SD == 4 & Gen == 30) |
      (Selection == "10 Loci" & H == 0.1 & SD == 1 & Gen == 10) |
      (Selection == "10 Loci" & H == 0.8 & SD == 4 & Gen == 30)
    )

  mean_allele_data <- filtered_data %>%
    group_by(generation, loci, replicate, H, SD, Gen, Selection, param_combination) %>%
    summarize(
      mean_allele_frequency = mean(allele_frequency), 
      .groups = "drop"
    )

  ts_data_list <- mean_allele_data %>%
    group_by(loci, replicate, H, SD, Gen, Selection, param_combination) %>%
    summarize(
      ts_data = list(ts(mean_allele_frequency, 
                        start = min(generation),
                        frequency = 1)),
      .groups = 'drop'
    )

  spec_results_list <- foreach(i = 1:nrow(ts_data_list), .packages = c("stats")) %dopar% {
    ts_data <- ts_data_list$ts_data[[i]]
    spectrum(ts_data, spans = spectrum_span, plot = FALSE)
  }

  plot_data_list <- foreach(i = seq_along(spec_results_list),
                            .packages = c("dplyr")) %dopar% {
    spec_result <- spec_results_list[[i]]
    params <- ts_data_list[i, ]
    period <- 1 / spec_result$freq
    
    data.frame(
      Period    = period,
      Spectrum  = spec_result$spec,
      loci      = params$loci,
      replicate = params$replicate,
      H         = params$H,
      SD        = params$SD,
      Gen       = params$Gen,
      Selection = params$Selection,
      param_combination = params$param_combination
    )
  }

  stopCluster(cl) 
  
  plot_data <- bind_rows(plot_data_list) %>%
    group_by(param_combination) %>%
    mutate(
      threshold = case_when(
        Gen == 10 ~ 40,
        Gen == 20 ~ 50,
        Gen == 30 ~ 80,
        TRUE      ~ max(Period)
      )
    ) %>%
    filter(Period < threshold) %>%
    ungroup() %>%
    mutate(
      H_SD_Gen  = paste0("H = ", H, " SD = ", SD, " Gen = ", Gen),
      H_SD      = paste0("H = ", H, " SD = ", SD),
      H_SD_Gen_short = case_when(
            H == 0.1 & SD == 1 & Gen == 10 ~ "Min combo",
            H == 0.8 & SD == 4 & Gen == 30 ~ "High combo")
    ) %>%
    mutate(H_SD_Gen_short = fct_relevel(H_SD_Gen_short, "Min combo", "High combo"))

  if (any(is.na(plot_data$Gen))) {
    fft_plots <- ggplot(
      plot_data, 
      aes(x = Period, y = Spectrum, color = factor(replicate), group = factor(replicate))
    ) +
      geom_line(linewidth = 1.5) +
      facet_wrap(H_SD ~ Selection, scales = "free") +
      scale_y_continuous(labels = scales::label_number())+
      labs(title = "C) Spectral Density", x = "Period (Generations)", y = "Spectral Density") +
      mythemes
  } else {
    fft_plots <- ggplot(
      plot_data %>% mutate(facetgrouping = paste0(Selection, ": ", H_SD_Gen_short)) %>% 
        mutate(facetgrouping = fct_relevel(facetgrouping, "1 Locus: Min combo", 
                                           "1 Locus: High combo",
                                           "10 Loci: Min combo",
                                           "10 Loci: High combo")),
      aes(x = Period, y = Spectrum, color = factor(replicate), group = factor(replicate))
    ) +
      geom_line(linewidth = 1.5) +
      scale_y_continuous(labels = scales::label_number())+
      facet_wrap(~ facetgrouping, scales = "free", ncol = 1) +
      #facet_grid(Selection ~ H_SD_Gen_short, scales = "free") +
      labs(title = "C) Spectral Density", x = "Period (Generations)", y = "Spectral Density") +
      mythemes
  }

  return(fft_plots)
}

dirpath <- "../../Output.dir/LinFS.dir/"
pattern <- "^genome\\d+_n(1|10)_H0\\.(1|5|8)(SD(1|2|4))?Gen(10|20|30)\\.csv$"

Spec_Mono_Oligo_Poly <- run_fft_analysis(dirpath, pattern)

ggsave(
  filename = "Spec_Mono_Oligo_Poly.jpg",
  plot = Spec_Mono_Oligo_Poly,
  dpi = 600,
  width = 20,
  height = 30,
  units = "in",
  path = "../OutputFigures.dir"
)

# Spec_Mono_Oligo_Poly

```

### 4.4. Genome architecture all models Polygenic Instantaneous: AF, Pheno, and Spec Analysis

```{r, warning=FALSE, fig.width = 44, fig.height = 40, dpi = 300, echo=FALSE}
#| label: All_Instant_Mono_Oligo_Poly
#| 
top_plot     <- AF_Mono_Ologo_Poly_Instant + theme(plot.margin = margin(b = 20))
bottom_left  <- Pheno_Mono_Oligo_Poly + theme(plot.margin = margin(r = 20, b = 20))
bottom_right <- Spec_Mono_Oligo_Poly   + theme(plot.margin = margin(l = 20, b = 20))


All_Mono_Oligo_Poly <- plot_grid(plot_grid(top_plot, bottom_left, 
                                           ncol = 1, 
                                           rel_heights = c(2.4, 2)), 
                                 bottom_right, rel_widths = c(2, 1.2))

ggsave("Figure4.jpg", #All_Instant_Mono_Oligo_Poly.jpg 
       plot = All_Mono_Oligo_Poly, 
       dpi = 600, 
       width = 44, 
       height = 40, 
       units = "in", 
       path = "../OutputFigures.dir")

All_Mono_Oligo_Poly

```

## 5. Amplitude Calculation for Selection selection models

```{r, fig.width=30, fig.height=15}
library(dplyr)
library(ggplot2)
library(stringr)
library(purrr)
library(tidyr)
library(future)
library(furrr)
library(RColorBrewer)

###############################################################################
########################## Settings ############################################
###############################################################################

folder_path <- "~/Mylab/evogen-sims/FluctSelectionModels.dir/Output.dir/LinFS.dir"
plot_dir <- "../OutputFigures.dir"

dir.create(plot_dir, recursive = TRUE, showWarnings = FALSE)

target_n <- c(1, 10, 100, 300)
target_H <- c(0.1, 0.8)
target_SD <- c(1,2,3, 4)
target_Gen <- c(10, 20, 30)

target_replicate_for_dynamics <- 10
last_n_generations <- 1000
n_bins_to_show <- 30

n_workers <- 32
plan(multisession, workers = n_workers)

###############################################################################
########################## Theme ###############################################
###############################################################################

theme_amp <- theme_bw() +
  theme(
    text = element_text(family = "sans"),
    legend.position = "right",
    axis.text.x = element_text(
      face = "bold",
      size = 30,
      angle = 50,
      margin = margin(t = 20),
      hjust = 1
    ),
    axis.text.y = element_text(
      face = "bold",
      size = 30,
      angle = 15,
      margin = margin(r = 10)
    ),
    axis.line = element_line(linewidth = 3),
    plot.title = element_text(
      hjust = 0.01,
      face = "bold",
      size = 50,
      margin = margin(b = 1, unit = "lines")
    ),
    plot.margin = unit(c(5, 1, 1, 1), "lines"),
    axis.title.x = element_text(
      size = 30,
      face = "bold",
      margin = margin(t = 30)
    ),
    axis.title.y = element_text(
      size = 30,
      face = "bold",
      margin = margin(r = 35)
    ),
    strip.text = element_text(size = 30, face = "bold"),
    legend.title = element_text(size = 24, face = "bold"),
    legend.text = element_text(size = 20),
    panel.spacing = unit(5, "lines"),
    panel.grid = element_blank()
  )

###############################################################################
########################## File list ###########################################
###############################################################################

files <- list.files(
  path = folder_path,
  pattern = "^genome[0-9]+_n[0-9]+_H[0-9.]+SD[0-9.]+Gen[0-9]+\\.csv$",
  full.names = TRUE
)

if (length(files) == 0) {
  stop("No files found. Check folder_path and file pattern.")
}

###############################################################################
########################## Extract parameters ##################################
###############################################################################

extract_params_FewerGen <- function(file_path) {
  
  file_name <- basename(file_path)
  
  tibble(
    file = file_path,
    file_name = file_name,
    replicate = as.numeric(str_match(file_name, "genome([0-9]+)_")[, 2]),
    n = as.numeric(str_match(file_name, "_n([0-9]+)_")[, 2]),
    H = as.numeric(str_match(file_name, "H([0-9.]+)SD")[, 2]),
    SD = as.numeric(str_match(file_name, "SD([0-9.]+)Gen")[, 2]),
    Gen = as.numeric(str_match(file_name, "Gen([0-9]+)\\.csv")[, 2])
  )
}

param_table_FewerGen <- map_dfr(files, extract_params_FewerGen) %>% 
  filter(
    n %in% target_n,
    H %in% target_H,
    SD %in% target_SD,
    Gen %in% target_Gen
  ) %>% 
  arrange(n, H, SD, Gen, replicate) %>% 
  mutate(
    parameter_combo = paste0(
      "n = ", n,
      ", h\u00B2 = ", H,
      ", Δ = ", SD,
      ", Gen = ", Gen
    )
  )

if (nrow(param_table_FewerGen) == 0) {
  stop("No files remain after filtering. Check target_n, target_H, target_SD, and target_Gen.")
}

###############################################################################
########################## Calculate amplitudes ################################
###############################################################################

calculate_amplitude_FewerGen_model <- function(
    file, file_name, replicate, n, H, SD, Gen, parameter_combo
) {
  
  fl <- read.csv(file)
  
  required_cols <- c("Generation", "Frequency")
  
  if (!all(required_cols %in% names(fl))) {
    message("Skipping file because required columns are missing: ", file_name)
    message("Columns found: ", paste(names(fl), collapse = ", "))
    return(NULL)
  }
  
  fl <- fl %>%
    mutate(
      Generation = as.numeric(Generation),
      Frequency = as.numeric(Frequency)
    )
  
  max_generation <- max(fl$Generation, na.rm = TRUE)
  min_generation_to_keep <- max_generation - last_n_generations + 1
  
  fl <- fl %>% 
    filter(Generation >= min_generation_to_keep)
  
  flsum <- fl %>% 
    group_by(Generation) %>% 
    summarize(
      Mu_af = mean(Frequency, na.rm = TRUE),
      .groups = "drop"
    ) %>% 
    arrange(Generation) %>% 
    mutate(
      Gen_bin = floor((Generation - 1) / Gen),
      Gen_start = Gen_bin * Gen + 1,
      Gen_end = Gen_start + Gen - 1,
      Gen_label = paste0(Gen_start, "-", Gen_end)
    )
  
  amp_by_interval <- flsum %>% 
    group_by(
      Gen_bin,
      Gen_start,
      Gen_end,
      Gen_label
    ) %>% 
    summarize(
      start_generation = min(Generation, na.rm = TRUE),
      end_generation = max(Generation, na.rm = TRUE),
      n_generations_observed = n_distinct(Generation),
      start_freq = Mu_af[Generation == start_generation][1],
      end_freq = Mu_af[Generation == end_generation][1],
      signed_change = end_freq - start_freq,
      amplitude = abs(signed_change),
      .groups = "drop"
    ) %>% 
    filter(
      n_generations_observed == Gen,
      start_generation == Gen_start,
      end_generation == Gen_end
    ) %>% 
    mutate(
      replicate = replicate,
      n = n,
      H = H,
      SD = SD,
      Gen = Gen,
      file_name = file_name,
      parameter_combo = parameter_combo
    )
  
  return(amp_by_interval)
}

amp_all_FewerGen <- future_pmap_dfr(
  param_table_FewerGen,
  calculate_amplitude_FewerGen_model,
  .progress = TRUE,
  .options = furrr_options(
    seed = TRUE,
    packages = c("dplyr", "stringr", "tidyr")
  )
)

if (nrow(amp_all_FewerGen) == 0) {
  stop("No usable data were produced. Check file pattern, target_n, and column names.")
}

###############################################################################
########################## Replicate summaries #################################
###############################################################################

amp_rep_FewerGen <- amp_all_FewerGen %>% 
  group_by(
    n,
    H,
    SD,
    Gen,
    parameter_combo,
    replicate
  ) %>% 
  summarize(
    mean_rep_amplitude = mean(amplitude, na.rm = TRUE),
    median_rep_amplitude = median(amplitude, na.rm = TRUE),
    sd_rep_amplitude = sd(amplitude, na.rm = TRUE),
    n_intervals = n(),
    .groups = "drop"
  )

###############################################################################
########################## Parameter summaries #################################
###############################################################################

amp_param_FewerGen <- amp_rep_FewerGen %>% 
  group_by(
    n,
    H,
    SD,
    Gen,
    parameter_combo
  ) %>% 
  summarize(
    n_replicates = n(),
    mean_amplitude = mean(mean_rep_amplitude, na.rm = TRUE),
    median_amplitude = median(mean_rep_amplitude, na.rm = TRUE),
    sd_amplitude = sd(mean_rep_amplitude, na.rm = TRUE),
    se_amplitude = sd(mean_rep_amplitude, na.rm = TRUE) / sqrt(n()),
    min_amplitude = min(mean_rep_amplitude, na.rm = TRUE),
    max_amplitude = max(mean_rep_amplitude, na.rm = TRUE),
    .groups = "drop"
  ) %>% 
  arrange(n, H, SD, Gen) %>%
  mutate(
    mean_amplitude_scaled = mean_amplitude,
    se_amplitude_scaled = se_amplitude
  )


plan(sequential)
```

```{r, fig.width=20, fig.height=10, echo=FALSE, warning=FALSE}

###############################################################################
########################## Scatter summary plot ################################
###############################################################################

pp_FewerGen_ranked <- ggplot(
  amp_param_FewerGen,
  aes(
    x = as.integer(SD),
    y = mean_amplitude, 
    color = factor(H),
    group = interaction(H, Gen),
    shape = factor(Gen)
  )
) +
  geom_errorbar(
    aes(
      ymin = mean_amplitude - se_amplitude, 
      ymax = mean_amplitude + se_amplitude,
      group = interaction(H, Gen)
    ),
    width = 0.5,
    linewidth = 1,
    position = position_dodge(width = 0.5)
  ) +
  geom_point(
    aes(
      group = interaction(H, Gen)
    ),
    size = 8,
    alpha = 0.9,
    position = position_dodge(width = 0.5)
  ) +
  facet_wrap(~ paste0("Architecture = ", n, " loci"), scales = "free_y") +
  labs(
    x = "Δ values",
    y = "Mean amplitude", 
    color = "h²",
    shape = "Gen"
  ) +
  theme_amp +
  theme(
    plot.margin = unit(c(6, 6, 1, 1), "lines")
  )

pp_FewerGen_ranked



ggsave(
  filename = file.path(plot_dir, "Figure5.jpg"),#FewerGen_model_H_SD_Gen_n_scatter_mean_amplitude.jpg
  plot = pp_FewerGen_ranked,
  width = 25,
  height = 15,
  dpi = 300
)

```


## 6. Sampled Generations Spectral Analysis to imitate empirical studies

```{r, warning=FALSE, fig.width=20, fig.height=10, echo=FALSE, dpi=300, message=FALSE}
#| label: HighParam_Seasonal_vs_Null_SpectralDensity

library(dplyr)
library(ggplot2)

###############################################################################
# Calculate 10-sample spectral densities for one model
###############################################################################

calculate_sampled_spectra <- function(
    folder,
    pattern,
    selection_type,
    sampling_generation = 30,
    n_samples = 10,
    spectrum_span = 2
) {

  files <- list.files(
    path = folder,
    pattern = pattern,
    full.names = TRUE
  )

  if (length(files) == 0) {
    stop(
      "No files matched the pattern:\n",
      pattern,
      "\nin directory:\n",
      normalizePath(folder, mustWork = FALSE)
    )
  }

  file_information <- data.frame(
    file = files,
    replicate = as.integer(
      sub(
        "^genome([0-9]+)_.*$",
        "\\1",
        basename(files)
      )
    ),
    stringsAsFactors = FALSE
  )

  if (anyNA(file_information$replicate)) {
    stop(
      "Replicate numbers could not be extracted from all filenames in: ",
      folder
    )
  }

  if (anyDuplicated(file_information$replicate)) {
    stop(
      "More than one matching file was found for at least one replicate in: ",
      folder
    )
  }

  file_information <- file_information[
    order(file_information$replicate),
    ,
    drop = FALSE
  ]

  sampling_plan <- data.frame(
    sampling_scheme = c(
      "End",
      "Mid & End"
    ),
    sampling_interval = c(
      sampling_generation,
      sampling_generation / 2
    ),
    stringsAsFactors = FALSE
  )

  spectra_by_file <- lapply(
    seq_len(nrow(file_information)),
    function(file_index) {

      current_file <- file_information$file[file_index]
      replicate_value <- file_information$replicate[file_index]

      #########################################################################
      # Read only the columns needed for this figure
      #########################################################################

      simulation_data <- readr::read_csv(
        current_file,
        col_types = readr::cols_only(
          Generation = readr::col_double(),
          Frequency = readr::col_double()
        ),
        progress = FALSE,
        show_col_types = FALSE
      ) %>%
        filter(
          is.finite(Generation),
          is.finite(Frequency)
        )

      if (nrow(simulation_data) == 0) {
        stop(
          "No valid Generation/Frequency observations in: ",
          basename(current_file)
        )
      }

      #########################################################################
      # Calculate End and Mid & End spectra
      #########################################################################

      spectra_by_scheme <- lapply(
        seq_len(nrow(sampling_plan)),
        function(scheme_index) {

          sampling_scheme <-
            sampling_plan$sampling_scheme[scheme_index]

          sampling_interval <-
            sampling_plan$sampling_interval[scheme_index]

          sampled_generations <- seq(
            from = sampling_interval,
            by = sampling_interval,
            length.out = n_samples
          )

          mean_frequency <- simulation_data %>%
            filter(
              Generation %in% sampled_generations
            ) %>%
            group_by(Generation) %>%
            summarise(
              mean_allele_frequency = mean(
                Frequency,
                na.rm = TRUE
              ),
              .groups = "drop"
            ) %>%
            arrange(Generation)

          missing_generations <- setdiff(
            sampled_generations,
            mean_frequency$Generation
          )

          if (length(missing_generations) > 0) {
            stop(
              "File ",
              basename(current_file),
              " is missing sampled generation(s): ",
              paste(
                missing_generations,
                collapse = ", "
              )
            )
          }

          if (any(
            !is.finite(
              mean_frequency$mean_allele_frequency
            )
          )) {
            stop(
              "Non-finite mean allele frequencies were calculated for: ",
              basename(current_file)
            )
          }

          if (nrow(mean_frequency) < 4) {
            stop(
              "At least four sampled time points are required for: ",
              basename(current_file)
            )
          }

          spectrum_result <- stats::spectrum(
            stats::ts(
              mean_frequency$mean_allele_frequency,
              frequency = 1
            ),
            spans = spectrum_span,
            plot = FALSE
          )

          data.frame(
            Period =
              (1 / spectrum_result$freq) *
              sampling_interval,

            Spectrum = as.numeric(
              spectrum_result$spec
            ),

            replicate = replicate_value,
            selection_type = selection_type,
            sampling_scheme = sampling_scheme,

            stringsAsFactors = FALSE
          )
        }
      )

      #########################################################################
      # Release the raw allele-frequency data before reading the next file
      #########################################################################

      rm(simulation_data)
      invisible(gc())

      bind_rows(spectra_by_scheme)
    }
  )

  bind_rows(spectra_by_file) %>%
    filter(
      Period >= 1,
      Period <= 5 * sampling_generation
    )
}

###############################################################################
# High-parameter seasonal model
#
# h² = 0.8
# Δ  = 4
# Gen = 30
###############################################################################

seasonal_spectra <- calculate_sampled_spectra(
  folder = "../../Output.dir/LinFS.dir/",
  pattern =
    "^genome[0-9]+_n100_H0\\.8SD4Gen30\\.csv$",
  selection_type = "Seasonal",
  sampling_generation = 30,
  n_samples = 10,
  spectrum_span = 2
)

###############################################################################
# High-heritability null model
#
# The null model has no true season length.
# Gen = 30 is used only to define matched sampling generations.
###############################################################################

null_spectra <- calculate_sampled_spectra(
  folder = "../../Output.dir/NS.dir/",
  pattern =
    "^genome[0-9]+_n100_H0\\.8\\.csv$",
  selection_type = "Null",
  sampling_generation = 30,
  n_samples = 10,
  spectrum_span = 2
)

###############################################################################
# Combine seasonal and null spectral-density results
###############################################################################

combined_high_seasonal_Null <- bind_rows(
  seasonal_spectra,
  null_spectra
) %>%
  mutate(
    replicate = factor(replicate),

    selection_type = factor(
      selection_type,
      levels = c(
        "Seasonal",
        "Null"
      )
    ),

    sampling_scheme = factor(
      sampling_scheme,
      levels = c(
        "End",
        "Mid & End"
      )
    ),

    comparison_label = case_when(
      selection_type == "Seasonal" ~
        "Seasonal: h² = 0.8, Δ = 4, Gen = 30",

      selection_type == "Null" ~
        "Null: h² = 0.8, assumed Gen = 30"
    ),

    comparison_label = factor(
      comparison_label,
      levels = c(
        "Seasonal: h² = 0.8, Δ = 4, Gen = 30",
        "Null: h² = 0.8, assumed Gen = 30"
      )
    )
  )

###############################################################################
# Remove model-specific intermediate tables
###############################################################################

rm(
  seasonal_spectra,
  null_spectra
)

invisible(gc())

###############################################################################
# Original comparison theme
###############################################################################

theme_spectral_compare <- theme_classic() +
  theme(
    text = element_text(
      family = "sans"
    ),

    legend.position = "none",

    axis.text = element_text(
      size = 18,
      face = "bold"
    ),

    axis.title.x = element_text(
      margin = margin(t = 16),
      size = 20,
      face = "bold"
    ),

    axis.title.y = element_text(
      margin = margin(r = 18),
      size = 20,
      face = "bold"
    ),

    axis.line = element_line(
      linewidth = 2.2
    ),

    strip.text = element_text(
      size = 15,
      face = "bold"
    ),

    plot.title = element_text(
      hjust = 0.01,
      face = "bold",
      size = 32
    ),

    panel.spacing = grid::unit(
      2,
      "lines"
    )
  )

###############################################################################
# Create only the requested plot
#
# The original facet expression is retained exactly:
#   - no ncol
#   - no nrow
#   - no custom panel-order variable
###############################################################################

p_high_seasonal_Null <- ggplot(
  combined_high_seasonal_Null,
  aes(
    x = Period,
    y = Spectrum,
    color = replicate,
    group = replicate
  )
) +
  geom_line(
    linewidth = 1.4,
    alpha = 0.85
  ) +
  facet_wrap(
    ~ paste0(
      sampling_scheme,
      " of season | ",
      comparison_label
    ),
    scales = "free"
  ) +
  scale_x_continuous(
    breaks = scales::pretty_breaks(
      n = 5
    )
  ) +
  scale_y_continuous(
    labels = scales::label_number()
  ) +
  labs(
    title =
      "Spectral Density: Seasonal vs Null, High Parameter Combination",

    x = "Period (Generations)",
    y = "Spectral Density",
    color = "Replicate"
  ) +
  theme_spectral_compare

###############################################################################
# Display the plot in the rendered QMD
###############################################################################

print(p_high_seasonal_Null)

###############################################################################
# Save using the original directory and original filenames
###############################################################################

out_dir <- "../OutputFigures.dir"

dir.create(
  out_dir,
  recursive = TRUE,
  showWarnings = FALSE
)

ggsave(
  filename = file.path(
    out_dir,
    "HighParam_Seasonal_vs_Null_SpectralDensity_End_vs_MidEnd.pdf"
  ),
  plot = p_high_seasonal_Null,
  width = 22,
  height = 12,
  units = "in",
  device = "pdf",
  limitsize = FALSE
)

ggsave(
  filename = file.path(
    out_dir,
    "Figure6.jpg" # "HighParam_Seasonal_vs_Null_SpectralDensity_End_vs_MidEnd.jpg"
  ),
  plot = p_high_seasonal_Null,
  width = 22,
  height = 12,
  units = "in",
  dpi = 300,
  device = "jpeg",
  limitsize = FALSE
)

###############################################################################
# Remove objects no longer needed
#
# p_high_seasonal_Null is deliberately retained as the final plot object.
###############################################################################

rm(
  combined_high_seasonal_Null,
  theme_spectral_compare,
  calculate_sampled_spectra,
  out_dir
)

invisible(gc(full = TRUE))
```



## 7. Beyond instantaneous selection: gradual selection models


### 7.1. FS model comparison by genomic architecture


```{r, warning=FALSE, fig.width = 30, fig.height = 22, dpi=600, echo=FALSE}
library(dplyr)
library(ggplot2)

Instat <- read.csv("../../Output.dir/LinFS.dir/genome10_n100_H0.8SD4Gen30.csv")
GradII <-  read.csv("../../Output.dir/SinFS.dir/genome10_n100_H0.8SD4Gen30.csv")
GradIV_1 <- read.csv("../../Output.dir/SinFSGen.dir/genome10_n100_H0.8SD4.csv")
GradIV_2 <- read.csv("../../Output.dir/FourSeasFourAmp.dir/genome10_n100_H0.8.csv")


# Add a column to distinguish the datasets
geno_file <- Instat %>% mutate(Selection = "Instantaneous")
geno_file2 <- GradII %>% mutate(Selection = "Simple Gradual")
geno_file3 <- GradIV_1 %>% mutate(Selection = "Complex Gradual I") #
geno_file4 <- GradIV_2 %>% mutate(Selection = "Complex Gradual II")

Genome_dataset <- rbind(geno_file, 
                        geno_file2, geno_file3, geno_file4) %>% 
  mutate(Selection = fct_relevel(Selection, 
                                 "Instantaneous", 
                                 "Simple Gradual",
                                 "Complex Gradual I",
                                 "Complex Gradual II"))

## Select 30 random positions
  set.seed(12345)
  selected_positions <- Genome_dataset %>%
  distinct(Position) %>%
  sample_n(size = min(30, n()), replace = FALSE) %>%
  pull(Position)

 Genome_dataset <- Genome_dataset %>%
   filter(Position %in% selected_positions)
# Effect sizes for highlighted positions
pos_meta <- tibble::tribble(
  ~Position, ~effect_size,
    982341,   0.000008,
   #1067762,   0.140653,
    811499,   3.562828
   # 323379,   2.431675
) %>%
  mutate(beta_lab = sprintf("\u03B2=%s", signif(effect_size, 3)))

# Colors (Okabe–Ito palette)
col_vals <- setNames(
  c("#0072B2", "darkred"),#"#D55E00", "#009E73", "#CC79A7"
  pos_meta$beta_lab
)

df <- Genome_dataset %>%
  filter(Generation <= 1000) %>%
  left_join(pos_meta, by = "Position") %>%
  mutate(is_highlight = !is.na(effect_size))

# Right-edge labels (effect only)
lab_df <- df %>%
  filter(is_highlight) %>%
  group_by(Selection, Position, beta_lab) %>%
  filter(Generation == max(Generation)) %>%
  ungroup()

AF_FS_model_comparison <-
  ggplot(df, aes(Generation, Frequency, group = Position)) +
  # Background
  geom_line(data = dplyr::filter(df, !is_highlight),
            color = "grey70", linewidth = 0.5, alpha = 0.6) +
  # Highlights (legend keyed by β only)
  geom_line(data = dplyr::filter(df, is_highlight),
            aes(color = beta_lab), linewidth = 1.1, alpha = 0.95) +
  # On-plot labels showing β only
  # geom_text(data = lab_df,
  #           aes(label = beta_lab, color = beta_lab),
  #           hjust = 0, nudge_x = 12, size = 3.6, show.legend = FALSE) +
  scale_color_manual(name = "Effect size", values = col_vals) +
 # scale_x_continuous(expand = expansion(mult = c(0.01, 0.10))) +
  facet_wrap(Selection ~ .) +
  labs(x = "Generation", y = "Allele Frequency") +
  theme_bw() +
  theme(legend.position = "bottom") +
  mythemes

ggsave("Figure7.jpg", 
       plot = AF_FS_model_comparison, 
       dpi = 800, width = 30, height = 22,
       units = "in", bg = "white", path = "../OutputFigures.dir") 

print(AF_FS_model_comparison)

```


## 8. Fluctuating Population size and selection

```{r, fig.width=20, fig.height=10}
rm(list = ls())

library(dplyr)
library(tidyr)
library(ggplot2)
library(patchwork)
library(stringr)
library(purrr)
library(future)
library(furrr)
library(scales)

###############################################################################
########################## Settings ############################################
###############################################################################

plot_dir <- "../OutputFigures.dir"
dir.create(plot_dir, recursive = TRUE, showWarnings = FALSE)

target_n <- c(300)

target_replicates <- 1:30

target_H_amplitude <- c(0.1, 0.8)
target_SD_amplitude <- c(1, 4)
target_Gen_amplitude <- c(10, 30)

dynamics_parameter_regime <- tibble(
  H = 0.8,
  SD = 4,
  Gen = 30
)

spectral_parameter_regime <- tibble(
  Regime = c("Low", "High"),
  H = c(0.1, 0.8),
  SD = c(1, 4),
  Gen = c(10, 30)
)

target_n_dynamics <- target_n
target_replicate_for_dynamics <- 5

last_n_generations <- 1000
n_positions_for_dynamics <- 30

spectrum_span <- 2

if (length(spectrum_span) == 1 && spectrum_span %% 2 == 0) {
  spectrum_span <- 2
}

n_workers <- 32
available_workers <- future::availableCores()
n_workers_used <- min(n_workers, available_workers)

future::plan(multisession, workers = n_workers_used)

###############################################################################
############## Models to compare and their respective directories ##############
###############################################################################

model_sources <- tibble(
  Model = c(
    "Constant_Selection Instantaneous_Population",
    "Instantaneous_Selection Constant_Population",
    "Instantaneous_Selection Instantaneous_Population"
  ),
  Selection = c(
    "Constant_Selection",
    "Instantaneous_Selection",
    "Instantaneous_Selection"
  ),
  Population = c(
    "Instantaneous_Population",
    "Constant_Population",
    "Instantaneous_Population"
  ),
  folder_path = c(
    "~/Mylab/EvoGenFP.sims/FluctPopulationModels.dir/Output.dir/ConstSelInstatPop",
    "~/Mylab/evogen-sims/FluctSelectionModels.dir/Output.dir/LinFS.dir",
    "~/Mylab/EvoGenFP.sims/FluctPopulationModels.dir/Output.dir/InstSelInstatPop"
  )
) %>%
  mutate(
    folder_path = path.expand(folder_path)
  )

###############################################################################
########################## Theme ###############################################
###############################################################################

theme_amp <- theme_bw() +
  theme(
    text = element_text(family = "sans"),
    legend.position = "right",

    axis.text.x = element_text(
      face = "bold",
      size = 20,
      angle = 45,
      margin = margin(t = 10),
      hjust = 1
    ),
    axis.text.y = element_text(
      face = "bold",
      size = 20,
      angle = 0,
      margin = margin(r = 10)
    ),

    axis.line = element_line(linewidth = 1.5),

    plot.title = element_text(
      hjust = 0.01,
      face = "bold",
      size = 28,
      margin = margin(b = 0.5, unit = "lines")
    ),

    plot.margin = unit(c(1, 1, 1, 1), "lines"),

    axis.title.x = element_text(
      size = 22,
      face = "bold",
      margin = margin(t = 20)
    ),
    axis.title.y = element_text(
      size = 22,
      face = "bold",
      margin = margin(r = 20)
    ),

    strip.text = element_text(size = 16, face = "bold"),
    legend.title = element_text(size = 18, face = "bold"),
    legend.text = element_text(size = 16),
    panel.spacing = unit(1.5, "lines"),
    panel.grid = element_blank()
  )

###############################################################################
########################## Helper functions ####################################
###############################################################################

safe_num <- function(x) {
  suppressWarnings(as.numeric(x))
}

clean_model_label <- function(x) {
  x %>%
    str_replace_all("_", " ") %>%
    str_replace(" Constant Population", "\nConstant Population") %>%
    str_replace(" Instantaneous Population", "\nInstantaneous Population")
}

make_factor_columns <- function(df) {
  df %>%
    mutate(
      Model = factor(
        Model,
        levels = model_sources$Model
      ),
      Model_Label = factor(
        clean_model_label(as.character(Model)),
        levels = clean_model_label(model_sources$Model)
      ),
      Selection = factor(
        Selection,
        levels = c(
          "Constant_Selection",
          "Instantaneous_Selection"
        )
      ),
      Population = factor(
        Population,
        levels = c(
          "Constant_Population",
          "Instantaneous_Population"
        )
      ),
      Architecture = factor(
        Architecture,
        levels = paste0("Architecture = ", sort(target_n), " loci")
      ),
      H_factor = factor(
        H,
        levels = target_H_amplitude
      ),
      SD_factor = factor(
        SD,
        levels = target_SD_amplitude
      ),
      Gen_factor = factor(
        Gen,
        levels = target_Gen_amplitude
      ),
      parameter_combo = factor(
        parameter_combo,
        levels = unique(parameter_combo[order(H, SD, Gen)])
      )
    )
}

###############################################################################
########################## Flexible parameter parser ############################
###############################################################################

extract_params_any_model <- function(
    file,
    Model,
    Selection,
    Population
) {

  file_name <- basename(file)

  # Pattern A:
  # genome5_n300_H0.8SD4Gen30.csv
  replicate_a <- str_match(file_name, "^genome([0-9]+)_")[, 2]
  n_a <- str_match(file_name, "_n([0-9]+)_")[, 2]
  H_a <- str_match(file_name, "H([0-9]+(?:\\.[0-9]+)?)SD")[, 2]
  SD_a <- str_match(file_name, "SD([0-9]+(?:\\.[0-9]+)?)(?:Gen|\\.csv)")[, 2]
  Gen_a <- str_match(file_name, "Gen([0-9]+)")[, 2]

  # Pattern B:
  # genome_repl5_loci300_h0.8_Gen30_SD4.csv
  replicate_b <- str_match(file_name, "genome_repl([0-9]+)_")[, 2]
  n_b <- str_match(file_name, "_loci([0-9]+)_")[, 2]
  H_b <- str_match(file_name, "_h([0-9]+(?:\\.[0-9]+)?)")[, 2]
  Gen_b <- str_match(file_name, "_Gen([0-9]+)")[, 2]
  SD_b <- str_match(file_name, "_SD([0-9]+(?:\\.[0-9]+)?)")[, 2]

  # Pattern C:
  # repl5_loci300_h0.8_Gen30_SD4.csv
  replicate_c <- str_match(file_name, "^repl([0-9]+)_")[, 2]
  n_c <- str_match(file_name, "_loci([0-9]+)_")[, 2]
  H_c <- str_match(file_name, "_h([0-9]+(?:\\.[0-9]+)?)")[, 2]
  Gen_c <- str_match(file_name, "_Gen([0-9]+)")[, 2]
  SD_c <- str_match(file_name, "_SD([0-9]+(?:\\.[0-9]+)?)")[, 2]

  replicate <- coalesce(
    safe_num(replicate_a),
    safe_num(replicate_b),
    safe_num(replicate_c)
  )

  n <- coalesce(
    safe_num(n_a),
    safe_num(n_b),
    safe_num(n_c)
  )

  H <- coalesce(
    safe_num(H_a),
    safe_num(H_b),
    safe_num(H_c)
  )

  SD <- coalesce(
    safe_num(SD_a),
    safe_num(SD_b),
    safe_num(SD_c)
  )

  Gen <- coalesce(
    safe_num(Gen_a),
    safe_num(Gen_b),
    safe_num(Gen_c)
  )

  tibble(
    Model = as.character(Model),
    Selection = as.character(Selection),
    Population = as.character(Population),
    file = file,
    file_name = file_name,
    replicate = replicate,
    n = n,
    H = H,
    SD = SD,
    Gen = Gen
  )
}

###############################################################################
########################## File list ###########################################
###############################################################################

files_by_model <- model_sources %>%
  mutate(
    file = map(
      folder_path,
      ~ list.files(
        path = .x,
        pattern = "\\.csv$",
        full.names = TRUE
      )
    )
  ) %>%
  select(Model, Selection, Population, file) %>%
  unnest(file)

if (nrow(files_by_model) == 0) {
  stop("No files found. Check model_sources$folder_path.")
}

###############################################################################
########################## Raw parameter table #################################
###############################################################################

param_table_raw <- pmap_dfr(
  files_by_model,
  extract_params_any_model
) %>%
  filter(
    !is.na(replicate),
    !is.na(n),
    n %in% target_n,
    replicate %in% target_replicates
  )

if (nrow(param_table_raw) == 0) {
  stop("No files remain after basic n and replicate filtering.")
}

###############################################################################
########################## Parameter parsing diagnostics ########################
###############################################################################

param_parse_check <- param_table_raw %>%
  mutate(
    missing_H = is.na(H),
    missing_SD = is.na(SD),
    missing_Gen = is.na(Gen)
  ) %>%
  count(
    Model,
    Selection,
    Population,
    missing_H,
    missing_SD,
    missing_Gen,
    name = "n_files"
  ) %>%
  arrange(Model, missing_H, missing_SD, missing_Gen)

print(param_parse_check)

bad_parameter_files <- param_table_raw %>%
  filter(
    is.na(H) | is.na(SD) | is.na(Gen)
  ) %>%
  select(Model, Selection, Population, file_name, replicate, n, H, SD, Gen)

if (nrow(bad_parameter_files) > 0) {
  print(bad_parameter_files)
  stop(
    "Some files are missing H, SD, or Gen. ",
    "This likely means the filename parser is failing."
  )
}

###############################################################################
########################## Final parameter table ###############################
###############################################################################

param_table_FewerGen <- param_table_raw %>%
  filter(
    !is.na(H),
    !is.na(SD),
    !is.na(Gen),
    H %in% target_H_amplitude,
    SD %in% target_SD_amplitude,
    Gen %in% target_Gen_amplitude
  ) %>%
  distinct(
    Model,
    Selection,
    Population,
    file,
    file_name,
    replicate,
    n,
    H,
    SD,
    Gen,
    .keep_all = TRUE
  ) %>%
  arrange(Model, n, H, SD, Gen, replicate) %>%
  mutate(
    Architecture = paste0("Architecture = ", n, " loci"),
    parameter_combo = paste0(
      "h2 = ", H,
      " | Delta = ", SD,
      " | Gen = ", Gen
    ),
    full_parameter_label = paste0(
      "n = ", n,
      " | h2 = ", H,
      " | Delta = ", SD,
      " | Gen = ", Gen
    )
  ) %>%
  make_factor_columns()

if (nrow(param_table_FewerGen) == 0) {
  stop(
    "No files remain after filtering. Expected n = 300, replicates 1:30, H = 0.1/0.8, SD = 1/4, Gen = 10/30."
  )
}

###############################################################################
########################## Reuse / mixing diagnostics ###########################
###############################################################################

file_parameter_reuse_check <- param_table_FewerGen %>%
  group_by(Model, Selection, Population, file_name, replicate, n) %>%
  summarize(
    n_H_labels = n_distinct(H),
    n_SD_labels = n_distinct(SD),
    n_Gen_labels = n_distinct(Gen),
    n_parameter_labels = n_distinct(paste(H, SD, Gen, sep = "_")),
    parameter_labels = paste(
      sort(unique(paste0("H=", H, ", SD=", SD, ", Gen=", Gen))),
      collapse = " | "
    ),
    .groups = "drop"
  ) %>%
  filter(n_parameter_labels > 1)

# if (nrow(file_parameter_reuse_check) > 0) {
#   print(file_parameter_reuse_check)
#   stop(
#     "Some files are being reused across multiple parameter labels. ",
#     "This is parameter mixing and should not happen."
#   )
# }

###############################################################################
########################## Replicate check #####################################
###############################################################################

replicate_completeness <- param_table_FewerGen %>%
  group_by(
    Model,
    Selection,
    Population,
    Architecture,
    n,
    H,
    SD,
    Gen
  ) %>%
  summarize(
    n_replicates = n_distinct(replicate),
    replicates = paste(sort(unique(replicate)), collapse = ", "),
    .groups = "drop"
  ) %>%
  arrange(Model, Architecture, H, SD, Gen)

replicate_check <- replicate_completeness %>%
  filter(n_replicates != length(target_replicates))

if (nrow(replicate_check) > 0) {
  print(replicate_check)
  stop(
    "Some model/parameter combinations do not have exactly ",
    length(target_replicates),
    " replicates. Check replicate_completeness."
  )
}

###############################################################################
########################## Single-replicate dynamics ###########################
###############################################################################

param_table_dynamics <- param_table_FewerGen %>%
  filter(
    replicate == target_replicate_for_dynamics,
    n %in% target_n_dynamics
  ) %>%
  semi_join(
    dynamics_parameter_regime,
    by = c("H", "SD", "Gen")
  ) %>%
  arrange(Model, Architecture, H, SD, Gen) %>%
  make_factor_columns()

if (nrow(param_table_dynamics) == 0) {
  stop(
    "No files found for allele dynamics. Expected replicate ",
    target_replicate_for_dynamics,
    ", n = 300, H = 0.8, SD = 4, Gen = 30."
  )
}

sample_single_replicate_dynamics <- function(
    Model,
    Selection,
    Population,
    file,
    file_name,
    replicate,
    n,
    H,
    SD,
    Gen,
    Architecture,
    parameter_combo,
    full_parameter_label,
    H_factor = NULL,
    SD_factor = NULL,
    Gen_factor = NULL,
    Model_Label = NULL,
    target_replicate_for_dynamics = 5,
    n_positions = 30,
    seed = 5463456
) {

  if (replicate != target_replicate_for_dynamics) {
    return(NULL)
  }

  fl <- read.csv(file)

  required_cols <- c("Generation", "Frequency", "Position")

  if (!all(required_cols %in% names(fl))) {
    return(NULL)
  }

  fl <- fl %>%
    mutate(
      Generation = safe_num(Generation),
      Frequency = safe_num(Frequency),
      Position = as.factor(Position)
    ) %>%
    filter(
      !is.na(Generation),
      !is.na(Frequency),
      !is.na(Position)
    )

  if (nrow(fl) == 0) {
    return(NULL)
  }

  set.seed(
    seed +
      as.integer(n) +
      as.integer(SD) +
      as.integer(Gen) +
      as.integer(H * 100)
  )

  sampled_positions <- sample(
    unique(fl$Position),
    min(n_positions, length(unique(fl$Position))),
    replace = FALSE
  )

  fl %>%
    filter(Position %in% sampled_positions) %>%
    mutate(
      Model = as.character(Model),
      Selection = as.character(Selection),
      Population = as.character(Population),
      replicate = replicate,
      n = n,
      H = H,
      SD = SD,
      Gen = Gen,
      Architecture = as.character(Architecture),
      file_name = file_name,
      parameter_combo = as.character(parameter_combo),
      full_parameter_label = as.character(full_parameter_label)
    )
}

single_rep_dynamics_FewerGen <- pmap_dfr(
  param_table_dynamics,
  sample_single_replicate_dynamics,
  target_replicate_for_dynamics = target_replicate_for_dynamics,
  n_positions = n_positions_for_dynamics,
  seed = 768678
)

if (nrow(single_rep_dynamics_FewerGen) == 0) {
  stop(
    "No single-replicate dynamics data were produced. Check replicate, n = 300, high parameter regime, and file contents."
  )
}

single_rep_dynamics_FewerGen <- single_rep_dynamics_FewerGen %>%
  make_factor_columns()

###############################################################################
########################## Dynamics plot #######################################
###############################################################################

p_single_rep_dynamics_high_by_model <- ggplot(
  single_rep_dynamics_FewerGen %>% filter(Generation <= 1000),
  aes(
    x = Generation,
    y = Frequency,
    group = interaction(
      Model,
      Architecture,
      H,
      SD,
      Gen,
      file_name,
      Position
    )
  )
) +
  geom_line(
    alpha = 0.35,
    linewidth = 0.45
  ) +
  facet_wrap(
    . ~ Model_Label,
    scales = "free_y",
    ncol = 1
  ) +
  labs(
    title = "A) Allele frequency dynamics",
    x = "Generation",
    y = "Allele frequency"
  ) +
  theme_amp +
  theme(
    legend.position = "none",
    strip.text = element_text(size = 13, face = "bold"),
    axis.text.x = element_text(
      face = "bold",
      size = 11,
      angle = 45,
      hjust = 1
    ),
    axis.text.y = element_text(
      face = "bold",
      size = 11,
      angle = 0
    ),
    axis.title.x = element_text(size = 18, face = "bold"),
    axis.title.y = element_text(size = 18, face = "bold"),
    plot.title = element_text(size = 22, face = "bold"),
    panel.spacing = unit(1.2, "lines")
  )

#p_single_rep_dynamics_high_by_model

###############################################################################
########################## Spectral analysis ###################################
###############################################################################
# Mean AF spectrum:
# mean allele frequency across positions at each generation, then spectrum.
###############################################################################

param_table_spectral <- param_table_FewerGen %>%
  inner_join(
    spectral_parameter_regime,
    by = c("H", "SD", "Gen")
  ) %>%
  mutate(
    Regime = factor(Regime, levels = c("Low", "High"))
  ) %>%
  arrange(Model, Architecture, Regime, H, SD, Gen, replicate) %>%
  make_factor_columns()

if (nrow(param_table_spectral) == 0) {
  stop(
    "No files found for spectral analysis. Expected n = 300, Low: H = 0.1, SD = 1, Gen = 10; High: H = 0.8, SD = 4, Gen = 30."
  )
}

calculate_spectrum_model <- function(
    Model,
    Selection,
    Population,
    file,
    file_name,
    replicate,
    n,
    H,
    SD,
    Gen,
    Architecture,
    parameter_combo,
    full_parameter_label,
    Regime,
    H_factor = NULL,
    SD_factor = NULL,
    Gen_factor = NULL,
    Model_Label = NULL,
    spectrum_span = 2
) {

  fl <- read.csv(file)

  required_cols <- c("Generation", "Frequency")

  if (!all(required_cols %in% names(fl))) {
    return(NULL)
  }

  fl <- fl %>%
    mutate(
      Generation = safe_num(Generation),
      Frequency = safe_num(Frequency)
    ) %>%
    filter(
      !is.na(Generation),
      !is.na(Frequency),
      is.finite(Generation),
      is.finite(Frequency)
    )

  if (nrow(fl) == 0) {
    return(NULL)
  }

  mean_allele_data <- fl %>%
    group_by(Generation) %>%
    summarize(
      mean_allele_frequency = mean(Frequency, na.rm = TRUE),
      .groups = "drop"
    ) %>%
    arrange(Generation)

  if (nrow(mean_allele_data) < 8) {
    return(NULL)
  }

  series <- as.numeric(mean_allele_data$mean_allele_frequency)
  series <- series[is.finite(series)]

  if (length(series) < 8) {
    return(NULL)
  }

  if (sd(series, na.rm = TRUE) == 0) {
    return(NULL)
  }

  spec_result <- tryCatch(
    stats::spectrum(
      series,
      spans = spectrum_span,
      plot = FALSE
    ),
    error = function(e) NULL
  )

  if (is.null(spec_result)) {
    return(NULL)
  }

  ok_spec <- is.finite(spec_result$freq) &
    spec_result$freq > 0 &
    is.finite(spec_result$spec)

  if (!any(ok_spec)) {
    return(NULL)
  }

  tibble(
    Period = 1 / spec_result$freq[ok_spec],
    Spectrum = as.numeric(spec_result$spec[ok_spec]),
    Model = as.character(Model),
    Selection = as.character(Selection),
    Population = as.character(Population),
    replicate = replicate,
    n = n,
    H = H,
    SD = SD,
    Gen = Gen,
    Regime = as.character(Regime),
    Architecture = as.character(Architecture),
    file_name = file_name,
    parameter_combo = as.character(parameter_combo),
    full_parameter_label = as.character(full_parameter_label)
  )
}

spec_all_FewerGen <- future_pmap_dfr(
  param_table_spectral,
  calculate_spectrum_model,
  spectrum_span = spectrum_span,
  .progress = FALSE,
  .options = furrr_options(
    seed = TRUE,
    packages = c("dplyr", "tidyr", "stringr", "purrr", "stats")
  )
)

if (nrow(spec_all_FewerGen) == 0) {
  stop("No usable spectral data were produced.")
}

spec_all_FewerGen <- spec_all_FewerGen %>%
  mutate(
    Regime = factor(Regime, levels = c("Low", "High")),
    threshold = case_when(
      Gen == 10 ~ 40,
      Gen == 20 ~ 50,
      Gen == 30 ~ 80,
      TRUE ~ 80
    )
  ) %>%
  filter(
    Period < threshold
  ) %>%
  make_factor_columns()

###############################################################################
########################## Spectral replicate check ############################
###############################################################################

spec_replicate_completeness <- spec_all_FewerGen %>%
  group_by(
    Model,
    Architecture,
    Regime,
    H,
    SD,
    Gen
  ) %>%
  summarize(
    n_replicates = n_distinct(replicate),
    replicates = paste(sort(unique(replicate)), collapse = ", "),
    .groups = "drop"
  ) %>%
  arrange(Model, Architecture, Regime, H, SD, Gen)

spec_replicate_check <- spec_replicate_completeness %>%
  filter(n_replicates != length(target_replicates))

if (nrow(spec_replicate_check) > 0) {
  print(spec_replicate_check)
  stop(
    "Some spectral results were not calculated from exactly ",
    length(target_replicates),
    " replicates. Check spec_replicate_completeness."
  )
}

###############################################################################
########################## Spectral plot #######################################
###############################################################################

p_spectral_by_model <- ggplot(
  spec_all_FewerGen,
  aes(
    x = Period,
    y = Spectrum,
    color = factor(replicate),
    group = interaction(
      Model,
      Architecture,
      Regime,
      H,
      SD,
      Gen,
      replicate
    )
  )
) +
  geom_line(
    linewidth = 0.9,
    alpha = 0.75
  ) +
  scale_y_continuous(
    labels = scales::scientific_format()
  ) +
  facet_wrap(
    vars(Regime, Model_Label),
    ncol = 2, dir = "v",
    scales = "free"
  ) +
  labs(
    title = "B) Spectral density across replicates",
    x = "Period",
    y = "Spectrum",
    color = "Replicate"
  ) +
  theme_amp +
  theme(
    legend.position = "none",
    strip.text = element_text(size = 13, face = "bold"),
    axis.text.x = element_text(
      face = "bold",
      size = 11,
      angle = 45,
      hjust = 1
    ),
    axis.text.y = element_text(
      face = "bold",
      size = 11,
      angle = 0
    ),
    axis.title.x = element_text(size = 18, face = "bold"),
    axis.title.y = element_text(size = 18, face = "bold"),
    plot.title = element_text(size = 22, face = "bold"),
    panel.spacing = unit(1.2, "lines")
  )

#p_spectral_by_model

###############################################################################
########################## Combined plot #######################################
###############################################################################

combined_dynamics_spectral <- (
  p_single_rep_dynamics_high_by_model +
    p_spectral_by_model
) +
  plot_layout(
    widths = c(1.5, 4)
  )

combined_dynamics_spectral

###############################################################################
########################## Optional saving #####################################
###############################################################################

ggsave(
  filename = file.path(
    plot_dir,
    "Figure8.pdf"
  ),
  plot = combined_dynamics_spectral,
  width = 20,
  height = 13,
  units = "in",
  device = cairo_pdf
)

ggsave(
  filename = file.path(
    plot_dir,
    "Figure8.jpg" #"combined_dynamics_spectral_population_models.jpg"
  ),
  plot = combined_dynamics_spectral,
  width = 20,
  height = 13,
  units = "in",
  device = "png"
)
```

### ----------- END ------------------------
