---
title: "New Organized Figures"
author: "E.T"
format:
  docx:
    toc: true
    fontsize: 10pt
    fig-cap-location: bottom
    fig-numbering: false  
  html:
    toc: true
  pdf:
    toc: true
    knitr:
      opts_chunk:
        dev: "cairo_png"
        dev.args:
        bg: "white" 
editor: visual
---

> This file contains all plots for publication in sequence.

```{r, echo=FALSE, message=FALSE, warning=FALSE}

setwd("/mnt/pixstor/kingeg-lab/etb68/evogen-sims/FluctSelectionModels.dir/WritingFigures.dir/CodeFigures.dir")

library(forcats)
library(stringi)
library(tidyr)
library(dplyr)
library(stringr)
library(ggplot2)
library(patchwork)
library(cowplot)
library(purrr)
library(doParallel)

theme_set(theme_cowplot())
mythemes <- function(){
  theme(axis.title = element_text(face = "bold"),
        axis.text = element_text(face = "italic"),
        plot.title = element_text(hjust = 0.5),
        legend.position = "none")
}
```

## 0.Fitness landscapes

### 0.1 Fitness under C = 125

```{r, echo=FALSE,fig.width=8, fig.height=4, warning=FALSE}
#| label: Change in fitness as we shift optimum
#| fig-cap: "Figure L: Change in fitness as the optimum moves away from the phenotype (vertical dashed line). The numbers are the fitness values at given optimum and each point is at 0.5 interval."
#| fig-pos: "H"
# Needed Parameters
C_value <- 125 # Constant to control the steepness
optimum <- seq(-4, 4, by = 0.5)

# Calculating fitness at phenotype zero (hypothetical mean phenotype) for each optimum value
df <- tibble(
  optimum = optimum,
  fitness_at_zero = exp(- (1 / C_value) * (0 - optimum)^2)
)

# Subset the data to include only points every 0.5 interval
df_label <- df %>% 
  filter(round(optimum * 2) == optimum * 2)

# Create the plot
pfitness <- ggplot(df, aes(x = optimum, y = fitness_at_zero)) +
  geom_line(size = 3) +
  geom_vline(xintercept = 0, linetype = "dashed", size = 2, color = "black")+
  geom_point(data = df_label, size = 7, color = "darkred") +
  geom_text(data = df_label, 
            aes(label = round(fitness_at_zero, 3)), 
            vjust = -0.8, hjust = -1, size = 7, angle= 270,color = "darkred") +
  ylim(0.85, 1)+
  labs(
   # title = "Fitness at Phenotype Zero as a Function of Optimum",
    x = "Distance to Optimum",
    y = "Fitness Value"
  ) +
theme_set(theme_classic())+
  theme(text = element_text(family = "sans"), 
        legend.position = "none",
        axis.text = element_text(size = 20, face = "bold"),
        axis.line = element_line(size = 3),
        strip.text = element_text(size = 17, face = "bold"),
        plot.title = element_text(hjust = 0.01, face = "bold", size = 40),
        axis.title.x = element_text(margin = margin(t = 20), size = 20, face = "bold"),
        axis.title.y = element_text(margin = margin(r = 25), size = 20, face = "bold"),
        panel.spacing = unit(4, "lines"))

ggsave("Figure1.jpg", plot = pfitness, dpi = 600, width = 20, height = 10, units = "in", path = "../OutputFigures.dir")

print(pfitness)
```

### 0.2. Alternative fitness landascapes

```{r}
##library(tidyverse)

C_values <- seq(25, 200, by = 25)

df <- tidyr::expand_grid(distance = 0:20, C = C_values) %>%
  mutate(
    fitness = exp(-(distance^2) / C),
    C_fac   = factor(C, levels = C_values, ordered = TRUE),
    # small per-C offset for visual separation
    x_off   = scales::rescale(as.integer(C_fac), to = c(-0.18, 0.18)),
    distance_j = distance + x_off
  )

# Okabe–Ito palette (color-blind safe, very distinct)
colors <- c(
  "black",
  "magenta", 
  "skyblue", 
  "grey",
  "firebrick", 
  "blue",
  "orange", 
  "purple"
)
colors <- setNames(colors, levels(df$C_fac))
lt <- c("solid","dashed","dotted","dotdash","longdash","twodash","dotted","dotdash")
names(lt) <- levels(df$C_fac)

ggplot(df, aes(distance_j, fitness,
                colour = C_fac, linetype = C_fac, group = C_fac)) +
  geom_line(linewidth = 0.7) +
  geom_vline(xintercept = 4, linetype = "dashed", linewidth = 0.6, color = "darkred") +
  annotate("text", x = 5.5, y = 1.02, label = "Used Max SD = 4",
           vjust = -0.2, fontface = "bold", size = 5, color = "darkred") +
  scale_colour_manual(values = colors, name = "C") +
  scale_linetype_manual(values = lt, name = "C") +  # same name => one legend
  scale_x_continuous(breaks = 0:20, limits = c(-0.5, 20.5)) +
  scale_y_continuous(limits = c(0, 1.05), expand = expansion(mult = c(0, 0.05))) +
  guides(colour = guide_legend(nrow = 2), linetype = guide_legend(nrow = 2)) +
  labs(x = "Distance |Z - Zopt|", y = "Fitness") +
  theme_classic() +
  theme(legend.position = "bottom")
```

```{r}
breaks <- seq(0, 1, by = 0.05)
C_vals <- seq(25, 200, by = 5)  # denser grid looks smoother
df <- tidyr::expand_grid(distance = 0:5, C = C_vals) %>%
  mutate(fitness01 = exp(-(distance^2) / C))

ggplot(df, aes(x = C, y = distance, z = fitness01)) +
  geom_contour_filled(breaks = breaks) +
  scale_fill_viridis_d(name = "Fitness (0–1)") +
  scale_x_continuous(breaks = seq(25, 200, 25)) +
  scale_y_continuous(breaks = 0:5) +
  labs(x = "C Value (Width)", y = "Distance |p - o|") +
  theme_classic()
```

```{r}

# Intersection point and its fitness 
mark <- tibble(C = 125, distance = 4) %>%
  mutate(fitness01 = exp(-(distance^2) / C))

ggplot(df, aes(x = C, y = distance, z = fitness01)) +
  geom_contour_filled(breaks = breaks) +
  scale_fill_viridis_d(name = "Fitness (0–1)") +
  scale_x_continuous(breaks = seq(25, 200, 25)) +
  scale_y_continuous(breaks = 0:5) +
  geom_vline(xintercept = 125, linetype = "dashed", linewidth = 0.6) +
  geom_hline(yintercept = 4,   linetype = "dashed", linewidth = 0.6) +
  # point at the intersection
  geom_point(data = mark, aes(C, distance), inherit.aes = FALSE,
             shape = 21, size = 3.2, stroke = 1, fill = "white") +
  geom_label(
    data = mark,
    aes(C, distance, label = sprintf("Fitness = %.3f", fitness01)),
    inherit.aes = FALSE,
    nudge_x = 12, nudge_y = 0.3,
    size = 4.2, label.size = 0.5
  ) +
  labs(x = "C Value (Width)", y = "Distance |Z - Zopt|") +
  theme_classic() +
  theme(
    text = element_text(family = "sans"),
    axis.text = element_text(face = "bold"),
    plot.title     = element_text(face = "bold"),
    axis.title = element_text(face = "bold"),
    strip.text     = element_text(face = "bold"))
```

## 1. Selection Model Setting

### 1.0. Infinitessimal model

```{r, echo=FALSE, fig.width=8, fig.height=4, dpi = 1200, warning=FALSE}
#| label: Exponential_Model
########### Infinitisimal Model #################
a = 5
b = 25
x = seq(1:100)
y <- function(x){
  Y = a*exp(-x/b)
}
Y <- y(x)
z = data.frame(Y, x)

Inf_ModPlot <- z %>% ggplot(aes(x,Y))+
  geom_line(linewidth = 2)+
  annotate("text", x = 55, y = max(Y)/1.5, label = "Exponential Effects", fontface = "bold", size = 10) +  #  Add this line
  labs(title = "A", x = "Loci", y = "Effect")+
  theme_set(theme_bw())+
  theme(text = element_text(family = "sans"), 
        legend.position = "none",
        axis.text = element_text(size = 20, face = "bold"),
        axis.line = element_line(size = 3),
        strip.text = element_text(size = 17, face = "bold"),
        plot.title = element_text(hjust = 0.01, face = "bold", size = 40),
        axis.title.x = element_text(margin = margin(t = 20), size = 20, face = "bold"),
        axis.title.y = element_text(margin = margin(r = 25), size = 20, face = "bold"),
        panel.spacing = unit(4, "lines"))

ggsave("Exponential_Model.jpg", plot = Inf_ModPlot, dpi = 1200, width = 7, height = 4, units = "in", path = "../OutputFigures.dir")

Inf_ModPlot
```

### 1.1 Constant model

```{r, echo=FALSE, fig.width=8, fig.height=4, dpi = 1200, warning=FALSE}
# Generation sequence from 1 to 2000
Generation <- c(1:2000)


# Initialize Optimum vector
Optimum = rep(0, length(Generation))

Optimum <- seq(-4, 4, length.out = 2000)
df <- data.frame(Generation, Optimum) %>% filter(Generation <= 100)

Const_ModPlot <- ggplot(df) + 
  geom_blank(aes(Generation, Optimum, ymax = 4)) +
 # geom_hline(yintercept = 0, color = "darkred", size = 3)+
 #annotate("text", x = 100, y = 0, 
  #         label = "Mean Phenotype", 
  #         size = 10, vjust = -.5, col = "darkred")+
  geom_hline(yintercept = 2, size = 3)+
#annotate("text", x = 100, y = 2.1, label = "Optium", size = 10, vjust = -.5, col = "black")+
  labs(title = "A", x = "Generation", y = "Optimum")+
  theme(text = element_text(family = "sans"), 
        legend.position = "none",
        axis.text = element_text(size = 20, face = "bold"),
        axis.line = element_line(size = 3),
        strip.text = element_text(size = 17, face = "bold"),
        plot.title = element_text(hjust = 0.01, face = "bold", size = 40),
        axis.title.x = element_text(margin = margin(t = 20), size = 30, face = "bold"),
        axis.title.y = element_text(margin = margin(r = 25), size = 30, face = "bold"),
        panel.spacing = unit(4, "lines"))
 
 ggsave("Constant_Model.jpg", plot = Const_ModPlot, dpi = 1200, width = 7, height = 4, units = "in", path = "../OutputFigures.dir")

```

### 1.2 Instantaneous Selection model

```{r, echo=FALSE, fig.width=8, fig.height=4, dpi = 1200, warning=FALSE}
#| label: Instant_Model
Opti_Gen <- tibble(Generation = seq(1:100),
                   Optimum1 = rep(c(rep(110, 10), rep(90, 10)), 5),
                   Optimum2 = rep(c(rep(105, 10), rep(95, 10)), 5))

mu_pheno = mean(Opti_Gen$Optimum1)

Opt_Data <- Opti_Gen %>% 
  filter(Generation == 0 | Generation %% 25 != 0)

Instant_Model <- ggplot()+
  geom_line(data = Opt_Data, aes(x = Generation, y = (Optimum1 - 100)/2.5), size = 1)+
  labs(title = "B", x = "Generation", y = "Optimum")+
  theme_set(theme_bw())+ 
  theme(text = element_text(family = "sans"), 
        legend.position = "none",
        axis.text = element_text(size = 20, face = "bold"),
        axis.line = element_line(size = 3),
        strip.text = element_text(size = 17, face = "bold"),
        plot.title = element_text(hjust = 0.01, face = "bold", size = 40),
        axis.title.x = element_text(margin = margin(t = 20), size = 30, face = "bold"),
        axis.title.y = element_text(margin = margin(r = 25), size = 30, face = "bold"),
        panel.spacing = unit(4, "lines"))


ggsave("Instant_Model.jpg", plot = Instant_Model, dpi = 1200, width = 7, height = 4, units = "in", path = "../OutputFigures.dir")
 
Instant_Model
```

### 1.3 Gradual Two Season Selection model

```{r, echo=FALSE, fig.width=8, fig.height=4, dpi = 1200, warning=FALSE}
#| label: Gradual_Two_Season_Model
Generation <- seq(1, 100, length.out = 400) 
phenotypes <- rnorm(10000, 0, 1)
Optimum <- 10 *sin( pi* Generation / 25) /2.5
df <- data.frame(Generation, Optimum) 

GradI <- ggplot(df) + 
  geom_line(aes(Generation, Optimum), size = 3) + 
  theme_set(theme_bw())+
  labs(title = "C", x = "Generation", y = "Optimum")+
  theme_set(theme_bw())+ 
  theme(text = element_text(family = "sans"), 
        legend.position = "none",
        axis.text = element_text(size = 20, face = "bold"),
        axis.line = element_line(size = 3),
        strip.text = element_text(size = 17, face = "bold"),
        plot.title = element_text(hjust = 0.01, face = "bold", size = 40),
        axis.title.x = element_text(margin = margin(t = 20), size = 30, face = "bold"),
        axis.title.y = element_text(margin = margin(r = 25), size = 30, face = "bold"),
        panel.spacing = unit(4, "lines"))


ggsave("Gradual_Two_Season_Model.jpg", plot = GradI, dpi = 1200, width = 7, height = 4, units = "in", path = "../OutputFigures.dir")
 
GradI
```

### 1.4 Gradual Four Season Selection model

> This is an old one

```{r, echo=FALSE, fig.width=8, fig.height=4, dpi = 1200, warning=FALSE}
#| label: Gradual_Four_Season_Model
# Generation sequence from 1 to 2000
Generation <- c(1:300)
phenotypes <- rnorm(10000, 0, 1)

# Signals vector
signals = c(12, 22, 10, 16) # 5, 10, 20, 30

# Initialize Optimum vector
Optimum = rep(0, length(Generation))

# Loop over each signal to calculate the Optimum
for (i in signals) {
  Optimum = Optimum + (mean(phenotypes) + sd(phenotypes)*4) * sin((22/7) * Generation / i)
}
Optimum = Optimum / 4

df <- data.frame(Generation, Optimum)

# Plot the Optimum over the first 501 generations

GradII <- ggplot(df) + 
    geom_line(aes(Generation, Optimum), size = 3) + 
  ylim(-4, 4) +  
  labs(title = "D", x = "Generation", y = "Optimum")+
  theme_set(theme_bw())+ 
  theme(text = element_text(family = "sans"), 
        legend.position = "none",
        axis.text = element_text(size = 20, face = "bold"),
        axis.line = element_line(size = 3),
        strip.text = element_text(size = 17, face = "bold"),
        plot.title = element_text(hjust = 0.01, face = "bold", size = 40),
        axis.title.x = element_text(margin = margin(t = 20), size = 30, face = "bold"),
        axis.title.y = element_text(margin = margin(r = 25), size = 30, face = "bold"),
        panel.spacing = unit(4, "lines"))


# ggsave("Gradual_Four_Season_Model.jpg", plot = GradII, dpi = 1200, width = 7, height = 4, units = "in", path = "../OutputFigures.dir")
 
GradII
```

> New with four different selection strength

```{r, echo=FALSE, fig.width=8, fig.height=4, dpi = 1200, warning=FALSE}
#| label: Gradual_Four_Season_Model_NEW
set.seed(3564);
seasons = c(12,22,10,16);
year = sum(seasons);
sd_values = c(3,1,4,2);
pheno = rnorm(10000);
mu_p = mean(pheno);
sd_p = sd(pheno);

current_time = 1;
year_counter = 1;
season_counter = 1;

total_time = 500;
n_opt = numeric(total_time);

while(current_time <= total_time){
  for(i in seq_along(seasons)){
    if(current_time > total_time) break;
    season_length = seasons[i];
    sd_val = sd_values[i];
    remain_time = total_time - current_time + 1;
    act_length = min(season_length, remain_time);
    
    time_pt = 1:act_length;
    opt = mu_p + sd_val * sd_p * sin(2*pi*time_pt/season_length);
    end_time = current_time + act_length - 1;
    n_opt[current_time:end_time] = opt;
    current_time = current_time + act_length;
    season_counter = current_time + 1;
  }
}

df <- data.frame(Generation = seq(1,total_time), Optimum =  n_opt)

# Plot the Optimum over the first 120 generations marking a two cycles

ggplot(df[1:120,]) + 
    geom_line(aes(Generation, Optimum), size = 3) + 
  ylim(-4, 4) +  
  labs(title = "D", x = "Generation", y = "Optimum")+
  theme_set(theme_bw())+ 
  theme(text = element_text(family = "sans"), 
        legend.position = "none",
        axis.text = element_text(size = 20, face = "bold"),
        axis.line = element_line(size = 3),
        strip.text = element_text(size = 17, face = "bold"),
        plot.title = element_text(hjust = 0.01, face = "bold", size = 40),
        axis.title.x = element_text(margin = margin(t = 20), size = 30, face = "bold"),
        axis.title.y = element_text(margin = margin(r = 25), size = 30, face = "bold"),
        panel.spacing = unit(4, "lines"))
```

> New with same selection strength

```{r, echo=FALSE, fig.width=8, fig.height=4, dpi = 1200, warning=FALSE}
#| label: Gradual_Four_Season_Model_NEW_sameSD
set.seed(3564);
seasons = c(12,22,10,16);
year = sum(seasons);
#sd_values = c(3,1,4,2);
sd_values = c(4,4,4,4);
pheno = rnorm(10000);
mu_p = mean(pheno);
sd_p = sd(pheno);

current_time = 1;
year_counter = 1;
season_counter = 1;

total_time = 500;
n_opt = numeric(total_time);

while(current_time <= total_time){
  for(i in seq_along(seasons)){
    if(current_time > total_time) break;
    season_length = seasons[i];
    sd_val = sd_values[i];
    remain_time = total_time - current_time + 1;
    act_length = min(season_length, remain_time);
    
    time_pt = 1:act_length;
    opt = mu_p + sd_val * sd_p * sin(2*pi*time_pt/season_length);
    end_time = current_time + act_length - 1;
    n_opt[current_time:end_time] = opt;
    current_time = current_time + act_length;
    season_counter = current_time + 1;
  }
}

df <- data.frame(Generation = seq(1,total_time), Optimum =  n_opt)

# df <- read.csv("~/Mylab/evogen-sims/FluctSelectionModels.dir/Output.dir/SinFSGen.dir/MeanPhenotypes1_n300_H0.8SD4.csv") %>%
#   dplyr::select(c(Generation, Optimum))

 df <- read.csv("~/Mylab/evogen-sims/FluctSelectionModels.dir/Output.dir/SinFS.dir/MeanPhenotypes13_n300_H0.5SD1Gen30.csv") %>% 
   dplyr::select(c(Generation, Optimum))

# Plot the Optimum over the first 120 generations marking a two cycles

ggplot(df[1:120,]) + 
    geom_line(aes(Generation, Optimum), size = 3) +  
  labs(title = "D", x = "Generation", y = "Optimum")+
  theme_set(theme_bw())+ 
  theme(text = element_text(family = "sans"), 
        legend.position = "none",
        axis.text = element_text(size = 20, face = "bold"),
        axis.line = element_line(size = 3),
        strip.text = element_text(size = 17, face = "bold"),
        plot.title = element_text(hjust = 0.01, face = "bold", size = 40),
        axis.title.x = element_text(margin = margin(t = 20), size = 30, face = "bold"),
        axis.title.y = element_text(margin = margin(r = 25), size = 30, face = "bold"),
        panel.spacing = unit(4, "lines"))
```

## 2. Instantaneous Selection for Polygenic Traits

```{r, message=FALSE, echo=FALSE, warning=FALSE}
###############################################################################
# Required Libraries
###############################################################################
library(parallel)
library(doParallel)
library(foreach)
library(dplyr)
library(ggplot2)
library(future)
library(purrr)
library(furrr)
library(cowplot)  
#library(stringr)
###############################################################################
# Custom Theme
###############################################################################
mythemes <- theme_bw() +
  theme(
    text = element_text(family = "sans"), 
    legend.position = "none",
    axis.text.x = element_text(face = "bold", size = 50, angle =25, margin = margin(t = 20), hjust = 1),
    axis.text.y = element_text(face = "bold", size = 50, angle = 15, margin = margin(r = 10)),
    axis.line = element_line(size = 3),
    plot.title      = element_text(hjust = 0.01, face = "bold", size = 70, margin = margin(b = 1, unit = "lines")),
    plot.margin = unit(c(5, 1, 1, 1), "lines"),
    axis.title.x = element_text(size = 50, face = "bold", margin = margin(t = 30)),
    axis.title.y = element_text(size = 50, face = "bold", margin = margin(r = 35)),
    strip.text = element_text(size = 50, face = "bold"),
    panel.spacing = unit(5, "lines"),
    panel.grid = element_blank()
  )

```

### 2.1. Polygenic Instantaneous AF

```{r, warning=FALSE, fig.width = 30, fig.height = 30, dpi = 1200, echo=FALSE}
###############################################################################
# Function to extract H, SD, and Gen values from filename
###############################################################################
extract_params <- function(filename) {
  base <- basename(filename)
  
  h_value <- as.numeric(sub(".*_H(0\\.[0-9]+).*", "\\1", base))
  sd_value <- as.numeric(sub(".*SD([0-9]+).*", "\\1", base))
  gen_value <- as.numeric(sub(".*Gen([0-9]+).*", "\\1", base))
  
  list(H = h_value, SD = sd_value, Gen = gen_value)
}

###############################################################################
# Main function to read files, process data, and create the plot
###############################################################################
create_plot <- function(path, pattern) {
  file_list <- list.files(path = path, pattern = pattern, full.names = TRUE)
  
  combined_dataset <- map_df(file_list, function(file) {
    data   <- read.csv(file, header = TRUE) %>% 
                filter(Generation <= 1000)
    params <- extract_params(file)
    
    data %>% 
      mutate(
        H = params$H,
        SD = params$SD,
        Gen = params$Gen
      )
  })
  
  # Randomly select at most 15 positions for visibility
  set.seed(12345)
  unique_positions   <- unique(combined_dataset$Position)
  selected_positions <- sample(unique_positions, size = min(30, length(unique_positions)))
  
  filtered_dataset <- combined_dataset %>% 
    filter(Position %in% selected_positions)
  
  # Positions with high and small effect
  
  highlight_colors <- c(
  `982341`  = "#0072B2",
 # `1067762` = "#D55E00",
  #`811499`  = "#009E73",
  #`323379`  = "#CC79A7",
 `811499`  = "darkred",
  other     = "grey70"
)

Freq_Instant_Poly <- filtered_dataset %>%
  mutate(
    H_SD_Gen = paste0("h\u00B2 = ", H, " Δ = ", SD, " Gen = ", Gen),
    pos_key  = dplyr::case_when(
      Position == 982341  ~ "982341",
    #  Position == 1067762 ~ "1067762",
      Position == 811499  ~ "811499",
     # Position == 323379  ~ "323379",
      TRUE ~ "other"
    ),
    line_size = ifelse(pos_key == "other", 0.5, 1.2)
  ) %>% 
  ggplot(aes(x = Generation, y = Frequency,
             group = factor(Position),
             color = pos_key, size = line_size)) +
  geom_line() +
  scale_color_manual(values = highlight_colors) +
  scale_size_identity() +
  facet_wrap(~ H_SD_Gen, scales = "free", ncol = 2, dir = "v") +
  theme_bw() +
  labs(
    title = "A) Allele Frequency",
    x     = "Generation",
    y     = "Frequency"
  ) +
  mythemes
  
  Freq_Instant_Poly
}

path    <- "../../Output.dir/LinFS.dir"
pattern <- "^genome10_n100_H(0\\.1|0\\.8)SD(1|4)Gen(10|30)\\.csv$"
Freq_Instant_Poly <- create_plot(path, pattern)

# Save to file
ggsave(
  filename = "Instant_Poly_AF.jpg",
  plot = Freq_Instant_Poly,
  dpi  = 600,
  width = 30,
  height = 25,
  units  = "in",
  path = "../OutputFigures.dir"
)

print(Freq_Instant_Poly)

```

### 2.2. Polygenic Instantaneous Phenotypes

```{r, warning=FALSE, fig.width = 25, fig.height = 20, dpi = 1200, echo=FALSE}
#| label: Instant_Poly_Pheno
extract_params <- function(filename) {
  h_value <- as.numeric(sub(".*_H(0\\.\\d+).*", "\\1", basename(filename)))
  sd_value <- as.numeric(sub(".*SD(\\d+).*", "\\1", basename(filename)))
  gen_value <- as.numeric(sub(".*Gen(\\d+).*", "\\1", basename(filename)))
  replicate_value <- as.numeric(sub(".*MeanPhenotypes(\\d+)_.*", "\\1", basename(filename)))
  
  list(
    H = h_value,
    SD = sd_value,
    Gen = gen_value,
    Replicate = replicate_value
  )
}

file_list <- list.files(
  path = "../../Output.dir/LinFS.dir",
  pattern = "MeanPhenotypes\\d+_n100_H(0\\.1|0\\.8)SD(1|4)Gen(10|30)\\.csv",
  full.names = TRUE
)

combined_dataset <- map_df(file_list, function(file) {
  data   <- read.csv(file, header = TRUE)
  params <- extract_params(file)
  
  data %>%
    mutate(
      H = params$H,
      SD = params$SD,
      Gen = params$Gen,
      Replicate = params$Replicate,
      Optimum = ifelse(Optimum == max(Optimum, na.rm = TRUE), "High", "Low")
    ) %>%
    filter(
      Generation <= 1000,
      (H == 0.1 & SD == 1 & Gen == 10) |
      (H == 0.8 & SD == 4 & Gen == 30)
    )
})

Pheno_Instant_Poly <- combined_dataset %>% 
  mutate(
    SD_Gen = paste0("Δ = ", SD, " Gen = ", Gen),
    H_SD_Gen = paste0("h\u00B2 = ", H, " Δ = ", SD, " Gen = ", Gen),
    H_SD = paste0("h\u00B2 = ", H, " Δ = ", SD),
    H_label = paste0("h\u00B2 = ", H)
  ) %>% 
  ggplot(aes(x = Generation, y = Phenotype)) +          
    geom_line(aes(group = Replicate), color = "gray50", alpha = 0.5, size = 1) +
    # stat_summary(
    #   fun = mean, aes(group = 1), geom = "line", alpha = 1,     size = 3
    # ) + #  color = "red", 
    facet_wrap(~ H_SD_Gen, scales = "free", ncol = 1, dir = "v") +
    theme_bw() +
    labs(title = "B) Phenotypes", x = "Generation", y = "Phenotype") +
    mythemes

ggsave(
  filename = "Instant_Poly_Pheno.jpg",
  plot = Pheno_Instant_Poly,
  dpi = 1200,
  width = 25, 
  height = 15, 
  units = "in", 
  path = "../OutputFigures.dir"
)

print(Pheno_Instant_Poly)
```

### 2.3. Polygenic Instantaneous Spec Analysis

```{r, warning=FALSE, fig.width = 20, fig.height = 15, echo=FALSE, dpi = 1200}
#| label: Instant_Poly_SpecAnalysis

###############################################################################
################## Function for spectral analysis ############################
###############################################################################

run_fft_analysis <- function(folder_path, pattern, spectrum_span = 2) {
  
  # Create the directory to save images if it doesn't exist
  last_dir <- basename(normalizePath(folder_path))
  
  #### Function for AF files
  file_list <- list.files(
    path = folder_path,
    pattern = pattern,
    full.names = TRUE
  )
  
###########################################
######## DataFrame for all replicates #####
###########################################
  
  files_df <- data.frame(file_name = file_list) %>%
    mutate(
  base_name = basename(file_name),
  genome = ifelse(
    grepl("genome\\d+", base_name),
    as.numeric(sub(".*genome(\\d+).*", "\\1", base_name)),
    NA_real_
  ),
  n = ifelse(
    grepl("_n\\d+", base_name),
    as.numeric(sub(".*_n(\\d+).*", "\\1", base_name)),
    NA_real_
  ),
  H = ifelse(
    grepl("_H[0-9]+\\.?[0-9]*", base_name),
    as.numeric(sub(".*_H([0-9]+\\.?[0-9]*).*", "\\1", base_name)),
    NA_real_
  ),
 SD = ifelse(
    grepl("SD[0-9]+(\\.[0-9]+)?", base_name),
    as.numeric(sub(".*SD([0-9]+(?:\\.[0-9]+)?).*", "\\1", base_name)),
    NA_real_
  ),
 Gen = ifelse(
    grepl("Gen\\d+", base_name),
    as.numeric(sub(".*Gen(\\d+).*", "\\1", base_name)),
    NA_real_
  )
)%>%
    mutate(
      param_combination = paste0(
        "n_", n, "_H", H,
        ifelse(!is.na(SD),  paste0("_SD", SD),  ""),
        ifelse(!is.na(Gen), paste0("_Gen", Gen), "")
      )
    )

###...................................#######
### parallelization for files reading #######
###...................................#######
  
  num_cores_to_use <- min(detectCores() - 16, 64) # check the cores before
  cluster_type   <- if (.Platform$OS.type == "windows") "PSOCK" else "FORK"
  cl <- makeCluster(num_cores_to_use, type = cluster_type)
  registerDoParallel(cl)
  
  combined_data_list <- foreach(i = seq_along(files_df$file_name),
                                .packages = c("dplyr")) %dopar% {
    file   <- files_df$file_name[i]
    params <- files_df[i, ]
    df     <- read.csv(file)
    df %>%
      mutate(
        allele_id = as.factor(Position),
        generation  = as.numeric(Generation),
        allele_frequency = Frequency,
        sample_size = 10000,
        file = params$base_name,
        genome = params$genome,
        n = params$n,
        H = params$H,
        SD = params$SD,
        Gen = params$Gen,
        param_combination= params$param_combination
      ) %>%
      dplyr::select(
        allele_id, generation, allele_frequency, sample_size, file,
        genome, n, H, SD, Gen, param_combination
      )
  }
  
  combined_data <- bind_rows(combined_data_list)
  
  stopCluster(cl)
  
  mean_allele_data <- combined_data %>%
    group_by(generation, n, genome, H, SD, Gen, param_combination) %>%
    summarize(mean_allele_frequency = mean(allele_frequency), .groups = "drop")

####'''''''''''''''''''''''#####
#### Convert to time series ####
####'''''''''''''''''''''''#####

  ts_data_list <- mean_allele_data %>%
    group_by(n, genome, H, SD, Gen, param_combination) %>%
    summarize(
      ts_data = list(ts(mean_allele_frequency,
                        start = min(generation),
                        frequency = 1)), #frequency = 1
      .groups = 'drop'
    )
  
### Compute spectral density ####
  
  spec_results_list <- lapply(ts_data_list$ts_data, function(ts_data) {
    spectrum(ts_data, spans = spectrum_span, plot = FALSE)
  })
  
#### Prepare data for plotting
  plot_data_list <- list()
  for (i in seq_along(spec_results_list)) {
    spec_result <- spec_results_list[[i]]
    params      <- ts_data_list[i, ]
    # compute period
    period      <- 1 / spec_result$freq
    
    df_spec <- data.frame(
      Period = period,
      Spectrum = spec_result$spec,
      n = params$n,
      genome = params$genome,
      H = params$H,
      SD = params$SD,
      Gen = params$Gen,
      param_combination = params$param_combination
    ) 
    
    plot_data_list[[i]] <- df_spec
  }
  
  # Combine spectral data
  plot_data <- bind_rows(plot_data_list)
  
  # Limit Period by threshold for each param_combination 
  plot_data <- plot_data %>%
    group_by(param_combination) %>%
    mutate(
      threshold = case_when(
        Gen == 10 ~ 40,  # keep period < 40 if Gen=10
        Gen == 30 ~ 80,  # keep period < 80 if Gen=30
        TRUE      ~ max(Period)
      )
    ) %>%
    ungroup() %>%
    # Keep only the two combos: (H=0.1,SD=1,Gen=10) or (H=0.8,SD=4,Gen=30)
    filter(
      Period < threshold &
      (
        (H == 0.1 & SD == 1 & Gen == 10) | 
        (H == 0.8 & SD == 4 & Gen == 30)
      )
    )
  
  # Creating labels 
  plot_data <- plot_data %>%
    mutate(
      H_label  = paste0("H = ", H),
      SD_label = ifelse(!is.na(SD),  paste0("Δ = ", SD),  "No Δ"),
      Gen_label= ifelse(!is.na(Gen), paste0("Gen = ", Gen), "No Gen"),
      H_SD_Gen = paste0("h\u00B2 = ", H, " Δ=", SD, " Gen=", Gen)
    )
  
  spec_plot_comb1 <- ggplot( plot_data, 
                            aes(x = Period, y = Spectrum, 
                                color = factor(genome), group = factor(genome))) +
    geom_line(linewidth = 3) +
    facet_wrap(~ H_SD_Gen, scales = "free", ncol = 1) +
    scale_y_continuous(labels = scales::label_number())+
    #scale_y_continuous(labels = scales::label_scientific())+
    labs(
      title = "C) Spectral Density", x = "Period (Generations)", y = "Spectral Density") +
    mythemes
  
  return(spec_plot_comb1)
}

###############################################################################
################## Run The Function for Spectral Analysis ####################
###############################################################################

dirpath   <- "../../Output.dir/LinFS.dir/"
my_pattern<- "^genome\\d+_n100_H0\\.(1|8)(SD(1|4))?(Gen(10|30))?\\.csv$"


final_plot <- run_fft_analysis(dirpath, my_pattern)

ggsave("Instant_Poly_SpecAnalysis_Combined.jpg",
       plot = final_plot,
       dpi = 1200, width = 25, height = 15, units = "in",
       path = "../OutputFigures.dir")


final_plot
```

### 2.4. Combined Polygenic Instantaneous for AF, Pheno, and Spec Analysis

```{r, warning=FALSE, fig.width = 30, fig.height = 20, dpi = 1200, echo=FALSE}
#| label: Instant_Poly_AF_Pheno_SpecAnalysis_comb

top_row <- plot_grid(
  Pheno_Instant_Poly, 
  final_plot,
  ncol = 1, 
  rel_heights = c(1, 1)
)

combined_plot <- plot_grid(
  Freq_Instant_Poly, 
  top_row, 
  ncol = 2,
  rel_widths = c(2, 1)
)

ggsave(
  filename = "Figure2.jpg", #"Instant_Poly_AF_Pheno_SpecAnalysis.jpg",
  plot     = combined_plot,
  dpi      = 600,
  width    = 49,
  height   = 30,
  units    = "in",
  path     = "../OutputFigures.dir"
)
combined_plot  

```

## 3. Genetic Architecture: Instantaneous models

### 3.1. AF monogenic, oligogenic, and Polygenic

```{r, warning=FALSE, fig.width = 25, fig.height = 22, dpi = 1200, echo=FALSE}
#| label: AF_Mono_Ologo_Poly_Instant
read_files <- function() {
  file_list <- list.files(path = "../../Output.dir/LinFS.dir/", pattern = "genome10_n(1|10)_H0\\.(1|5|8)(SD(1|2|4))?Gen(10|20|30)\\.csv$", full.names = TRUE)
  
  datasets <- lapply(file_list, function(file) {
    data <- read.csv(file)
    matches <- regmatches(file, regexec("genome10_n([0-9]+)_H([0-9\\.]+)SD([0-9]+)Gen([0-9]+)", file))[[1]]
    selection_type <- as.numeric(matches[2])
    selection_label <- ifelse(selection_type == 1, "1 Locus",
                              ifelse(selection_type == 10, "10 Loci", "100 Loci"))
    
    data <- data %>% 
      mutate(Selection = selection_label,
             H = as.numeric(matches[3]),
             SD = as.numeric(matches[4]),
             Gen = as.numeric(matches[5]))
    return(data)
  })
  
  return(bind_rows(datasets))
}

#########################
### Read in the data ####
##########################

Genome_dataset <- read_files() %>% 
  filter(Generation <= 1000) %>% 
  mutate(Selection = fct_relevel(Selection, 
                                 "1 Locus",  
                                 "10 Loci", 
                                 "100 Loci"))

# select up to 15 unique positions for each group
set.seed(123)
selected_positions <- Genome_dataset %>%
  group_by(Selection) %>%
  group_map(~ {
    positions <- unique(.x$Position)
    if (length(positions) > 30) {
      sample(positions, 30)
    } else {
      positions
    }
  }) %>%
  unlist()

filtered_dataset <- Genome_dataset %>%
  filter(Position %in% selected_positions)

filtered_dataset <- filtered_dataset %>%
  filter((H == 0.1 & SD == 1 & Gen == 10) |
         (H == 0.5 & SD == 2 & Gen == 20) |
          (H == 0.8 & SD == 4 & Gen == 30))

filtered_dataset <- filtered_dataset %>%
  mutate(Color = case_when(
    Selection == "1 Locus" ~ "magenta",
    Selection == "10 Loci" & Position == "427101" ~ "magenta", #1037246
    Selection == "100 Loci" & Position == "323379" ~ "magenta", # 201349
    TRUE ~ "black"
  ),
  LineSize = case_when(
    Color == "magenta" ~ 2,
    TRUE ~ 0.5
  ))


AF_Mono_Ologo_Poly_Instant <- filtered_dataset %>%
  filter(Generation <= 1000) %>%
  mutate(H_SD_Gen = paste0("H = ", H, " SD =  ", SD, " Gen = ", Gen)) %>% 
  mutate(
    H_SD_Gen_short = case_when(
      H == 0.1 & SD == 1 & Gen == 10 ~ "Min combo",
      H == 0.5 & SD == 2 & Gen == 20 ~ "Med combo",
      H == 0.8 & SD == 4 & Gen == 30 ~ "High combo"
    )) %>%
  mutate(
    H_SD_Gen_short = fct_relevel(H_SD_Gen_short, "Min combo", "Med combo", "High combo")
  ) %>%
  ggplot(aes(x = Generation, y = Frequency, group = factor(Position), 
              size = LineSize)) + #color = Color,
  geom_line(alpha = 0.7) + 
 # scale_color_identity() +
  scale_size_identity() +
  facet_grid(H_SD_Gen_short ~ Selection) +
  labs(title = "A) Allele Frequency", x = "Generation", y = "Frequency") +
  theme_bw() +
  mythemes

ggsave(
  filename = "AF_Mono_Ologo_Poly_Instant.jpg",
  plot     = AF_Mono_Ologo_Poly_Instant,
  dpi      = 600,
  width    = 49,
  height   = 30,
  units    = "in",
  path     = "../OutputFigures.dir"
)

 AF_Mono_Ologo_Poly_Instant
```

### 3.2. Pheno monogenic, oligogenic, and Polygenic

```{r, warning=FALSE, fig.width = 25, fig.height = 20, dpi = 1200, echo=FALSE}
#| label: Pheno_Mono_Oligo_Poly_Instant

dirpath <- "../../Output.dir/LinFS.dir/"
pattern <- "^MeanPhenotypes\\d+_n(1|10)_H0\\.(1|5|8)(SD(1|2|4))?(Gen(10|20|30))?\\.csv$"

process_files <- function(dirpath, pattern) {
  
  # List matching files
  files <- list.files(dirpath, pattern = pattern, full.names = TRUE)
  
  dataframes <- list()
  
  for (file in files) {
    replicate <- as.numeric( sub(".*MeanPhenotypes(\\d+)_.*", "\\1", basename(file)))
    H <- as.numeric( sub(".*_H(0\\.\\d+).*", "\\1", basename(file)))
    loci <- as.numeric( sub(".*_n(\\d+)_.*", "\\1", basename(file)))
    SD <- as.numeric( sub(".*SD(\\d+).*", "\\1", basename(file)))
    Gen <- as.numeric( sub(".*Gen(\\d+).*", "\\1", basename(file)))
    
    
    selection_label <- ifelse(loci == 1, "1 Locus",
                       ifelse(loci == 10, "10 Loci", "100 Loci"))
    
    data <- read.csv(file, header = TRUE) %>%
      mutate(
        H = H,
        loci = loci,
        SD = SD,
        Gen = Gen,
        replicate = as.factor(replicate),
        Selection = selection_label,
        
        h2_sd = paste0("h2 = ", H, " sd = ", SD),
        loci_gen = paste0("loci = ", loci, " gen = ", Gen),
        Fitness = exp(-(1/125) * (Phenotype - Optimum)^2)) %>%
      filter(
        Generation <= 1000
      )
    
    dataframes[[file]] <- data
  }
  
  combined_data <- bind_rows(dataframes)
  
 #combined_data <- combined_data %>%
  #  filter(!replicate %in% c("1", "13", "28"))
  
  return(combined_data)
}

combined_data <- process_files(dirpath, pattern)

Pheno_Mono_Oligo_Poly <- combined_data %>%
  filter(
    (H == 0.1 & SD == 1 & Gen == 10) |
    (H == 0.8 & SD == 4 & Gen == 30)
  ) %>%
  mutate(
    H_SD_Gen_short = case_when(
      H == 0.1 & SD == 1 & Gen == 10 ~ "Min combo",
      H == 0.8 & SD == 4 & Gen == 30 ~ "High combo"
    )
  ) %>%
  mutate(
    H_SD_Gen_short = fct_relevel(H_SD_Gen_short, "Min combo", "High combo")
  ) %>%
  ggplot(aes(x = Generation, y = Phenotype)) +
  geom_line(aes(group = replicate),
            color = "gray50", alpha = 0.7, size = 0.5) +
  # stat_summary(
  #   fun = mean, aes(group = 1), geom = "line",
  #   color = "red", alpha = 0.7, size = 3
  # ) +
  facet_grid(H_SD_Gen_short ~ Selection, scales = "free") +
  labs(
    title = "B) Phenotypes",
    x = "Generation",
    y = "Phenotypes"
  ) +
  theme_bw() +
  mythemes

ggsave(
  filename = "Pheno_Mono_Oligo_Poly.jpg",
  plot     = Pheno_Mono_Oligo_Poly,
  dpi      = 600,
  width    = 49,
  height   = 30,
  units    = "in",
  path     = "../OutputFigures.dir"
)

 Pheno_Mono_Oligo_Poly

```

### 3.3. Spec_Analysis monogenic, oligogenic, and Polygenic

```{r, warning=FALSE, fig.width = 10, fig.height = 20, dpi = 1200, echo=FALSE}
#| label: Spec_Analysis_Mono_Oligo_Poly_Instant

run_fft_analysis <- function(folder_path, pattern, spectrum_span = 2) {
  
  # 1) Find all files
  file_list <- list.files(path = folder_path, pattern = pattern, full.names = TRUE)
  
  files_df <- data.frame(file_name = file_list) %>%
    mutate(
      base_name = basename(file_name),
      replicate <- as.numeric( sub(".*genome(\\d+)_.*", "\\1", base_name)),
      genome = ifelse(
        grepl("genome\\d+", base_name),
        as.numeric(sub(".*genome(\\d+).*", "\\1", base_name)),
        NA_real_),
      loci = ifelse(
        grepl("_n\\d+", base_name),
        as.numeric(sub(".*_n(\\d+).*", "\\1", base_name)),
        NA_real_),
      H = ifelse(
        grepl("_H[0-9]+\\.?[0-9]*", base_name),
        as.numeric(sub(".*_H([0-9]+\\.?[0-9]*).*", "\\1", base_name)),
        NA_real_),
      SD = ifelse(
        grepl("SD[0-9]+(\\.[0-9]+)?", base_name),
        as.numeric(sub(".*SD([0-9]+(?:\\.[0-9]+)?).*", "\\1", base_name)),
        NA_real_),
      Gen = ifelse(
        grepl("Gen\\d+", base_name),
        as.numeric(sub(".*Gen(\\d+).*", "\\1", base_name)),
        NA_real_),
     Selection = case_when(
        loci == 1 ~ "1 Locus",
        loci == 10 ~ "10 Loci",
        TRUE ~ "Unknown"
      ),
      
      param_combination = paste0(
        "loci_", loci, "_H", H, 
        ifelse(!is.na(SD), paste0("_SD", SD), ""), 
        ifelse(!is.na(Gen), paste0("_Gen", Gen), "")
      )
    )

  num_cores_to_use <- min(detectCores() - 16, 64) # check the cores before
  cluster_type   <- if (.Platform$OS.type == "windows") "PSOCK" else "FORK"
  cl <- makeCluster(num_cores_to_use, type = cluster_type)
  registerDoParallel(cl)

  combined_data_list <- foreach(i = seq_along(files_df$file_name), 
                                .packages = c("dplyr")) %dopar% {
    file  <- files_df$file_name[i]
    params <- files_df[i, ]
    
    df <- read.csv(file) 
    data <- df %>%
      mutate(
        allele_id       = as.factor(Position),
        generation      = as.numeric(Generation),
        allele_frequency= Frequency,
        file            = params$base_name,
        replicate       = params$replicate,
        loci            = params$loci,
        H               = params$H,
        SD              = params$SD,
        Gen             = params$Gen,
        Selection       = params$Selection,
        param_combination = params$param_combination
      ) %>%
      dplyr::select(
        allele_id, generation, allele_frequency, replicate, 
        loci, H, SD, Gen, Selection, param_combination
      )
    data
  }
  combined_data <- bind_rows(combined_data_list)
  
  filtered_data <- combined_data %>%
    filter(
      (Selection == "1 Locus"  & H == 0.1 & SD == 1 & Gen == 10) |
      (Selection == "1 Locus"  & H == 0.8 & SD == 4 & Gen == 30) |
      (Selection == "10 Loci" & H == 0.1 & SD == 1 & Gen == 10) |
      (Selection == "10 Loci" & H == 0.8 & SD == 4 & Gen == 30)
    )

  mean_allele_data <- filtered_data %>%
    group_by(generation, loci, replicate, H, SD, Gen, Selection, param_combination) %>%
    summarize(
      mean_allele_frequency = mean(allele_frequency), 
      .groups = "drop"
    )

  ts_data_list <- mean_allele_data %>%
    group_by(loci, replicate, H, SD, Gen, Selection, param_combination) %>%
    summarize(
      ts_data = list(ts(mean_allele_frequency, 
                        start = min(generation),
                        frequency = 1)),
      .groups = 'drop'
    )

  spec_results_list <- foreach(i = 1:nrow(ts_data_list), .packages = c("stats")) %dopar% {
    ts_data <- ts_data_list$ts_data[[i]]
    spectrum(ts_data, spans = spectrum_span, plot = FALSE)
  }

  plot_data_list <- foreach(i = seq_along(spec_results_list),
                            .packages = c("dplyr")) %dopar% {
    spec_result <- spec_results_list[[i]]
    params <- ts_data_list[i, ]
    period <- 1 / spec_result$freq
    
    data.frame(
      Period    = period,
      Spectrum  = spec_result$spec,
      loci      = params$loci,
      replicate = params$replicate,
      H         = params$H,
      SD        = params$SD,
      Gen       = params$Gen,
      Selection = params$Selection,
      param_combination = params$param_combination
    )
  }

  stopCluster(cl) 
  
  plot_data <- bind_rows(plot_data_list) %>%
    group_by(param_combination) %>%
    mutate(
      threshold = case_when(
        Gen == 10 ~ 40,
        Gen == 20 ~ 50,
        Gen == 30 ~ 80,
        TRUE      ~ max(Period)
      )
    ) %>%
    filter(Period < threshold) %>%
    ungroup() %>%
    mutate(
      H_SD_Gen  = paste0("H = ", H, " SD = ", SD, " Gen = ", Gen),
      H_SD      = paste0("H = ", H, " SD = ", SD),
      H_SD_Gen_short = case_when(
            H == 0.1 & SD == 1 & Gen == 10 ~ "Min combo",
            H == 0.8 & SD == 4 & Gen == 30 ~ "High combo")
    ) %>%
    mutate(H_SD_Gen_short = fct_relevel(H_SD_Gen_short, "Min combo", "High combo"))

  if (any(is.na(plot_data$Gen))) {
    fft_plots <- ggplot(
      plot_data, 
      aes(x = Period, y = Spectrum, color = factor(replicate), group = factor(replicate))
    ) +
      geom_line(linewidth = 1.5) +
      facet_wrap(H_SD ~ Selection, scales = "free") +
      scale_y_continuous(labels = scales::label_number())+
      labs(title = "C) Spectral Density", x = "Period (Generations)", y = "Spectral Density") +
      mythemes
  } else {
    fft_plots <- ggplot(
      plot_data %>% mutate(facetgrouping = paste0(Selection, ": ", H_SD_Gen_short)) %>% 
        mutate(facetgrouping = fct_relevel(facetgrouping, "1 Locus: Min combo", 
                                           "1 Locus: High combo",
                                           "10 Loci: Min combo",
                                           "10 Loci: High combo")),
      aes(x = Period, y = Spectrum, color = factor(replicate), group = factor(replicate))
    ) +
      geom_line(linewidth = 1.5) +
      scale_y_continuous(labels = scales::label_number())+
      facet_wrap(~ facetgrouping, scales = "free", ncol = 1) +
      #facet_grid(Selection ~ H_SD_Gen_short, scales = "free") +
      labs(title = "C) Spectral Density", x = "Period (Generations)", y = "Spectral Density") +
      mythemes
  }

  return(fft_plots)
}

dirpath <- "../../Output.dir/LinFS.dir/"
pattern <- "^genome\\d+_n(1|10)_H0\\.(1|5|8)(SD(1|2|4))?Gen(10|20|30)\\.csv$"

Spec_Mono_Oligo_Poly <- run_fft_analysis(dirpath, pattern)

ggsave(
  filename = "Spec_Mono_Oligo_Poly.jpg",
  plot     = Spec_Mono_Oligo_Poly,
  dpi      = 600,
  width    = 20,
  height   = 30,
  units    = "in",
  path     = "../OutputFigures.dir"
)

Spec_Mono_Oligo_Poly

```

### 3.4. Genome architecture all models Polygenic Instantaneous: AF, Pheno, and Spec Analysis

```{r, warning=FALSE, fig.width = 22, fig.height = 20, dpi = 1200, echo=FALSE}
#| label: All_Instant_Mono_Oligo_Poly
#| 
top_plot     <- AF_Mono_Ologo_Poly_Instant + theme(plot.margin = margin(b = 20))
bottom_left  <- Pheno_Mono_Oligo_Poly + theme(plot.margin = margin(r = 20, b = 20))
bottom_right <- Spec_Mono_Oligo_Poly   + theme(plot.margin = margin(l = 20, b = 20))


All_Mono_Oligo_Poly <- plot_grid(plot_grid(top_plot, bottom_left, 
                                           ncol = 1, 
                                           rel_heights = c(2.4, 2)), 
                                 bottom_right, rel_widths = c(2, 1.2))

ggsave("Figure3.jpg", #All_Instant_Mono_Oligo_Poly.jpg
       plot = All_Mono_Oligo_Poly, 
       dpi = 600, 
       width = 44, 
       height = 40, 
       units = "in", 
       path = "../OutputFigures.dir")

All_Mono_Oligo_Poly

```

### 3.5 Fixed percentages for each architecture

```{r, fig.height=5, fig.width=10, echo=FALSE, dpi = 1200, message=FALSE}
#| label: Fixation_Percentages
#### Parameter combination as colors
library(furrr)
library(fs)
#library(stringr)
library(dplyr)

path <- "../../Output.dir/LinFS.dir/"
pattern <- "^genome\\d+_n\\d+_H0.(1|5|8)(SD[1|4])?Gen(10|30)?\\.csv$" 

# List files using list.files (full paths, filtering by regex)
files <- list.files(path, pattern, full.names = TRUE)

if (length(files) == 0) {
  stop("No files found matching the pattern in the specified path.")
}

available_cores <- parallel::detectCores()
workers_to_use <- max(1, available_cores - 4)  
plan(multicore, workers = workers_to_use)

process_file <- function(file) {
  filename <- path_file(file)
  repl_val <- as.numeric(sub(".*genome(\\d+)_.*", "\\1", basename(filename)))
  H_val <- as.numeric(sub(".*_H(0\\.\\d+).*", "\\1", basename(filename)))
  loci_val <- as.numeric(sub(".*_n(\\d+)_.*", "\\1", basename(filename)))
  SD_val <- as.numeric(sub(".*SD(\\d+).*", "\\1", basename(filename)))
  Gen_val <- as.numeric(sub(".*Gen(\\d+).*", "\\1", basename(filename)))
  
  df <- read.csv(file) %>%
    dplyr::select(-any_of("Origin")) %>%
    mutate(
      Position = as_factor(Position),
      repl = (repl_val),
      H    = (H_val),
      loci = (loci_val),
      SD   = (SD_val),
      Gen  = (Gen_val)
    )
  
  required <- c("H", "loci", "SD", "Gen", "repl", "Position")
  missing_cols <- setdiff(required, names(df))
  if (length(missing_cols) > 0) {
    warning("File ", filename, " is missing the following columns: ",
            paste(missing_cols, collapse = ", "))
  }
  return(df)
}

combined_data <- future_map_dfr(files, process_file, .options = furrr_options(chunk_size = 100))

data_with_fix <- combined_data %>%
  group_by(H, loci, SD, Gen, repl, Position) %>%
  filter(Frequency == 1 | (Frequency < 1 & Generation == max(Generation) & max(Generation) < 2000)) %>% 
  distinct(H, loci, SD, Gen, repl, Position) %>% 
  ungroup()

replicate_summary <- data_with_fix %>%
  group_by(H, loci, SD, Gen, repl) %>%
  summarise(
    fixed_count = n_distinct(Position),
    total_count = 30 * loci,  # count of unique loci in this replicate
    .groups = "drop"
  ) %>% 
  distinct()


parameter_summary <- replicate_summary %>%
  group_by(H, loci, SD, Gen, total_count) %>%
  summarise(
    total_fixed    = sum(fixed_count),
    total_possible = total_count,
    Perc_Loci      = total_fixed * 100 / total_possible,
    .groups = "drop"
  ) %>%
  mutate(
    Gen_SD  = paste0("Gen = ", Gen, " SD = ", SD),
    H_label = paste0("H = ", H),
    Combo   = paste0(H_label, ", ", Gen_SD)
  ) %>% 
  distinct()

Fixation_Percentages <-
  ggplot(
    parameter_summary %>%
      mutate(
        H   = as_factor(H),
        loci= as_factor(loci),
        SD  = as_factor(SD),
        Gen = as_factor(Gen)
      ),
    aes(
      x = loci,
      y = Perc_Loci,
      color = H,
      shape = SD,
      linetype = Gen,
      group = interaction(H, Gen, SD)
    )
  ) +
  geom_line(linewidth = 3) +
  geom_point(size = 7, stroke = 0) +
  labs(
    x = "Number of Loci",
    y = "Percentage of Loci Fixed (%)",
    color = "Heritability (h\u00B2)",
    linetype = "Season Length (Gen)",
    shape = "Distance to Optimum (Δ)"
  ) +
  scale_color_manual(values = c("darkblue", "gray50", "firebrick")) +
  scale_linetype_manual(
    values = c("solid", "dashed", "dotted", "dotdash", "longdash", "twodash")
  ) +
  theme_bw() +
  theme(
    text           = element_text(family = "sans"),
    axis.text.x    = element_text(face = "bold", size = 30, angle = 15,
                                  hjust = 1, margin = margin(t = 10)),
    axis.text.y    = element_text(face = "bold", size = 30, angle = 15,
                                  margin = margin(r = 10)),
    axis.line      = element_line(linewidth = 1.2),
    plot.title     = element_text(hjust = 0.01, face = "bold", size = 30),
    axis.title.x   = element_text(size = 30, face = "bold",
                                  margin = margin(t = 30)),
    axis.title.y   = element_text(size = 30, face = "bold",
                                  margin = margin(r = 35)),
    strip.text     = element_text(size = 30, face = "bold"),
    panel.spacing  = unit(5, "lines"),
    panel.grid     = element_blank(),
    legend.position= c(0.95, 0.95),
    legend.justification = c("right", "top"),
    legend.text    = element_text(size = 32, face = "bold"),
    legend.title   = element_text(size = 34, face = "bold"),
    legend.key.width = unit(2.5, "cm")  
  ) +
  guides(
    color    = guide_legend(override.aes = list(shape = 16, size = 6), byrow = TRUE),
    linetype = guide_legend(override.aes = list(linewidth = 2, color = "black"))
  )

ggsave("Figure4.jpg", #Fixation_Percentages.jpg
       plot = Fixation_Percentages, 
       dpi = 600, 
       width = 40, 
       height = 20, 
       units = "in", 
       path = "../OutputFigures.dir")

print(Fixation_Percentages)

```

## 4. Beyond instantaneous selection: gradual selection models

### 4.1. AF Freq All models by parameters

```{r, warning=FALSE, fig.width = 22, fig.height = 10, dpi=1200, echo=FALSE}
#| label: AF_FS_model_comparison
mono1 <- read.csv("../../Output.dir/LinFS.dir/genome10_n100_H0.8SD4Gen30.csv")
mono2 <-  read.csv("../../Output.dir/SinFS.dir/genome10_n100_H0.8SD4Gen30.csv")
mono3 <- read.csv("../../Output.dir/SinFSGen.dir/genome10_n100_H0.8SD4.csv")


# Add a column to distinguish the datasets
geno_file <- mono1 %>% mutate(Selection = "Instantaneous")
geno_file2 <- mono2 %>% mutate(Selection = "Simple Gradual")
geno_file3 <- mono3 %>% mutate(Selection = "Complex Gradual I")

Genome_dataset <- rbind(geno_file, 
                        geno_file2, geno_file3) %>% 
  mutate(Selection = fct_relevel(Selection, 
                                 "Instantaneous", 
                                 "Simple Gradual", 
                                 "Complex Gradual I"))

## Select 30 random positions
  set.seed(12345)
  selected_positions <- Genome_dataset %>%
  distinct(Position) %>%
  sample_n(size = min(30, n()), replace = FALSE) %>%
  pull(Position)

 Genome_dataset <- Genome_dataset %>%
      filter(Position %in% selected_positions)
  
AF_FS_model_comparison <- Genome_dataset %>% 
  filter(Generation <= 1000) %>%
  ggplot(aes(x = Generation, y = Frequency, group = factor(Position))) +
  geom_line(
    aes(
      color = factor(Position == 323379), # Highlight the position 
      size  = factor(Position == 323379)
    ),
    alpha = 0.8
  ) +
  scale_color_manual(values = c("TRUE" = "magenta", "FALSE" = "grey")) +
  scale_size_manual(values  = c("TRUE" = 2, "FALSE" = 0.5)) +
  facet_wrap(Selection ~ .) +
  theme_bw() +
  mythemes
  
ggsave(
  filename = "Figure6.jpg", #AF_FS_model_comparison.jpg#
  plot = AF_FS_model_comparison,
  dpi = 600, width = 30, height = 15, units = "in",
  path = "../OutputFigures.dir"
)

print(AF_FS_model_comparison)

```

### 4.2. FS model comparison by genomic architecture

### 4.2.1. AF All models comparisons

```{r,  warning=FALSE, fig.width = 30, fig.height = 22, dpi=1200, echo=FALSE}
# Load necessary libraries
library(dplyr)
library(ggplot2)
library(forcats)
library(cowplot)

n_values <- c(1, 10, 100) # Loci to compare
gene_number_labels <- c("1" = "1 Locus", "10" = "10 Loci", "100" = "100 Loci")

selections <- list(#"LinFS.dir" = "Instantaneous",
  "SinFS.dir" = "Simple Gradual",
  "SinFSGen.dir" = "Complex Gradual I"
)

dataset_list <- list()

for (n in n_values) {
  for (dir_name in names(selections)) {
    selection_label <- selections[[dir_name]]
    if (dir_name == "SinFSGen.dir") {
      filename <- paste0("../../Output.dir/", dir_name, "/genome10_n", n, "_H0.5SD4.csv")
    } else {
      filename <- paste0("../../Output.dir/", dir_name, "/genome10_n", n, "_H0.5SD4Gen20.csv")
    }
    
    if (file.exists(filename)) {
      data <- read.csv(filename)
      
  data <- data %>%
    mutate(Selection = selection_label,
          Gene_Number = gene_number_labels[as.character(n)])
      
      dataset_list[[length(dataset_list) + 1]] <- data
    } else {
      warning(paste("File not found:", filename))
    }
  }
}

Genome_dataset <- bind_rows(dataset_list) %>%
  mutate(
    Selection = fct_relevel(Selection, "Simple Gradual", "Complex Gradual I"), #"Instantaneous", 
    Gene_Number = fct_relevel(Gene_Number, "1 Locus", "10 Loci", "100 Loci")
  )

monogenic_positions <- Genome_dataset %>%
  filter(Gene_Number == "1 Locus") %>%
  pull(Position) %>%
  unique()
monogenic_highlight <- ifelse(length(monogenic_positions) >= 1, monogenic_positions[1], NA)

highlight_positions <- data.frame(
  Gene_Number = c("1 Locus", "10 Loci", "100 Loci"),
  Highlight_Position = c(monogenic_highlight, 427101, 323379) # 1037246, 201349
)

Genome_dataset <- Genome_dataset %>%
  left_join(highlight_positions, by = "Gene_Number") %>%
  mutate(Highlight = Position == Highlight_Position)


# Get all positions for Polygenic
Polygenic_positions <- Genome_dataset %>%
  filter(Gene_Number == "100 Loci") %>%
  pull(Position) %>%
  unique()

Polygenic_highlight <- highlight_positions %>%
  filter(Gene_Number == "100 Loci") %>%
  pull(Highlight_Position)

# Remove the highlighted position from positions to sample 
positions_to_sample <- setdiff(Polygenic_positions, Polygenic_highlight)

# Randomly sample 29 positions (since we have 1 highlighted position)
set.seed(123) 
sampled_positions <- sample(positions_to_sample, 
                            size = min(29, length(positions_to_sample)), 
                            replace = FALSE)

selected_Polygenic_positions <- c(sampled_positions, Polygenic_highlight)

Genome_dataset_filtered <- Genome_dataset %>%
  filter(
    (Gene_Number != "100 Loci") | (Position %in% selected_Polygenic_positions)
  )

All_models_freq <- Genome_dataset_filtered %>% 
  filter(Generation <= 1000) %>%
  ggplot(aes(x = Generation, 
             y = Frequency, 
             group = factor(Position), 
             color = as.factor(Highlight),
             size = as.factor(Highlight))) +
  geom_line(alpha = 0.8) +
  scale_size_manual(values = c("TRUE" = 2, "FALSE" = 1)) +
  scale_color_manual(values = c("TRUE" = "magenta", "FALSE" = "grey")) +
  labs(title = "A) Allele Frequency", x = "Generation", y = "Frequency") +
  facet_grid(Selection ~ Gene_Number) +
  theme_bw()+
  mythemes
  
ggsave("All_models_freq.jpg", 
       plot = All_models_freq, 
       dpi = 600, width = 30, height = 20,
       units = "in", path = "../OutputFigures.dir")

print(All_models_freq)
```

```{r, warning=FALSE, fig.width = 30, fig.height = 22, dpi=1200, echo=FALSE}
library(dplyr)
library(ggplot2)

Instat <- read.csv("../../Output.dir/LinFS.dir/genome10_n100_H0.8SD4Gen30.csv")
GradII <-  read.csv("../../Output.dir/SinFS.dir/genome10_n100_H0.8SD4Gen30.csv")
GradIV_1 <- read.csv("../../Output.dir/SinFSGen.dir/genome10_n100_H0.8SD4.csv")
GradIV_2 <- read.csv("../../Output.dir/FourSeasFourAmp.dir/genome10_n100_H0.8.csv")


# Add a column to distinguish the datasets
geno_file <- Instat %>% mutate(Selection = "Instantaneous")
geno_file2 <- GradII %>% mutate(Selection = "Simple Gradual")
geno_file3 <- GradIV_1 %>% mutate(Selection = "Complex Gradual I") #
geno_file4 <- GradIV_2 %>% mutate(Selection = "Complex Gradual II")

Genome_dataset <- rbind(geno_file, 
                        geno_file2, geno_file3, geno_file4) %>% 
  mutate(Selection = fct_relevel(Selection, 
                                 "Instantaneous", 
                                 "Simple Gradual",
                                 "Complex Gradual I",
                                 "Complex Gradual II"))

## Select 30 random positions
  set.seed(12345)
  selected_positions <- Genome_dataset %>%
  distinct(Position) %>%
  sample_n(size = min(30, n()), replace = FALSE) %>%
  pull(Position)

 Genome_dataset <- Genome_dataset %>%
   filter(Position %in% selected_positions)
# Effect sizes for highlighted positions
pos_meta <- tibble::tribble(
  ~Position, ~effect_size,
    982341,   0.000008,
   #1067762,   0.140653,
    811499,   3.562828
   # 323379,   2.431675
) %>%
  mutate(beta_lab = sprintf("\u03B2=%s", signif(effect_size, 3)))

# Colors (Okabe–Ito palette)
col_vals <- setNames(
  c("#0072B2", "darkred"),#"#D55E00", "#009E73", "#CC79A7"
  pos_meta$beta_lab
)

df <- Genome_dataset %>%
  filter(Generation <= 1000) %>%
  left_join(pos_meta, by = "Position") %>%
  mutate(is_highlight = !is.na(effect_size))

# Right-edge labels (effect only)
lab_df <- df %>%
  filter(is_highlight) %>%
  group_by(Selection, Position, beta_lab) %>%
  filter(Generation == max(Generation)) %>%
  ungroup()

AF_FS_model_comparison <-
  ggplot(df, aes(Generation, Frequency, group = Position)) +
  # Background
  geom_line(data = dplyr::filter(df, !is_highlight),
            color = "grey70", linewidth = 0.5, alpha = 0.6) +
  # Highlights (legend keyed by β only)
  geom_line(data = dplyr::filter(df, is_highlight),
            aes(color = beta_lab), linewidth = 1.1, alpha = 0.95) +
  # On-plot labels showing β only
  # geom_text(data = lab_df,
  #           aes(label = beta_lab, color = beta_lab),
  #           hjust = 0, nudge_x = 12, size = 3.6, show.legend = FALSE) +
  scale_color_manual(name = "Effect size", values = col_vals) +
 # scale_x_continuous(expand = expansion(mult = c(0.01, 0.10))) +
  facet_wrap(Selection ~ .) +
  labs(x = "Generation", y = "Allele Frequency") +
  theme_bw() +
  theme(legend.position = "bottom") +
  mythemes

ggsave("Figure5.jpg", 
       plot = AF_FS_model_comparison, 
       dpi = 800, width = 30, height = 22,
       units = "in", bg = "white", path = "../OutputFigures.dir")

print(AF_FS_model_comparison)

```

### 4.2.2. Phenotype All models comparisons

```{r,  warning=FALSE, fig.width = 30, fig.height = 22, dpi=1200, echo=FALSE, message=FALSE}
#| label: All_models_Pheno

n_values <- c(1, 10, 100)
gene_number_labels <- c("1" = "1 Locus", "10" = "10 Loci", "100" = "100 Loci")

selections <- list(
  #"LinFS.dir" = "Instantaneous",
  "SinFS.dir" = "Simple Gradual",
  "SinFSGen.dir" = "Complex Gradual I"
)

phenotype_list <- list()
for (n in n_values) {
  for (dir_name in names(selections)) {
    selection_label <- selections[[dir_name]]
    if (dir_name == "SinFSGen.dir") {
      file_pattern <- paste0("MeanPhenotypes\\d+_n", n, "_H0\\.5SD4\\.csv$")
      file_path <- paste0("../../Output.dir/", dir_name)
    } else {
      file_pattern <- paste0("MeanPhenotypes\\d+_n", n, "_H0\\.5SD4Gen20\\.csv$")
      file_path <- paste0("../../Output.dir/", dir_name)
    }
    file_list <- list.files(
      path = file_path,
      pattern = file_pattern,
      full.names = TRUE
    )
    
    for (file in file_list) {
      data <- read.csv(file)
      replicate_value <- as.numeric( sub(".*MeanPhenotypes(\\d+)_.*", "\\1", basename(file)))
      
      data <- data %>%
        mutate(
          Selection = selection_label,
          Gene_Number = gene_number_labels[as.character(n)],
          Replicate = replicate_value
        )
      phenotype_list[[length(phenotype_list) + 1]] <- data
    }
  }
}

Phenotype_dataset <- bind_rows(phenotype_list) %>%
  mutate(
    Selection = fct_relevel(Selection, "Instantaneous", "Simple Gradual", "Complex Gradual I"),
    Gene_Number = fct_relevel(Gene_Number, "1 Locus", "10 Loci", "100 Loci")
  )

All_models_Pheno <- Phenotype_dataset %>% filter(Generation <= 1000) %>% 
  ggplot(aes(x = Generation, y = Phenotype, group = Replicate)) +
  #geom_boxplot() + # outlier.size = 0.5, width = 0.6, alpha = 0.7
  geom_line(linewidth = 1, alpha = 0.7, color = "black") + # outlier.size = 0.5, width = 0.6, alpha = 0.7
  stat_summary(fun = mean,                              
               aes(group = 1), 
               geom = "line", 
               color = "red", 
               alpha = 1, 
               size = 3) +
  facet_grid(Selection ~ Gene_Number) +
  labs(title = "B) Phenotypes", x = "Generation", y = "Phenotype")+
  theme_bw()+
  mythemes

ggsave("All_models_Pheno.jpg", plot = All_models_Pheno, dpi = 600, width = 30, height = 25, units = "in", path = "../OutputFigures.dir")

print(All_models_Pheno)
```

### 4.2.3. Spectral All models comparisons

```{r,  warning=FALSE, fig.width = 49, fig.height = 22, dpi=600, echo=FALSE, message=FALSE}
#| label: All_models_Spec2
n_values <- c(1, 10, 100)
gene_number_labels <- c("1" = "1 Locus", "10" = "10 Loci", "100" = "100 Loci")

selections <- list(
  #"LinFS.dir" = "Instantaneous",
  "SinFS.dir" = "Simple Gradual",
  "SinFSGen.dir" = "Complex Gradual I"
)

allele_freq_list <- list()
for (n in n_values) {
  for (dir_name in names(selections)) {
    selection_label <- selections[[dir_name]]
    if (dir_name == "SinFSGen.dir") {
      file_pattern <- paste0("genome\\d+_n", n, "_H0\\.5SD4\\.csv$")
      file_path <- paste0("../../Output.dir/", dir_name)
    } else {
      file_pattern <- paste0("genome\\d+_n", n, "_H0\\.5SD4Gen20\\.csv$")
      file_path <- paste0("../../Output.dir/", dir_name)
    }
    
    file_list <- list.files(
      path = file_path,
      pattern = file_pattern,
      full.names = TRUE
    )
    
    for (file in file_list) {
      data <- read.csv(file)
      replicate_value <- as.numeric( sub(".*genome(\\d+)_.*", "\\1", basename(file)))
      
      data <- data %>%
        mutate(
          Selection = selection_label,
          Gene_Number = gene_number_labels[as.character(n)],
          Replicate = factor(replicate_value)
        )
      
      allele_freq_list[[length(allele_freq_list) + 1]] <- data
    }
  }
}

AlleleFreq_dataset <- bind_rows(allele_freq_list) %>%
  mutate(
    Selection = fct_relevel(Selection, "Instantaneous", "Simple Gradual", "Complex Gradual I"),
    Gene_Number = fct_relevel(Gene_Number, "1 Locus", "10 Loci", "100 Loci")
  )

  num_cores_to_use <- min(detectCores() - 16, 32) # check the cores before
  cluster_type   <- if (.Platform$OS.type == "windows") "PSOCK" else "FORK"
  cl <- makeCluster(num_cores_to_use, type = cluster_type)
  registerDoParallel(cl)

grouped_data <- AlleleFreq_dataset %>%
  group_by(Selection, Gene_Number, Replicate)

unique_combinations <- grouped_data %>%
  summarize() %>%
  ungroup()

spectral_results <- foreach(i = 1:nrow(unique_combinations), .packages = c("dplyr", "stats")) %dopar% {
  sel <- unique_combinations$Selection[i]
  gene_num <- unique_combinations$Gene_Number[i]
  rep <- unique_combinations$Replicate[i]
  
  df <- AlleleFreq_dataset %>%
    filter(Selection == sel, Gene_Number == gene_num, Replicate == rep) %>%
    arrange(Generation)
  
  mean_freq_df <- df %>%
    group_by(Generation) %>%
    summarize(Mean_Frequency = mean(Frequency, na.rm = TRUE)) %>%
    arrange(Generation)
  
ts_data <- ts(mean_freq_df$Mean_Frequency, 
              start = min(mean_freq_df$Generation), frequency = 1)
  
spec_result <- spectrum(ts_data, spans = 2, plot = FALSE)
period <- 1 / spec_result$freq
  
  data.frame(
    Period = period,
    Spectrum = spec_result$spec,
    Selection = sel,
    Gene_Number = gene_num,
    Replicate = rep
  )
}

# Stop cluster
stopCluster(cl)

spectral_data <- bind_rows(spectral_results)

spectral_data <- spectral_data %>%
  filter(Period < 80)

All_models_Spec <- spectral_data %>%
  mutate(
    Facet_formula = factor(
      paste0(Gene_Number, " ", Selection),
      levels = c(
        "1 Locus Instantaneous", "10 Loci Instantaneous", "100 Loci Instantaneous",
        "1 Locus Simple Gradual", "10 Loci Simple Gradual", "100 Loci Simple Gradual",
        "1 Locus Complex Gradual I", "10 Loci Complex Gradual I", "100 Loci Complex Gradual I"
      )
    )
  ) %>% 
  ggplot(aes(x = Period, y = Spectrum, group = Replicate, color = Replicate)) +
  geom_line(alpha = 1, size = 2) +
  scale_y_continuous(labels = scales::label_number())+
  #facet_wrap( ~ Selection + Gene_Number, scales = "free", ncol = 3) +
  facet_wrap( ~ Facet_formula, scales = "free", ncol = 3, dir = "h") +
  #scale_color_viridis_d() +  # Use a discrete color palette
  labs(
    x = "Period (Generations)",
    y = "Spectral Density",
    color = "Replicate"
  ) +
  labs(title = "C) Spectral Density", x = "Period (Generations)",
       y = "Spectral Density")+
  theme_bw()+
  mythemes
    

ggsave("All_models_Spec.jpg", plot = All_models_Spec, dpi = 600, width = 49, height = 30, units = "in", path = "../OutputFigures.dir")

print(All_models_Spec)

```

```{r,  warning=FALSE, fig.width = 30, fig.height = 18, dpi=1600, echo=FALSE, message=FALSE}
#| label: All_models_Spec
n_values <- c(1, 10,100)#1, 
gene_number_labels <- c("1" = "1 Locus", "10" = "10 Loci", "100" = "100 Loci", "300" = "300 Loci")

selections <- list(
#"LinFS.dir" = "Instantaneous",
"SinFS.dir" = "Simple Gradual",
"SinFSGen.dir" = "Complex Gradual I", 
"FourSeasFourAmp.dir" = "Complex Gradual II"
)

allele_freq_list <- list()
for (n in n_values) {
  for (dir_name in names(selections)) {
    selection_label <- selections[[dir_name]]
    if (dir_name == "SinFSGen.dir") {
      file_pattern <- paste0("genome\\d+_n", n, "_H0\\.5SD2\\.csv$")
      file_path <- paste0("../../Output.dir/", dir_name)
    }else if (dir_name == "FourSeasFourAmp.dir") {
      file_pattern <- paste0("genome\\d+_n", n, "_H0\\.5\\.csv$")
      file_path <- paste0("../../Output.dir/", dir_name)
    } else {
      file_pattern <- paste0("genome\\d+_n", n, "_H0\\.5SD2Gen20\\.csv$")
      file_path <- paste0("../../Output.dir/", dir_name)
    }
    
    file_list <- list.files(
      path = file_path,
      pattern = file_pattern,
      full.names = TRUE
    )
    
    for (file in file_list) {
      data <- read.csv(file) #%>% filter(Generation >=1800)
      replicate_value <- as.numeric( sub(".*genome(\\d+)_.*", "\\1", basename(file)))
      
      data <- data %>%
        mutate(
          Selection = selection_label,
          Gene_Number = gene_number_labels[as.character(n)],
          Replicate = factor(replicate_value)
        )
      
      allele_freq_list[[length(allele_freq_list) + 1]] <- data
    }
  }
}

AlleleFreq_dataset <- bind_rows(allele_freq_list) %>%
  mutate(
    Selection = fct_relevel(Selection, "Instantaneous", "Simple Gradual", "Complex Gradual I", "Complex Gradual II"),
    Gene_Number = fct_relevel(Gene_Number, "1 Locus", "10 Loci", "100 Loci", "300 Loci")
  )

  num_cores_to_use <- min(detectCores() - 16, 32) # check the cores before
  cluster_type   <- if (.Platform$OS.type == "windows") "PSOCK" else "FORK"
  cl <- makeCluster(num_cores_to_use, type = cluster_type)
  registerDoParallel(cl)

grouped_data <- AlleleFreq_dataset %>%
  group_by(Selection, Gene_Number, Replicate)

unique_combinations <- grouped_data %>%
  summarize() %>%
  ungroup()

spectral_results <- foreach(i = 1:nrow(unique_combinations), .packages = c("dplyr", "stats")) %dopar% {
  sel <- unique_combinations$Selection[i]
  gene_num <- unique_combinations$Gene_Number[i]
  rep <- unique_combinations$Replicate[i]
  
  df <- AlleleFreq_dataset %>%
    filter(Selection == sel, Gene_Number == gene_num, Replicate == rep) %>%
    arrange(Generation)
  
  mean_freq_df <- df %>%
    group_by(Generation) %>%
    summarize(Mean_Frequency = mean(Frequency, na.rm = TRUE)) %>%
    arrange(Generation)
  
ts_data <- ts(mean_freq_df$Mean_Frequency, 
              start = min(mean_freq_df$Generation), frequency = 1)
  
spec_result <- spectrum(ts_data, spans = 2, plot = FALSE)
period <- 1 / spec_result$freq
  
  data.frame(
    Period = period,
    Spectrum = spec_result$spec,
    Selection = sel,
    Gene_Number = gene_num,
    Replicate = rep
  )
}

# Stop cluster
stopCluster(cl)

spectral_data <- bind_rows(spectral_results)

spectral_data <- spectral_data %>%
  filter(Period < 80)

All_models_Spec <- spectral_data %>%
  mutate(
    Facet_formula = factor(
      paste0(Gene_Number, " ", Selection),
      levels = c(
        "1 Locus Instantaneous", "10 Loci Instantaneous", "100 Loci Instantaneous",  "300 Loci Instantaneous",
        "1 Locus Simple Gradual", "10 Loci Simple Gradual", "100 Loci Simple Gradual",  "300 Loci Simple Gradual",
        "1 Locus Complex Gradual I", "10 Loci Complex Gradual I", "100 Loci Complex Gradual I" , "300 Loci Complex Gradual I" ,
        "1 Locus Complex Gradual II", "10 Loci Complex Gradual II", "100 Loci Complex Gradual II", "300 Loci Complex Gradual II"
      )
    )
  ) %>% 
  ggplot(aes(x = Period, y = Spectrum, group = Replicate, color = Replicate)) +
  geom_line(alpha = 1, size = 2) +
  scale_y_continuous(labels = scales::label_number())+
  #facet_wrap( ~ Selection + Gene_Number, scales = "free", ncol = 3) +
  facet_wrap( ~ Facet_formula, scales = "free", ncol = 3, dir = "h") +
  #scale_color_viridis_d() +  # Use a discrete color palette
  labs(
    x = "Period (Generations)",
    y = "Spectral Density",
    color = "Replicate"
  ) +
  labs(title = "Spectral Density", x = "Period (Generations)",
       y = "Spectral Density")+
  theme_bw()+
  mythemes
    
# 
# ggsave("All_models_Spec.jpg", plot = All_models_Spec, dpi = 600, width = 49, height = 30, units = "in", path = "../OutputFigures.dir")

ggsave("Figure6.jpg",  plot = All_models_Spec, width = 70, height = 30, units = "in", path = "../OutputFigures.dir", limitsize = FALSE)

print(All_models_Spec)
```

### 4.2.4. Combined gradual models, comparison on architecture

```{r, warning=FALSE, fig.width = 30, fig.height = 35, dpi = 600, echo=FALSE}
#| label: Combined_gradual_models_architecture

CGMA <- plot_grid(
  All_models_freq,
  All_models_Pheno,
  All_models_Spec,
  ncol = 1,
  rel_heights = c(2.2, 2.2, 2.1)
) +
  theme(panel.spacing = unit(1, "lines"))

#Combined_gradual_models_architecture.jpg

 ggsave("Combined_gradual_models_architecture.jpg",  plot = CGMA, width = 50, height = 70, units = "in", path = "../OutputFigures.dir", limitsize = FALSE)

print(CGMA)
```

## 5. Differences between FS models and Null and constant selection models

### 5.1. Spectral Null Polygenic

```{r, warning=FALSE, fig.width = 12, fig.height = 8, dpi = 1200, echo=FALSE}
library(cowplot)
library(purrr)

run_fft_analysis <- function(folder_path, pattern, spectrum_span = 2) {
  theme_set(theme_cowplot())
 
  file_list <- list.files(path = folder_path, pattern = pattern, full.names = TRUE)

  if (length(file_list) == 0) {
    stop("No files found with the given pattern.")
  }

  files_df <- data.frame(file_name = file_list) %>%
    mutate(
      base_name = basename(file_name),
      replicate <- as.numeric( sub(".*genome(\\d+)_.*", "\\1", base_name)),
      genome = ifelse(
        grepl("genome\\d+", base_name),
        as.numeric(sub(".*genome(\\d+).*", "\\1", base_name)),
        NA_real_),
      n = ifelse(
        grepl("_n\\d+", base_name),
        as.numeric(sub(".*_n(\\d+).*", "\\1", base_name)),
        NA_real_),
      H = ifelse(
        grepl("_H[0-9]+\\.?[0-9]*", base_name),
        as.numeric(sub(".*_H([0-9]+\\.?[0-9]*).*", "\\1", base_name)),
        NA_real_),
      SD = ifelse(
        grepl("SD[0-9]+(\\.[0-9]+)?", base_name),
        as.numeric(sub(".*SD([0-9]+(?:\\.[0-9]+)?).*", "\\1", base_name)),
        NA_real_),
      Gen = ifelse(
        grepl("Gen\\d+", base_name),
        as.numeric(sub(".*Gen(\\d+).*", "\\1", base_name)),
        NA_real_),
      Selection = case_when(
        n == "1" ~ "1 Locus",
        n == "10" ~ "10 Loci",
        n == "100" ~ "100 Loci",
        TRUE ~ "Unknown"
      )
    ) %>%
    mutate(
      param_combination = paste0("n_", n, "_H", H, 
                                 ifelse(!is.na(SD), paste0("_SD", SD), ""), 
                                 ifelse(!is.na(Gen), paste0("_Gen", Gen), ""))
    )

  num_cores_to_use <- min(detectCores() - 16, 64) # check the cores before
  cluster_type   <- if (.Platform$OS.type == "windows") "PSOCK" else "FORK"
  cl <- makeCluster(num_cores_to_use, type = cluster_type)
  registerDoParallel(cl)

  combined_data_list <- foreach(i = seq_along(files_df$file_name), 
                                .packages = c("dplyr")) %dopar% {
    file <- files_df$file_name[i]
    params <- files_df[i, ]
    df <- read.csv(file)
    data <- df %>%
      mutate(
        allele_id = as.factor(Position),
        generation = as.numeric(Generation),
        allele_frequency = Frequency,
        file = params$base_name,
        genome = params$genome,
        n = params$n,
        H = params$H,
        SD = params$SD,
        Gen = params$Gen,
        Selection = params$Selection,
        param_combination = params$param_combination
      ) %>%
      dplyr::select(allele_id, generation, allele_frequency, genome, n, H, SD, Gen, Selection, param_combination)
    data
  }
  combined_data <- bind_rows(combined_data_list)

  filtered_data <- combined_data %>%
    filter(
      (H == 0.1 & (SD == 1 | is.na(SD)) & (Gen == 10 | is.na(Gen))) |
      (H == 0.5 & (SD == 2 | is.na(SD)) & (Gen == 20 | is.na(Gen))) |
      (H == 0.8 & (SD == 4 | is.na(SD)) & (Gen == 30 | is.na(Gen)))
    )

  # Calculate the mean allele frequency for each grouping
  mean_allele_data <- filtered_data %>%
    group_by(generation, n, genome, H, SD, Gen, Selection, param_combination) %>%
    summarize(mean_allele_frequency = mean(allele_frequency), .groups = "drop")

  # Create time series objects
  ts_data_list <- mean_allele_data %>%
    group_by(n, genome, H, SD, Gen, Selection, param_combination) %>%
    summarize(ts_data = list(ts(mean_allele_frequency, start = min(generation), frequency = 1)), .groups = 'drop')

  # Compute spectral density estimates
  spec_results_list <- foreach(i = 1:nrow(ts_data_list), .packages = c("stats")) %dopar% {
    ts_data <- ts_data_list$ts_data[[i]]
    spectrum(ts_data, spans = spectrum_span, plot = FALSE)
  }

  plot_data_list <- foreach(i = seq_along(spec_results_list), 
                            .packages = c("dplyr")) %dopar% {
    spec_result <- spec_results_list[[i]]
    params <- ts_data_list[i, ]
    period <- 1 / spec_result$freq
    data.frame(
      Period = period,
      Spectrum = spec_result$spec,
      n = params$n,
      genome = params$genome,
      H = params$H,
      SD = params$SD,
      Gen = params$Gen,
      Selection = params$Selection,
      param_combination = params$param_combination
    )
  }

  stopCluster(cl)
  plot_data <- bind_rows(plot_data_list)

  plot_data <- plot_data %>%
    group_by(param_combination) %>%
    mutate(threshold = case_when(
      !is.na(Gen) & Gen == 10 ~ 40,
      !is.na(Gen) & Gen == 20 ~ 50,
      !is.na(Gen) & Gen == 30 ~ 80,
      TRUE ~ 60
    )) %>%
    filter(Period < threshold) %>%
    ungroup() %>%
    mutate(
      H_label = paste0("H = ", H),
      SD_label = ifelse(!is.na(SD), paste0("SD = ", SD), "No SD"),
      Gen_label = ifelse(!is.na(Gen), paste0("Gen = ", Gen), "No Gen"),
      n_label = paste0("n_", n)
    )

  fft_plots <- ggplot(plot_data, aes(x = Period, y = Spectrum, color = factor(genome), group = factor(genome))) +
    geom_line(linewidth = 1.1) +
    scale_y_continuous(labels = scales::scientific_format())+
    #scale_y_continuous(labels = scales::label_number())+
    #facet_wrap(Selection ~ H_label + SD_label + Gen_label, scales = "free", ncol = 1) +
    facet_wrap(Selection ~ ., scales = "free", ncol = 1) +
    labs(title = "A) Null Model", x = NULL, y = NULL) +
    mythemes

  return(fft_plots)
}

dirpath <- "../../Output.dir/NS.dir/"

pattern <- "^genome\\d+_n(100)_H0\\.(1|8)(SD(1|4))?(Gen(10|30))?\\.csv$"#1|10|

neut_spec_plots <- run_fft_analysis(dirpath, pattern)
```

### Constant Selection

```{r, warning=FALSE, fig.width = 12, fig.height = 8, dpi = 1200, echo=FALSE}

run_fft_analysis <- function(folder_path, pattern, spectrum_span = 2) {
  
  theme_set(theme_cowplot())
  
  
  file_list <- list.files(path = folder_path, pattern = pattern, full.names = TRUE)

  if (length(file_list) == 0) {
    stop("No files found with the given pattern.")
  }

  files_df <- data.frame(file_name = file_list) %>%
    mutate(
      base_name = basename(file_name),
      replicate <- as.numeric( sub(".*genome(\\d+)_.*", "\\1", base_name)),
      genome = ifelse(
        grepl("genome\\d+", base_name),
        as.numeric(sub(".*genome(\\d+).*", "\\1", base_name)),
        NA_real_),
      n = ifelse(
        grepl("_n\\d+", base_name),
        as.numeric(sub(".*_n(\\d+).*", "\\1", base_name)),
        NA_real_),
      H = ifelse(
        grepl("_H[0-9]+\\.?[0-9]*", base_name),
        as.numeric(sub(".*_H([0-9]+\\.?[0-9]*).*", "\\1", base_name)),
        NA_real_),
      SD = ifelse(
        grepl("SD[0-9]+(\\.[0-9]+)?", base_name),
        as.numeric(sub(".*SD([0-9]+(?:\\.[0-9]+)?).*", "\\1", base_name)),
        NA_real_),
      Gen = ifelse(
        grepl("Gen\\d+", base_name),
        as.numeric(sub(".*Gen(\\d+).*", "\\1", base_name)),
        NA_real_),
      Selection = case_when(
        n == "1" ~ "1 Locus",
        n == "10" ~ "10 Loci",
        n == "100" ~ "100 Loci",
        TRUE ~ "Unknown"
      )
    ) %>%
    mutate(
      param_combination = paste0("n_", n, "_H", H, 
                                 ifelse(!is.na(SD), paste0("_SD", SD), ""), 
                                 ifelse(!is.na(Gen), paste0("_Gen", Gen), ""))
    )

  num_cores_to_use <- min(detectCores() - 16, 64) # check the cores before
  cluster_type   <- if (.Platform$OS.type == "windows") "PSOCK" else "FORK"
  cl <- makeCluster(num_cores_to_use, type = cluster_type)
  registerDoParallel(cl)

  combined_data_list <- foreach(i = seq_along(files_df$file_name), .packages = c("dplyr")) %dopar% {
    file <- files_df$file_name[i]
    params <- files_df[i, ]
    df <- read.csv(file)
    data <- df %>%
      mutate(
        allele_id = as.factor(Position),
        generation = as.numeric(Generation),
        allele_frequency = Frequency,
        file = params$base_name,
        genome = params$genome,
        n = params$n,
        H = params$H,
        SD = params$SD,
        Gen = params$Gen,
        Selection = params$Selection,
        param_combination = params$param_combination
      ) %>%
      dplyr::select(allele_id, generation, allele_frequency, genome, n, H, SD, Gen, Selection, param_combination)
    data
  }
  combined_data <- bind_rows(combined_data_list)

  filtered_data <- combined_data %>%
    filter(
      (H == 0.1 & (SD == 1 | is.na(SD)) & (Gen == 10 | is.na(Gen))) |
      (H == 0.5 & (SD == 2 | is.na(SD)) & (Gen == 20 | is.na(Gen))) |
      (H == 0.8 & (SD == 4 | is.na(SD)) & (Gen == 30 | is.na(Gen)))
    )

  mean_allele_data <- filtered_data %>%
    group_by(generation, n, genome, H, SD, Gen, Selection, param_combination) %>%
    summarize(mean_allele_frequency = mean(allele_frequency), .groups = "drop")

  # Create time series objects
  ts_data_list <- mean_allele_data %>%
    group_by(n, genome, H, SD, Gen, Selection, param_combination) %>%
    summarize(ts_data = list(ts(mean_allele_frequency, start = min(generation), frequency = 1)), .groups = 'drop')

  # Compute spectral density estimates 
  spec_results_list <- foreach(i = 1:nrow(ts_data_list), .packages = c("stats")) %dopar% {
    ts_data <- ts_data_list$ts_data[[i]]
    spectrum(ts_data, spans = spectrum_span, plot = FALSE)
  }

  plot_data_list <- foreach(i = seq_along(spec_results_list), .packages = c("dplyr")) %dopar% {
    spec_result <- spec_results_list[[i]]
    params <- ts_data_list[i, ]
    period <- 1 / spec_result$freq
    data.frame(
      Period = period,
      Spectrum = spec_result$spec,
      n = params$n,
      genome = params$genome,
      H = params$H,
      SD = params$SD,
      Gen = params$Gen,
      Selection = params$Selection,
      param_combination = params$param_combination
    )
  }

  stopCluster(cl)

  # Combine all plot data
  plot_data <- bind_rows(plot_data_list)

  plot_data <- plot_data %>%
    group_by(param_combination) %>%
    mutate(threshold = case_when(
      !is.na(Gen) & Gen == 10 ~ 40,
      !is.na(Gen) & Gen == 20 ~ 50,
      !is.na(Gen) & Gen == 30 ~ 80,
      TRUE ~ 80
    )) %>%
    filter(Period < threshold) %>%
    ungroup() %>%
    mutate(
      H_label = paste0("h\u00B2 = ", H),
      SD_label = ifelse(!is.na(SD), paste0("SD = ", SD), "No SD"),
      Gen_label = ifelse(!is.na(Gen), paste0("Gen = ", Gen), "No Gen"),
      n_label = paste0("n_", n)
    )

  fft_plots <- ggplot(
  plot_data %>% mutate(FacetTerm = paste0(Selection)),
  aes(x = Period, y = Spectrum, color = factor(genome), group = factor(genome))
) +
  geom_line(linewidth = 1.1) +
  scale_y_continuous(labels = scales::scientific_format()) +
  #scale_x_continuous(breaks = seq(0, 40, by = 2)) +  
  facet_wrap(FacetTerm ~ ., scales = "free", ncol = 1) +
  labs(title = "B) Constant Optima  model", x = NULL, y = NULL) +
  mythemes

  return(fft_plots)
}

dirpath <- "../../Output.dir/CS.dir/"
#dirpath <- "../../Output.dir/FourSeasFourAmp.dir/"
#pattern <- "^genome\\d+_n(1|10|100)_H0\\.(8)(SD(1))?(Gen(10|30))?\\.csv$"
pattern <- "^genome\\d+_n(1|10|100)_H0\\.(1)(SD(1))?(Gen(10|30))?\\.csv$" #1|10|

Const_spec_plots <- run_fft_analysis(dirpath, pattern)
Const_spec_plots <- Const_spec_plots 
Const_spec_plots
```

### 5.2. Spectral Gradual II Polygenic

```{r, warning=FALSE, fig.width = 12, fig.height = 8, dpi = 1200, echo=FALSE}

run_fft_analysis <- function(folder_path, pattern, spectrum_span = 2) {
  
  theme_set(theme_cowplot())
  
  
  file_list <- list.files(path = folder_path, pattern = pattern, full.names = TRUE)

  if (length(file_list) == 0) {
    stop("No files found with the given pattern.")
  }

  files_df <- data.frame(file_name = file_list) %>%
    mutate(
      base_name = basename(file_name),
      replicate <- as.numeric( sub(".*genome(\\d+)_.*", "\\1", base_name)),
      genome = ifelse(
        grepl("genome\\d+", base_name),
        as.numeric(sub(".*genome(\\d+).*", "\\1", base_name)),
        NA_real_),
      n = ifelse(
        grepl("_n\\d+", base_name),
        as.numeric(sub(".*_n(\\d+).*", "\\1", base_name)),
        NA_real_),
      H = ifelse(
        grepl("_H[0-9]+\\.?[0-9]*", base_name),
        as.numeric(sub(".*_H([0-9]+\\.?[0-9]*).*", "\\1", base_name)),
        NA_real_),
      SD = ifelse(
        grepl("SD[0-9]+(\\.[0-9]+)?", base_name),
        as.numeric(sub(".*SD([0-9]+(?:\\.[0-9]+)?).*", "\\1", base_name)),
        NA_real_),
      Gen = ifelse(
        grepl("Gen\\d+", base_name),
        as.numeric(sub(".*Gen(\\d+).*", "\\1", base_name)),
        NA_real_),
      Selection = case_when(
        n == "1" ~ "1 Locus",
        n == "10" ~ "10 Loci",
        n == "100" ~ "100 Loci",
        TRUE ~ "Unknown"
      )
    ) %>%
    mutate(
      param_combination = paste0("n_", n, "_H", H, 
                                 ifelse(!is.na(SD), paste0("_SD", SD), ""), 
                                 ifelse(!is.na(Gen), paste0("_Gen", Gen), ""))
    )

  num_cores_to_use <- min(detectCores() - 16, 64) # check the cores before
  cluster_type   <- if (.Platform$OS.type == "windows") "PSOCK" else "FORK"
  cl <- makeCluster(num_cores_to_use, type = cluster_type)
  registerDoParallel(cl)

  combined_data_list <- foreach(i = seq_along(files_df$file_name), .packages = c("dplyr")) %dopar% {
    file <- files_df$file_name[i]
    params <- files_df[i, ]
    df <- read.csv(file)
    data <- df %>%
      mutate(
        allele_id = as.factor(Position),
        generation = as.numeric(Generation),
        allele_frequency = Frequency,
        file = params$base_name,
        genome = params$genome,
        n = params$n,
        H = params$H,
        SD = params$SD,
        Gen = params$Gen,
        Selection = params$Selection,
        param_combination = params$param_combination
      ) %>%
      dplyr::select(allele_id, generation, allele_frequency, genome, n, H, SD, Gen, Selection, param_combination)
    data
  }
  combined_data <- bind_rows(combined_data_list)

  filtered_data <- combined_data %>%
    filter(
      (H == 0.1 & (SD == 1 | is.na(SD)) & (Gen == 10 | is.na(Gen))) |
      (H == 0.5 & (SD == 2 | is.na(SD)) & (Gen == 20 | is.na(Gen))) |
      (H == 0.8 & (SD == 4 | is.na(SD)) & (Gen == 30 | is.na(Gen)))
    )

  mean_allele_data <- filtered_data %>%
    group_by(generation, n, genome, H, SD, Gen, Selection, param_combination) %>%
    summarize(mean_allele_frequency = mean(allele_frequency), .groups = "drop")

  # Create time series objects
  ts_data_list <- mean_allele_data %>%
    group_by(n, genome, H, SD, Gen, Selection, param_combination) %>%
    summarize(ts_data = list(ts(mean_allele_frequency, start = min(generation), frequency = 1)), .groups = 'drop')

  # Compute spectral density estimates 
  spec_results_list <- foreach(i = 1:nrow(ts_data_list), .packages = c("stats")) %dopar% {
    ts_data <- ts_data_list$ts_data[[i]]
    spectrum(ts_data, spans = spectrum_span, plot = FALSE)
  }

  plot_data_list <- foreach(i = seq_along(spec_results_list), .packages = c("dplyr")) %dopar% {
    spec_result <- spec_results_list[[i]]
    params <- ts_data_list[i, ]
    period <- 1 / spec_result$freq
    data.frame(
      Period = period,
      Spectrum = spec_result$spec,
      n = params$n,
      genome = params$genome,
      H = params$H,
      SD = params$SD,
      Gen = params$Gen,
      Selection = params$Selection,
      param_combination = params$param_combination
    )
  }

  stopCluster(cl)

  # Combine all plot data
  plot_data <- bind_rows(plot_data_list)

  plot_data <- plot_data %>%
    group_by(param_combination) %>%
    mutate(threshold = case_when(
      !is.na(Gen) & Gen == 10 ~ 40,
      !is.na(Gen) & Gen == 20 ~ 50,
      !is.na(Gen) & Gen == 30 ~ 80,
      TRUE ~ 80
    )) %>%
    filter(Period < threshold) %>%
    ungroup() %>%
    mutate(
      H_label = paste0("h\u00B2 = ", H),
      SD_label = ifelse(!is.na(SD), paste0("SD = ", SD), "No SD"),
      Gen_label = ifelse(!is.na(Gen), paste0("Gen = ", Gen), "No Gen"),
      n_label = paste0("n_", n)
    )

  fft_plots <- ggplot(
  plot_data %>% mutate(FacetTerm = paste0(Selection)),
  aes(x = Period, y = Spectrum, color = factor(genome), group = factor(genome))
) +
  geom_line(linewidth = 1.1) +
  scale_y_continuous(labels = scales::scientific_format()) +
  #scale_x_continuous(breaks = seq(0, 40, by = 2)) +  
  facet_wrap(FacetTerm ~ ., scales = "free", ncol = 1) +
  labs(title = "C) Complex Gradual I", x = NULL, y = NULL) +
  mythemes

  return(fft_plots)
}

dirpath <- "../../Output.dir/SinFSGen.dir/"
#dirpath <- "../../Output.dir/FourSeasFourAmp.dir/"
#pattern <- "^genome\\d+_n(1|10|100)_H0\\.(8)(SD(1))?(Gen(10|30))?\\.csv$"
pattern <- "^genome\\d+_n(100)_H0\\.(1)(SD(1))?(Gen(10|30))?\\.csv$" #1|10|

gradII_spec_plots <- run_fft_analysis(dirpath, pattern)
gradII_spec_plots <- gradII_spec_plots 
```

### 5.3 Spectral Null and Grad II Polygenic

```{r, warning=FALSE, fig.width = 30, fig.height = 20, dpi=1200, echo=FALSE}
#| label: Spectral_Null_and_GradII_Polygenic
library(cowplot)
library(ggplot2)

neut_spec_plots <- neut_spec_plots + 
  theme(axis.title = element_blank())

gradII_spec_plots <- gradII_spec_plots + 
  theme(axis.title = element_blank())

adjusted_neut_spec_plots <- neut_spec_plots +
  theme(
    plot.margin = margin(t = 1,  # top
                         r = 2,  # right
                         b = 1,  # bottom
                         l = 1,  # left
                         unit = "lines")
  )


adjusted_gradII_spec_plots <- gradII_spec_plots +
  theme(
    plot.margin = margin(t = 1,
                         r = 1,
                         b = 1,
                         l = 2,
                         unit = "lines")
  )

combined_plot <- plot_grid(
  adjusted_neut_spec_plots,
  adjusted_gradII_spec_plots,
  ncol = 1,
  rel_widths = c(1, 1)
)

Spectral_Null_and_GradII_Polygenic <- ggdraw() +
  draw_plot(combined_plot, x = 0.05, y = 0.05, width = 0.95, height = 0.95) +
  draw_label("Periodicity (Generations)", 
             x = 0.5, y = 0.015, 
             vjust = 0, size = 60, fontface = "bold") +
  draw_label("Spectral Density", 
             x = 0.015, y = 0.5, angle = 90, 
             hjust = 0, size = 60, fontface = "bold")

#Spectral_Null_and_GradII_Polygenic.jpg

ggsave("Figure7.jpg", plot = Spectral_Null_and_GradII_Polygenic, width = 35, height = 20, bg = "white", path = "../OutputFigures.dir")


print(Spectral_Null_and_GradII_Polygenic)

```

### 5.4 Allele Frequency Dynamics

```{r, warning=FALSE, fig.width = 22, fig.height = 10, dpi=1200, echo=FALSE}
#| label: AF_CSNSFS_model_comparison
mono1 <- read.csv("../../Output.dir/NS.dir/genome10_n100_H0.1.csv")
mono2 <-  read.csv("../../Output.dir/CS.dir/genome10_n100_H0.1SD1.csv")
mono3 <- read.csv("../../Output.dir/SinFSGen.dir/genome10_n100_H0.1SD1.csv")


# Add a column to distinguish the datasets
geno_file <- mono1 %>% mutate(Selection = "Null model")
geno_file2 <- mono2 %>% mutate(Selection = "Constant model")
geno_file3 <- mono3 %>% mutate(Selection = "Complex Gradual I")

Genome_dataset <- rbind(geno_file, 
                        geno_file2, geno_file3) %>% 
  mutate(Selection = fct_relevel(Selection, 
                                 "Null model", 
                                 "Constant model",
                                 "Complex Gradual I"))

## Select 30 random positions
  set.seed(12345)
  selected_positions <- Genome_dataset %>%
  distinct(Position) %>%
  sample_n(size = min(30, n()), replace = FALSE) %>%
  pull(Position)

 Genome_dataset <- Genome_dataset %>%
   filter(Position %in% selected_positions)
# Effect sizes for highlighted positions
pos_meta <- tibble::tribble(
  ~Position, ~effect_size,
    982341,   0.000008,
   #1067762,   0.140653,
    811499,   3.562828
   # 323379,   2.431675
) %>%
  mutate(beta_lab = sprintf("\u03B2=%s", signif(effect_size, 3)))

# Colors (Okabe–Ito palette)
col_vals <- setNames(
  c("#0072B2", "darkred"),#"#D55E00", "#009E73", "#CC79A7"
  pos_meta$beta_lab
)

df <- Genome_dataset %>%
  filter(Generation <= 1000) %>%
  left_join(pos_meta, by = "Position") %>%
  mutate(is_highlight = !is.na(effect_size))

# Right-edge labels (effect only)
lab_df <- df %>%
  filter(is_highlight) %>%
  group_by(Selection, Position, beta_lab) %>%
  filter(Generation == max(Generation)) %>%
  ungroup()

AF_CSNSFS_model_comparison <-
  ggplot(df, aes(Generation, Frequency, group = Position)) +
  # Background
  geom_line(data = dplyr::filter(df, !is_highlight),
            color = "grey70", linewidth = 0.5, alpha = 0.6) +
  geom_line(data = dplyr::filter(df, is_highlight),
            aes(color = beta_lab), linewidth = 1.1, alpha = 0.95) +
  scale_color_manual(name = "Effect size", values = col_vals) +
  facet_wrap(Selection ~ .) +
  labs(title = "Allele Frequency Dynamics", x = "Generation", y = "Allele Frequency") +
  theme_bw() +
  theme(legend.position = "bottom") +
  mythemes

ggsave("AF_CSNSFS_model_comparison.jpg", 
       plot = AF_CSNSFS_model_comparison, 
       dpi = 600, width = 30, height = 20,
       units = "in", bg = "white", path = "../OutputFigures.dir")

print(AF_CSNSFS_model_comparison)

```

```{r, warning=FALSE, fig.width = 30, fig.height = 10, dpi=1200, echo=FALSE}
run_fft_by_selection <- function(
  folder_paths,                   
  pattern,                        
  selection_labels = NULL, 
  spectrum_span = 2, 
  max_period = NULL,
  selection_levels = c("Null model", 
                       "Constant model", 
                       "Complex Gradual I")
) {
  suppressPackageStartupMessages({
    library(dplyr)
    library(stringr)
    library(foreach)
    library(doParallel)
    library(readr)
    library(ggplot2)
  })
  if (requireNamespace("cowplot", quietly = TRUE)) {
    theme_set(cowplot::theme_cowplot())
  } else {
    theme_set(theme_bw())
  }

  # collect all files from all dirs
  folder_paths <- as.character(folder_paths)
  stopifnot(length(folder_paths) >= 1)

  file_list <- unlist(lapply(folder_paths, function(p) {
    list.files(path = p, pattern = pattern, full.names = TRUE)
  }), use.names = FALSE)

  if (length(file_list) == 0) {
    stop("No files found across the provided directories with the given pattern.")
  }

  files_df <- tibble(file_path = file_list) %>%
    mutate(
      base_name = basename(file_path),
      dir_base = basename(dirname(file_path)),
      # replicate: prefer _repl#, else genome#
      replicate = coalesce(str_extract(base_name, "(?<=_repl)\\d+") %>% as.integer(),
                      str_extract(base_name, "(?<=genome)\\d+") %>% as.integer()),
      n = str_extract(base_name, "(?<=_n)\\d+") %>% as.integer(),
      H = str_extract(base_name, "(?<=_H)\\d+(?:\\.\\d+)?") %>% as.numeric(),
      SD = str_extract(base_name, "(?<=SD)\\d+(?:\\.\\d+)?") %>% as.numeric(),  # optional
      Gen = str_extract(base_name, "(?<=Gen)\\d+") %>% as.integer() # optional
    )

  map_selection <- function(d) {
    if (!is.null(selection_labels) && !is.na(selection_labels[d])) {
      return(selection_labels[d])
    }
    if (grepl("^NS", d, ignore.case = TRUE)) return("Null model")
    if (grepl("^CS", d, ignore.case = TRUE)) return("Constant model")
    if (grepl("SinFSGen|FourSeas|Grad", d, ignore.case = TRUE))
      return("Complex Gradual I")
    d
  }
  files_df <- files_df %>% mutate(Selection = vapply(dir_base, map_selection, character(1)))

  num_cores_to_use <- min(detectCores() - 16, 64) # check the cores before
  cluster_type   <- if (.Platform$OS.type == "windows") "PSOCK" else "FORK"
  cl <- makeCluster(num_cores_to_use, type = cluster_type)
  registerDoParallel(cl)

  # read each file, mean across positions per generation (replicate-level series)
  per_file_means <- foreach(i = seq_len(nrow(files_df)), .packages = c("dplyr", "readr")) %dopar% {
    f <- files_df[i, ]
    dat <- readr::read_csv(f$file_path, show_col_types = FALSE)

    # Expect: Position, Generation, Frequency
    # Aggregate across positions per generation
    dat %>%
      transmute(
        generation = as.integer(Generation),
        allele_frequency = as.numeric(Frequency)
      ) %>%
      group_by(generation) %>%
      summarise(mean_allele_frequency = mean(allele_frequency, na.rm = TRUE), .groups = "drop") %>%
      mutate(
        Selection = f$Selection,
        replicate = ifelse(is.na(f$replicate), i, f$replicate),
        base_name = f$base_name,
        n = f$n,
        H = f$H,
        SD = f$SD,  
        Gen = f$Gen 
      )
  }
  series_df <- bind_rows(per_file_means)

  # build time series per Selection and replicate
  ts_df <- series_df %>%
    arrange(Selection, replicate, generation) %>%
    group_by(Selection, replicate, n, H, SD, Gen) %>%
    summarise(
      ts_data = list(ts(mean_allele_frequency,
                        start = min(generation, na.rm = TRUE),
                        frequency = 1)),
      .groups = "drop"
    )

  # spectra
  spec_list <- foreach(i = seq_len(nrow(ts_df)), .packages = "stats") %dopar% {
    spectrum(ts_df$ts_data[[i]], spans = spectrum_span, plot = FALSE)
  }

  # assemble plot data
  plot_df <- bind_rows(lapply(seq_along(spec_list), function(i) {
    s <- spec_list[[i]]
    p <- ts_df[i, ]
    tibble(
      Period    = 1 / s$freq,
      Spectrum  = s$spec,
      Selection = p$Selection,
      replicate = p$replicate,
      n  = p$n, H = p$H, SD = p$SD, Gen = p$Gen
    )
  }))

  if (!is.null(max_period)) {
    plot_df <- plot_df %>% filter(Period <= max_period)%>%
    mutate(
      Selection = stringr::str_trim(Selection),
      Selection = factor(Selection, levels = selection_levels)
    )
  }
 closeAllConnections()
  ggplot(plot_df, aes(Period, Spectrum, color = factor(replicate), 
                      group = factor(replicate))) +
    geom_line(linewidth = 1.0, alpha = 0.9) +
    scale_y_continuous(labels = scales::scientific_format()) +
    labs(
      title = "Spectral Density",
      x = "Period (Generations)", y = "Spectrum Density", color = "Replicate"
    ) +
    facet_wrap(~ Selection, scales = "free_y", ncol = 3)+
    mythemes
}

dirs <- c(
  "../../Output.dir/NS.dir",
  "../../Output.dir/CS.dir",
  "../../Output.dir/SinFSGen.dir"
)

sel_map <- c(
  "NS.dir" = "Null model",
  "CS.dir" = "Constant model",
  "SinFSGen.dir" = "Complex Gradual I"
)

pattern <- "^genome\\d+_n(100)_H0\\.(1)(SD(1))?(Gen(10))?\\.csv$"

spec_plot <- run_fft_by_selection(
  folder_paths     = dirs,
  pattern          = pattern,
  selection_labels = sel_map,
  spectrum_span    = 2,  
  max_period       = 80
)

spec_plot
```

```{r, warning=FALSE, fig.width = 30, fig.height = 20, dpi=1200, echo=FALSE}
#| label: Spectral_Null_Constant_and_GradII_Polygenic
library(cowplot)
library(ggplot2)

neut_spec_plots <- AF_CSNSFS_model_comparison + 
  theme(axis.title = element_blank())

gradII_spec_plots <- spec_plot + 
  theme(axis.title = element_blank())

adjusted_neut_spec_plots <- neut_spec_plots +
  theme(
    plot.margin = margin(t = 1,  # top
                         r = 2,  # right
                         b = 1,  # bottom
                         l = 1,  # left
                         unit = "lines")
  )


adjusted_gradII_spec_plots <- gradII_spec_plots +
  theme(
    plot.margin = margin(t = 1,
                         r = 1,
                         b = 1,
                         l = 2,
                         unit = "lines")
  )

Spectral_Null_Constant_and_GradII_Polygenic <- plot_grid(
  adjusted_neut_spec_plots,
  adjusted_gradII_spec_plots,
  ncol = 1,
  rel_widths = c(1, 1.2)
)


#Spectral_Null_Constant_and_GradII_Polygenic.jpg
# 
 ggsave("Figure7.jpg", plot = Spectral_Null_Constant_and_GradII_Polygenic, width = 35, height = 20, bg = "white", path = "../OutputFigures.dir")


print(Spectral_Null_Constant_and_GradII_Polygenic)

```

## Extra Code, not for published paper. This is to consider spectal analysis for some generations, not all 2000.

## 6. Sampled Generations Spectral Analysis

### 6.1 Spectral Instantaneous sampled Generations: End vs End_Mid Samples

```{r, warning=FALSE, fig.width = 30, fig.height = 15, echo=FALSE, dpi = 1200}
#| label: Instant_Poly_SpecAnalysis_Sampled

library(doParallel)
library(foreach)
library(dplyr)
library(ggplot2)

run_fft_analysis <- function(folder_path, pattern, spectrum_span = c(2, 2),
                             sampling_scheme = c("end", "mid_end")) {

  sampling_scheme <- match.arg(sampling_scheme)

  last_dir <- basename(normalizePath(folder_path))

  file_list <- list.files(
    path = folder_path,
    pattern = pattern,
    full.names = TRUE
  )

  if (length(file_list) == 0) {
    stop("No files are found")
  } else {
    cat("The number of files is ", length(file_list), "\n")
  }

  files_df <- data.frame(file_name = file_list) %>%
    dplyr::mutate(
      base_name = basename(file_name),
      genome = ifelse(
        grepl("genome\\d+", base_name),
        as.numeric(sub(".*genome(\\d+).*", "\\1", base_name)),
        NA_real_
      ),
      n = ifelse(
        grepl("_n\\d+", base_name),
        as.numeric(sub(".*_n(\\d+).*", "\\1", base_name)),
        NA_real_
      ),
      H = ifelse(
        grepl("_H[0-9]+\\.?[0-9]*", base_name),
        as.numeric(sub(".*_H([0-9]+\\.?[0-9]*).*", "\\1", base_name)),
        NA_real_
      ),
      SD = ifelse(
        grepl("SD[0-9]+(\\.[0-9]+)?", base_name),
        as.numeric(sub(".*SD([0-9]+(?:\\.[0-9]+)?).*", "\\1", base_name)),
        NA_real_
      ),
      Gen = ifelse(
        grepl("Gen\\d+", base_name),
        as.numeric(sub(".*Gen(\\d+).*", "\\1", base_name)),
        NA_real_
      )
    ) %>%
    dplyr::mutate(
      param_combination = paste0(
        "n_", n, "_H", H,
        ifelse(!is.na(SD),  paste0("_SD", SD),  ""),
        ifelse(!is.na(Gen), paste0("_Gen", Gen), "")
      )
    )

  # Use Hihj and Low coombinations only
  files_df <- files_df %>%
    dplyr::filter(
      (H == 0.1 & SD == 1 & Gen == 10) |
      (H == 0.8 & SD == 4 & Gen == 30)
    )


  cores_available <- parallel::detectCores(logical = TRUE)
  num_cores_to_use <- max(1, min(cores_available - 2, 32))
  cluster_type <- if (.Platform$OS.type == "windows") "PSOCK" else "FORK"
  cl <- parallel::makeCluster(num_cores_to_use, type = cluster_type)
  on.exit(try(parallel::stopCluster(cl), silent = TRUE), add = TRUE)
  doParallel::registerDoParallel(cl)

  combined_data_list <- foreach::foreach(
    i = seq_along(files_df$file_name),
    .packages = c("dplyr"),
    .export   = "sampling_scheme"
  ) %dopar% {
    file   <- files_df$file_name[i]
    params <- files_df[i, ]

    full_df <- utils::read.csv(file, stringsAsFactors = FALSE)

    out <- full_df %>%
      dplyr::mutate(
        allele_id = as.factor(Position),
        generation  = as.numeric(Generation),
        allele_frequency = Frequency,
        sample_size = 10000,
        file = params$base_name,
        genome = params$genome,
        n = params$n,
        H = params$H,
        SD = params$SD,
        Gen = params$Gen,
        param_combination = params$param_combination
      ) %>%
      dplyr::select(
        allele_id, generation, allele_frequency, sample_size, file,
        genome, n, H, SD, Gen, param_combination
      ) %>%
      dplyr::group_by(allele_id)

    if (sampling_scheme == "end") {
      out <- out %>%
        dplyr::filter(generation == min(generation) |
                      generation %% Gen == 0)
    } else {
      out <- out %>%
        dplyr::filter(generation == min(generation) |
                      generation %% (Gen / 2) == 0)
    }

    out %>% dplyr::ungroup()
  }

  combined_data <- dplyr::bind_rows(combined_data_list)


  mean_allele_data <- combined_data %>%
    dplyr::group_by(generation, n, genome, H, SD, Gen, param_combination) %>%
    dplyr::summarize(
      mean_allele_frequency = mean(allele_frequency),
      .groups = "drop"
    ) %>%
    dplyr::arrange(n, genome, H, SD, Gen, param_combination, generation)

  ts_data_list <- mean_allele_data %>%
    dplyr::group_by(n, genome, H, SD, Gen, param_combination) %>%
    dplyr::summarize(
      ts_data = list(stats::ts(mean_allele_frequency,
                               start = min(generation),
                               frequency = 1)),
      .groups = "drop"
    )

  spec_results_list <- lapply(ts_data_list$ts_data, function(ts_data) {
    spans_use <- if (length(ts_data) >= 8) spectrum_span else NULL
    stats::spectrum(ts_data, spans = spans_use, plot = FALSE)
  })

  plot_data_list <- vector("list", length(spec_results_list))
  for (i in seq_along(spec_results_list)) {
    spec_result = spec_results_list[[i]]
    params  = ts_data_list[i, ]

    # Rescale period from sample-steps to generations
    interval <- if (sampling_scheme == "end") params$Gen else params$Gen / 2
    period_samples <- 1 / spec_result$freq

    df_spec = data.frame(
      Period_samples = period_samples,
      Period = period_samples * interval,
      Spectrum = spec_result$spec,
      n = params$n,
      genome = params$genome,
      H = params$H,
      SD = params$SD,
      Gen = params$Gen,
      param_combination = params$param_combination
    )
    plot_data_list[[i]] = df_spec
  }

  plot_data = dplyr::bind_rows(plot_data_list)

  plot_data <- plot_data %>%
    dplyr::group_by(param_combination) %>%
    dplyr::mutate(
      threshold = dplyr::case_when(
        Gen == 10 ~ 40,
        Gen == 30 ~ 80,
        TRUE ~ max(Period)
      )
    ) %>%
    dplyr::ungroup() %>%
    dplyr::filter(
      Period < threshold &
        (
          (H == 0.1 & SD == 1 & Gen == 10) |
          (H == 0.8 & SD == 4 & Gen == 30)
        )
    ) %>%
    dplyr::mutate(
      H_SD_Gen = paste0("h\u00B2 = ", H, " \u0394 = ", SD, " Gen=", Gen)
    )

  scheme_title <- if (sampling_scheme == "end") {
    "A) Spectral Density: Sampling at the end of each season"
  } else {
    "B) Spectral Density: Sampling at the middle & end of each season"
  }

  spec_plot_comb1 = ggplot2::ggplot(
    plot_data,
    ggplot2::aes(x = Period, y = Spectrum, color = factor(genome), group = factor(genome))
  ) +
    ggplot2::geom_line(linewidth = 3) +
    ggplot2::facet_wrap(~ H_SD_Gen, scales = "free", ncol = 2) +
    ggplot2::scale_y_continuous(labels = scales::label_number()) +
    ggplot2::labs(
      title = scheme_title, x = "Period (Generations)", y = "Spectral Density"
    ) +
    ggplot2::theme_classic() +
    ggplot2::theme(text = ggplot2::element_text(family = "sans"),
        legend.position = "none",
        axis.text = ggplot2::element_text(size = 20, face = "bold"),
        axis.line = ggplot2::element_line(size = 3),
        strip.text = ggplot2::element_text(size = 17, face = "bold"),
        plot.title = ggplot2::element_text(hjust = 0.01, face = "bold", size = 40),
        axis.title.x = ggplot2::element_text(margin = ggplot2::margin(t = 20), size = 20, face = "bold"),
        axis.title.y = ggplot2::element_text(margin = ggplot2::margin(r = 25), size = 20, face = "bold"),
        panel.spacing = ggplot2::unit(4, "lines"))

  return(spec_plot_comb1)
}

###############################################################################
################## Running The Function for Spectral Analysis ####################
###############################################################################

dirpath    <- "../../Output.dir/LinFS.dir/"
my_pattern <- "^genome\\d+_n100_H0\\.(1SD1Gen10|8SD4Gen30)\\.csv$"

library(patchwork)

plot_end     <- run_fft_analysis(dirpath, my_pattern, sampling_scheme = "end")
plot_mid_end <- run_fft_analysis(dirpath, my_pattern, sampling_scheme = "mid_end")

combined_plot <- plot_end / plot_mid_end

jpeg_device <- if (requireNamespace("ragg", quietly = TRUE)) ragg::agg_jpeg else "jpeg"

ggsave("Seasonal_Instant_Poly_SpecAnalysis_Combined_2000.jpg",
       plot = combined_plot,
       device = jpeg_device,
       dpi = 300, width = 25, height = 30, units = "in",
       path = "../OutputFigures.dir/SpectralDensity.dir")

combined_plot

```

#### Only first 500 Generations

```{r, warning=FALSE, fig.width = 30, fig.height = 15, echo=FALSE, dpi = 1200}

library(doParallel)
library(foreach)
library(dplyr)
library(ggplot2)

run_fft_analysis <- function(folder_path, pattern, spectrum_span = c(2, 2),
                             sampling_scheme = c("end", "mid_end"),
                             max_generation = 500) {

  sampling_scheme <- match.arg(sampling_scheme)

  last_dir <- basename(normalizePath(folder_path))

  file_list <- list.files(
    path = folder_path,
    pattern = pattern,
    full.names = TRUE
  )


  files_df <- data.frame(file_name = file_list) %>%
    dplyr::mutate(
      base_name = basename(file_name),
      genome = ifelse(
        grepl("genome\\d+", base_name),
        as.numeric(sub(".*genome(\\d+).*", "\\1", base_name)),
        NA_real_
      ),
      n = ifelse(
        grepl("_n\\d+", base_name),
        as.numeric(sub(".*_n(\\d+).*", "\\1", base_name)),
        NA_real_
      ),
      H = ifelse(
        grepl("_H[0-9]+\\.?[0-9]*", base_name),
        as.numeric(sub(".*_H([0-9]+\\.?[0-9]*).*", "\\1", base_name)),
        NA_real_
      ),
      SD = ifelse(
        grepl("SD[0-9]+(\\.[0-9]+)?", base_name),
        as.numeric(sub(".*SD([0-9]+(?:\\.[0-9]+)?).*", "\\1", base_name)),
        NA_real_
      ),
      Gen = ifelse(
        grepl("Gen\\d+", base_name),
        as.numeric(sub(".*Gen(\\d+).*", "\\1", base_name)),
        NA_real_
      )
    ) %>%
    dplyr::mutate(
      param_combination = paste0(
        "n_", n, "_H", H,
        ifelse(!is.na(SD),  paste0("_SD", SD),  ""),
        ifelse(!is.na(Gen), paste0("_Gen", Gen), "")
      )
    )

  # Keep only the high (0.8/4/30) and low (0.1/1/10) combinations
  files_df <- files_df %>%
    dplyr::filter(
      (H == 0.1 & SD == 1 & Gen == 10) |
      (H == 0.8 & SD == 4 & Gen == 30)
    )


  cores_available <- parallel::detectCores(logical = TRUE)
  num_cores_to_use <- max(1, min(cores_available - 2, 32))
  cluster_type <- if (.Platform$OS.type == "windows") "PSOCK" else "FORK"
  cl <- parallel::makeCluster(num_cores_to_use, type = cluster_type)
  on.exit(try(parallel::stopCluster(cl), silent = TRUE), add = TRUE)
  doParallel::registerDoParallel(cl)

  combined_data_list <- foreach::foreach(
    i = seq_along(files_df$file_name),
    .packages = c("dplyr"),
    .export   = c("sampling_scheme", "max_generation")
  ) %dopar% {
    file   <- files_df$file_name[i]
    params <- files_df[i, ]

    full_df <- utils::read.csv(file, stringsAsFactors = FALSE)

    out <- full_df %>%
      dplyr::mutate(
        allele_id = as.factor(Position),
        generation  = as.numeric(Generation),
        allele_frequency = Frequency,
        sample_size = 10000,
        file = params$base_name,
        genome = params$genome,
        n = params$n,
        H = params$H,
        SD = params$SD,
        Gen = params$Gen,
        param_combination = params$param_combination
      ) %>%
      dplyr::select(
        allele_id, generation, allele_frequency, sample_size, file,
        genome, n, H, SD, Gen, param_combination
      ) %>%
      dplyr::filter(generation <= max_generation) %>%   # first 500 generations only
      dplyr::group_by(allele_id)

    if (sampling_scheme == "end") {
      out <- out %>%
        dplyr::filter(generation == min(generation) |
                      generation %% Gen == 0)
    } else {
      out <- out %>%
        dplyr::filter(generation == min(generation) |
                      generation %% (Gen / 2) == 0)
    }

    out %>% dplyr::ungroup()
  }

  combined_data <- dplyr::bind_rows(combined_data_list)

  mean_allele_data <- combined_data %>%
    dplyr::group_by(generation, n, genome, H, SD, Gen, param_combination) %>%
    dplyr::summarize(
      mean_allele_frequency = mean(allele_frequency),
      .groups = "drop"
    ) %>%
    dplyr::arrange(n, genome, H, SD, Gen, param_combination, generation)

  ts_data_list <- mean_allele_data %>%
    dplyr::group_by(n, genome, H, SD, Gen, param_combination) %>%
    dplyr::summarize(
      ts_data = list(stats::ts(mean_allele_frequency,
                               start = min(generation),
                               frequency = 1)),
      .groups = "drop"
    )

  spec_results_list <- lapply(ts_data_list$ts_data, function(ts_data) {
    spans_use <- if (length(ts_data) >= 8) spectrum_span else NULL
    stats::spectrum(ts_data, spans = spans_use, plot = FALSE)
  })

  plot_data_list <- vector("list", length(spec_results_list))
  for (i in seq_along(spec_results_list)) {
    spec_result = spec_results_list[[i]]
    params  = ts_data_list[i, ]

    # Rescale period from sample-steps to generations
    interval <- if (sampling_scheme == "end") params$Gen else params$Gen / 2
    period_samples <- 1 / spec_result$freq

    df_spec = data.frame(
      Period_samples = period_samples,
      Period = period_samples * interval,
      Spectrum = spec_result$spec,
      n = params$n,
      genome = params$genome,
      H = params$H,
      SD = params$SD,
      Gen = params$Gen,
      param_combination = params$param_combination
    )
    plot_data_list[[i]] = df_spec
  }

  plot_data = dplyr::bind_rows(plot_data_list)


  plot_data <- plot_data %>%
    dplyr::group_by(param_combination) %>%
    dplyr::mutate(
      threshold = dplyr::case_when(
        Gen == 10 ~ 60,
        Gen == 30 ~ 150,
        TRUE ~ max(Period)
      )
    ) %>%
    dplyr::ungroup() %>%
    dplyr::filter(
      Period < threshold &
        (
          (H == 0.1 & SD == 1 & Gen == 10) |
          (H == 0.8 & SD == 4 & Gen == 30)
        )
    ) %>%
    dplyr::mutate(
      H_SD_Gen = paste0("h\u00B2 = ", H, " \u0394 = ", SD, " Gen=", Gen)
    )

  scheme_title <- if (sampling_scheme == "end") {
    "A) Spectral Density: Sampling at the end of each season"
  } else {
    "B) Spectral Density: Sampling at the middle & end of each season"
  }

  spec_plot_comb1 = ggplot2::ggplot(
    plot_data,
    ggplot2::aes(x = Period, y = Spectrum, color = factor(genome), group = factor(genome))
  ) +
    ggplot2::geom_line(linewidth = 3) +
    ggplot2::facet_wrap(~ H_SD_Gen, scales = "free", ncol = 2) +
    ggplot2::scale_y_continuous(labels = scales::label_number()) +
    ggplot2::labs(
      title = scheme_title, x = "Period (Generations)", y = "Spectral Density"
    ) +
    ggplot2::theme_classic() +
    ggplot2::theme(text = ggplot2::element_text(family = "sans"),
        legend.position = "none",
        axis.text = ggplot2::element_text(size = 20, face = "bold"),
        axis.line = ggplot2::element_line(size = 3),
        strip.text = ggplot2::element_text(size = 17, face = "bold"),
        plot.title = ggplot2::element_text(hjust = 0.01, face = "bold", size = 40),
        axis.title.x = ggplot2::element_text(margin = ggplot2::margin(t = 20), size = 20, face = "bold"),
        axis.title.y = ggplot2::element_text(margin = ggplot2::margin(r = 25), size = 20, face = "bold"),
        panel.spacing = ggplot2::unit(4, "lines"))

  return(spec_plot_comb1)
}

###############################################################################
################## Run The Function for Spectral Analysis ####################
###############################################################################

dirpath    <- "../../Output.dir/LinFS.dir/"
my_pattern <- "^genome\\d+_n100_H0\\.(1SD1Gen10|8SD4Gen30)\\.csv$"

library(patchwork)

plot_end     <- run_fft_analysis(dirpath, my_pattern, sampling_scheme = "end")
plot_mid_end <- run_fft_analysis(dirpath, my_pattern, sampling_scheme = "mid_end")

combined_plot <- plot_end / plot_mid_end

jpeg_device <- if (requireNamespace("ragg", quietly = TRUE)) ragg::agg_jpeg else "jpeg"

ggsave("Seasonal_Instant_Poly_SpecAnalysis_Combined_500.jpg",
       plot = combined_plot,
       device = jpeg_device,
       dpi = 300, width = 25, height = 30, units = "in",
       path = "../OutputFigures.dir/SpectralDensity.dir")

combined_plot
```

#### Ten Samples Only

```{r, warning=FALSE, fig.width = 30, fig.height = 15, echo=FALSE, dpi = 1200}

library(dplyr)
library(ggplot2)
library(purrr)
library(tibble)
library(tidyr)
library(scales)
library(patchwork)


###############################################################################
#################### Defining files, number of sequency, and the spans#######
###############################################################################

dirpath <- "../../Output.dir/LinFS.dir/"
my_pattern <- "^genome\\d+_n100_H0\\.(1|8)SD(1|4)Gen(10|30)\\.csv$"

# Number of sampled time points after the first generation
nseq <- 10

# Spectral smoothing span
spectrum_span <- 2

###############################################################################
########################## Extracting parameters ##############################
###############################################################################

parse_simulation_files <- function(dirpath, pattern) {
  
  file_list <- list.files(
    path = dirpath,
    pattern = pattern,
    full.names = TRUE
  )
  

  files_df <- tibble(file_name = file_list) %>%
    mutate(
      base_name = basename(file_name),
      
      replicate = ifelse(
        grepl("genome\\d+", base_name),
        as.numeric(sub(".*genome(\\d+).*", "\\1", base_name)),
        NA_real_
      ),
      
      n = ifelse(
        grepl("_n\\d+", base_name),
        as.numeric(sub(".*_n(\\d+).*", "\\1", base_name)),
        NA_real_
      ),
      
      H = ifelse(
        grepl("_H[0-9]+\\.?[0-9]*", base_name),
        as.numeric(sub(".*_H([0-9]+\\.?[0-9]*).*", "\\1", base_name)),
        NA_real_
      ),
      
      SD = ifelse(
        grepl("SD[0-9]+(\\.[0-9]+)?", base_name),
        as.numeric(sub(".*SD([0-9]+(?:\\.[0-9]+)?).*", "\\1", base_name)),
        NA_real_
      ),
      
      Gen = ifelse(
        grepl("Gen\\d+", base_name),
        as.numeric(sub(".*Gen(\\d+).*", "\\1", base_name)),
        NA_real_
      )
    ) %>%
    mutate(
      parameter_label = case_when(
        H == 0.1 & SD == 1 & Gen == 10 ~ "h² = 0.1 Δ = 1 Gen=10",
        H == 0.8 & SD == 4 & Gen == 30 ~ "h² = 0.8 Δ = 4 Gen=30",
        TRUE ~ paste0("h² = ", H, " Δ = ", SD, " Gen=", Gen)
      )
    )
  
  files_df
}

###############################################################################
########################## Function for spectral analysis######################
###############################################################################

run_fft_one_file <- function(
    file_name,
    replicate,
    H,
    SD,
    Gen,
    parameter_label,
    nseq = 10,
    spectrum_span = 2
) {
  
  full_df <- utils::read.csv(file_name, stringsAsFactors = FALSE)
  
  interval <- Gen
  
  #first_generation <- min(full_df$Generation, na.rm = TRUE)
  
  #########################################################################
  #### Sampling 1: first generation + first nseq end samples ########
  #########################################################################
  
  end_generations <- c(
    #first_generation,
    seq(
      from = interval,
      by = interval,
      length.out = nseq
    )
  ) %>%
    unique() %>%
    sort()
  
  gens_end <- full_df %>%
    filter(Generation %in% end_generations) %>%
    mutate(
      allele_id = as.factor(Position),
      sampling_scheme = "End",
      sampling_interval = interval
    )
  
  #########################################################################
  #### Sampling 2: first generation + first nseq mid/end samples ####
  #########################################################################
  
  mid_end_generations <- c(
   # first_generation,
    seq(
      from = interval / 2,
      by = interval / 2,
      length.out = nseq
    )
  ) %>%
    unique() %>%
    sort()
  
  gens_mid_end <- full_df %>%
    filter(Generation %in% mid_end_generations) %>%
    mutate(
      allele_id = as.factor(Position),
      sampling_scheme = "Mid & End",
      sampling_interval = interval / 2
    )
  
  #########################################################################
  #### Combine sampled data ###############################################
  #########################################################################
  
  sampled_data <- bind_rows(
    gens_end,
    gens_mid_end
  )
  
  
  #########################################################################
  #### Mean allele frequency per sampled generation #######################
  #########################################################################
  
  mean_allele_data <- sampled_data %>%
    group_by(sampling_scheme, sampling_interval, Generation) %>%
    summarize(
      mean_allele_frequency = mean(Frequency, na.rm = TRUE),
      .groups = "drop"
    ) %>%
    arrange(sampling_scheme, Generation)
  
  #########################################################################
  #### Computing the spectral density ######################################
  #########################################################################
  
  spectrum_data <- mean_allele_data %>%
    group_by(sampling_scheme, sampling_interval) %>%
    summarize(
      n_timepoints = n(),
      sampled_generations = list(Generation),
      ts_data = list(stats::ts(mean_allele_frequency, frequency = 1)),
      .groups = "drop"
    ) %>%
    filter(n_timepoints >= 4) %>%
    mutate(
      spec_result = map(
        ts_data,
        ~ stats::spectrum(
          .x,
          spans = spectrum_span,
          plot = FALSE
        )
      )
    ) %>%
    mutate(
      spectrum_tbl = map2(
        spec_result,
        sampling_interval,
        ~ tibble(
          Period_sample_units = 1 / .x$freq,
          
          # Convert period from sampled observations to real generations
          Period = (1 / .x$freq) * .y,
          
          Spectrum = as.numeric(.x$spec)
        )
      )
    ) %>%
    select(
      sampling_scheme,
      sampling_interval,
      n_timepoints,
      sampled_generations,
      spectrum_tbl
    ) %>%
    tidyr::unnest(spectrum_tbl) %>%
    mutate(
      replicate = replicate,
      H = H,
      SD = SD,
      Gen = Gen,
      parameter_label = parameter_label,
      file = basename(file_name)
    )
  
  spectrum_data
}

###############################################################################
########################## Low/High Multiple-File FFT ####################
###############################################################################

run_fft_low_high_multiple_files <- function(
    dirpath,
    pattern,
    nseq = 10,
    spectrum_span = 2,
    show_legend = FALSE
) {
  
  files_df <- parse_simulation_files(
    dirpath = dirpath,
    pattern = pattern
  )
  
  #########################################################################
  #### Keep only high and low combinations #############################
  #########################################################################
  
  files_df <- files_df %>%
    filter(
      (H == 0.1 & SD == 1 & Gen == 10) |
        (H == 0.8 & SD == 4 & Gen == 30)
    ) %>%
    mutate(
      parameter_label = case_when(
        H == 0.1 & SD == 1 & Gen == 10 ~ "h² = 0.1 Δ = 1 Gen=10",
        H == 0.8 & SD == 4 & Gen == 30 ~ "h² = 0.8 Δ = 4 Gen=30"
      ),
      parameter_label = factor(
        parameter_label,
        levels = c(
          "h² = 0.1 Δ = 1 Gen=10",
          "h² = 0.8 Δ = 4 Gen=30"
        )
      )
    )
  
  
  #########################################################################
  #### Apply FFT to each replicate/file ###################################
  #########################################################################
  
  plot_data <- pmap_dfr(
    list(
      file_name = files_df$file_name,
      replicate = files_df$replicate,
      H = files_df$H,
      SD = files_df$SD,
      Gen = files_df$Gen,
      parameter_label = files_df$parameter_label
    ),
    function(file_name, replicate, H, SD, Gen, parameter_label) {
      run_fft_one_file(
        file_name = file_name,
        replicate = replicate,
        H = H,
        SD = SD,
        Gen = Gen,
        parameter_label = parameter_label,
        nseq = nseq,
        spectrum_span = spectrum_span
      )
    }
  )
  
  
  #########################################################################
  #### Clean labels and enforce order #####################################
  #########################################################################
  
  plot_data <- plot_data %>%
    mutate(
      replicate = factor(replicate),
      sampling_scheme = factor(
        sampling_scheme,
        levels = c("End", "Mid & End")
      ),
      parameter_label = factor(
        parameter_label,
        levels = c(
          "h² = 0.1 Δ = 1 Gen=10",
          "h² = 0.8 Δ = 4 Gen=30"
        )
      )
    )
  
  #########################################################################
  #### The sa,pling includes the very first generation #############################
  #########################################################################
  # With the first generation included, the time series has one extra point,
  # but the regular sampling interval used for period conversion remains:
  #
  # End:       Gen
  # Mid & End: Gen / 2
  
  plot_data <- plot_data %>%
    mutate(
      period_min = case_when(
        sampling_scheme == "End" ~ 1, #2 * Gen,
        sampling_scheme == "Mid & End" ~ 1, #~ Gen,
        TRUE ~ NA_real_
      ),
      period_max = case_when(
        sampling_scheme == "End" ~ 5 * Gen,
        sampling_scheme == "Mid & End" ~ 5 * Gen,
        TRUE ~ NA_real_
      )
    ) %>%
    filter(
      Period >= period_min,
      Period <= period_max
    )

  #########################################################################
  #### Split into End and Mid & End #######################################
  #########################################################################
  
  plot_data_end <- plot_data %>%
    filter(sampling_scheme == "End")
  
  plot_data_mid_end <- plot_data %>%
    filter(sampling_scheme == "Mid & End")
  
  #########################################################################
  #### Common theme #######################################################
  #########################################################################
  
  theme_spectral <- theme_classic() +
    theme(
      text = element_text(family = "sans"),
      
      legend.position = ifelse(show_legend, "right", "none"),
      
      axis.text = element_text(
        size = 18,
        face = "bold"
      ),
      
      axis.title.x = element_text(
        margin = margin(t = 16),
        size = 20,
        face = "bold"
      ),
      
      axis.title.y = element_text(
        margin = margin(r = 18),
        size = 20,
        face = "bold"
      ),
      
      axis.line = element_line(
        linewidth = 2.2
      ),
      
      strip.text = element_text(
        size = 15,
        face = "bold"
      ),
      
      plot.title = element_text(
        hjust = 0.01,
        face = "bold",
        size = 34
      ),
      
      legend.title = element_text(
        size = 14,
        face = "bold"
      ),
      
      legend.text = element_text(
        size = 12
      ),
      
      panel.spacing = grid::unit(2.2, "lines")
    )
  
  #########################################################################
  #### A) End plot ########################################################
  #########################################################################
  
  p_end <- ggplot(
    plot_data_end,
    aes(
      x = Period,
      y = Spectrum,
      color = replicate,
      group = replicate
    )
  ) +
    geom_line(linewidth = 1.6, alpha = 0.85) +
   # geom_point()+
    facet_wrap(
      ~ parameter_label,
      scales = "free",
      nrow = 1
    ) +
    scale_x_continuous(
      breaks = scales::pretty_breaks(n = 5)
    ) +
    scale_y_continuous(
      labels = scales::label_number()
    ) +
    labs(
      title = "A) Spectral Density: Sampling at the end of each season",
      x = "Period (Generations)",
      y = "Spectral Density",
      color = "Replicate"
    ) +
    theme_spectral
  
  #########################################################################
  #### B) Mid & End plot ##################################################
  #########################################################################
  
  p_mid_end <- ggplot(
    plot_data_mid_end,
    aes(
      x = Period,
      y = Spectrum,
      color = replicate,
      group = replicate
    )
  ) +
    geom_line(linewidth = 1.6, alpha = 0.85) +
     #geom_point()+ 
    facet_wrap(
      ~ parameter_label,
      scales = "free",
      nrow = 1
    ) +
    scale_x_continuous(
      breaks = scales::pretty_breaks(n = 5)
    ) +
    scale_y_continuous(
      labels = scales::label_number()
    ) +
    labs(
      title = "B) Spectral Density: Sampling at the middle & end of each season",
      x = "Period (Generations)",
      y = "Spectral Density",
      color = "Replicate"
    ) +
    theme_spectral
  
  #########################################################################
  #### Combine with patchwork #############################################
  #########################################################################
  
  final_plot <- p_end / p_mid_end
  
  #return(final_plot)
  
  return(list(plot_data_end =plot_data_end, plot_data_mid_end = plot_data_mid_end, final_plot = final_plot))
}

###############################################################################
########################## Run: Exact Low and High Combos ######################
###############################################################################

final_plot_low_high <- run_fft_low_high_multiple_files(
  dirpath = dirpath,
  pattern = my_pattern,
  nseq = nseq,
  spectrum_span = spectrum_span,
  show_legend = FALSE
)

final_plot_low_high$final_plot

# ###############################################################################
# ########################## Save plot ###########################################
# ###############################################################################
# 
# out_dir <- "../OutputFigures.dir"
# 
# if (!dir.exists(out_dir)) {
#   dir.create(out_dir, recursive = TRUE)
# }
# 
# ggsave(
#   filename = file.path(
#     out_dir,
#     "SpectralDensity_End_vs_MidEnd_FirstGeneration_First10Samples_ExactLowHigh_ByReplicate.pdf"
#   ),
#   plot = final_plot_low_high,
#   width = 24,
#   height = 12,
#   units = "in",
#   device = "pdf",
#   limitsize = FALSE
# )
# 
# ggsave(
#   filename = file.path(
#     out_dir,
#     "SpectralDensity_End_vs_MidEnd_FirstGeneration_First10Samples_ExactLowHigh_ByReplicate.jpg"
#   ),
#   plot = final_plot_low_high,
#   width = 24,
#   height = 12,
#   units = "in",
#   dpi = 300,
#   device = "jpeg",
#   limitsize = FALSE
# )
endt <- final_plot_low_high$plot_data_end
endt_f<- endt %>% filter(Gen == 10, SD == 1, H == 0.1, replicate==10)
head(endt_f)
nrow(endt_f)
```

#### Plots for constant Selection

```{r, warning=FALSE, fig.width = 20, fig.height = 10, echo=FALSE, dpi = 1200}
library(dplyr)
library(ggplot2)
library(purrr)
library(tibble)
library(tidyr)
library(scales)
library(patchwork)

###############################################################################
########################## Main reusable function ##############################
###############################################################################

run_fft_sampling_analysis <- function(
    dirpath,
    dataset_name = basename(normalizePath(dirpath)),
    pattern = "^genome\\d+_n100_H0\\.(1|8)(SD(1|4))?(Gen(10|30))?\\.csv$",
    nseq = 10,
    spectrum_span = 2,
    show_legend = FALSE,
    save_plot = FALSE,
    out_dir = "../OutputFigures.dir",
    output_prefix = NULL
) {
  
  #########################################################################
  #### Parse simulation files #############################################
  #########################################################################
  
  parse_simulation_files <- function(dirpath, pattern, dataset_name) {
    
    file_list <- list.files(
      path = dirpath,
      pattern = pattern,
      full.names = TRUE
    )
    
    if (length(file_list) == 0) {
      stop("No files found in: ", dirpath)
    }
    
    files_df <- tibble(
      file_name = file_list,
      dataset = dataset_name
    ) %>%
      mutate(
        base_name = basename(file_name),
        
        replicate = ifelse(
          grepl("genome\\d+", base_name),
          as.numeric(sub(".*genome(\\d+).*", "\\1", base_name)),
          NA_real_
        ),
        
        n = ifelse(
          grepl("_n\\d+", base_name),
          as.numeric(sub(".*_n(\\d+).*", "\\1", base_name)),
          NA_real_
        ),
        
        H = ifelse(
          grepl("_H[0-9]+\\.?[0-9]*", base_name),
          as.numeric(sub(".*_H([0-9]+\\.?[0-9]*).*", "\\1", base_name)),
          NA_real_
        ),
        
        SD = ifelse(
          grepl("SD[0-9]+(\\.[0-9]+)?", base_name),
          as.numeric(sub(".*SD([0-9]+(?:\\.[0-9]+)?).*", "\\1", base_name)),
          NA_real_
        ),
        
        Gen = ifelse(
          grepl("Gen\\d+", base_name),
          as.numeric(sub(".*Gen(\\d+).*", "\\1", base_name)),
          NA_real_
        )
      ) %>%
      mutate(
        selection_type = case_when(
          !is.na(Gen) ~ "Seasonal",
          is.na(Gen) & !is.na(SD) ~ "Constant",
          is.na(Gen) & is.na(SD) ~ "Null",
          TRUE ~ NA_character_
        ),
        
        ###################################################################
        #### Keep matched parameter combinations ##########################
        ###################################################################
        # Matched low combination:
        #   H = 0.1, SD = 1, Gen = 10
        #
        # Matched high combination:
        #   H = 0.8, SD = 4, Gen = 30
        #
        # If Gen is absent:
        #   H = 0.1, SD = 1 gets assumed Gen = 10
        #   H = 0.8, SD = 4 gets assumed Gen = 30
        #
        # If SD and Gen are absent:
        #   H = 0.1 gets assumed Gen = 10
        #   H = 0.8 gets assumed Gen = 30
        
        combo_type = case_when(
          H == 0.1 & SD == 1 & Gen == 10 ~ "low",
          H == 0.8 & SD == 4 & Gen == 30 ~ "high",
          
          H == 0.1 & SD == 1 & is.na(Gen) ~ "low",
          H == 0.8 & SD == 4 & is.na(Gen) ~ "high",
          
          H == 0.1 & is.na(SD) & is.na(Gen) ~ "low",
          H == 0.8 & is.na(SD) & is.na(Gen) ~ "high",
          
          TRUE ~ NA_character_
        ),
        
        Gen_for_sampling = case_when(
          combo_type == "low" ~ 10,
          combo_type == "high" ~ 30,
          TRUE ~ NA_real_
        ),
        
        parameter_label = case_when(
          selection_type == "Seasonal" & combo_type == "low" ~
            "Seasonal: h² = 0.1, Δ = 1, Gen = 10",
          
          selection_type == "Seasonal" & combo_type == "high" ~
            "Seasonal: h² = 0.8, Δ = 4, Gen = 30",
          
          selection_type == "Constant" & combo_type == "low" ~
            "Constant: h² = 0.1, Δ = 1, assumed Gen = 10",
          
          selection_type == "Constant" & combo_type == "high" ~
            "Constant: h² = 0.8, Δ = 4, assumed Gen = 30",
          
          selection_type == "Null" & combo_type == "low" ~
            "Null: h² = 0.1, assumed Gen = 10",
          
          selection_type == "Null" & combo_type == "high" ~
            "Null: h² = 0.8, assumed Gen = 30",
          
          TRUE ~ NA_character_
        )
      )
    
    files_df
  }
  
  #########################################################################
  #### One-file spectral analysis #########################################
  #########################################################################
  
  run_fft_one_file <- function(
      file_name,
      dataset,
      replicate,
      H,
      SD,
      Gen,
      Gen_for_sampling,
      selection_type,
      combo_type,
      parameter_label,
      nseq = 10,
      spectrum_span = 2
  ) {
    
    full_df <- utils::read.csv(file_name, stringsAsFactors = FALSE)
    
    full_df <- full_df %>%
      mutate(
        Generation = as.numeric(Generation)
      ) %>%
      arrange(Generation)
    
    interval <- Gen_for_sampling
    
    if (is.na(interval)) {
      warning("No valid Gen_for_sampling for file: ", basename(file_name))
      return(NULL)
    }
    
    #######################################################################
    #### End sampling #####################################################
    #######################################################################
    
    end_generations <- seq(
      from = interval,
      by = interval,
      length.out = nseq
    )
    
    gens_end <- full_df %>%
      filter(Generation %in% end_generations) %>%
      mutate(
        allele_id = as.factor(Position),
        sampling_scheme = "End",
        sampling_interval = interval
      )
    
    #######################################################################
    #### Mid & End sampling ###############################################
    #######################################################################
    
    mid_end_generations <- seq(
      from = interval / 2,
      by = interval / 2,
      length.out = nseq
    )
    
    gens_mid_end <- full_df %>%
      filter(Generation %in% mid_end_generations) %>%
      mutate(
        allele_id = as.factor(Position),
        sampling_scheme = "Mid & End",
        sampling_interval = interval / 2
      )
    
    sampled_data <- bind_rows(
      gens_end,
      gens_mid_end
    )
    
    if (nrow(sampled_data) == 0) {
      warning("No sampled generations found for file: ", basename(file_name))
      return(NULL)
    }
    
    #######################################################################
    #### Mean allele frequency per sampled generation #####################
    #######################################################################
    
    mean_allele_data <- sampled_data %>%
      group_by(sampling_scheme, sampling_interval, Generation) %>%
      summarize(
        mean_allele_frequency = mean(Frequency, na.rm = TRUE),
        .groups = "drop"
      ) %>%
      arrange(sampling_scheme, Generation)
    
    #######################################################################
    #### Spectral density #################################################
    #######################################################################
    
    spectrum_data <- mean_allele_data %>%
      group_by(sampling_scheme, sampling_interval) %>%
      summarize(
        n_timepoints = n(),
        sampled_generations = list(Generation),
        ts_data = list(stats::ts(mean_allele_frequency, frequency = 1)),
        .groups = "drop"
      ) %>%
      filter(n_timepoints >= 4) %>%
      mutate(
        spec_result = map(
          ts_data,
          ~ stats::spectrum(
            .x,
            spans = spectrum_span,
            plot = FALSE
          )
        )
      ) %>%
      mutate(
        spectrum_tbl = map2(
          spec_result,
          sampling_interval,
          ~ tibble(
            Period_sample_units = 1 / .x$freq,
            
            ###############################################################
            #### Convert period back to real generations #################
            ###############################################################
            
            Period = (1 / .x$freq) * .y,
            
            Spectrum = as.numeric(.x$spec)
          )
        )
      ) %>%
      select(
        sampling_scheme,
        sampling_interval,
        n_timepoints,
        sampled_generations,
        spectrum_tbl
      ) %>%
      tidyr::unnest(spectrum_tbl) %>%
      mutate(
        dataset = dataset,
        replicate = replicate,
        H = H,
        SD = SD,
        Gen = Gen,
        Gen_for_sampling = Gen_for_sampling,
        selection_type = selection_type,
        combo_type = combo_type,
        parameter_label = parameter_label,
        file = basename(file_name)
      )
    
    spectrum_data
  }
  
  #########################################################################
  #### Parse and filter files #############################################
  #########################################################################
  
  files_df <- parse_simulation_files(
    dirpath = dirpath,
    pattern = pattern,
    dataset_name = dataset_name
  )
  
  files_df <- files_df %>%
    filter(
      !is.na(combo_type),
      !is.na(Gen_for_sampling),
      !is.na(parameter_label)
    )
  
  if (nrow(files_df) == 0) {
    stop("No files remain after matched parameter filtering in: ", dirpath)
  }
  
  cat(dataset_name, ": number of files used = ", nrow(files_df), "\n")
  
  #########################################################################
  #### Apply FFT ##########################################################
  #########################################################################
  
  plot_data <- pmap_dfr(
    list(
      file_name = files_df$file_name,
      dataset = files_df$dataset,
      replicate = files_df$replicate,
      H = files_df$H,
      SD = files_df$SD,
      Gen = files_df$Gen,
      Gen_for_sampling = files_df$Gen_for_sampling,
      selection_type = files_df$selection_type,
      combo_type = files_df$combo_type,
      parameter_label = files_df$parameter_label
    ),
    function(
      file_name,
      dataset,
      replicate,
      H,
      SD,
      Gen,
      Gen_for_sampling,
      selection_type,
      combo_type,
      parameter_label
    ) {
      run_fft_one_file(
        file_name = file_name,
        dataset = dataset,
        replicate = replicate,
        H = H,
        SD = SD,
        Gen = Gen,
        Gen_for_sampling = Gen_for_sampling,
        selection_type = selection_type,
        combo_type = combo_type,
        parameter_label = parameter_label,
        nseq = nseq,
        spectrum_span = spectrum_span
      )
    }
  )
  
  if (nrow(plot_data) == 0) {
    stop("No spectrum data produced for: ", dirpath)
  }
  
  #########################################################################
  #### Clean labels #######################################################
  #########################################################################
  
  plot_data <- plot_data %>%
    mutate(
      replicate = factor(replicate),
      
      sampling_scheme = factor(
        sampling_scheme,
        levels = c("End", "Mid & End")
      ),
      
      selection_type = factor(
        selection_type,
        levels = c("Seasonal", "Constant", "Null")
      ),
      
      combo_type = factor(
        combo_type,
        levels = c("low", "high")
      ),
      
      parameter_label = factor(
        parameter_label,
        levels = c(
          "Seasonal: h² = 0.1, Δ = 1, Gen = 10",
          "Seasonal: h² = 0.8, Δ = 4, Gen = 30",
          "Constant: h² = 0.1, Δ = 1, assumed Gen = 10",
          "Constant: h² = 0.8, Δ = 4, assumed Gen = 30",
          "Null: h² = 0.1, assumed Gen = 10",
          "Null: h² = 0.8, assumed Gen = 30"
        )
      )
    )
  
  #########################################################################
  #### Period min/max filter ##############################################
  #########################################################################
  
  plot_data <- plot_data %>%
    mutate(
      period_min = 1,
      period_max = 5 * Gen_for_sampling
    ) %>%
    filter(
      Period >= period_min,
      Period <= period_max
    )
  
  if (nrow(plot_data) == 0) {
    stop("No data remain after period filtering for: ", dirpath)
  }
  
  #########################################################################
  #### Split data #########################################################
  #########################################################################
  
  plot_data_end <- plot_data %>%
    filter(sampling_scheme == "End")
  
  plot_data_mid_end <- plot_data %>%
    filter(sampling_scheme == "Mid & End")
  
  #########################################################################
  #### Theme ##############################################################
  #########################################################################
  
  theme_spectral <- theme_classic() +
    theme(
      text = element_text(family = "sans"),
      legend.position = ifelse(show_legend, "right", "none"),
      
      axis.text = element_text(
        size = 18,
        face = "bold"
      ),
      
      axis.title.x = element_text(
        margin = margin(t = 16),
        size = 20,
        face = "bold"
      ),
      
      axis.title.y = element_text(
        margin = margin(r = 18),
        size = 20,
        face = "bold"
      ),
      
      axis.line = element_line(
        linewidth = 2.2
      ),
      
      strip.text = element_text(
        size = 13,
        face = "bold"
      ),
      
      plot.title = element_text(
        hjust = 0.01,
        face = "bold",
        size = 30
      ),
      
      legend.title = element_text(
        size = 14,
        face = "bold"
      ),
      
      legend.text = element_text(
        size = 12
      ),
      
      panel.spacing = grid::unit(2.0, "lines")
    )
  
  #########################################################################
  #### End plot ###########################################################
  #########################################################################
  
  p_end <- ggplot(
    plot_data_end,
    aes(
      x = Period,
      y = Spectrum,
      color = replicate,
      group = replicate
    )
  ) +
    geom_line(linewidth = 1.4, alpha = 0.85) +
    facet_wrap(
      ~ parameter_label,
      scales = "free",
      nrow = 1
    ) +
    scale_x_continuous(
      breaks = scales::pretty_breaks(n = 5)
    ) +
    scale_y_continuous(
      labels = scales::label_number()
    ) +
    labs(
      #title = paste0(dataset_name, ": Spectral Density — End"),
      title = paste0("A) End of Season Sampling "),
      x = "Period (Generations)",
      y = "Spectral Density",
      color = "Replicate"
    ) +
    theme_spectral
  
  #########################################################################
  #### Mid & End plot #####################################################
  #########################################################################
  
  p_mid_end <- ggplot(
    plot_data_mid_end,
    aes(
      x = Period,
      y = Spectrum,
      color = replicate,
      group = replicate
    )
  ) +
    geom_line(linewidth = 1.4, alpha = 0.85) +
    facet_wrap(
      ~ parameter_label,
      scales = "free",
      nrow = 1
    ) +
    scale_x_continuous(
      breaks = scales::pretty_breaks(n = 5)
    ) +
    scale_y_continuous(
      labels = scales::label_number()
    ) +
    labs(
     # title = paste0(dataset_name, ": Spectral Density — Mid & End"),
      title = paste0("B) Mid & End of Season Sampling"),
      x = "Period (Generations)",
      y = "Spectral Density",
      color = "Replicate"
    ) +
    theme_spectral
  
  final_plot <- p_end / p_mid_end
  
  #########################################################################
  #### Optional save ######################################################
  #########################################################################
  
  if (save_plot) {
    
    if (is.null(output_prefix)) {
      output_prefix <- paste0(dataset_name, "_SpectralDensity")
    }
    
    if (!dir.exists(out_dir)) {
      dir.create(out_dir, recursive = TRUE)
    }
    
    ggsave(
      filename = file.path(out_dir, paste0(output_prefix, ".pdf")),
      plot = final_plot,
      width = 24,
      height = 12,
      units = "in",
      device = "pdf",
      limitsize = FALSE
    )
    
    ggsave(
      filename = file.path(out_dir, paste0(output_prefix, ".jpg")),
      plot = final_plot,
      width = 24,
      height = 12,
      units = "in",
      dpi = 300,
      device = "jpeg",
      limitsize = FALSE
    )
  }
  
  #########################################################################
  #### Return #############################################################
  #########################################################################
  
  return(
    list(
      dataset = dataset_name,
      files_used = files_df,
      plot_data = plot_data,
      plot_data_end = plot_data_end,
      plot_data_mid_end = plot_data_mid_end,
      final_plot = final_plot
    )
  )
}

###############################################################################
########################## Run one directory ###################################
###############################################################################

cs_results <- run_fft_sampling_analysis(
  dirpath = "../../Output.dir/CS.dir/",
  dataset_name = "CS",
  nseq = 10,
  spectrum_span = 2,
  show_legend = FALSE,
  save_plot = FALSE
)

cs_results$final_plot

ns_results <- run_fft_sampling_analysis(
  dirpath = "../../Output.dir/NS.dir/",
  dataset_name = "NS",
  nseq = 10,
  spectrum_span = 2,
  show_legend = FALSE,
  save_plot = FALSE
)

ns_results$final_plot

linfs_results <- run_fft_sampling_analysis(
  dirpath = "../../Output.dir/LinFS.dir/",
  dataset_name = "LinFS",
  nseq = 10,
  spectrum_span = 2,
  show_legend = FALSE,
  save_plot = FALSE
)

linfs_results$final_plot

```

##### Save all the plots

```{r}
###############################################################################
############ Save the plots into their own directory  #########################
###############################################################################

out_dir <- "../OutputFigures.dir/SpectralDensity.dir"

if (!dir.exists(out_dir)) {
  dir.create(out_dir, recursive = TRUE)
}

###############################################################################
########################## Save CS plot ########################################
###############################################################################

ggsave(
  filename = file.path(out_dir, "CS_SpectralDensity_End_vs_MidEnd.pdf"),
  plot = cs_results$final_plot,
  width = 24,
  height = 12,
  units = "in",
  device = "pdf",
  limitsize = FALSE
)

ggsave(
  filename = file.path(out_dir, "CS_SpectralDensity_End_vs_MidEnd.jpg"),
  plot = cs_results$final_plot,
  width = 24,
  height = 12,
  units = "in",
  dpi = 300,
  device = "jpeg",
  limitsize = FALSE
)

###############################################################################
########################## Save NS plot ########################################
###############################################################################

ggsave(
  filename = file.path(out_dir, "NS_SpectralDensity_End_vs_MidEnd.pdf"),
  plot = ns_results$final_plot,
  width = 24,
  height = 12,
  units = "in",
  device = "pdf",
  limitsize = FALSE
)

ggsave(
  filename = file.path(out_dir, "NS_SpectralDensity_End_vs_MidEnd.jpg"),
  plot = ns_results$final_plot,
  width = 24,
  height = 12,
  units = "in",
  dpi = 300,
  device = "jpeg",
  limitsize = FALSE
)

###############################################################################
########################## Save LinFS plot #####################################
###############################################################################

ggsave(
  filename = file.path(out_dir, "LinFS_SpectralDensity_End_vs_MidEnd.pdf"),
  plot = linfs_results$final_plot,
  width = 24,
  height = 12,
  units = "in",
  device = "pdf",
  limitsize = FALSE
)

ggsave(
  filename = file.path(out_dir, "LinFS_SpectralDensity_End_vs_MidEnd.jpg"),
  plot = linfs_results$final_plot,
  width = 24,
  height = 12,
  units = "in",
  dpi = 300,
  device = "jpeg",
  limitsize = FALSE
)
```

#### Seasonal and Null Selection Plots

```{r, fig.width = 20, fig.height=10}
###############################################################################
############ Combined Seasonal vs Null plot: High only ######################
###############################################################################

combined_high_seasonal_Null <- bind_rows(
  linfs_results$plot_data,
  ns_results$plot_data
) %>%
  filter(
    combo_type == "high",
    selection_type %in% c("Seasonal", "Null")
  ) %>%
  mutate(
    selection_type = factor(
      selection_type,
      levels = c("Seasonal", "Null")
    ),
    sampling_scheme = factor(
      sampling_scheme,
      levels = c("End", "Mid & End")
    ),
    comparison_label = case_when(
      selection_type == "Seasonal" ~ "Seasonal: h² = 0.8, Δ = 4, Gen = 30",
      selection_type == "Null"  ~ "Null: h² = 0.8, assumed Gen = 30"
    ),
    comparison_label = factor(
      comparison_label,
      levels = c(
        "Seasonal: h² = 0.8, Δ = 4, Gen = 30",
        "Null: h² = 0.8, assumed Gen = 30"
      )
    )
  )

###############################################################################
########################## Theme ###############################################
###############################################################################

theme_spectral_compare <- theme_classic() +
  theme(
    text = element_text(family = "sans"),
    legend.position = "none",
    
    axis.text = element_text(
      size = 18,
      face = "bold"
    ),
    
    axis.title.x = element_text(
      margin = margin(t = 16),
      size = 20,
      face = "bold"
    ),
    
    axis.title.y = element_text(
      margin = margin(r = 18),
      size = 20,
      face = "bold"
    ),
    
    axis.line = element_line(
      linewidth = 2.2
    ),
    
    strip.text = element_text(
      size = 15,
      face = "bold"
    ),
    
    plot.title = element_text(
      hjust = 0.01,
      face = "bold",
      size = 32
    ),
    
    panel.spacing = grid::unit(2.0, "lines")
  )

###############################################################################
########################## Combined plot #######################################
###############################################################################

p_high_seasonal_Null <- ggplot(
  combined_high_seasonal_Null,
  aes(
    x = Period,
    y = Spectrum,
    color = replicate,
    group = replicate
  )
) +
  geom_line(linewidth = 1.4, alpha = 0.85) +
  facet_wrap(
     ~ paste0(sampling_scheme, " of season | ",comparison_label),
    scales = "free"
  ) +
  scale_x_continuous(
    breaks = scales::pretty_breaks(n = 5)
  ) +
  scale_y_continuous(
    labels = scales::label_number()
  ) +
  labs(
    title = "Spectral Density: Seasonal vs Null, High Parameter Combination",
    x = "Period (Generations)",
    y = "Spectral Density",
    color = "Replicate"
  ) +
  theme_spectral_compare

p_high_seasonal_Null

###############################################################################
########################## Save combined comparison ############################
###############################################################################

out_dir <- "../OutputFigures.dir/SpectralDensity.dir"

if (!dir.exists(out_dir)) {
  dir.create(out_dir, recursive = TRUE)
}

ggsave(
  filename = file.path(
    out_dir,
    "HighParam_Seasonal_vs_Null_SpectralDensity_End_vs_MidEnd.pdf"
  ),
  plot = p_high_seasonal_Null,
  width = 22,
  height = 12,
  units = "in",
  device = "pdf",
  limitsize = FALSE
)

ggsave(
  filename = file.path(
    out_dir,
    "HighParam_Seasonal_vs_Null_SpectralDensity_End_vs_MidEnd.jpg"
  ),
  plot = p_high_seasonal_Null,
  width = 22,
  height = 12,
  units = "in",
  dpi = 300,
  device = "jpeg",
  limitsize = FALSE
)
```

### 6.2. Amplitude Calculation for Selection selection models

```{r, fig.width=30, fig.height=15}
library(dplyr)
library(ggplot2)
library(stringr)
library(purrr)
library(tidyr)
library(future)
library(furrr)
library(RColorBrewer)

###############################################################################
########################## Settings ############################################
###############################################################################

folder_path <- "~/Mylab/evogen-sims/FluctSelectionModels.dir/Output.dir/LinFS.dir"
plot_dir <- "../OutputFigures.dir/Amplitudes_plt.dir"

dir.create(plot_dir, recursive = TRUE, showWarnings = FALSE)

target_n <- c(1, 10, 100, 300)
target_H <- c(0.1, 0.8)
target_SD <- c(1,2,3, 4)
target_Gen <- c(10, 20, 30)

target_replicate_for_dynamics <- 10
last_n_generations <- 1000
n_bins_to_show <- 30

n_workers <- 32
plan(multisession, workers = n_workers)

###############################################################################
########################## Theme ###############################################
###############################################################################

theme_amp <- theme_bw() +
  theme(
    text = element_text(family = "sans"),
    legend.position = "right",
    axis.text.x = element_text(
      face = "bold",
      size = 30,
      angle = 50,
      margin = margin(t = 20),
      hjust = 1
    ),
    axis.text.y = element_text(
      face = "bold",
      size = 30,
      angle = 15,
      margin = margin(r = 10)
    ),
    axis.line = element_line(linewidth = 3),
    plot.title = element_text(
      hjust = 0.01,
      face = "bold",
      size = 50,
      margin = margin(b = 1, unit = "lines")
    ),
    plot.margin = unit(c(5, 1, 1, 1), "lines"),
    axis.title.x = element_text(
      size = 30,
      face = "bold",
      margin = margin(t = 30)
    ),
    axis.title.y = element_text(
      size = 30,
      face = "bold",
      margin = margin(r = 35)
    ),
    strip.text = element_text(size = 30, face = "bold"),
    legend.title = element_text(size = 24, face = "bold"),
    legend.text = element_text(size = 20),
    panel.spacing = unit(5, "lines"),
    panel.grid = element_blank()
  )

###############################################################################
########################## File list ###########################################
###############################################################################

files <- list.files(
  path = folder_path,
  pattern = "^genome[0-9]+_n[0-9]+_H[0-9.]+SD[0-9.]+Gen[0-9]+\\.csv$",
  full.names = TRUE
)

if (length(files) == 0) {
  stop("No files found. Check folder_path and file pattern.")
}

###############################################################################
########################## Extract parameters ##################################
###############################################################################

extract_params_FewerGen <- function(file_path) {
  
  file_name <- basename(file_path)
  
  tibble(
    file = file_path,
    file_name = file_name,
    replicate = as.numeric(str_match(file_name, "genome([0-9]+)_")[, 2]),
    n = as.numeric(str_match(file_name, "_n([0-9]+)_")[, 2]),
    H = as.numeric(str_match(file_name, "H([0-9.]+)SD")[, 2]),
    SD = as.numeric(str_match(file_name, "SD([0-9.]+)Gen")[, 2]),
    Gen = as.numeric(str_match(file_name, "Gen([0-9]+)\\.csv")[, 2])
  )
}

param_table_FewerGen <- map_dfr(files, extract_params_FewerGen) %>% 
  filter(
    n %in% target_n,
    H %in% target_H,
    SD %in% target_SD,
    Gen %in% target_Gen
  ) %>% 
  arrange(n, H, SD, Gen, replicate) %>% 
  mutate(
    parameter_combo = paste0(
      "n = ", n,
      ", h\u00B2 = ", H,
      ", Δ = ", SD,
      ", Gen = ", Gen
    )
  )

if (nrow(param_table_FewerGen) == 0) {
  stop("No files remain after filtering. Check target_n, target_H, target_SD, and target_Gen.")
}

###############################################################################
########################## Calculate amplitudes ################################
###############################################################################

calculate_amplitude_FewerGen_model <- function(
    file, file_name, replicate, n, H, SD, Gen, parameter_combo
) {
  
  fl <- read.csv(file)
  
  required_cols <- c("Generation", "Frequency")
  
  if (!all(required_cols %in% names(fl))) {
    message("Skipping file because required columns are missing: ", file_name)
    message("Columns found: ", paste(names(fl), collapse = ", "))
    return(NULL)
  }
  
  fl <- fl %>%
    mutate(
      Generation = as.numeric(Generation),
      Frequency = as.numeric(Frequency)
    )
  
  max_generation <- max(fl$Generation, na.rm = TRUE)
  min_generation_to_keep <- max_generation - last_n_generations + 1
  
  fl <- fl %>% 
    filter(Generation >= min_generation_to_keep)
  
  flsum <- fl %>% 
    group_by(Generation) %>% 
    summarize(
      Mu_af = mean(Frequency, na.rm = TRUE),
      .groups = "drop"
    ) %>% 
    arrange(Generation) %>% 
    mutate(
      Gen_bin = floor((Generation - 1) / Gen),
      Gen_start = Gen_bin * Gen + 1,
      Gen_end = Gen_start + Gen - 1,
      Gen_label = paste0(Gen_start, "-", Gen_end)
    )
  
  amp_by_interval <- flsum %>% 
    group_by(
      Gen_bin,
      Gen_start,
      Gen_end,
      Gen_label
    ) %>% 
    summarize(
      start_generation = min(Generation, na.rm = TRUE),
      end_generation = max(Generation, na.rm = TRUE),
      n_generations_observed = n_distinct(Generation),
      start_freq = Mu_af[Generation == start_generation][1],
      end_freq = Mu_af[Generation == end_generation][1],
      signed_change = end_freq - start_freq,
      amplitude = abs(signed_change),
      .groups = "drop"
    ) %>% 
    filter(
      n_generations_observed == Gen,
      start_generation == Gen_start,
      end_generation == Gen_end
    ) %>% 
    mutate(
      replicate = replicate,
      n = n,
      H = H,
      SD = SD,
      Gen = Gen,
      file_name = file_name,
      parameter_combo = parameter_combo
    )
  
  return(amp_by_interval)
}

amp_all_FewerGen <- future_pmap_dfr(
  param_table_FewerGen,
  calculate_amplitude_FewerGen_model,
  .progress = FALSE,
  .options = furrr_options(
    seed = TRUE,
    packages = c("dplyr", "stringr", "tidyr")
  )
)

if (nrow(amp_all_FewerGen) == 0) {
  stop("No usable data were produced. Check file pattern, target_n, and column names.")
}

###############################################################################
########################## Replicate summaries #################################
###############################################################################

amp_rep_FewerGen <- amp_all_FewerGen %>% 
  group_by(
    n,
    H,
    SD,
    Gen,
    parameter_combo,
    replicate
  ) %>% 
  summarize(
    mean_rep_amplitude = mean(amplitude, na.rm = TRUE),
    median_rep_amplitude = median(amplitude, na.rm = TRUE),
    sd_rep_amplitude = sd(amplitude, na.rm = TRUE),
    n_intervals = n(),
    .groups = "drop"
  )

plan(sequential)
```

```{r, fig.width=20, fig.height=10}

###############################################################################
########################## Scatter summary plot ################################
###############################################################################

pp_FewerGen_ranked <- ggplot(
  amp_param_FewerGen,
  aes(
    x = as.integer(SD),
    y = mean_amplitude, 
    color = factor(H),
    group = interaction(H, Gen),
    shape = factor(Gen)
  )
) +
  geom_errorbar(
    aes(
      ymin = mean_amplitude - se_amplitude, 
      ymax = mean_amplitude + se_amplitude,
      group = interaction(H, Gen)
    ),
    width = 0.5,
    linewidth = 1,
    position = position_dodge(width = 0.5)
  ) +
  geom_point(
    aes(
      group = interaction(H, Gen)
    ),
    size = 8,
    alpha = 0.9,
    position = position_dodge(width = 0.5)
  ) +
  facet_wrap(~ paste0("Architecture = ", n, " loci"), scales = "free_y") +
  labs(
    x = "Δ values",
    y = "Mean amplitude", 
    color = "h²",
    shape = "Gen"
  ) +
  theme_amp +
  theme(
    plot.margin = unit(c(6, 6, 1, 1), "lines")
  )

pp_FewerGen_ranked



ggsave(
  filename = file.path(plot_dir, "FewerGen_model_H_SD_Gen_n_scatter_mean_amplitude.png"),
  plot = pp_FewerGen_ranked,
  width = 25,
  height = 15,
  dpi = 300
)

ggsave(
  filename = file.path(plot_dir, "FewerGen_model_H_SD_Gen_n_scatter_mean_amplitude.pdf"),
  plot = pp_FewerGen_ranked,
  width = 25,
  height = 15,
  device = cairo_pdf
)
```

## 7. Fluctuating Population size and selection

```{r, fig.width=20, fig.height=20}
rm(list = ls())
library(dplyr)
library(tidyr)
library(ggplot2)
library(patchwork)
library(stringr)
library(purrr)
library(future)
library(furrr)
library(scales)

###############################################################################
########################## Settings ############################################
###############################################################################

plot_dir <- "/home/etb68/Mylab/evogen-sims/FluctSelectionModels.dir/WritingFigures.dir/OutputFigures.dir/Amplitudes_plt.dir/PopModels"
dir.create(plot_dir, recursive = TRUE, showWarnings = FALSE)

target_n <- c(300)

target_replicates <- 1:30

target_H_amplitude <- c(0.1, 0.8)
target_SD_amplitude <- c(1, 4)
target_Gen_amplitude <- c(10, 30)

dynamics_parameter_regime <- tibble(
  H = 0.8,
  SD = 4,
  Gen = 30
)

spectral_parameter_regime <- tibble(
  Regime = c("Low", "High"),
  H = c(0.1, 0.8),
  SD = c(1, 4),
  Gen = c(10, 30)
)

target_n_dynamics <- target_n
target_replicate_for_dynamics <- 5


default_Gen_if_missing <- 30

last_n_generations <- 1000
n_positions_for_dynamics <- 30

spectrum_span <- 2

# spectrum() smoothing
if (length(spectrum_span) == 1 && spectrum_span %% 2 == 0) {
  spectrum_span <- spectrum_span + 1
}

n_workers <- 32
available_workers <- future::availableCores()
n_workers_used <- min(n_workers, available_workers)

future::plan(multisession, workers = n_workers_used)

###############################################################################
############## Model to compare and their respective directoties ##############
###############################################################################

model_sources <- tibble(
  Model = c(
    "Constant_Selection Instantaneous_Population",
    "Null_Selection Instantaneous_Population",
    "Instantaneous_Selection Constant_Population",
    "Instantaneous_Selection Instantaneous_Population"
  ),
  Selection = c(
    "Constant_Selection",
    "Null_Selection",
    "Instantaneous_Selection",
    "Instantaneous_Selection"
  ),
  Population = c(
    "Instantaneous_Population",
    "Instantaneous_Population",
    "Constant_Population",
    "Instantaneous_Population"
  ),
  folder_path = c(
    "~/Mylab/EvoGenFP.sims/FluctPopulationModels.dir/Output.dir/ConstSelInstatPop",
    "~/Mylab/EvoGenFP.sims/FluctPopulationModels.dir/Output.dir/NeutrSelInstatPop",
    "~/Mylab/evogen-sims/FluctSelectionModels.dir/Output.dir/LinFS.dir",
    "~/Mylab/EvoGenFP.sims/FluctPopulationModels.dir/Output.dir/InstSelInstatPop"
  )
) %>%
  mutate(
    folder_path = path.expand(folder_path)
  )

###############################################################################
########################## Theme ###############################################
###############################################################################

theme_amp <- theme_bw() +
  theme(
    text = element_text(family = "sans"),
    legend.position = "right",
    
    axis.text.x = element_text(
      face = "bold",
      size = 20,
      angle = 45,
      margin = margin(t = 10),
      hjust = 1
    ),
    axis.text.y = element_text(
      face = "bold",
      size = 20,
      angle = 0,
      margin = margin(r = 10)
    ),
    
    axis.line = element_line(linewidth = 1.5),
    
    plot.title = element_text(
      hjust = 0.01,
      face = "bold",
      size = 28,
      margin = margin(b = 0.5, unit = "lines")
    ),
    
    plot.margin = unit(c(1, 1, 1, 1), "lines"),
    
    axis.title.x = element_text(
      size = 22,
      face = "bold",
      margin = margin(t = 20)
    ),
    axis.title.y = element_text(
      size = 22,
      face = "bold",
      margin = margin(r = 20)
    ),
    
    strip.text = element_text(size = 16, face = "bold"),
    legend.title = element_text(size = 18, face = "bold"),
    legend.text = element_text(size = 16),
    panel.spacing = unit(1.5, "lines"),
    panel.grid = element_blank()
  )

###############################################################################
########################## Helper functions ####################################
###############################################################################

safe_num <- function(x) {
  suppressWarnings(as.numeric(x))
}

clean_model_label <- function(x) {
  x %>%
    str_replace_all("_", " ") %>%
    str_replace(" Constant Population", "\nConstant Population") %>%
    str_replace(" Instantaneous Population", "\nInstantaneous Population")
}

make_factor_columns <- function(df) {
  df %>%
    mutate(
      Model = factor(
        Model,
        levels = model_sources$Model
      ),
      Model_Label = factor(
        clean_model_label(as.character(Model)),
        levels = clean_model_label(model_sources$Model)
      ),
      Selection = factor(
        Selection,
        levels = c(
          "Null_Selection",
          "Constant_Selection",
          "Instantaneous_Selection"
        )
      ),
      Population = factor(
        Population,
        levels = c(
          "Constant_Population",
          "Instantaneous_Population"
        )
      ),
      Architecture = factor(
        Architecture,
        levels = paste0("Architecture = ", sort(target_n), " loci")
      ),
      H_factor = factor(
        H,
        levels = target_H_amplitude
      ),
      SD_factor = factor(
        SD,
        levels = target_SD_amplitude
      ),
      Gen_factor = factor(
        Gen,
        levels = target_Gen_amplitude
      ),
      parameter_combo = factor(
        parameter_combo,
        levels = unique(parameter_combo[order(H, SD, Gen)])
      )
    )
}

###############################################################################
########################## Flexible parameter parser ############################
###############################################################################

extract_params_any_model <- function(
    file,
    Model,
    Selection,
    Population,
    default_Gen_if_missing = 30
) {
  
  file_name <- basename(file)
  
  # Pattern A:
  # genome5_n300_H0.8SD4Gen30.csv
  replicate_a <- str_match(file_name, "^genome([0-9]+)_")[, 2]
  n_a <- str_match(file_name, "_n([0-9]+)_")[, 2]
  H_a <- str_match(file_name, "H([0-9]+(?:\\.[0-9]+)?)SD")[, 2]
  SD_a <- str_match(file_name, "SD([0-9]+(?:\\.[0-9]+)?)(?:Gen|\\.csv)")[, 2]
  Gen_a <- str_match(file_name, "Gen([0-9]+)")[, 2]
  
  # Pattern B:
  # genome_repl5_loci300_h0.8_Gen30_SD4.csv
  replicate_b <- str_match(file_name, "genome_repl([0-9]+)_")[, 2]
  n_b <- str_match(file_name, "_loci([0-9]+)_")[, 2]
  H_b <- str_match(file_name, "_h([0-9]+(?:\\.[0-9]+)?)")[, 2]
  Gen_b <- str_match(file_name, "_Gen([0-9]+)")[, 2]
  SD_b <- str_match(file_name, "_SD([0-9]+(?:\\.[0-9]+)?)")[, 2]
  
  # Pattern C:
  # repl5_loci300_h0.8_Gen30_SD4.csv
  replicate_c <- str_match(file_name, "^repl([0-9]+)_")[, 2]
  n_c <- str_match(file_name, "_loci([0-9]+)_")[, 2]
  H_c <- str_match(file_name, "_h([0-9]+(?:\\.[0-9]+)?)")[, 2]
  Gen_c <- str_match(file_name, "_Gen([0-9]+)")[, 2]
  SD_c <- str_match(file_name, "_SD([0-9]+(?:\\.[0-9]+)?)")[, 2]
  
  replicate <- coalesce(
    safe_num(replicate_a),
    safe_num(replicate_b),
    safe_num(replicate_c)
  )
  
  n <- coalesce(
    safe_num(n_a),
    safe_num(n_b),
    safe_num(n_c)
  )
  
  H <- coalesce(
    safe_num(H_a),
    safe_num(H_b),
    safe_num(H_c)
  )
  
  SD <- coalesce(
    safe_num(SD_a),
    safe_num(SD_b),
    safe_num(SD_c)
  )
  
  Gen <- coalesce(
    safe_num(Gen_a),
    safe_num(Gen_b),
    safe_num(Gen_c)
  )
  
  tibble(
    Model = as.character(Model),
    Selection = as.character(Selection),
    Population = as.character(Population),
    file = file,
    file_name = file_name,
    replicate = replicate,
    n = n,
    H = H,
    SD = SD,
    Gen = Gen
  )
}

###############################################################################
########################## File list ###########################################
###############################################################################

files_by_model <- model_sources %>%
  mutate(
    file = map(
      folder_path,
      ~ list.files(
        path = .x,
        pattern = "\\.csv$",
        full.names = TRUE
      )
    )
  ) %>%
  select(Model, Selection, Population, file) %>%
  unnest(file)

if (nrow(files_by_model) == 0) {
  stop("No files found. Check model_sources$folder_path.")
}

###############################################################################
########################## Raw parameter table #################################
###############################################################################

param_table_raw <- pmap_dfr(
  files_by_model,
  extract_params_any_model,
  default_Gen_if_missing = default_Gen_if_missing
) %>%
  filter(
    !is.na(replicate),
    !is.na(n),
    n %in% target_n,
    replicate %in% target_replicates
  )

if (nrow(param_table_raw) == 0) {
  stop("No files remain after basic n and replicate filtering.")
}

###############################################################################
########################## Parameter parsing diagnostics ########################
###############################################################################

param_parse_check <- param_table_raw %>%
  mutate(
    missing_H = is.na(H),
    missing_SD = is.na(SD),
    missing_Gen = is.na(Gen)
  ) %>%
  count(
    Model,
    Selection,
    Population,
    missing_H,
    missing_SD,
    missing_Gen,
    name = "n_files"
  ) %>%
  arrange(Model, missing_H, missing_SD, missing_Gen)

print(param_parse_check)

bad_non_null_files <- param_table_raw %>%
  filter(
    Selection != "Null_Selection",
    is.na(H) | is.na(SD) | is.na(Gen)
  ) %>%
  select(Model, Selection, Population, file_name, replicate, n, H, SD, Gen)

if (nrow(bad_non_null_files) > 0) {
  print(bad_non_null_files)
  stop(
    "Some non-null selection files are missing H, SD, or Gen. ",
    "This likely means the filename parser is failing."
  )
}

###############################################################################
########################## Expand null-selection rows if needed ################
###############################################################################
# Important:
# Null_Selection Instantaneous_Population is your null-selection +
# fluctuating/instantaneous population-size model.
#
# H and SD can be expanded for Null_Selection because selection is absent.
# Gen should ideally be parsed from the filename. If Gen is missing, this code
# uses default_Gen_if_missing rather than expanding the same file across both
# Gen = 10 and Gen = 30.
###############################################################################

expand_null_or_keep_row <- function(
    Model,
    Selection,
    Population,
    file,
    file_name,
    replicate,
    n,
    H,
    SD,
    Gen
) {
  
  if (Selection == "Null_Selection") {
    
    H_values <- if (is.na(H)) {
      target_H_amplitude
    } else {
      H
    }
    
    SD_values <- if (is.na(SD)) {
      target_SD_amplitude
    } else {
      SD
    }
    
    Gen_values <- if (is.na(Gen)) {
      default_Gen_if_missing
    } else {
      Gen
    }
    
    expand_grid(
      H = H_values,
      SD = SD_values,
      Gen = Gen_values
    ) %>%
      mutate(
        Model = Model,
        Selection = Selection,
        Population = Population,
        file = file,
        file_name = file_name,
        replicate = replicate,
        n = n
      ) %>%
      select(
        Model,
        Selection,
        Population,
        file,
        file_name,
        replicate,
        n,
        H,
        SD,
        Gen
      )
    
  } else {
    
    tibble(
      Model = Model,
      Selection = Selection,
      Population = Population,
      file = file,
      file_name = file_name,
      replicate = replicate,
      n = n,
      H = H,
      SD = SD,
      Gen = Gen
    )
  }
}

param_table_FewerGen <- pmap_dfr(
  param_table_raw,
  expand_null_or_keep_row
) %>%
  filter(
    !is.na(H),
    !is.na(SD),
    !is.na(Gen),
    H %in% target_H_amplitude,
    SD %in% target_SD_amplitude,
    Gen %in% target_Gen_amplitude
  ) %>%
  distinct(
    Model,
    Selection,
    Population,
    file,
    file_name,
    replicate,
    n,
    H,
    SD,
    Gen,
    .keep_all = TRUE
  ) %>%
  arrange(Model, n, H, SD, Gen, replicate) %>%
  mutate(
    Architecture = paste0("Architecture = ", n, " loci"),
    parameter_combo = paste0(
      "h2 = ", H,
      " | Delta = ", SD,
      " | Gen = ", Gen
    ),
    full_parameter_label = paste0(
      "n = ", n,
      " | h2 = ", H,
      " | Delta = ", SD,
      " | Gen = ", Gen
    )
  ) %>%
  make_factor_columns()

if (nrow(param_table_FewerGen) == 0) {
  stop(
    "No files remain after filtering. Expected n = 300, replicates 1:30, H = 0.1/0.8, SD = 1/4, Gen = 10/30."
  )
}

###############################################################################
########################## Reuse / mixing diagnostics ###########################
###############################################################################

file_parameter_reuse_check <- param_table_FewerGen %>%
  group_by(Model, Selection, Population, file_name, replicate, n) %>%
  summarize(
    n_H_labels = n_distinct(H),
    n_SD_labels = n_distinct(SD),
    n_Gen_labels = n_distinct(Gen),
    n_parameter_labels = n_distinct(paste(H, SD, Gen, sep = "_")),
    parameter_labels = paste(
      sort(unique(paste0("H=", H, ", SD=", SD, ", Gen=", Gen))),
      collapse = " | "
    ),
    .groups = "drop"
  ) %>%
  filter(n_parameter_labels > 1)

if (nrow(file_parameter_reuse_check) > 0) {
  print(file_parameter_reuse_check)
  message(
    "Some files are used under multiple parameter labels. ",
    "This is expected only for Null_Selection files expanded across H/SD."
  )
}

bad_gen_reuse <- file_parameter_reuse_check %>%
  filter(
    Selection == "Null_Selection",
    n_Gen_labels > 1
  )

if (nrow(bad_gen_reuse) > 0) {
  print(bad_gen_reuse)
  stop(
    "A Null_Selection file is being reused across multiple Gen labels. ",
    "This would mix Gen = 10 and Gen = 30 and should not happen."
  )
}

bad_non_null_reuse <- file_parameter_reuse_check %>%
  filter(
    Selection != "Null_Selection"
  )

if (nrow(bad_non_null_reuse) > 0) {
  print(bad_non_null_reuse)
  stop(
    "A non-null file is being reused across multiple parameter labels. ",
    "This is parameter mixing and should not happen."
  )
}

###############################################################################
########################## Optional diagnostics ################################
###############################################################################

missing_parameter_report <- param_table_raw %>%
  filter(
    Selection == "Null_Selection",
    is.na(H) | is.na(SD) | is.na(Gen)
  ) %>%
  distinct(
    Model,
    Selection,
    Population,
    file_name,
    H,
    SD,
    Gen
  )

if (nrow(missing_parameter_report) > 0) {
  message(
    "Some Null_Selection files did not encode H, SD, or Gen. ",
    "H/SD were expanded for plotting. Missing Gen was assigned default_Gen_if_missing."
  )
  print(missing_parameter_report)
}

###############################################################################
########################## Replicate check #####################################
###############################################################################

replicate_completeness <- param_table_FewerGen %>%
  group_by(
    Model,
    Selection,
    Population,
    Architecture,
    n,
    H,
    SD,
    Gen
  ) %>%
  summarize(
    n_replicates = n_distinct(replicate),
    replicates = paste(sort(unique(replicate)), collapse = ", "),
    .groups = "drop"
  ) %>%
  arrange(Model, Architecture, H, SD, Gen)

replicate_check <- replicate_completeness %>%
  filter(n_replicates != length(target_replicates))

if (nrow(replicate_check) > 0) {
  print(replicate_check)
  stop(
    "Some model/parameter combinations do not have exactly ",
    length(target_replicates),
    " replicates. Check replicate_completeness."
  )
}

###############################################################################
########################## Single-replicate dynamics ###########################
###############################################################################

param_table_dynamics <- param_table_FewerGen %>%
  filter(
    replicate == target_replicate_for_dynamics,
    n %in% target_n_dynamics
  ) %>%
  semi_join(
    dynamics_parameter_regime,
    by = c("H", "SD", "Gen")
  ) %>%
  arrange(Model, Architecture, H, SD, Gen) %>%
  make_factor_columns()

if (nrow(param_table_dynamics) == 0) {
  stop(
    "No files found for allele dynamics. Expected replicate ",
    target_replicate_for_dynamics,
    ", n = 300, H = 0.8, SD = 4, Gen = 30."
  )
}

sample_single_replicate_dynamics <- function(
    Model,
    Selection,
    Population,
    file,
    file_name,
    replicate,
    n,
    H,
    SD,
    Gen,
    Architecture,
    parameter_combo,
    full_parameter_label,
    H_factor = NULL,
    SD_factor = NULL,
    Gen_factor = NULL,
    Model_Label = NULL,
    target_replicate_for_dynamics = 5,
    n_positions = 30,
    seed = 5463456
) {
  
  if (replicate != target_replicate_for_dynamics) {
    return(NULL)
  }
  
  fl <- read.csv(file)
  
  required_cols <- c("Generation", "Frequency", "Position")
  
  if (!all(required_cols %in% names(fl))) {
    return(NULL)
  }
  
  fl <- fl %>%
    mutate(
      Generation = safe_num(Generation),
      Frequency = safe_num(Frequency),
      Position = as.factor(Position)
    ) %>%
    filter(
      !is.na(Generation),
      !is.na(Frequency),
      !is.na(Position)
    )
  
  if (nrow(fl) == 0) {
    return(NULL)
  }
  
  fl_sampled_time <- fl
  
  set.seed(
    seed +
      as.integer(n) +
      as.integer(SD) +
      as.integer(Gen) +
      as.integer(H * 100)
  )
  
  sampled_positions <- sample(
    unique(fl_sampled_time$Position),
    min(n_positions, length(unique(fl_sampled_time$Position))),
    replace = FALSE
  )
  
  fl_sampled_time %>%
    filter(Position %in% sampled_positions) %>%
    mutate(
      Model = as.character(Model),
      Selection = as.character(Selection),
      Population = as.character(Population),
      replicate = replicate,
      n = n,
      H = H,
      SD = SD,
      Gen = Gen,
      Architecture = as.character(Architecture),
      file_name = file_name,
      parameter_combo = as.character(parameter_combo),
      full_parameter_label = as.character(full_parameter_label)
    )
}

single_rep_dynamics_FewerGen <- pmap_dfr(
  param_table_dynamics,
  sample_single_replicate_dynamics,
  target_replicate_for_dynamics = target_replicate_for_dynamics,
  n_positions = n_positions_for_dynamics,
  seed = 768678
)

if (nrow(single_rep_dynamics_FewerGen) == 0) {
  stop(
    "No single-replicate dynamics data were produced. Check replicate, n = 300, high parameter regime, and file contents."
  )
}

single_rep_dynamics_FewerGen <- single_rep_dynamics_FewerGen %>%
  make_factor_columns()

###############################################################################
########################## Dynamics plot #######################################
###############################################################################

p_single_rep_dynamics_high_by_model <- ggplot(
  single_rep_dynamics_FewerGen %>% filter(Generation <= 1000),
  aes(
    x = Generation,
    y = Frequency,
    group = interaction(
      Model,
      Architecture,
      H,
      SD,
      Gen,
      file_name,
      Position
    )
  )
) +
  geom_line(
    alpha = 0.35,
    linewidth = 0.45
  ) +
  facet_wrap(
    . ~ Model_Label,
    scales = "free_y",
    ncol = 1
  ) +
  labs(
    title = "A) Allele frequency dynamics",
    x = "Generation",
    y = "Allele frequency"
  ) +
  theme_amp +
  theme(
    legend.position = "none",
    strip.text = element_text(size = 13, face = "bold"),
    axis.text.x = element_text(
      face = "bold",
      size = 11,
      angle = 45,
      hjust = 1
    ),
    axis.text.y = element_text(
      face = "bold",
      size = 11,
      angle = 0
    ),
    axis.title.x = element_text(size = 18, face = "bold"),
    axis.title.y = element_text(size = 18, face = "bold"),
    plot.title = element_text(size = 22, face = "bold"),
    panel.spacing = unit(1.2, "lines")
  )

p_single_rep_dynamics_high_by_model

###############################################################################
########################## Spectral analysis ###################################
###############################################################################
# Mean AF spectrum:
# mean allele frequency across positions at each generation, then spectrum.
###############################################################################

param_table_spectral <- param_table_FewerGen %>%
  inner_join(
    spectral_parameter_regime,
    by = c("H", "SD", "Gen")
  ) %>%
  mutate(
    Regime = factor(Regime, levels = c("Low", "High"))
  ) %>%
  arrange(Model, Architecture, Regime, H, SD, Gen, replicate) %>%
  make_factor_columns()

if (nrow(param_table_spectral) == 0) {
  stop(
    "No files found for spectral analysis. Expected n = 300, Low: H = 0.1, SD = 1, Gen = 10; High: H = 0.8, SD = 4, Gen = 30."
  )
}

calculate_spectrum_model <- function(
    Model,
    Selection,
    Population,
    file,
    file_name,
    replicate,
    n,
    H,
    SD,
    Gen,
    Architecture,
    parameter_combo,
    full_parameter_label,
    Regime,
    H_factor = NULL,
    SD_factor = NULL,
    Gen_factor = NULL,
    Model_Label = NULL,
    spectrum_span = 2
) {
  
  fl <- read.csv(file)
  
  required_cols <- c("Generation", "Frequency")
  
  if (!all(required_cols %in% names(fl))) {
    return(NULL)
  }
  
  fl <- fl %>%
    mutate(
      Generation = safe_num(Generation),
      Frequency = safe_num(Frequency)
    ) %>%
    filter(
      !is.na(Generation),
      !is.na(Frequency),
      is.finite(Generation),
      is.finite(Frequency)
    )
  
  if (nrow(fl) == 0) {
    return(NULL)
  }
  
  mean_allele_data <- fl %>%
    group_by(Generation) %>%
    summarize(
      mean_allele_frequency = mean(Frequency, na.rm = TRUE),
      .groups = "drop"
    ) %>%
    arrange(Generation)
  
  if (nrow(mean_allele_data) < 8) {
    return(NULL)
  }
  
  series <- as.numeric(mean_allele_data$mean_allele_frequency)
  series <- series[is.finite(series)]
  
  if (length(series) < 8) {
    return(NULL)
  }
  
  if (sd(series, na.rm = TRUE) == 0) {
    return(NULL)
  }
  
  spec_result <- tryCatch(
    stats::spectrum(
      series,
      spans = spectrum_span,
      plot = FALSE
    ),
    error = function(e) NULL
  )
  
  if (is.null(spec_result)) {
    return(NULL)
  }
  
  ok_spec <- is.finite(spec_result$freq) &
    spec_result$freq > 0 &
    is.finite(spec_result$spec)
  
  if (!any(ok_spec)) {
    return(NULL)
  }
  
  tibble(
    Period = 1 / spec_result$freq[ok_spec],
    Spectrum = as.numeric(spec_result$spec[ok_spec]),
    Model = as.character(Model),
    Selection = as.character(Selection),
    Population = as.character(Population),
    replicate = replicate,
    n = n,
    H = H,
    SD = SD,
    Gen = Gen,
    Regime = as.character(Regime),
    Architecture = as.character(Architecture),
    file_name = file_name,
    parameter_combo = as.character(parameter_combo),
    full_parameter_label = as.character(full_parameter_label)
  )
}

spec_all_FewerGen <- future_pmap_dfr(
  param_table_spectral,
  calculate_spectrum_model,
  spectrum_span = spectrum_span,
  .progress = FALSE,
  .options = furrr_options(
    seed = TRUE,
    packages = c("dplyr", "tidyr", "stringr", "purrr", "stats")
  )
)

if (nrow(spec_all_FewerGen) == 0) {
  stop("No usable spectral data were produced.")
}

spec_all_FewerGen <- spec_all_FewerGen %>%
  mutate(
    Regime = factor(Regime, levels = c("Low", "High")),
    threshold = case_when(
      Gen == 10 ~ 40,
      Gen == 20 ~ 50,
      Gen == 30 ~ 80,
      TRUE ~ 80
    )
  ) %>%
  filter(
    Period < threshold
  ) %>%
  make_factor_columns()

###############################################################################
########################## Spectral replicate check ############################
###############################################################################

spec_replicate_completeness <- spec_all_FewerGen %>%
  group_by(
    Model,
    Architecture,
    Regime,
    H,
    SD,
    Gen
  ) %>%
  summarize(
    n_replicates = n_distinct(replicate),
    replicates = paste(sort(unique(replicate)), collapse = ", "),
    .groups = "drop"
  ) %>%
  arrange(Model, Architecture, Regime, H, SD, Gen)

spec_replicate_check <- spec_replicate_completeness %>%
  filter(n_replicates != length(target_replicates))

if (nrow(spec_replicate_check) > 0) {
  print(spec_replicate_check)
  stop(
    "Some spectral results were not calculated from exactly ",
    length(target_replicates),
    " replicates. Check spec_replicate_completeness."
  )
}

###############################################################################
########################## Spectral plot #######################################
###############################################################################

p_spectral_by_model <- ggplot(
  spec_all_FewerGen,
  aes(
    x = Period,
    y = Spectrum,
    color = factor(replicate),
    group = interaction(
      Model,
      Architecture,
      Regime,
      H,
      SD,
      Gen,
      replicate
    )
  )
) +
  geom_line(
    linewidth = 0.9,
    alpha = 0.75
  ) +
  scale_y_continuous(
    labels = scales::scientific_format()
  ) +
  facet_wrap(
    vars(Regime, Model_Label),
    ncol = 2,
    scales = "free"
  ) +
  labs(
    title = "B) Spectral density across replicates",
    x = "Period",
    y = "Spectrum",
    color = "Replicate"
  ) +
  theme_amp +
  theme(
    legend.position = "none",
    strip.text = element_text(size = 13, face = "bold"),
    axis.text.x = element_text(
      face = "bold",
      size = 11,
      angle = 45,
      hjust = 1
    ),
    axis.text.y = element_text(
      face = "bold",
      size = 11,
      angle = 0
    ),
    axis.title.x = element_text(size = 18, face = "bold"),
    axis.title.y = element_text(size = 18, face = "bold"),
    plot.title = element_text(size = 22, face = "bold"),
    panel.spacing = unit(1.2, "lines")
  )

p_spectral_by_model

###############################################################################
########################## Combined plot #######################################
###############################################################################

combined_dynamics_spectral <- (
  p_single_rep_dynamics_high_by_model +
    p_spectral_by_model
) +
  plot_layout(
    widths = c(1.5, 4)
  )

combined_dynamics_spectral

###############################################################################
########################## Optional saving #####################################
###############################################################################

ggsave(
  filename = file.path(
    plot_dir,
    "combined_dynamics_spectral_population_models_with_null_instantaneous_population.pdf"
  ),
  plot = combined_dynamics_spectral,
  width = 20,
  height = 20,
  units = "in",
  device = cairo_pdf
)

ggsave(
  filename = file.path(
    plot_dir,
    "combined_dynamics_spectral_population_models_with_null_instantaneous_population.png"
  ),
  plot = combined_dynamics_spectral,
  width = 20,
  height = 20,
  units = "in",
  device = "png"
)
```

### ----------- END ------------------------