---
title: "Supplemental Figures"
author: "E.T"
format:
  docx:
    toc: true
    fontsize: 10pt
    fig-cap-location: bottom
    fig-numbering: false  
  pdf:
    toc: true
  html:
    toc: true
    knitr:
      opts_chunk:
        dev: "cairo_png"
execute:
  warning: false
  message: false
  repos: https://cloud.r-project.org
editor: visual
---

```{r, echo=FALSE, message=FALSE}
#| label: setup

#| include: false

# Setting the directory containing the document to be the home directory and destination 

document_dir <- Sys.getenv("QUARTO_DOCUMENT_PATH", unset = "")

if (!nzchar(document_dir)) {

  if (requireNamespace("rstudioapi", quietly = TRUE) && rstudioapi::isAvailable()) {
    active_file <- rstudioapi::getActiveDocumentContext()$path
    document_dir <- if (nzchar(active_file)) {
      dirname(active_file)
      } else {
        getwd()
        }
    } else {
      document_dir <- getwd()
    }
  }

document_dir <- normalizePath(
  document_dir, winslash = "/", mustWork = TRUE
)

setwd(document_dir)

knitr::opts_knit$set(root.dir = document_dir)
library(forcats)
library(stringi)
library(tidyr)
library(dplyr)
library(stringr)
library(ggplot2)
library(patchwork)
library(cowplot)
library(purrr)
library(doParallel)

```

```{r, echo=FALSE, warning=FALSE}
###############################################################################
################################## Custom Theme ###############################
###############################################################################
mythemes <- theme_bw() +
  theme(
    text = element_text(family = "sans"), 
    legend.position = "none",
    axis.text.x = element_text(face = "bold", size = 40, angle =25, margin = margin(t = 20), hjust = 1),
    axis.text.y = element_text(face = "bold", size = 40, angle = 15, margin = margin(r = 10)),
    axis.line = element_line(size = 3),
    plot.title = element_text(hjust = 0.01, face = "bold", size = 80, margin = margin(b = 1, unit = "lines")),
    plot.margin = unit(c(5, 1, 1, 1), "lines"),
    axis.title.x = element_text(size = 40, face = "bold", margin = margin(t = 30)),
    axis.title.y = element_text(size = 40, face = "bold", margin = margin(r = 35)),
    strip.text = element_text(size = 40, face = "bold"),
    panel.spacing = unit(5, "lines"),
    panel.grid = element_blank()
  )

```


# 1. Null model

```{r, warning=FALSE, fig.width = 20, fig.height = 5, echo=FALSE, message=FALSE}
## | label: NS_All_Locus_AllReplicates
## | fig-cap: "SI 1.1.1. Single locus 30 replicates allele frequency dynamics for gradual two equal seasons selection model, showing all parameter interactions. The highlighted line indicates the mean allele frequency for each generation."
## | fig-pos: "H"
library(dplyr)
library(ggplot2)


#####################################################
######### data processing function ##################
#####################################################

process_files <- function(dirpath, pattern) {
  
  files <- list.files(dirpath, pattern = pattern, full.names = TRUE)
  
  # List to store data frames
  dataframes <- list()
  
  # Get parameters from the file name and read dataset
  for (file in files) {
    fname <- basename(file) 
    H <- as.numeric(sub(".*_H(0\\.\\d+).*", "\\1", fname))
    loci <- as.numeric( sub(".*_n(\\d+)_.*", "\\1", fname))
    SD <- as.numeric(sub(".*SD(\\d+).*", "\\1", fname))
    Gen <- as.numeric(sub(".*Gen(\\d+).*", "\\1", fname))
    replicate <- as.numeric(sub(".*genome(\\d+)_.*", "\\1", fname))
    
    
    data <- read.csv(file, header = TRUE) %>% 
      mutate(
        H         = H,
        loci      = loci,
        SD        = SD,
        Gen       = Gen,
        replicate = as.factor(replicate),
        h2_sd     = paste0("h\u00B2 = ", H, " sd = ", SD),
        loci_gen  = paste0("loci = ", loci, " gen = ", Gen),
        loci_facet = paste0("Loci = ", loci)
      ) %>%
      mutate(loci_facet = factor(loci_facet, 
                                 levels = c("Loci = 1", "Loci = 10", "Loci = 70",
                                            "Loci = 100", "Loci = 300")))
    
    dataframes[[fname]] <- data
  }
  
  # Combine all dataframes into one 
  combined_data <- bind_rows(dataframes)
  
  return(combined_data)
}

########################################################################
######### Process the files to get combined data #####################
########################################################################

dirpath <- "../../Output.dir/NS.dir/"
pattern <- "^genome\\d+_n(1|10|300)_H0\\.(8)(SD(1|2|4))?(Gen(10|20|30))?\\.csv$"

combined_data <- process_files(dirpath, pattern)

# For each replicate (and loci group), randomly sample one position
# (Assuming the CSVs have a column named "Position")
set.seed(45696546)  # for reproducibility

sampled_data <- combined_data %>%
  group_by(replicate, loci) %>%
  group_modify(~ {
      unique_pos <- unique(.x$Position)
      # If there's only one unique position, retain it; otherwise, sample one
      selected_pos <- if(length(unique_pos) == 1) unique_pos else sample(unique_pos, 1)
      filter(.x, Position == selected_pos)
  }) %>%
  ungroup()


########################################################################
######### Create the plot using the sampled data #####################
########################################################################

sampledreplc_AF <- sampled_data %>%
  mutate(
    H_SD_Gen = paste0("h\u00B2 = ", H, "\u0394\ = ", SD, " Gen = ", Gen)
  ) %>% 
  ggplot(aes(x = Generation, y = Frequency, color = replicate)) +
  geom_line(aes(group = (replicate)),
            #color = (replicate), #"gray50", 
            alpha = 1, 
            size = 0.2) +
  # stat_summary(fun = mean,
  #              aes(group = 1), 
  #              geom = "line", 
  #              color = "red3", 
  #              alpha = 1, 
  #              size = 1) +
  facet_wrap(~ loci_facet, ncol = 3) +
  labs(
    x = "Generation",
    y = "Frequency"
  ) +
  theme_bw() +
  theme(
    text = element_text(family = "sans"),
    legend.position = "none",
    axis.text.x = element_text(face = "bold", size = 20, angle = 35,
                               hjust = 1, margin = margin(t = 10)),
    axis.text.y = element_text(face = "bold", size = 20, angle = 15,
                               margin = margin(r = 10)),
    axis.line   = element_line(size = 2),
    plot.title  = element_text(hjust = 0.01, face = "bold", size = 20),
    axis.title.x = element_text(size = 30, face = "bold",
                                margin = margin(t = 10)),
    axis.title.y = element_text(size = 30, face = "bold",
                                margin = margin(r = 10)),
    strip.text = element_text(size = 20, face = "bold"),
    panel.spacing = unit(5, "lines"),
    panel.grid = element_blank()
  )

```

## 1.1. Null selection Allele frequency

```{r, fig.width = 20, fig.height = 5, echo=FALSE, message = FALSE}
#| label: NS_All_Locus_AllReplicates
#| fig-cap: "SI 1.1. Allele frequency dynamics for monogenic, oligogec (10 loci), and polygenic (300 loci) traits models. Each line represent a single locus sampled from all loci within a single replicate of each model."
#| 
sampledreplc_AF

ggsave(filename = "SI_5.1.sampledreplc_AF.jpg", sampledreplc_AF, path = "../OutputFigures.dir/SupplementalFigures.dir", width = 20, height = 5, units = "in", dpi = 300, limitsize = FALSE)
```

## 1.2. Null selection phenotypes

```{r, echo=FALSE}
pheno_processing <- function(dirpath, pattern) {
  mythemes <- theme_bw() +
    theme(
      text            = element_text(family = "sans"), 
      legend.position = "none",
      axis.text.x     = element_text(face = "bold", size = 20, angle = 25, 
                                       margin = margin(t = 20), hjust = 1),
      axis.text.y     = element_text(face = "bold", size = 20, angle = 15, 
                                       margin = margin(r = 10)),
      axis.line       = element_line(size = 3),
      plot.title      = element_text(hjust = 0.01, face = "bold", size = 80, 
                                       margin = margin(b = 1, unit = "lines")),
      plot.margin     = unit(c(5, 1, 1, 1), "lines"),
      axis.title.x    = element_text(size = 30, face = "bold", margin = margin(t = 30)),
      axis.title.y    = element_text(size = 30, face = "bold", margin = margin(r = 35)),
      strip.text      = element_text(size = 20, face = "bold"),
      panel.spacing   = unit(5, "lines"),
      panel.grid      = element_blank()
    )
  
  files <- list.files(dirpath, pattern, full.names = TRUE)
 
  data_list <- list()

  for(file in files) {
    fname <- basename(file) 
    herit <- as.numeric(sub(".*_H(0\\.\\d+).*", "\\1", fname))
    loci <- as.numeric( sub(".*_n(\\d+)_.*", "\\1", fname))
    replicate_id <- as.numeric(sub(".*MeanPhenotypes(\\d+)_.*", "\\1", fname))
    
    
   data <- read.csv(file, header = TRUE) %>%
  mutate(
    replicate  = as.factor(replicate_id),
    herit      = herit,  # ensure herit is numeric
    loci       = loci,   # ensure loci is numeric
    #loci_facet = paste0("Loci = ", loci, ": h\u00B2 = ", herit)
    loci_facet = paste0("Loci = ", loci)
      ) %>%
      mutate(loci_facet = factor(loci_facet, 
                                 levels = c("Loci = 1", "Loci = 10", "Loci = 70",
                                            "Loci = 100", "Loci = 300")))
    data_list[[file]] <- data
  }
  
  combined_data <- bind_rows(data_list)

  
  # Create the plot using the chosen facet variable.
  p <- combined_data %>%
    ggplot(aes(Generation, Phenotype, color = replicate)) +
    geom_line(size = 1) +
    facet_wrap(~loci_facet, scales = "free", ncol = 3) +
    mythemes
  
  return(list(combined_data = combined_data, plot = p))
}

```

```{r, fig.width = 40, fig.height = 15, echo=FALSE, message = FALSE}
#| label: Ns_Pheno_All_architectures
#| fig-cap: "SI 1.2. Mean population phenotypic plot across 30 replicates (each line represents a single replicate) for Null selection, showing parameter interactions."
#| fig-pos: "H"
dirpath <- "../../Output.dir/NS.dir/"
pattern <- "^MeanPhenotypes\\d+_n(1|10|300)_H0\\.(8)(SD(1|2|4))?(Gen(10|20|30))?\\.csv$"
result <- pheno_processing(dirpath, pattern)

Ns_Pheno_All_architectures <- result$plot
Ns_Pheno_All_architectures

ggsave(filename = "SI_5.2.NS_Pheno_All_architectures.jpg", Ns_Pheno_All_architectures, path = "../OutputFigures.dir/SupplementalFigures.dir", width = 40, height = 15, units = "in", dpi = 300, limitsize = FALSE)
```

## 1.3. Null selection spectral analysis

```{r, echo=FALSE}

run_fft_analysis <- function(folder_path, pattern, spectrum_span = 2) {
  library(parallel)
  library(doParallel)
  library(foreach)
  library(dplyr)
  library(ggplot2)
  library(cowplot)
  
  
  # Set a classic theme globally
  theme_set(theme_classic())
  
  mythemes <- theme_bw() +
    theme(
      text            = element_text(family = "sans"), 
      legend.position = "none",
      axis.text.x     = element_text(face = "bold", size = 20, angle = 25, 
                                       margin = margin(t = 20), hjust = 1),
      axis.text.y     = element_text(face = "bold", size = 20, angle = 15, 
                                       margin = margin(r = 10)),
      axis.line       = element_line(size = 3),
      plot.title      = element_text(hjust = 0.01, face = "bold", size = 80, 
                                       margin = margin(b = 1, unit = "lines")),
      plot.margin     = unit(c(5, 1, 1, 1), "lines"),
      axis.title.x    = element_text(size = 30, face = "bold", margin = margin(t = 30)),
      axis.title.y    = element_text(size = 30, face = "bold", margin = margin(r = 35)),
      strip.text      = element_text(size = 20, face = "bold"),
      panel.spacing   = unit(5, "lines"),
      panel.grid      = element_blank()
    )
  
  # List files matching the pattern
  file_list <- list.files(path = folder_path, pattern = pattern, full.names = TRUE)
  if (length(file_list) == 0) {
    stop("No files found with the given pattern.")
  }
  
  # Create a data frame of file names and extract parameters
  files_df <- data.frame(file_name = file_list, stringsAsFactors = FALSE) %>%
    mutate(
      base_name = basename(file_name),  
      n = ifelse(
         grepl("_n\\d+", base_name),
         as.numeric(sub(".*_n(\\d+).*", "\\1", base_name)),
         NA_real_
           ),
      replct <- as.numeric(sub(".*genome(\\d+)_.*", "\\1", base_name)),
      H = ifelse(
         grepl("_H[0-9]+\\.?[0-9]*", base_name),
         as.numeric(sub(".*_H([0-9]+\\.?[0-9]*).*", "\\1", base_name)),
         NA_real_
        ),
      Genome = case_when(
        n == "1"   ~ "Monogenic",
        n == "10"  ~ "Oligogenic",
        n == "70"  ~ "Polygenic 70",
        n == "100" ~ "Polygenic 100",
        n == "300" ~ "Polygenic 300",
        TRUE       ~ "Unknown"
      )
    ) %>%
    mutate(
      n = as.numeric(n),
      H = as.numeric(H),
      # Use n here so the facet label matches your desired order
      param_combination = paste0("Loci = ", n, ": h\u00B2 = ", H)
    )
  
  # Set up the parallel backend using detected cores
  cl <- makeCluster(64)
  registerDoParallel(cl)
  
  # Read and combine data from all replicate files in parallel.
  combined_data_list <- foreach(i = seq_along(files_df$file_name), 
                                .packages = c("dplyr")) %dopar% {
    file <- files_df$file_name[i]
    params <- files_df[i, ]
    df <- read.csv(file)
    data <- df %>%
      mutate(
        allele_id = as.factor(Position),
        generation = as.numeric(Generation),
        allele_frequency = Frequency,
        file = params$base_name,
        replct = params$replct,
        H = params$H,
        Genome = params$Genome,
        n = params$n,
        param_combination = params$param_combination
      ) %>%
      dplyr::select(allele_id, generation, allele_frequency, replct, H, Genome, n, param_combination)
    data
  }
  combined_data <- bind_rows(combined_data_list)
  
  filtered_data <- combined_data
  
  # Calculating the mean allele frequency for each grouping
  mean_allele_data <- filtered_data %>%
    group_by(generation, replct, H, Genome, n, param_combination) %>%
    summarize(mean_allele_frequency = mean(allele_frequency), .groups = "drop")
  
  # Creating time series objects per grouping
  ts_data_list <- mean_allele_data %>%
    group_by(Genome, replct, H, n, param_combination) %>%
    summarize(ts_data = list(ts(mean_allele_frequency, start = min(generation), frequency = 1)),
              .groups = 'drop')
  
  # Computing spectral density estimates in parallel
  spec_results_list <- foreach(i = 1:nrow(ts_data_list), .packages = c("stats")) %dopar% {
    ts_data <- ts_data_list$ts_data[[i]]
    spectrum(ts_data, spans = spectrum_span, plot = FALSE)
  }
  
  # Preparing data for plotting
  plot_data_list <- foreach(i = seq_along(spec_results_list), 
                            .packages = c("dplyr")) %dopar% {
    spec_result <- spec_results_list[[i]]
    params <- ts_data_list[i, ]
    period <- 1 / spec_result$freq
    data.frame(
      Period = period,
      Spectrum = spec_result$spec,
      replct = params$replct,
      H = params$H,
      Genome = params$Genome,
      n = params$n,
      param_combination = params$param_combination
    )
  }
  
  stopCluster(cl)
  
  # Combine plot data and filter based on a threshold
  plot_data <- bind_rows(plot_data_list) %>%
    group_by(param_combination) %>%
    mutate(threshold = 80) %>%
    filter(Period < threshold) %>%
    ungroup() %>%
    #mutate(loci_facet = paste0("Loci = ", n, ": h\u00B2 = ", H))
    mutate(loci_facet = paste0("Loci = ", n)) %>%
    mutate(loci_facet = factor(loci_facet,
                               levels = c("Loci = 1", "Loci = 10", "Loci = 70", 
                                          "Loci = 100", "Loci = 300")))
  

  fft_plots <- ggplot(plot_data, aes(x = Period, y = Spectrum, color = factor(replct), group = factor(replct))) +
    geom_line(size = 1.1) +
    facet_wrap(~ loci_facet, scales = "free", ncol = 3) +
    labs(x = "Period (Generations)", y = "Spectral Density") +
    mythemes
  
  return(fft_plots)
}

```

```{r, fig.width = 40, fig.height = 15, echo=FALSE}
#| label: Ns_SpectralAnalysis_All_architectures
#| fig-cap: "SI 1.3. Spectral density across 30 replicates for all genetic architecture under Null selection model. The density plots do not show any peak as selection is purely driven by random drift."
#| fig-pos: "H"
#| 
dirpath <- "../../Output.dir/NS.dir/"
pattern <- "^genome\\d+_n(1|10|300)_H0\\.(8)(SD(1|2|4))?(Gen(10|20|30))?\\.csv$" 
result <- run_fft_analysis(dirpath, pattern, spectrum_span = 2)
Ns_SpectralAnalysis_All_architectures <- result

ggsave(filename = "SI_1.3.NS_SpectralAnalysis_All_architectures.jpg", Ns_SpectralAnalysis_All_architectures, path = "../OutputFigures.dir/SupplementalFigures.dir", width = 40, height = 15, units = "in", dpi = 300, limitsize = FALSE)

Ns_SpectralAnalysis_All_architectures
```

# 2. Constant model

## 2.1. Allele frequency all parameters for a single replicate

```{r, warning=FALSE, echo=FALSE, message=FALSE}
rm(list = ls())
source("AlleleFrequencyPlotCode.R")
dirpath <- "../../Output.dir/CS.dir/"
pattern <- pattern <- "^genome1_n(10|70|300)(?:\\D|$)" 
result <- process_files(dirpath, pattern, "loci")

plots <- result$plots
```

### 2.1.1. Monogenic

```{r, fig.height = 20, fig.width = 30, echo=FALSE}
#| label: CS_Single_Locus_AllReplicates
#| fig-cap: "SI 2.1.1. Single locus 30 replicates allele frequency dynamics for constant selection model, showing all parameter interactions. The highlighted line indicates the mean allele frequency for each generation."
#| fig-pos: "H"
#| 
#####################################################
######### data processing function ##################
#####################################################

process_files <- function(dirpath, pattern) {
  
  files <- list.files(dirpath, pattern = pattern, full.names = TRUE)
  

  dataframes <- list()
  
  # Extracting parameters
  
  for (file in files) {
    fname <- basename(file) 
    H <- as.numeric(sub(".*_H(0\\.\\d+).*", "\\1", fname))
    loci <- as.numeric( sub(".*_n(\\d+)_.*", "\\1", fname))
    SD <- as.numeric(sub(".*SD(\\d+).*", "\\1", fname))
    replicate <- as.numeric(sub(".*genome(\\d+)_.*", "\\1", fname))
    
    data <- read.csv(file, header = TRUE) %>% 
      mutate(
        H         = H,
        loci      = loci,
        SD        = SD,
        replicate = as.factor(replicate))

    dataframes[[fname]] <- data
  }
  
  # Combine all dataframes into one 
  
  combined_data <- bind_rows(dataframes)
  
  return(combined_data)
}

########################################################################
######### Process the files to get combined data and make a plot ######
#######################################################################

dirpath <- "../../Output.dir/CS.dir/"
pattern <- "^genome\\d+_n(1)_H0\\.(1|5|8)(SD(1|2|4))?(Gen(10|20|30))?\\.csv$"

combined_data <- process_files(dirpath, pattern)

CS_SingleLocusAF <- combined_data %>%
  mutate(
    h2_sd = paste0("SD = ", SD, ": ",  "h\u00B2 = ", H)
  ) %>% 
  ggplot(aes(x = Generation, y = Frequency)) +
  geom_line(aes(group = replicate),
            color = "gray50", 
            alpha = 0.8, 
            size = 0.5) +
  stat_summary(fun = mean,
               aes(group = 1), 
               geom = "line", 
               color = "red3", 
               alpha = 1, 
               size = 2) +
  facet_wrap(~ h2_sd, ncol = 3) +
  labs(
    x = "Generation",
    y = "Frequency"
  ) +
  theme_bw() +
  theme(
    text = element_text(family = "sans"),
    legend.position = "none",
    axis.text.x = element_text(face = "bold", size = 40, angle = 35,
                               hjust = 1, margin = margin(t = 10)),
    axis.text.y = element_text(face = "bold", size = 40, angle = 15,
                               margin = margin(r = 10)),
    axis.line   = element_line(size = 2),
    plot.title  = element_text(hjust = 0.01, face = "bold", size = 40),
    axis.title.x = element_text(size = 40, face = "bold",
                                margin = margin(t = 10)),
    axis.title.y = element_text(size = 40, face = "bold",
                                margin = margin(r = 10)),
    strip.text = element_text(size = 40, face = "bold"),
    panel.spacing = unit(5, "lines"),
    panel.grid = element_blank()
  )

CS_SingleLocusAF

ggsave(filename = "SI_2.1.1.CS_SingleLocusAF.jpg", CS_SingleLocusAF, path = "../OutputFigures.dir/SupplementalFigures.dir", width = 30, height = 20, units = "in", dpi = 300, limitsize = FALSE)
```

### 2.1.2. Oligogenic

```{r, fig.height = 40, fig.width = 50, echo=FALSE}
#| label: Constant_Olig_AF
#| fig-cap: "SI 2.1.2. Allele frequency dynamics for all parameter combinations from a single replicate, constant selection model. Each line  represents the frequency trajectory for a locus from oligogenic trait (10 loci)."
#| fig-pos: "H"

Constant_Olig_AF <- plots[[10]] +
  ggtitle("AF: Constantant Oligogenic") +
  theme(
    plot.title = element_text(
      hjust = 0.5,         
      size = 70, 
      color = "firebrick4",
      margin = margin(b = 40) 
    )
  )

print(Constant_Olig_AF)

ggsave(filename = "SI_2.1.2.Constant_Olig_AF.jpg", Constant_Olig_AF, path = "../OutputFigures.dir/SupplementalFigures.dir", width = 50, height = 40, units = "in", dpi = 300, limitsize = FALSE)
```

### 2.1.3. Polygenic 70 loci

```{r, fig.height = 40, fig.width = 50, echo=FALSE}
#| label: Constant_Poly_70_AF
#| fig-cap: "SI 2.1.3: Allele frequency dynamics for all parameter combinations from a single replicate, constant selection model. Each line  represents the frequency trajectory for a locus of 30 sampled loci from polygenic trait (70 loci)."
#| fig-pos: "H"

Constant_Poly_70_AF <- plots[[70]] +
  ggtitle("AF: Constantant Polygenic (70 loci)") +
  theme(
    plot.title = element_text(
      hjust = 0.5,         
      size = 70, 
      color = "firebrick4",
      margin = margin(b = 40) 
    )
  )
print(Constant_Poly_70_AF)

ggsave(filename = "SI_2.1.3.Constant_Poly_70_AF.jpg", Constant_Poly_70_AF, path = "../OutputFigures.dir/SupplementalFigures.dir", width = 50, height = 40, units = "in", dpi = 300, limitsize = FALSE)
```

### 2.1.4. Polygenic 300 loci

```{r, fig.height = 40, fig.width = 50, echo=FALSE}
#| label: Constant_Poly_300_AF
#| fig-cap: "SI 2.1.4. Allele frequency dynamics for all parameter combinations from a single replicate, constant selection model. Each line  represents the frequency trajectory for a locus of 30 sampled loci from polygenic trait (300 loci)."
#| fig-pos: "H"

Constant_Poly_300_AF <- plots[[300]] +
  ggtitle("AF: Constantant Polygenic (300 loci)") +
  theme(
    plot.title = element_text(
      hjust = 0.5,         
      size = 70, 
      color = "firebrick4",
      margin = margin(b = 40) 
    )
  )

print(Constant_Poly_300_AF)


ggsave(filename = "SI_2.1.4.Constant_Poly_300_AF.jpg", Constant_Poly_300_AF, path = "../OutputFigures.dir/SupplementalFigures.dir", width = 50, height = 40, units = "in", dpi = 300, limitsize = FALSE)
```

## 2.2. Phenotypes all params

```{r, echo=FALSE}
source("PhenotypePlotCode.R")
dirpath <- "../../Output.dir/CS.dir/"
pattern <- "^MeanPhenotypes"
result <- process_files(dirpath, pattern, "loci")
plots <- result$plots
```

### 2.2.1. Polygenic 70

```{r, fig.height = 40, fig.width = 50, echo=FALSE}
#| label: Constant_Poly_70_Pheno
#| fig-cap: "SI 2.2.1. Polygenic (70 loci) mean population phenotypic plot across 30 replicates (each line represents a single replicate) for constant selection, showing parameter interactions."
#| fig-pos: "H"

Constant_Poly_70_Pheno <- plots[[70]] +
  ggtitle("Phenotypes: Constantant Polygenic (70 loci)") +
  theme(
    plot.title = element_text(
      hjust = 0.5,         
      size = 70, 
      color = "firebrick4",
      margin = margin(b = 40) 
    )
  )
print(Constant_Poly_70_Pheno)


ggsave(filename = "SI_6.2.1.Constant_Poly_70_Pheno.jpg", Constant_Poly_70_Pheno, path = "../OutputFigures.dir/SupplementalFigures.dir", width = 50, height = 40, units = "in", dpi = 300, limitsize = FALSE)
```

### 2.2.2. Polygenic 100

```{r, fig.height = 40, fig.width = 50, echo=FALSE}
#| label: Constant_Poly_100_Pheno
#| fig-cap: "SI 2.2.2 Polygenic (100 loci) mean population phenotypic plot across 30 replicates (each line represents a single replicate) for constant selection, showing parameter interactions."
#| fig-pos: "H"

Constant_Poly_100_Pheno <- plots[[100]] +
  ggtitle("Phenotypes: Constantant Polygenic (100 loci)") +
  theme(
    plot.title = element_text(
      hjust = 0.5,         
      size = 70, 
      color = "firebrick4",
      margin = margin(b = 40) 
    )
  )
print(Constant_Poly_100_Pheno)


ggsave(filename = "SI_2.2.2.Constant_Poly_100_Pheno.jpg", Constant_Poly_100_Pheno, path = "../OutputFigures.dir/SupplementalFigures.dir", width = 50, height = 40, units = "in", dpi = 300, limitsize = FALSE)
```

### 2.2.3. Polygenic 300

```{r, fig.height = 40, fig.width = 50, echo=FALSE}
#| label: Constant_Poly_300_Pheno
#| fig-cap: "SI 2.2.3. Polygenic (300 loci) mean population phenotypic plot across 30 replicates (each line represents a single replicate) for constant selection, showing parameter interactions."
#| fig-pos: "H"
Constant_Poly_300_Pheno <- plots[[300]] +
  ggtitle("Phenotypes: Constantant Polygenic (300 loci)") +
  theme(
    plot.title = element_text(
      hjust = 0.5,         
      size = 70, 
      color = "firebrick4",
      margin = margin(b = 40) 
    )
  )
print(Constant_Poly_300_Pheno)


ggsave(filename = "SI_2.2.3.Constant_Poly_300_Pheno.jpg", Constant_Poly_300_Pheno, path = "../OutputFigures.dir/SupplementalFigures.dir", width = 50, height = 40, units = "in", dpi = 300, limitsize = FALSE)
```

## 2.3. Spectral analysis for all parameters

```{r, echo=FALSE}
run_fft_analysis <- function(folder_path, pattern, spectrum_span = 2) {
  library(parallel)
  library(doParallel)
  library(foreach)
  library(dplyr)
  library(ggplot2)
  library(cowplot)
  theme_set(theme_classic())
  mythemes <- theme_bw() +
    theme(
      text            = element_text(family = "sans"), 
      legend.position = "none",
      axis.text.x     = element_text(face = "bold", size = 40, angle = 25, 
                                       margin = margin(t = 20), hjust = 1),
      axis.text.y     = element_text(face = "bold", size = 40, angle = 15, 
                                       margin = margin(r = 10)),
      axis.line       = element_line(size = 3),
      plot.title      = element_text(hjust = 0.01, face = "bold", size = 80, 
                                       margin = margin(b = 1, unit = "lines")),
      plot.margin     = unit(c(5, 1, 1, 1), "lines"),
      axis.title.x    = element_text(size = 40, face = "bold", margin = margin(t = 30)),
      axis.title.y    = element_text(size = 40, face = "bold", margin = margin(r = 35)),
      strip.text      = element_text(size = 40, face = "bold"),
      panel.spacing   = unit(5, "lines"),
      panel.grid      = element_blank()
    )
  
  file_list <- list.files(path = folder_path, pattern = pattern, full.names = TRUE)
  
  if (length(file_list) == 0) {
    stop("No files found with the given pattern.")
  }
  # Create a data frame with filenames and extract parameters
  
  files_df <- data.frame(file_name = file_list) %>%
    mutate(
      base_name = basename(file_name),  
      n = ifelse(
         grepl("_n\\d+", base_name),
         as.numeric(sub(".*_n(\\d+).*", "\\1", base_name)),
         NA_real_
           ),
      replct <- as.numeric(sub(".*genome(\\d+)_.*", "\\1", base_name)),
      H = ifelse(
         grepl("_H[0-9]+\\.?[0-9]*", base_name),
         as.numeric(sub(".*_H([0-9]+\\.?[0-9]*).*", "\\1", base_name)),
         NA_real_
        ),
      SD = ifelse(
        grepl("SD[0-9]+(\\.[0-9]+)?", base_name),
        as.numeric(sub(".*SD([0-9]+(?:\\.[0-9]+)?).*", "\\1", base_name)),
        NA_real_
        ),
      Gen = ifelse(
        grepl("Gen\\d+", base_name),
        as.numeric(sub(".*Gen(\\d+).*", "\\1", base_name)),
        NA_real_
        ),
      Genome = case_when(
        n == "1" ~ "Monogenic",
        n == "10" ~ "Oligogenic",
        n == "70" ~ "Polygenic 70",
        n == "100" ~ "Polygenic 100",
        n == "300" ~ "Polygenic 300",
        TRUE ~ "Unknown"
      )
    ) %>%
    mutate(
      n = as.numeric(n),
      H = as.numeric(H),
      SD = as.numeric(SD),
      Gen = as.numeric(Gen),
      param_combination = paste0("n_", n, "_H", H, 
                                 ifelse(!is.na(SD), paste0("_SD", SD), ""), 
                                 ifelse(!is.na(Gen), paste0("_Gen", Gen), ""))
    )
  
  # Set up parallel backend
  
  num_cores <- detectCores()
  cl <- makeCluster(64)
  registerDoParallel(cl)
  
  # Read and combine data from all replicate files in parallel
  combined_data_list <- foreach(i = seq_along(files_df$file_name), .packages = c("dplyr")) %dopar% {
    file <- files_df$file_name[i]
    params <- files_df[i, ]
    df <- read.csv(file)
    data <- df %>%
      mutate(
        allele_id = as.factor(Position),
        generation = as.numeric(Generation),
        allele_frequency = Frequency,
        file = params$base_name,
        replct = params$replct,
        n = params$n,
        H = params$H,
        SD = params$SD,
        Gen = params$Gen,
        Genome = params$Genome,
        param_combination = params$param_combination
      ) %>%
      dplyr::select(allele_id, generation, allele_frequency, replct, n, H, SD, Gen, Genome, param_combination)
    data
  }
  combined_data <- bind_rows(combined_data_list)

  filtered_data <- combined_data 
  
  # Calculating the mean allele frequency for each grouping
  mean_allele_data <- filtered_data %>%
    group_by(generation, n, replct, H, SD, Gen, Genome, param_combination) %>%
    summarize(mean_allele_frequency = mean(allele_frequency), .groups = "drop")
  
  # Creating time series objects
  ts_data_list <- mean_allele_data %>%
    group_by(n, replct, H, SD, Gen, Genome, param_combination) %>%
    summarize(ts_data = list(ts(mean_allele_frequency, start = min(generation), frequency = 1)), .groups = 'drop')
  
  # Computing spectral density estimates in parallel
  spec_results_list <- foreach(i = 1:nrow(ts_data_list), .packages = c("stats")) %dopar% {
    ts_data <- ts_data_list$ts_data[[i]]
    spectrum(ts_data, spans = spectrum_span, plot = FALSE)
  }
  
  # Preparing data for plotting
  plot_data_list <- foreach(i = seq_along(spec_results_list), .packages = c("dplyr")) %dopar% {
    spec_result <- spec_results_list[[i]]
    params <- ts_data_list[i, ]
    period <- 1 / spec_result$freq
    data.frame(
      Period = period,
      Spectrum = spec_result$spec,
      n = params$n,
      replct = params$replct,
      H = params$H,
      SD = params$SD,
      Gen = params$Gen,
      Genome = params$Genome,
      param_combination = params$param_combination
    )
  }
  
  stopCluster(cl)
  

  plot_data <- bind_rows(plot_data_list)
  
  plot_data <- plot_data %>%
    group_by(param_combination) %>%
    mutate(threshold = case_when(
      Gen == 10 ~ 40,
      Gen == 20 ~ 50,
      Gen == 30 ~ 80,
      TRUE ~ 80
    )) %>%
    filter(Period < threshold) %>%
    ungroup() %>%
    mutate(
      Genome_Gen = paste0("Genome = ", Genome, " Gen = ", Gen),
      h2_sd = paste("H = ", H," ", "\u0394\ = ", SD, sep = ""), 
      #H_label = paste0("H = ", H),
      #SD_label = ifelse(!is.na(SD), paste0("SD = ", SD), "No SD"),
      Gen_label = ifelse(!is.na(Gen), paste0("Gen = ", Gen), "No Gen"),
      n_label = paste0("n_", n)
    )
  
  fft_plots <- list()
  
  uni_genomegen <- unique(plot_data$Genome_Gen)
  
  for(genomegen in uni_genomegen){
    myplot_data <- plot_data %>% filter(Genome_Gen == genomegen)

  fft_plots[[genomegen]] <- ggplot(myplot_data, aes(x = Period, y = Spectrum, color = factor(replct), group = factor(replct))) +
    geom_line(size = 1.1) +
    facet_wrap( ~ h2_sd, scales = "free") +
    labs(x = "Period (Generations)", y = "Spectral Density") +
    mythemes
  }
  
  return(fft_plots)
}

```

```{r, fig.height = 12, fig.width = 8, echo=FALSE}
dirpath <- "../../Output.dir/CS.dir/"
pattern <- "^genome"
result <- run_fft_analysis(dirpath, pattern, spectrum_span = 2)

```

### 2.3.1. Monogenic

```{r, fig.height = 40, fig.width = 50, echo=FALSE}
#| label: Constant_Mono_SA
#| fig-cap: "SI 2.3.1. Spectral density across 30 replicates for monogenic trait (single locus) with constant selection model, all parameter combinations. The density plots do not show any peak, and indication that there is no periodicity."
#| fig-pos: "H"

Constant_Mono_SA <- result[[1]] +
  ggtitle("Spectral Density: Constantant Monogenic") +
  theme(
    plot.title = element_text(
      hjust = 0.5,         
      size = 70, 
      color = "firebrick4",
      margin = margin(b = 40) 
    )
  )

print(Constant_Mono_SA)


ggsave(filename = "SI_2.3.1.Constant_Mono_SA.jpg", Constant_Mono_SA, path = "../OutputFigures.dir/SupplementalFigures.dir", width = 50, height = 40, units = "in", dpi = 300, limitsize = FALSE)
```

### 2.3.2. Polygenic 300

```{r, fig.height = 40, fig.width = 50, echo=FALSE}
#| label: Constant_Poly_300_SA
#| fig-cap: "SI 2.3.2. Spectral density across 30 replicates for polygenic trait (300 loci) with constant selection model, all parameter combinations. The density plots do not show any peak, and indication that there is no periodicity."
#| fig-pos: "H"

Constant_Poly_300_SA <- result[[5]] +
  ggtitle("Spectral Density: Constantant Polygenic (300 loci)") +
  theme(
    plot.title = element_text(
      hjust = 0.5,         
      size = 70, 
      color = "firebrick4",
      margin = margin(b = 40) 
    )
  )

print(Constant_Poly_300_SA)


ggsave(filename = "SI_2.3.2.Constant_Poly_300_SA.jpg", Constant_Poly_300_SA, path = "../OutputFigures.dir/SupplementalFigures.dir", width = 50, height = 40, units = "in", dpi = 300, limitsize = FALSE)
```



# 3. Long-term runs with mutation rate

```{r, echo=FALSE, message=FALSE}

#| label: LongTermRunsWithMutatioRate_10Ne

rm(list = ls())
library(dplyr)
library(tidyr)
library(ggplot2)
library(readr)
library(future)
library(furrr)

###############################################################################
############################ Settings ##########################################
###############################################################################

base_dir <- "/home/etb68/Mylab/evogen-sims/FluctSelectionModels.dir/Output.dir/LongRuns.dir"

plot_dir <- "/home/etb68/Mylab/evogen-sims/FluctSelectionModels.dir/WritingFigures.dir/OutputFigures.dir/PolymorphismMaintenance_plt.dir"
dir.create(plot_dir, recursive = TRUE, showWarnings = FALSE)

replicates <- 1:5

target_n   <- 100
target_H   <- c(0.1, 0.8)
target_SD  <- c(1, 4)
target_Gen <- c(10, 30)

n_workers <- 32
plan(multisession, workers = n_workers)

required_cols <- c("Generation", "Position", "Effect", "Origin", "Frequency")

###############################################################################
############################ Model folders #####################################
###############################################################################

folders <- tibble::tribble(
  ~folder,            ~selection,  ~mutation,
  "NS_Mut_Ext.dir",   "Null",      "Mutation",
  "NS_Ext.dir",       "Null",      "No mutation",
  "FS_Mut_Ext.dir",   "Seasonal",  "Mutation",
  "FS_Ext.dir",       "Seasonal",  "No mutation"
)

###############################################################################
############################ File list #########################################
###############################################################################

seasonal_files <- expand_grid(
  replicate = replicates,
  n = target_n,
  H = target_H,
  SD = target_SD,
  Gen = target_Gen
) %>%
  crossing(folders %>% filter(selection == "Seasonal")) %>%
  mutate(
    filename = paste0(
      "genome", replicate,
      "_n", n,
      "_H", H,
      "SD", SD,
      "Gen", Gen,
      ".csv"
    )
  )

null_files <- expand_grid(
  replicate = replicates,
  n = target_n,
  H = target_H
) %>%
  crossing(folders %>% filter(selection == "Null")) %>%
  mutate(
    SD = NA_real_,
    Gen = NA_real_,
    filename = paste0(
      "genome", replicate,
      "_n", n,
      "_H", H,
      ".csv"
    )
  )

files <- bind_rows(seasonal_files, null_files) %>%
  mutate(
    file = file.path(base_dir, folder, filename)
  ) %>%
  filter(file.exists(file)) %>%
  select(
    file, filename, replicate, n, H, SD, Gen, selection, mutation
  )

if (nrow(files) == 0) {
  stop("No target files were found. Check base_dir and parameter values.")
}

###############################################################################
############################ Helper functions ##################################
###############################################################################

read_sim_file <- function(file) {
  
  df <- tryCatch(
    read_csv(file, show_col_types = FALSE, progress = FALSE),
    error = function(e) {
      warning("Failed to read: ", file, " (", conditionMessage(e), ")")
      return(NULL)
    }
  )
  
  if (is.null(df) || nrow(df) == 0) {
    return(NULL)
  }
  
  missing_cols <- setdiff(required_cols, names(df))
  
  if (length(missing_cols) > 0) {
    warning(
      "Skipping ", file,
      " - missing columns: ",
      paste(missing_cols, collapse = ", ")
    )
    return(NULL)
  }
  
  df %>%
    mutate(
      Allele = paste(Position, Effect, Origin, sep = "_"),
      fixed_here = !is.na(Frequency) & Frequency == 1,
      lost_here = !is.na(Frequency) & Frequency == 0,
      segregating_here = !is.na(Frequency) & Frequency > 0 & Frequency < 1
    )
}

safe_mean <- function(x) {
  x <- x[is.finite(x)]
  if (length(x) == 0) return(NA_real_)
  mean(x)
}

###############################################################################
############################ Main calculation ##################################
###############################################################################

calculate_metrics <- function(file, info) {
  
  df <- read_sim_file(file)
  
  if (is.null(df)) {
    return(NULL)
  }
  
  generations <- sort(unique(df$Generation))
  first_generation <- min(generations)
  max_generation <- max(generations)
  
  first_cohort <- df %>%
    filter(Generation == first_generation, segregating_here) %>%
    distinct(Allele) %>%
    pull(Allele)
  
  if (length(first_cohort) == 0) {
    warning("No segregating first-cohort QTLs found in: ", file)
    return(NULL)
  }
  
  first_cohort_fates <- df %>%
    filter(Allele %in% first_cohort) %>%
    group_by(Allele) %>%
    summarise(
      last_seen = max(Generation),
      
      first_fixed = if (any(fixed_here)) {
        min(Generation[fixed_here])
      } else {
        NA_real_
      },
      
      first_zero = if (any(lost_here)) {
        min(Generation[lost_here])
      } else {
        NA_real_
      },
      
      .groups = "drop"
    ) %>%
    rowwise() %>%
    mutate(
      inferred_loss = if (
        is.na(first_fixed) &&
        last_seen < max_generation
      ) {
        generations[generations > last_seen][1]
      } else {
        NA_real_
      },
      
      first_lost = {
        losses <- c(first_zero, inferred_loss)
        losses <- losses[!is.na(losses)]
        if (length(losses) == 0) NA_real_ else min(losses)
      },
      
      absorbed_generation = {
        fates <- c(first_fixed, first_lost)
        fates <- fates[!is.na(fates)]
        if (length(fates) == 0) NA_real_ else min(fates)
      }
    ) %>%
    ungroup()
  
  total_first_cohort <- n_distinct(first_cohort_fates$Allele)
  
  first_cohort_metrics <- tibble(Generation = generations) %>%
    rowwise() %>%
    mutate(
      first_cohort_fixed_or_lost = sum(
        !is.na(first_cohort_fates$absorbed_generation) &
          first_cohort_fates$absorbed_generation <= Generation
      ),
      
      first_cohort_fixation_loss_rate =
        first_cohort_fixed_or_lost / total_first_cohort
    ) %>%
    ungroup() %>%
    arrange(Generation) %>%
    mutate(
      first_cohort_fixation_loss_rate =
        cummax(first_cohort_fixation_loss_rate)
    )
  
  segregating_metrics <- df %>%
    group_by(Generation) %>%
    summarise(
      segregating_qtl_alleles = n_distinct(Allele[segregating_here]),
      .groups = "drop"
    )
  
  first_cohort_metrics %>%
    left_join(segregating_metrics, by = "Generation") %>%
    mutate(
      segregating_qtl_alleles = replace_na(segregating_qtl_alleles, 0L),
      filename = info$filename,
      replicate = info$replicate,
      n = info$n,
      H = info$H,
      SD = info$SD,
      Gen = info$Gen,
      selection = info$selection,
      mutation = info$mutation
    )
}

###############################################################################
############################ Run analysis ######################################
###############################################################################

qtl_metrics <- files %>%
  mutate(row_id = row_number()) %>%
  split(.$row_id) %>%
  future_map_dfr(
    function(info) {
      calculate_metrics(
        file = info$file,
        info = info
      )
    },
    .options = furrr_options(seed = TRUE)
  )

plan(sequential)

if (nrow(qtl_metrics) == 0) {
  stop("No QTL metrics were returned.")
}

###############################################################################
############################ Duplicate null for facets #########################
###############################################################################

sdgen_grid <- expand_grid(
  SD = target_SD,
  Gen = target_Gen
)

qtl_disp <- bind_rows(
  qtl_metrics %>%
    filter(selection == "Seasonal"),
  
  qtl_metrics %>%
    filter(selection == "Null") %>%
    select(-SD, -Gen) %>%
    crossing(sdgen_grid)
)

###############################################################################
############################ Labels ############################################
###############################################################################

qtl_disp <- qtl_disp %>%
  mutate(
    model = case_when(
      selection == "Null" & mutation == "No mutation" ~ "Null + no mutation",
      selection == "Null" & mutation == "Mutation" ~ "Null + mutation",
      selection == "Seasonal" & mutation == "No mutation" ~ "Seasonal + no mutation",
      selection == "Seasonal" & mutation == "Mutation" ~ "Seasonal + mutation"
    ),
    
    model = factor(
      model,
      levels = c(
        "Null + mutation",
        "Null + no mutation",
        "Seasonal + mutation",
        "Seasonal + no mutation"
      )
    ),
    
    H_label = paste0("H = ", H),
    param_label = paste0("\u0394 = ", SD, ": Gen = ", Gen),
    replicate_label = paste0("Replicate = ", replicate)
  )

###############################################################################
############################ Mean across replicates ############################
###############################################################################

qtl_mean <- qtl_disp %>%
  group_by(
    Generation,
    H, SD, Gen,
    H_label, param_label,
    selection, mutation, model
  ) %>%
  summarise(
    mean_first_cohort_fixation_loss_rate =
      safe_mean(first_cohort_fixation_loss_rate),
    
    mean_segregating_qtl_alleles =
      safe_mean(segregating_qtl_alleles),
    
    n_replicates =
      sum(is.finite(first_cohort_fixation_loss_rate)),
    
    .groups = "drop"
  ) %>%
  filter(
    is.finite(mean_first_cohort_fixation_loss_rate),
    is.finite(mean_segregating_qtl_alleles)
  )

###############################################################################
############################ Theme #############################################
###############################################################################

theme_qtl <- theme_classic(base_size = 14) +
  theme(
    axis.text = element_text(color = "black"),
    axis.title = element_text(face = "bold", size = 15),
    plot.title = element_text(face = "bold", hjust = 0, size = 18),
    strip.text = element_text(face = "bold", size = 10),
    legend.title = element_text(face = "bold"),
    legend.position = "bottom",
    panel.spacing = unit(0.9, "lines")
  )

```

### 3.1. The cumulative fixation/loss rate of the initial QTL with and without recurrent mutation

```{r, fig.width=20, fig.height=10, echo=FALSE, message=FALSE}
#| label: IntialQTLs_MeanFixationRate_AcrossReplicate_ByReplicate
#| fig-cap: "SI 3.1. The cumulative fixation/loss rate of the initial QTL (new mutation excluded) comparison for null and instantaneous fluctuating selection models for a polygenic trait of 100 loci, with and without recurrent mutation, across parameter combinations. The top panel shows the average across 5 replicates, while the bottom panel shows the rate per replicate. In some low-heritability parameter combinations, fluctuating selection seems to exhibit a lower fixation rate than the null model during earlier generations (< 50,000 generations); however, this pattern is not consistent across all parameter combinations, and trajectories converge later in the simulation."
#| fig-pos: "H"
###############################################################################
############################ Plot 1 ############################################
## Mean initial QTL fixation/loss rate across replicates
###############################################################################

initial_QTL_fixation_loss_rate <- ggplot(
  qtl_mean,
  aes(
    x = Generation,
    y = mean_first_cohort_fixation_loss_rate,
    color = model,
    group = model
  )
) +
  geom_line(linewidth = 1.1, alpha = 0.7) +
  facet_grid(H_label ~ param_label) +
  coord_cartesian(ylim = c(0, 1)) +
  scale_y_continuous(breaks = seq(0, 1, 0.25)) +
  labs(
    x = "Generation",
    y = "Initial QTL fixation/loss rate",
    color = "Model",
    title = "Initial QTL fixation/loss across models"
  ) +
  theme_qtl

initial_QTL_fixation_loss_rate


###############################################################################
############################ Plot 2 ############################################
## Initial QTL fixation/loss rate by replicate
###############################################################################

initial_QTL_fixation_loss_rate_by_replicate <- ggplot(
  qtl_disp,
  aes(
    x = Generation,
    y = first_cohort_fixation_loss_rate,
    color = model,
    group = model
  )
) +
  geom_line(linewidth = 0.9, alpha = 0.7) +
  facet_grid(
    replicate_label ~ paste(param_label, H_label, sep = " : ")
  ) +
  coord_cartesian(ylim = c(0, 1)) +
  scale_y_continuous(breaks = seq(0, 1, 0.5)) +
  labs(
    x = "Generation",
    y = "Initial QTL fixation/loss rate",
    color = "Model",
    title = "Initial QTL fixation/loss by replicate"
  ) +
  theme_qtl +
  theme(
    strip.text = element_text(face = "bold", size = 8)
  )

initial_QTL_fixation_loss_rate_by_replicate


ggsave(filename = "SI_3.1.initial_QTL_fixation_loss_rate_by_replicate.jpg", initial_QTL_fixation_loss_rate_by_replicate, path = "../OutputFigures.dir/SupplementalFigures.dir", width = 20, height = 10, units = "in", dpi = 300, limitsize = FALSE)


```

### 3.2. The average number of segregating sites, comparing null and instantaneous fluctuating selection models

```{r, fig.width=20, fig.height=10, echo=FALSE, message=FALSE}
#| label: NumberOfSegregatingQTLs_MeanFixationRate_AcrossReplicate_ByReplicate
#| fig-cap: "SI 3.2. The average number of segregating sites, comparing null and instantaneous fluctuating selection models for a polygenic trait with 100 loci, with and without recurrent mutation, across parameter combinations. The top panel shows the average number of segregating sites across generations, including new mutations, while the bottom panel shows per replicate changes. Likewise, in some low-heritability parameter combinations, fluctuating selection seems to maintain more segregating variation than the null model during earlier generations (< 50,000 generations), but this pattern is not consistent across all parameter combinations, as trajectories converge later in the simulation. "
#| fig-pos: "H"
###############################################################################
############################ Plot 3 ############################################
## Mean number of segregating QTL alleles across replicates
###############################################################################

segregating_qtl_alleles_all_models <- ggplot(
  qtl_mean,
  aes(
    x = Generation,
    y = mean_segregating_qtl_alleles,
    color = model,
    group = model
  )
) +
  geom_line(linewidth = 1.1, alpha = 0.7) +
  facet_grid(H_label ~ param_label) +
  labs(
    x = "Generation",
    y = "Number of segregating QTL alleles",
    color = "Model",
    title = "Segregating QTL alleles across models"
  ) +
  theme_qtl

segregating_qtl_alleles_all_models

###############################################################################
############################ Plot 4 ############################################
## Number of segregating QTL alleles by replicate
###############################################################################

segregating_qtl_alleles_by_replicate <- ggplot(
  qtl_disp,
  aes(
    x = Generation,
    y = segregating_qtl_alleles,
    color = model,
    group = model
  )
) +
  geom_line(linewidth = 0.9, alpha = 0.7) +
  facet_grid(
    replicate_label ~ paste(param_label, H_label, sep = " : ")
  ) +
  labs(
    x = "Generation",
    y = "Number of segregating QTL alleles",
    color = "Model",
    title = "Segregating QTL alleles by replicate"
  ) +
  theme_qtl +
  theme(
    strip.text = element_text(face = "bold", size = 8)
  )

segregating_qtl_alleles_by_replicate

ggsave(filename = "SI_3.2.segregating_qtl_alleles_by_replicate.jpg", segregating_qtl_alleles_by_replicate, path = "../OutputFigures.dir/SupplementalFigures.dir", width = 20, height = 10, units = "in", dpi = 300, limitsize = FALSE)

```


```{r, echo=FALSE, message=FALSE}
#| label: saving all the plots
###############################################################################
############################ Save plots ########################################
###############################################################################

# ggsave(
#   file.path(plot_dir, "initial_QTL_fixation_loss_rate.pdf"),
#   initial_QTL_fixation_loss_rate,
#   width = 20,
#   height = 8,
#   limitsize = FALSE,
#   device = cairo_pdf
# )
# 
# ggsave(
#   file.path(plot_dir, "initial_QTL_fixation_loss_rate.png"),
#   initial_QTL_fixation_loss_rate,
#   width = 20,
#   height = 8,
#   limitsize = FALSE
# )
# 
# ggsave(
#   file.path(plot_dir, "segregating_qtl_alleles_all_models.pdf"),
#   segregating_qtl_alleles_all_models,
#   width = 20,
#   height = 8,
#   limitsize = FALSE,
#   device = cairo_pdf
# )
# 
# ggsave(
#   file.path(plot_dir, "segregating_qtl_alleles_all_models.png"),
#   segregating_qtl_alleles_all_models,
#   width = 20,
#   height = 8,
#   limitsize = FALSE
# )
# 
# ggsave(
#   file.path(plot_dir, "initial_QTL_fixation_loss_rate_by_replicate.pdf"),
#   initial_QTL_fixation_loss_rate_by_replicate,
#   width = 25,
#   height = 18,
#   limitsize = FALSE,
#   device = cairo_pdf
# )
# 
# ggsave(
#   file.path(plot_dir, "initial_QTL_fixation_loss_rate_by_replicate.png"),
#   initial_QTL_fixation_loss_rate_by_replicate,
#   width = 25,
#   height = 18,
#   limitsize = FALSE
# )
# 
# ggsave(
#   file.path(plot_dir, "segregating_qtl_alleles_by_replicate.pdf"),
#   segregating_qtl_alleles_by_replicate,
#   width = 25,
#   height = 18,
#   limitsize = FALSE,
#   device = cairo_pdf
# )
# 
# ggsave(
#   file.path(plot_dir, "segregating_qtl_alleles_by_replicate.png"),
#   segregating_qtl_alleles_by_replicate,
#   width = 25,
#   height = 18,
#   limitsize = FALSE
# )
```

# 4. Instantaneous model

## 4.1. Allele frequency all parameters

```{r, warning=FALSE, echo=FALSE, fig.width = 40, fig.height = 55, message=FALSE}
rm(list = ls())
source("AlleleFrequencyPlotCode.R")
dirpath <- "../../Output.dir/LinFS.dir/"
pattern <- "^genome1_n(10|70|300)(?:\\D|$)"
result <- process_files(dirpath, pattern, "loci_gen")
#
instantplots_AF <- result$plots
```

### 4.1.1. Monogenic

```{r, warning=FALSE, fig.width = 20, fig.height = 30, echo=FALSE, message=FALSE}
#| label: Single_Locus_AllReplicates
#| fig-cap: "SI 4.1.1. Single locus (30 replicates) allele frequency dynamics for instantaneous selection, showing all parameter interactions. The highlighted line indicates the mean allele frequency for each generation across replicates."
#| fig-pos: "H"

library(dplyr)
library(ggplot2)

#####################################################
######### data processing function ##################
#####################################################

process_files <- function(dirpath, pattern) {
  
  files <- list.files(dirpath, pattern = pattern, full.names = TRUE)
  

  dataframes <- list()
  
  # Extracting parameters
  
  for (file in files) {
    fname <- basename(file) 
    H <- as.numeric(sub(".*_H(0\\.\\d+).*", "\\1", fname))
    loci <- as.numeric( sub(".*_n(\\d+)_.*", "\\1", fname))
    SD <- as.numeric(sub(".*SD(\\d+).*", "\\1", fname))
    Gen <- as.numeric(sub(".*Gen(\\d+).*", "\\1", fname))
    replicate <- as.numeric(sub(".*genome(\\d+)_.*", "\\1", fname))
    
    data <- read.csv(file, header = TRUE) %>% 
      mutate(
        H         = H,
        loci      = loci,
        SD        = SD,
        Gen       = Gen,
        replicate = as.factor(replicate),
        h2_sd     = paste0("h2 = ", H, " sd = ", SD),
        loci_gen  = paste0("loci = ", loci, " gen = ", Gen)
      )
    
    dataframes[[fname]] <- data
  }
  
  # Combine all dataframes into one 
  
  combined_data <- bind_rows(dataframes)
  
  return(combined_data)
}

########################################################################
######### Process the files to get combined data and make a plot ######
#######################################################################

dirpath <- "../../Output.dir/LinFS.dir/"
pattern <- "^genome\\d+_n(1)_H0\\.(1|5|8)(SD(1|2|4))?(Gen(10|20|30))?\\.csv$"

combined_data <- process_files(dirpath, pattern)

SingleLocusAF <- combined_data %>%
  mutate(
    H_SD_Gen = paste0("h\u00B2 = ", H, "\u0394\ = ", SD, " Gen = ", Gen)
  ) %>% 
  ggplot(aes(x = Generation, y = Frequency)) +
  geom_line(aes(group = replicate),
            color = "gray50", 
            alpha = 0.8, 
            size = 0.5) +
  # geom_hline(yintercept = 0.5, 
  #            color = "red4", 
  #            alpha = 0.5, 
  #            size = 3) +
  stat_summary(fun = mean,
               aes(group = 1), 
               geom = "line", 
               color = "red4", 
               alpha = 1, 
               size = 2) +
  facet_wrap(~ H_SD_Gen, ncol = 3) +
  labs(
    x = "Generation",
    y = "Frequency"
  ) +
  theme_bw() +
  theme(
    text = element_text(family = "sans"),
    legend.position = "none",
    axis.text.x = element_text(face = "bold", size = 40, angle = 35,
                               hjust = 1, margin = margin(t = 10)),
    axis.text.y = element_text(face = "bold", size = 40, angle = 15,
                               margin = margin(r = 10)),
    axis.line   = element_line(size = 2),
    plot.title  = element_text(hjust = 0.01, face = "bold", size = 40),
    axis.title.x = element_text(size = 40, face = "bold",
                                margin = margin(t = 10)),
    axis.title.y = element_text(size = 40, face = "bold",
                                margin = margin(r = 10)),
    strip.text = element_text(size = 40, face = "bold"),
    panel.spacing = unit(5, "lines"),
    panel.grid = element_blank()
  )

SingleLocusAF

ggsave(filename = "SI_4.1.1.SingleLocusAF.jpg", SingleLocusAF, path = "../OutputFigures.dir/SupplementalFigures.dir", width = 70, height = 60, units = "in", dpi = 300, limitsize = FALSE)
```

### 4.1.2. Oligogenic

```{r, fig.height = 40, fig.width = 50, echo=FALSE}
#| label: Inst_AF_Loci10Gen10
#| fig-cap: "SI 4.1.2.1 Allele frequency dynamics for all parameter combinations with selection length of 10 generations from a single replicate, instantaneous selection model. Each line  represents the frequency trajectory for a locus from oligogenic trait (10 loci)."
#| fig-pos: "H"

Inst_AF_Loci10Gen10 <- instantplots_AF$`loci = 10 gen = 10` +
  ggtitle("Season Length (Gen) = 10") +
  theme(
    plot.title = element_text(
      hjust = 0.5,         
      size = 70, 
      color = "firebrick4",
      margin = margin(b = 40) 
    )
  )
ggsave(filename = "SI_4.1.2.1.Inst_AF_Loci10Gen10.jpg", Inst_AF_Loci10Gen10, path = "../OutputFigures.dir/SupplementalFigures.dir", width = 50, height = 40, units = "in", dpi = 300, limitsize = FALSE)

print(Inst_AF_Loci10Gen10)
```

```{r, fig.height = 40, fig.width = 50, echo=FALSE}
#| label: Inst_AF_Loci10Gen20
#| fig-cap: "SI 4.1.2.2. Allele frequency dynamics for all parameter combinations with selection length of 20 generations from a single replicate, instantaneous selection model. Each line  represents the frequency trajectory for a locus from oligogenic trait (10 loci)."
#| fig-pos: "H"
Inst_AF_Loci10Gen20 <- instantplots_AF$`loci = 10 gen = 20` +
  ggtitle("Season Length (Gen) = 20") +
  theme(
    plot.title = element_text(
      hjust = 0.5,         
      size = 70, 
      color = "firebrick4",
      margin = margin(b = 40) 
    )
  )

print(Inst_AF_Loci10Gen20)
ggsave(filename = "SI_4.1.2.2.Inst_AF_Loci10Gen20.jpg", Inst_AF_Loci10Gen20, path = "../OutputFigures.dir/SupplementalFigures.dir", width = 50, height = 40, units = "in", dpi = 300, limitsize = FALSE)

```

```{r, fig.height = 40, fig.width = 50, echo=FALSE}
#| label: Inst_AF_Loci10Gen30
#| fig-cap: "SI 4.1.2.3. Allele frequency dynamics for all parameter combinations with selection length of 30 generations from a single replicate, instantaneous selection model. Each line  represents the frequency trajectory for a locus from oligogenic trait (10 loci)."
#| fig-pos: "H"
Inst_AF_Loci10Gen30 <- instantplots_AF$`loci = 10 gen = 30` +
  ggtitle("Season Length (Gen) = 30") +
  theme(
    plot.title = element_text(
      hjust = 0.5,         
      size = 70, 
      color = "firebrick4",
      margin = margin(b = 40) 
    )
  )

print(Inst_AF_Loci10Gen30)

ggsave(filename = "SI 4.1.2.3.Inst_AF_Loci10Gen30.jpg", Inst_AF_Loci10Gen30, path = "../OutputFigures.dir/SupplementalFigures.dir", width = 50, height = 40, units = "in", dpi = 300, limitsize = FALSE)
```

### 4.1.3. Polygenic 70 loci

```{r, fig.height = 40, fig.width = 50, echo=FALSE}
#| label: Inst_AF_Loci70Gen10
#| fig-cap: "SI 4.1.3.1. Allele frequency dynamics for all parameter combinations with selection length of 10 generations from a single replicate, instantaneous selection model. Each line  represents the frequency trajectory for a locus from polygenic trait (70 loci)."
#| fig-pos: "H"
Inst_AF_Loci70Gen10 <- instantplots_AF$`loci = 70 gen = 10` +
  ggtitle("Season Length (Gen) = 10") +
  theme(
    plot.title = element_text(
      hjust = 0.5,         
      size = 70, 
      color = "firebrick4",
      margin = margin(b = 40) 
    )
  )

print(Inst_AF_Loci70Gen10)

ggsave(filename = "SI_4.1.3.1.Inst_AF_Loci70Gen10.jpg", Inst_AF_Loci70Gen10, path = "../OutputFigures.dir/SupplementalFigures.dir", width = 50, height = 40, units = "in", dpi = 300, limitsize = FALSE)
```

```{r, fig.height = 40, fig.width = 50, echo=FALSE}
#| label: Inst_AF_Loci70Gen20
#| fig-cap: "SI 4.1.3.2. Allele frequency dynamics for all parameter combinations with selection length of 20 generations from a single replicate, instantaneous selection model. Each line  represents the frequency trajectory for a locus from polygenic trait (70 loci)."
#| fig-pos: "H"
Inst_AF_Loci70Gen20 <- instantplots_AF$`loci = 70 gen = 20` +
  ggtitle("Season Length (Gen) = 20") +
  theme(
    plot.title = element_text(
      hjust = 0.5,         
      size = 70, 
      color = "firebrick4",
      margin = margin(b = 40) 
    )
  )

print(Inst_AF_Loci70Gen20)

ggsave(filename = "SI_4.1.3.2.Inst_AF_Loci70Gen20.jpg", Inst_AF_Loci70Gen20, path = "../OutputFigures.dir/SupplementalFigures.dir", width = 50, height = 40, units = "in", dpi = 300, limitsize = FALSE)
```

```{r, fig.height = 40, fig.width = 50, echo=FALSE}
#| label: Inst_AF_Loci70Gen30
#| fig-cap: "SI 4.1.3.3. Allele frequency dynamics for all parameter combinations with selection length of 30 generations from a single replicate, instantaneous selection model. Each line  represents the frequency trajectory for a locus from polygenic trait (70 loci)."
#| fig-pos: "H"
Inst_AF_Loci70Gen30 <- instantplots_AF$`loci = 70 gen = 30` +
  ggtitle("Season Length (Gen) = 30") +
  theme(
    plot.title = element_text(
      hjust = 0.5,         
      size = 70, 
      color = "firebrick4",
      margin = margin(b = 40) 
    )
  )

print(Inst_AF_Loci70Gen30)

ggsave(filename = "SI_4.1.3.3.Inst_AF_Loci70Gen30.jpg", Inst_AF_Loci70Gen30, path = "../OutputFigures.dir/SupplementalFigures.dir", width = 50, height = 40, units = "in", dpi = 300, limitsize = FALSE)
```

### 4.1.4. Polygenic 300 loci

```{r, fig.height = 40, fig.width = 50, echo=FALSE}
#| label: Inst_AF_Loci300Gen10
#| fig-cap: "SI 4.1.4.1. Allele frequency dynamics for all parameter combinations with selection length of 10 generations from a single replicate, instantaneous selection model. Each line  represents the frequency trajectory for a locus from polygenic trait (300 loci)."
#| fig-pos: "H"

Inst_AF_Loci300Gen10 <- instantplots_AF$`loci = 300 gen = 10` +
  ggtitle("Season Length (Gen) = 10") +
  theme(
    plot.title = element_text(
      hjust = 0.5,         
      size = 70, 
      color = "firebrick4",
      margin = margin(b = 40) 
    )
  )

print(Inst_AF_Loci300Gen10)

ggsave(filename = "SI_4.1.4.1.Inst_AF_Loci300Gen10.jpg", Inst_AF_Loci300Gen10, path = "../OutputFigures.dir/SupplementalFigures.dir", width = 50, height = 40, units = "in", dpi = 300, limitsize = FALSE)
```

```{r, fig.height = 40, fig.width = 50, echo=FALSE}
#| label: Inst_AF_Loci300Gen20
#| fig-cap: "SI 4.1.4.2. Allele frequency dynamics for all parameter combinations with selection length of 20 generations from a single replicate, instantaneous selection model. Each line  represents the frequency trajectory for a locus from polygenic trait (300 loci)."
#| fig-pos: "H"

Inst_AF_Loci300Gen20 <- instantplots_AF$`loci = 300 gen = 20` +
  ggtitle("Season Length (Gen) = 20") +
  theme(
    plot.title = element_text(
      hjust = 0.5,         
      size = 70, 
      color = "firebrick4",
      margin = margin(b = 40) 
    )
  )

print(Inst_AF_Loci300Gen20)

ggsave(filename = "SI_4.1.4.2.Inst_AF_Loci300Gen20.jpg", Inst_AF_Loci300Gen20, path = "../OutputFigures.dir/SupplementalFigures.dir", width = 50, height = 40, units = "in", dpi = 300, limitsize = FALSE)
```

```{r, fig.height = 40, fig.width = 50, echo=FALSE}
#| label: Inst_AF_Loci300Gen30
#| fig-cap: "SI 4.1.4.3. Allele frequency dynamics for all parameter combinations with selection length of 30 generations from a single replicate, instantaneous selection model. Each line  represents the frequency trajectory for a locus from polygenic trait (300 loci)."
#| fig-pos: "H"

Inst_AF_Loci300Gen30 <- instantplots_AF$`loci = 300 gen = 30` +
  ggtitle("Season Length (Gen) = 30") +
  theme(
    plot.title = element_text(
      hjust = 0.5,         
      size = 70, 
      color = "firebrick4",
      margin = margin(b = 40) 
    )
  )

print(Inst_AF_Loci300Gen30)

ggsave(filename = "SI_4.1.4.3.Inst_AF_Loci300Gen30.jpg", Inst_AF_Loci300Gen30, path = "../OutputFigures.dir/SupplementalFigures.dir", width = 50, height = 40, units = "in", dpi = 300, limitsize = FALSE)
```

## 4.2. Spectral analysis for all parameters

```{r, echo=FALSE}
run_fft_analysis <- function(folder_path, pattern, spectrum_span = 2) {
  library(parallel)
  library(doParallel)
  library(foreach)
  library(dplyr)
  library(ggplot2)
  library(cowplot)
  
  theme_set(theme_classic())
  
   mythemes <- theme_bw() +
    theme(
      text            = element_text(family = "sans"), 
      legend.position = "none",
      axis.text.x     = element_text(face = "bold", size = 40, angle = 25, 
                                       margin = margin(t = 20), hjust = 1),
      axis.text.y     = element_text(face = "bold", size = 40, angle = 15, 
                                       margin = margin(r = 10)),
      axis.line       = element_line(size = 3),
      plot.title      = element_text(hjust = 0.01, face = "bold", size = 80, 
                                       margin = margin(b = 1, unit = "lines")),
      plot.margin     = unit(c(5, 1, 1, 1), "lines"),
      axis.title.x    = element_text(size = 40, face = "bold", margin = margin(t = 30)),
      axis.title.y    = element_text(size = 40, face = "bold", margin = margin(r = 35)),
      strip.text      = element_text(size = 40, face = "bold"),
      panel.spacing   = unit(5, "lines"),
      panel.grid      = element_blank()
    )
  
  # File list
  
  file_list <- list.files(path = folder_path, pattern = pattern, full.names = TRUE)
  
  if (length(file_list) == 0) {
    stop("No files found with the given pattern.")
  }
  
  # Create a data frame with filenames and extract parameters
  
  files_df <- data.frame(file_name = file_list) %>%
    mutate(
      # base_name = basename(file_name),
      # replct = str_extract(base_name, "genome\\d+"),
      # n = str_extract(base_name, "_n\\d+") %>% str_remove("_n"),
      # H = str_extract(base_name, "_H\\d+\\.\\d*") %>% str_remove("_H"),
      # SD = str_extract(base_name, "SD\\d+(\\.\\d+)?"),
      # SD = ifelse(is.na(SD), NA, str_remove(SD, "SD")),
      # Gen = str_extract(base_name, "Gen\\d+"),
      # Gen = ifelse(is.na(Gen), NA, str_remove(Gen, "Gen")),
      base_name = basename(file_name),  
      n = ifelse(
         grepl("_n\\d+", base_name),
         as.numeric(sub(".*_n(\\d+).*", "\\1", base_name)),
         NA_real_
           ),
      replct <- as.numeric(sub(".*genome(\\d+)_.*", "\\1", base_name)),
      H = ifelse(
         grepl("_H[0-9]+\\.?[0-9]*", base_name),
         as.numeric(sub(".*_H([0-9]+\\.?[0-9]*).*", "\\1", base_name)),
         NA_real_
        ),
      SD = ifelse(
        grepl("SD[0-9]+(\\.[0-9]+)?", base_name),
        as.numeric(sub(".*SD([0-9]+(?:\\.[0-9]+)?).*", "\\1", base_name)),
        NA_real_
        ),
      Gen = ifelse(
        grepl("Gen\\d+", base_name),
        as.numeric(sub(".*Gen(\\d+).*", "\\1", base_name)),
        NA_real_
        ),
      Genome = case_when(
        n == "1" ~ "Monogenic",
        n == "10" ~ "Oligogenic",
        n == "70" ~ "Polygenic 70",
        n == "100" ~ "Polygenic 100",
        n == "300" ~ "Polygenic 300",
        TRUE ~ "Unknown"
      )
    ) %>%
     mutate(
      param_combination = paste0("n_", n, "_H", H, 
                                 ifelse(!is.na(SD), paste0("_SD", SD), ""), 
                                 ifelse(!is.na(Gen), paste0("_Gen", Gen), ""))
    )
  
  num_cores <- detectCores()
  cl <- makeCluster(64)
  registerDoParallel(cl)
  
  # Read and combine data from all replicate files in parallel
  combined_data_list <- foreach(i = seq_along(files_df$file_name), .packages = c("dplyr")) %dopar% {
    file <- files_df$file_name[i]
    params <- files_df[i, ]
    df <- read.csv(file)
    data <- df %>%
      mutate(
        allele_id = as.factor(Position),
        generation = as.numeric(Generation),
        allele_frequency = Frequency,
        file = params$base_name,
        replct = params$replct,
        n = params$n,
        H = params$H,
        SD = params$SD,
        Gen = params$Gen,
        Genome = params$Genome,
        param_combination = params$param_combination
      ) %>%
      dplyr::select(allele_id, generation, allele_frequency, replct, n, H, SD, Gen, Genome, param_combination)
    data
  }
  combined_data <- bind_rows(combined_data_list)

  filtered_data <- combined_data 
  
  # Calculating the mean allele frequency for each grouping
  mean_allele_data <- filtered_data %>%
    group_by(generation, n, replct, H, SD, Gen, Genome, param_combination) %>%
    summarize(mean_allele_frequency = mean(allele_frequency), .groups = "drop")
  
  # Creating time series objects
  ts_data_list <- mean_allele_data %>%
    group_by(n, replct, H, SD, Gen, Genome, param_combination) %>%
    summarize(ts_data = list(ts(mean_allele_frequency, start = min(generation), frequency = 1)), .groups = 'drop')
  
  # Computing spectral density 
  spec_results_list <- foreach(i = 1:nrow(ts_data_list), .packages = c("stats")) %dopar% {
    ts_data <- ts_data_list$ts_data[[i]]
    spectrum(ts_data, spans = spectrum_span, plot = FALSE)
  }
  
  # Preparing data for plotting
  plot_data_list <- foreach(i = seq_along(spec_results_list), .packages = c("dplyr")) %dopar% {
    spec_result <- spec_results_list[[i]]
    params <- ts_data_list[i, ]
    period <- 1 / spec_result$freq
    data.frame(
      Period = period,
      Spectrum = spec_result$spec,
      n = params$n,
      replct = params$replct,
      H = params$H,
      SD = params$SD,
      Gen = params$Gen,
      Genome = params$Genome,
      param_combination = params$param_combination
    )
  }
  
  stopCluster(cl)
  

  plot_data <- bind_rows(plot_data_list)
  

  plot_data <- plot_data %>%
    group_by(param_combination) %>%
    mutate(threshold = case_when(
      Gen == 10 ~ 40,
      Gen == 20 ~ 50,
      Gen == 30 ~ 80,
      TRUE ~ 80
    )) %>%
    filter(Period < threshold) %>%
    ungroup() %>%
    mutate(
      Genome_Gen = paste0("Genome = ", Genome, " Gen = ", Gen),
      h2_sd = paste("H = ", H," ", "\u0394\ = ", SD, sep = ""), 
      #H_label = paste0("H = ", H),
      #SD_label = ifelse(!is.na(SD), paste0("SD = ", SD), "No SD"),
      Gen_label = ifelse(!is.na(Gen), paste0("Gen = ", Gen), "No Gen"),
      n_label = paste0("n_", n)
    )
  
  fft_plots <- list()
  
  uni_genomegen <- unique(plot_data$Genome_Gen)
  
  for(genomegen in uni_genomegen){
    myplot_data <- plot_data %>% filter(Genome_Gen == genomegen)
    
  fft_plots[[genomegen]] <- ggplot(myplot_data, aes(x = Period, y = Spectrum, color = factor(replct), group = factor(replct))) +
    geom_line(size = 1.1) +
    facet_wrap( ~ h2_sd, scales = "free") +
    labs(x = "Period (Generations)", y = "Spectral Density") +
    mythemes
  }
  
  return(fft_plots)
}

```

```{r, echo=FALSE}
dirpath <- "../../Output.dir/LinFS.dir/"
pattern <- "^genome"
instantplots_SPA <- run_fft_analysis(dirpath, pattern, spectrum_span = 2)

```

#### 4.2.1. Monogenic

```{r, fig.height = 40, fig.width = 50, echo=FALSE}
#| label: Inst_Spect_Loci1Gen10
#| fig-cap: "SI 4.2.1.1. Spectral density across 30 replicates for monogenic trait (single locus) with instantaneous selection model, all parameter combinations with selection length of 10 generations. Each peak represents a full cycle of selection period."
#| fig-pos: "H"

Inst_Spect_Loci1Gen10 <- instantplots_SPA[[1]] +
  ggtitle("Season Length (Gen) = 10") +
  theme(
    plot.title = element_text(
      hjust = 0.5,         
      size = 70, 
      color = "firebrick4",
      margin = margin(b = 40) 
    )
  )

print(Inst_Spect_Loci1Gen10)

ggsave(filename = "SI_4.2.1.1.Inst_Spect_Loci1Gen10.jpg", Inst_Spect_Loci1Gen10, path = "../OutputFigures.dir/SupplementalFigures.dir", width = 50, height = 40, units = "in", dpi = 300, limitsize = FALSE)
```

```{r, fig.height = 40, fig.width = 50, echo=FALSE}
#| label: Inst_Spect_Loci1Gen20
#| fig-cap: "SI 4.2.1.2. Spectral density across 30 replicates for monogenic trait (single locus) with instantaneous selection model, all parameter combinations with selection length of 20 generations. Each peak represents a full cycle of selection period."
#| fig-pos: "H"

Inst_Spect_Loci1Gen20 <- instantplots_SPA[[2]] +
  ggtitle("Season Length (Gen) = 20") +
  theme(
    plot.title = element_text(
      hjust = 0.5,         
      size = 70, 
      color = "firebrick4",
      margin = margin(b = 40) 
    )
  )

print(Inst_Spect_Loci1Gen20)

ggsave(filename = "SI_4.2.1.2.Inst_Spect_Loci1Gen20.jpg", Inst_Spect_Loci1Gen20, path = "../OutputFigures.dir/SupplementalFigures.dir", width = 50, height = 40, units = "in", dpi = 300, limitsize = FALSE)
```

```{r, fig.height = 40, fig.width = 50, echo=FALSE}
#| label: Inst_Spect_Loci1Gen30
#| fig-cap: "SI 4.2.1.3. Spectral density across 30 replicates for monogenic trait (single locus) with instantaneous selection model, all parameter combinations with selection length of 30 generations. Each peak represents a full cycle of selection period."
#| fig-pos: "H"

Inst_Spect_Loci1Gen30 <- instantplots_SPA[[3]] +
  ggtitle("Season Length (Gen) = 30") +
  theme(
    plot.title = element_text(
      hjust = 0.5,         
      size = 70, 
      color = "firebrick4",
      margin = margin(b = 40) 
    )
  )

print(Inst_Spect_Loci1Gen30)

ggsave(filename = "SI_4.2.1.3.Inst_Spect_Loci1Gen30.jpg", Inst_Spect_Loci1Gen30, path = "../OutputFigures.dir/SupplementalFigures.dir", width = 50, height = 40, units = "in", dpi = 300, limitsize = FALSE)
```

### 4.2.2. Oligogenic

```{r, fig.height = 40, fig.width = 50, echo=FALSE}
#| label: Inst_Spect_Loci10Gen10
#| fig-cap: "SI 4.2.2.1. Spectral density across 30 replicates for oligogenic trait (10 loci) with instantaneous selection model, all parameter combinations with selection length of 10 generations. Each peak represents a full cycle of selection period."
#| fig-pos: "H"

Inst_Spect_Loci10Gen10 <- instantplots_SPA[[4]] +
  ggtitle("Season Length (Gen) = 10") +
  theme(
    plot.title = element_text(
      hjust = 0.5,         
      size = 70, 
      color = "firebrick4",
      margin = margin(b = 40) 
    )
  )

print(Inst_Spect_Loci10Gen10)

ggsave(filename = "SI_4.2.2.1.Inst_Spect_Loci10Gen10.jpg", Inst_Spect_Loci10Gen10, path = "../OutputFigures.dir/SupplementalFigures.dir", width = 50, height = 40, units = "in", dpi = 300, limitsize = FALSE)
```

```{r, fig.height = 40, fig.width = 50, echo=FALSE}
#| label: Inst_Spect_Loci10Gen20
#| fig-cap: "SI 4.2.2.2.  Spectral density across 30 replicates for oligogenic trait (10 loci) with instantaneous selection model, all parameter combinations with selection length of 20 generations. Each peak represents a full cycle of selection period."
#| fig-pos: "H"

Inst_Spect_Loci10Gen20 <- instantplots_SPA[[5]] +
  ggtitle("Season Length (Gen) = 20") +
  theme(
    plot.title = element_text(
      hjust = 0.5,         
      size = 70, 
      color = "firebrick4",
      margin = margin(b = 40) 
    )
  )

print(Inst_Spect_Loci10Gen20)

ggsave(filename = "SI_4.2.2.2.Inst_Spect_Loci10Gen20.jpg", Inst_Spect_Loci10Gen20, path = "../OutputFigures.dir/SupplementalFigures.dir", width = 50, height = 40, units = "in", dpi = 300, limitsize = FALSE)
```

```{r, fig.height = 40, fig.width = 50, echo=FALSE}
#| label: Inst_Spect_Loci10Gen30
#| fig-cap: "SI 4.2.2.3. Spectral density across 30 replicates for oligogenic trait (10 loci) with instantaneous selection model, all parameter combinations with selection length of 30 generations. Each peak represents a full cycle of selection period."
#| fig-pos: "H"

Inst_Spect_Loci10Gen30 <- instantplots_SPA[[6]] +
  ggtitle("Season Length (Gen) = 30") +
  theme(
    plot.title = element_text(
      hjust = 0.5,         
      size = 70, 
      color = "firebrick4",
      margin = margin(b = 40) 
    )
  )

print(Inst_Spect_Loci10Gen30)

ggsave(filename = "SI_4.2.2.3.Inst_Spect_Loci10Gen30.jpg", Inst_Spect_Loci10Gen30, path = "../OutputFigures.dir/SupplementalFigures.dir", width = 50, height = 40, units = "in", dpi = 300, limitsize = FALSE)
```

### 4.2.3. Polygenic 70

```{r, fig.height = 40, fig.width = 50, echo=FALSE}
#| label: Inst_Spect_Loci70Gen10
#| fig-cap: "SI 4.2.3.1. Spectral density across 30 replicates for polygenic trait (70 loci) with instantaneous selection model, all parameter combinations with selection length of 10 generations. Each peak represents a full cycle of selection period."
#| fig-pos: "H"

Inst_Spect_Loci70Gen10 <- instantplots_SPA[[7]] +
  ggtitle("Season Length (Gen) = 10") +
  theme(
    plot.title = element_text(
      hjust = 0.5,         
      size = 70, 
      color = "firebrick4",
      margin = margin(b = 40) 
    )
  )

print(Inst_Spect_Loci70Gen10)

ggsave(filename = "SI_4.2.3.1.Inst_Spect_Loci70Gen10.jpg", Inst_Spect_Loci70Gen10, path = "../OutputFigures.dir/SupplementalFigures.dir", width = 50, height = 40, units = "in", dpi = 300, limitsize = FALSE)
```

```{r, fig.height = 40, fig.width = 50, echo=FALSE}
#| label: Inst_Spect_Loci70Gen20
#| fig-cap: "SI 4.2.3.2. Spectral density across 30 replicates for polygenic trait (70 loci) with instantaneous selection model, all parameter combinations with selection length of 20 generations. Each peak represents a full cycle of selection period."
#| fig-pos: "H"

Inst_Spect_Loci70Gen20 <- instantplots_SPA[[8]] +
  ggtitle("Season Length (Gen) = 20") +
  theme(
    plot.title = element_text(
      hjust = 0.5,         
      size = 70, 
      color = "firebrick4",
      margin = margin(b = 40) 
    )
  )

print(Inst_Spect_Loci70Gen20)

ggsave(filename = "SI_4.2.3.2.Inst_Spect_Loci70Gen20.jpg", Inst_Spect_Loci70Gen20, path = "../OutputFigures.dir/SupplementalFigures.dir", width = 50, height = 40, units = "in", dpi = 300, limitsize = FALSE)
```

```{r, fig.height = 40, fig.width = 50, echo=FALSE}
#| label: Inst_Spect_Loci70Gen30
#| fig-cap: "SI 4.2.3.3. Spectral density across 30 replicates for polygenic trait (70 loci) with instantaneous selection model, all parameter combinations with selection length of 30 generations. Each peak represents a full cycle of selection period."
#| fig-pos: "H"

Inst_Spect_Loci70Gen30 <- instantplots_SPA[[9]] +
  ggtitle("Season Length (Gen) = 30") +
  theme(
    plot.title = element_text(
      hjust = 0.5,         
      size = 70, 
      color = "firebrick4",
      margin = margin(b = 40) 
    )
  )

print(Inst_Spect_Loci70Gen30)

ggsave(filename = "SI_4.2.3.3.Inst_Spect_Loci70Gen30.jpg", Inst_Spect_Loci70Gen30, path = "../OutputFigures.dir/SupplementalFigures.dir", width = 50, height = 40, units = "in", dpi = 300, limitsize = FALSE)
```

### 4.2.4. Polygenic 300

```{r, fig.height = 40, fig.width = 50, echo=FALSE}
#| label: Inst_Spect_Loci300Gen10
#| fig-cap: "SI 4.2.4.1. Spectral density across 30 replicates for polygenic trait (300 loci) with instantaneous selection model, all parameter combinations with selection length of 10 generations. Each peak represents a full cycle of selection period."
#| fig-pos: "H"

Inst_Spect_Loci300Gen10 <- instantplots_SPA[[13]] +
  ggtitle("Season Length (Gen) = 10") +
  theme(
    plot.title = element_text(
      hjust = 0.5,         
      size = 70, 
      color = "firebrick4",
      margin = margin(b = 40) 
    )
  )

print(Inst_Spect_Loci300Gen10)

ggsave(filename = "SI_4.2.4.1.Inst_Spect_Loci300Gen10.jpg", Inst_Spect_Loci300Gen10, path = "../OutputFigures.dir/SupplementalFigures.dir", width = 50, height = 40, units = "in", dpi = 300, limitsize = FALSE)
```

```{r, fig.height = 40, fig.width = 50, echo=FALSE}
#| label: Inst_Spect_Loci300Gen20
#| fig-cap: "SI 4.2.4.2. Spectral density across 30 replicates for polygenic trait (300 loci) with instantaneous selection model, all parameter combinations with selection length of 20 generations. Each peak represents a full cycle of selection period."
#| fig-pos: "H"

Inst_Spect_Loci300Gen20 <- instantplots_SPA[[14]] +
  ggtitle("Season Length (Gen) = 20") +
  theme(
    plot.title = element_text(
      hjust = 0.5,         
      size = 70, 
      color = "firebrick4",
      margin = margin(b = 40) 
    )
  )

print(Inst_Spect_Loci300Gen20)

ggsave(filename = "SI_4.2.4.2.Inst_Spect_Loci300Gen20.jpg", Inst_Spect_Loci300Gen20, path = "../OutputFigures.dir/SupplementalFigures.dir", width = 50, height = 40, units = "in", dpi = 300, limitsize = FALSE)
```

```{r, fig.height = 40, fig.width = 50, echo=FALSE}
#| label: Inst_Spect_Loci300Gen30
#| fig-cap: "SI 4.2.4.3. Spectral density across 30 replicates for polygenic trait (300 loci) with instantaneous selection model, all parameter combinations with selection length of 30 generations. Each peak represents a full cycle of selection period."
#| fig-pos: "H"

Inst_Spect_Loci300Gen30 <- instantplots_SPA[[15]] +
  ggtitle("Season Length (Gen) = 30") +
  theme(
    plot.title = element_text(
      hjust = 0.5,         
      size = 70, 
      color = "firebrick4",
      margin = margin(b = 40) 
    )
  )

print(Inst_Spect_Loci300Gen30)

ggsave(filename = "SI_4.2.4.3.Inst_Spect_Loci300Gen30.jpg", Inst_Spect_Loci300Gen30, path = "../OutputFigures.dir/SupplementalFigures.dir", width = 50, height = 40, units = "in", dpi = 300, limitsize = FALSE)
```


# 5. Fixed percentages for each architecture

```{r, fig.height=5, fig.width=10, echo=FALSE, dpi = 1200, message=FALSE}
#| label: Fixation_Percentages
#| fig-cap: "SI 5. Percentage of fixed loci across different genetic architectures based on parameter interactions from instantaneous selection model. The single locus trait exhibits the highest percentage of fixed loci among the 30 replicates, followed by the 10 loci model, while 70 loci or more shows a consistent fixation rate."
#| fig-pos: "H"
#### Parameter combination as colors
library(furrr)
library(fs)
#library(stringr)
library(dplyr)

path <- "../../Output.dir/LinFS.dir/"
pattern <- "^genome\\d+_n\\d+_H0.(1|5|8)(SD[1|4])?Gen(10|30)?\\.csv$" 

# List files using list.files (full paths, filtering by regex)
files <- list.files(path, pattern, full.names = TRUE)

if (length(files) == 0) {
  stop("No files found matching the pattern in the specified path.")
}

available_cores <- parallel::detectCores()
workers_to_use <- max(1, available_cores - 4)  
plan(multicore, workers = workers_to_use)

process_file <- function(file) {
  filename <- path_file(file)
  repl_val <- as.numeric(sub(".*genome(\\d+)_.*", "\\1", basename(filename)))
  H_val <- as.numeric(sub(".*_H(0\\.\\d+).*", "\\1", basename(filename)))
  loci_val <- as.numeric(sub(".*_n(\\d+)_.*", "\\1", basename(filename)))
  SD_val <- as.numeric(sub(".*SD(\\d+).*", "\\1", basename(filename)))
  Gen_val <- as.numeric(sub(".*Gen(\\d+).*", "\\1", basename(filename)))
  
  df <- read.csv(file) %>%
    dplyr::select(-any_of("Origin")) %>%
    mutate(
      Position = as_factor(Position),
      repl = (repl_val),
      H    = (H_val),
      loci = (loci_val),
      SD   = (SD_val),
      Gen  = (Gen_val)
    )
  
  required <- c("H", "loci", "SD", "Gen", "repl", "Position")
  missing_cols <- setdiff(required, names(df))
  if (length(missing_cols) > 0) {
    warning("File ", filename, " is missing the following columns: ",
            paste(missing_cols, collapse = ", "))
  }
  return(df)
}

combined_data <- future_map_dfr(files, process_file, .options = furrr_options(chunk_size = 100))

data_with_fix <- combined_data %>%
  group_by(H, loci, SD, Gen, repl, Position) %>%
  filter(Frequency == 1 | (Frequency < 1 & Generation == max(Generation) & max(Generation) < 2000)) %>% 
  distinct(H, loci, SD, Gen, repl, Position) %>% 
  ungroup()

replicate_summary <- data_with_fix %>%
  group_by(H, loci, SD, Gen, repl) %>%
  summarise(
    fixed_count = n_distinct(Position),
    total_count = 30 * loci,  # count of unique loci in this replicate
    .groups = "drop"
  ) %>% 
  distinct()


parameter_summary <- replicate_summary %>%
  group_by(H, loci, SD, Gen, total_count) %>%
  summarise(
    total_fixed    = sum(fixed_count),
    total_possible = total_count,
    Perc_Loci      = total_fixed * 100 / total_possible,
    .groups = "drop"
  ) %>%
  mutate(
    Gen_SD  = paste0("Gen = ", Gen, " SD = ", SD),
    H_label = paste0("H = ", H),
    Combo   = paste0(H_label, ", ", Gen_SD)
  ) %>% 
  distinct()

Fixation_Percentages <-
  ggplot(
    parameter_summary %>%
      mutate(
        H   = as_factor(H),
        loci= as_factor(loci),
        SD  = as_factor(SD),
        Gen = as_factor(Gen)
      ),
    aes(
      x = loci,
      y = Perc_Loci,
      color = H,
      shape = SD,
      linetype = Gen,
      group = interaction(H, Gen, SD)
    )
  ) +
  geom_line(linewidth = 3) +
  geom_point(size = 7, stroke = 0) +
  labs(
    x = "Number of Loci",
    y = "Percentage of Loci Fixed (%)",
    color = "Heritability (h\u00B2)",
    linetype = "Season Length (Gen)",
    shape = "Distance to Optimum (Δ)"
  ) +
  scale_color_manual(values = c("darkblue", "gray50", "firebrick")) +
  scale_linetype_manual(
    values = c("solid", "dashed", "dotted", "dotdash", "longdash", "twodash")
  ) +
  theme_bw() +
  theme(
    text           = element_text(family = "sans"),
    axis.text.x    = element_text(face = "bold", size = 30, angle = 15,
                                  hjust = 1, margin = margin(t = 10)),
    axis.text.y    = element_text(face = "bold", size = 30, angle = 15,
                                  margin = margin(r = 10)),
    axis.line      = element_line(linewidth = 1.2),
    plot.title     = element_text(hjust = 0.01, face = "bold", size = 30),
    axis.title.x   = element_text(size = 30, face = "bold",
                                  margin = margin(t = 30)),
    axis.title.y   = element_text(size = 30, face = "bold",
                                  margin = margin(r = 35)),
    strip.text     = element_text(size = 30, face = "bold"),
    panel.spacing  = unit(5, "lines"),
    panel.grid     = element_blank(),
    legend.position= c(0.95, 0.95),
    legend.justification = c("right", "top"),
    legend.text    = element_text(size = 32, face = "bold"),
    legend.title   = element_text(size = 34, face = "bold"),
    legend.key.width = unit(2.5, "cm")  
  ) +
  guides(
    color    = guide_legend(override.aes = list(shape = 16, size = 6), byrow = TRUE),
    linetype = guide_legend(override.aes = list(linewidth = 2, color = "black"))
  )

# ggsave("Fixation_Percentages.jpg",
#        plot = Fixation_Percentages, 
#        dpi = 600, 
#        width = 40, 
#        height = 20, 
#        units = "in", 
#        path = "../OutputFigures.dir/SupplementalFigures.dir")

print(Fixation_Percentages)


ggsave(filename = "SI_5.Fixation_Percentages.jpg", Fixation_Percentages, path = "../OutputFigures.dir/SupplementalFigures.dir", width = 40, height = 20, units = "in", dpi = 300, limitsize = FALSE)

```


# 6. Sampling Points for spectral analysis

```{r, warning=FALSE, fig.width = 20, fig.height = 10, echo=FALSE}
#| label: SamplingPointSpecAnalysis
#| fig-cap: "SI 6. Spectral analysis of instantaneous selection for a 100 loci model using 10 sampling points to compare the identification of spectral peaks under high versus low parameter combinations. Although seasonal signatures of selection can be identified with 10 samples under the high parameter combination, recovering the spectral peak remains challenging under the low parameter combination, which may require increasing the number of sampling points."
#| fig-pos: "H"
library(dplyr)
library(ggplot2)
library(purrr)
library(tibble)
library(tidyr)
library(scales)
library(patchwork)


###############################################################################
#################### Defining files, number of sequence and the spans#######
###############################################################################

dirpath <- "../../Output.dir/LinFS.dir/"
my_pattern <- "^genome\\d+_n100_H0\\.(1|8)SD(1|4)Gen(10|30)\\.csv$"

# Number of sampled time points after the first generation
nseq <- 10

# Spectral smoothing span
spectrum_span <- 2

###############################################################################
########################## Extracting parameters ##############################
###############################################################################

parse_simulation_files <- function(dirpath, pattern) {
  
  file_list <- list.files(
    path = dirpath,
    pattern = pattern,
    full.names = TRUE
  )
  

  files_df <- tibble(file_name = file_list) %>%
    mutate(
      base_name = basename(file_name),
      
      replicate = ifelse(
        grepl("genome\\d+", base_name),
        as.numeric(sub(".*genome(\\d+).*", "\\1", base_name)),
        NA_real_
      ),
      
      n = ifelse(
        grepl("_n\\d+", base_name),
        as.numeric(sub(".*_n(\\d+).*", "\\1", base_name)),
        NA_real_
      ),
      
      H = ifelse(
        grepl("_H[0-9]+\\.?[0-9]*", base_name),
        as.numeric(sub(".*_H([0-9]+\\.?[0-9]*).*", "\\1", base_name)),
        NA_real_
      ),
      
      SD = ifelse(
        grepl("SD[0-9]+(\\.[0-9]+)?", base_name),
        as.numeric(sub(".*SD([0-9]+(?:\\.[0-9]+)?).*", "\\1", base_name)),
        NA_real_
      ),
      
      Gen = ifelse(
        grepl("Gen\\d+", base_name),
        as.numeric(sub(".*Gen(\\d+).*", "\\1", base_name)),
        NA_real_
      )
    ) %>%
    mutate(
      parameter_label = case_when(
        H == 0.1 & SD == 1 & Gen == 10 ~ "h² = 0.1 Δ = 1 Gen=10",
        H == 0.8 & SD == 4 & Gen == 30 ~ "h² = 0.8 Δ = 4 Gen=30",
        TRUE ~ paste0("h² = ", H, " Δ = ", SD, " Gen=", Gen)
      )
    )
  
  files_df
}

###############################################################################
########################## Function for spectral analysis######################
###############################################################################

run_fft_one_file <- function(
    file_name,
    replicate,
    H,
    SD,
    Gen,
    parameter_label,
    nseq = 10,
    spectrum_span = 2
) {
  
  full_df <- utils::read.csv(file_name, stringsAsFactors = FALSE)
  
  interval <- Gen
  
  #first_generation <- min(full_df$Generation, na.rm = TRUE)
  
  #########################################################################
  #### Sampling 1: first generation + first nseq end samples ########
  #########################################################################
  
  end_generations <- c(
    #first_generation,
    seq(
      from = interval,
      by = interval,
      length.out = nseq
    )
  ) %>%
    unique() %>%
    sort()
  
  gens_end <- full_df %>%
    filter(Generation %in% end_generations) %>%
    mutate(
      allele_id = as.factor(Position),
      sampling_scheme = "End",
      sampling_interval = interval
    )
  
  #########################################################################
  #### Sampling 2: first generation + first nseq mid/end samples ####
  #########################################################################
  
  mid_end_generations <- c(
   # first_generation,
    seq(
      from = interval / 2,
      by = interval / 2,
      length.out = nseq
    )
  ) %>%
    unique() %>%
    sort()
  
  gens_mid_end <- full_df %>%
    filter(Generation %in% mid_end_generations) %>%
    mutate(
      allele_id = as.factor(Position),
      sampling_scheme = "Mid & End",
      sampling_interval = interval / 2
    )
  
  #########################################################################
  #### Combine sampled data ###############################################
  #########################################################################
  
  sampled_data <- bind_rows(
    gens_end,
    gens_mid_end
  )
  
  
  #########################################################################
  #### Mean allele frequency per sampled generation #######################
  #########################################################################
  
  mean_allele_data <- sampled_data %>%
    group_by(sampling_scheme, sampling_interval, Generation) %>%
    summarize(
      mean_allele_frequency = mean(Frequency, na.rm = TRUE),
      .groups = "drop"
    ) %>%
    arrange(sampling_scheme, Generation)
  
  #########################################################################
  #### Computing the spectral density ######################################
  #########################################################################
  
  spectrum_data <- mean_allele_data %>%
    group_by(sampling_scheme, sampling_interval) %>%
    summarize(
      n_timepoints = n(),
      sampled_generations = list(Generation),
      ts_data = list(stats::ts(mean_allele_frequency, frequency = 1)),
      .groups = "drop"
    ) %>%
    filter(n_timepoints >= 4) %>%
    mutate(
      spec_result = map(
        ts_data,
        ~ stats::spectrum(
          .x,
          spans = spectrum_span,
          plot = FALSE
        )
      )
    ) %>%
    mutate(
      spectrum_tbl = map2(
        spec_result,
        sampling_interval,
        ~ tibble(
          Period_sample_units = 1 / .x$freq,
          
          # Convert period from sampled observations to real generations
          Period = (1 / .x$freq) * .y,
          
          Spectrum = as.numeric(.x$spec)
        )
      )
    ) %>%
    select(
      sampling_scheme,
      sampling_interval,
      n_timepoints,
      sampled_generations,
      spectrum_tbl
    ) %>%
    tidyr::unnest(spectrum_tbl) %>%
    mutate(
      replicate = replicate,
      H = H,
      SD = SD,
      Gen = Gen,
      parameter_label = parameter_label,
      file = basename(file_name)
    )
  
  spectrum_data
}

###############################################################################
########################## Low/High Multiple-File FFT ####################
###############################################################################

run_fft_low_high_multiple_files <- function(
    dirpath,
    pattern,
    nseq = 10,
    spectrum_span = 2,
    show_legend = FALSE
) {
  
  files_df <- parse_simulation_files(
    dirpath = dirpath,
    pattern = pattern
  )
  
  #########################################################################
  #### Keep only high and low combinations #############################
  #########################################################################
  
  files_df <- files_df %>%
    filter(
      (H == 0.1 & SD == 1 & Gen == 10) |
        (H == 0.8 & SD == 4 & Gen == 30)
    ) %>%
    mutate(
      parameter_label = case_when(
        H == 0.1 & SD == 1 & Gen == 10 ~ "h² = 0.1 Δ = 1 Gen=10",
        H == 0.8 & SD == 4 & Gen == 30 ~ "h² = 0.8 Δ = 4 Gen=30"
      ),
      parameter_label = factor(
        parameter_label,
        levels = c(
          "h² = 0.1 Δ = 1 Gen=10",
          "h² = 0.8 Δ = 4 Gen=30"
        )
      )
    )
  
  
  #########################################################################
  #### Apply FFT to each replicate/file ###################################
  #########################################################################
  
  plot_data <- pmap_dfr(
    list(
      file_name = files_df$file_name,
      replicate = files_df$replicate,
      H = files_df$H,
      SD = files_df$SD,
      Gen = files_df$Gen,
      parameter_label = files_df$parameter_label
    ),
    function(file_name, replicate, H, SD, Gen, parameter_label) {
      run_fft_one_file(
        file_name = file_name,
        replicate = replicate,
        H = H,
        SD = SD,
        Gen = Gen,
        parameter_label = parameter_label,
        nseq = nseq,
        spectrum_span = spectrum_span
      )
    }
  )
  
  
  #########################################################################
  #### Clean labels and enforce order #####################################
  #########################################################################
  
  plot_data <- plot_data %>%
    mutate(
      replicate = factor(replicate),
      sampling_scheme = factor(
        sampling_scheme,
        levels = c("End", "Mid & End")
      ),
      parameter_label = factor(
        parameter_label,
        levels = c(
          "h² = 0.1 Δ = 1 Gen=10",
          "h² = 0.8 Δ = 4 Gen=30"
        )
      )
    )
  
  #########################################################################
  #### The sampling includes the very first generation #############################
  #########################################################################
  # With the first generation included, the time series has one extra point,
  # but the regular sampling interval used for period conversion remains:
  #
  # End:       Gen
  # Mid & End: Gen / 2
  
  plot_data <- plot_data %>%
    mutate(
      period_min = case_when(
        sampling_scheme == "End" ~ 1, #2 * Gen,
        sampling_scheme == "Mid & End" ~ 1, #~ Gen,
        TRUE ~ NA_real_
      ),
      period_max = case_when(
        sampling_scheme == "End" ~ 5 * Gen,
        sampling_scheme == "Mid & End" ~ 5 * Gen,
        TRUE ~ NA_real_
      )
    ) %>%
    filter(
      Period >= period_min,
      Period <= period_max
    )

  #########################################################################
  #### Split into End and Mid & End #######################################
  #########################################################################
  
  plot_data_end <- plot_data %>%
    filter(sampling_scheme == "End")
  
  plot_data_mid_end <- plot_data %>%
    filter(sampling_scheme == "Mid & End")
  
  #########################################################################
  #### Common theme #######################################################
  #########################################################################
  
  theme_spectral <- theme_classic() +
    theme(
      text = element_text(family = "sans"),
      
      legend.position = ifelse(show_legend, "right", "none"),
      
      axis.text = element_text(
        size = 18,
        face = "bold"
      ),
      
      axis.title.x = element_text(
        margin = margin(t = 16),
        size = 20,
        face = "bold"
      ),
      
      axis.title.y = element_text(
        margin = margin(r = 18),
        size = 20,
        face = "bold"
      ),
      
      axis.line = element_line(
        linewidth = 2.2
      ),
      
      strip.text = element_text(
        size = 15,
        face = "bold"
      ),
      
      plot.title = element_text(
        hjust = 0.01,
        face = "bold",
        size = 34
      ),
      
      legend.title = element_text(
        size = 14,
        face = "bold"
      ),
      
      legend.text = element_text(
        size = 12
      ),
      
      panel.spacing = grid::unit(2.2, "lines")
    )
  
  #########################################################################
  #### A) End plot ########################################################
  #########################################################################
  
  p_end <- ggplot(
    plot_data_end,
    aes(
      x = Period,
      y = Spectrum,
      color = replicate,
      group = replicate
    )
  ) +
    geom_line(linewidth = 1.6, alpha = 0.85) +
   # geom_point()+
    facet_wrap(
      ~ parameter_label,
      scales = "free",
      nrow = 1
    ) +
    scale_x_continuous(
      breaks = scales::pretty_breaks(n = 5)
    ) +
    scale_y_continuous(
      labels = scales::label_number()
    ) +
    labs(
      title = "A) Spectral Density: Sampling at the end of each season",
      x = "Period (Generations)",
      y = "Spectral Density",
      color = "Replicate"
    ) +
    theme_spectral
  
  #########################################################################
  #### B) Mid & End plot ##################################################
  #########################################################################
  
  p_mid_end <- ggplot(
    plot_data_mid_end,
    aes(
      x = Period,
      y = Spectrum,
      color = replicate,
      group = replicate
    )
  ) +
    geom_line(linewidth = 1.6, alpha = 0.85) +
     #geom_point()+ 
    facet_wrap(
      ~ parameter_label,
      scales = "free",
      nrow = 1
    ) +
    scale_x_continuous(
      breaks = scales::pretty_breaks(n = 5)
    ) +
    scale_y_continuous(
      labels = scales::label_number()
    ) +
    labs(
      title = "B) Spectral Density: Sampling at the middle & end of each season",
      x = "Period (Generations)",
      y = "Spectral Density",
      color = "Replicate"
    ) +
    theme_spectral
  
  #########################################################################
  #### Combine with patchwork #############################################
  #########################################################################
  
  final_plot <- p_end / p_mid_end
  
  #return(final_plot)
  
  return(list(plot_data_end =plot_data_end, plot_data_mid_end = plot_data_mid_end, final_plot = final_plot))
}

###############################################################################
########################## Run: Exact Low and High Combos ######################
###############################################################################

final_plot_low_high <- run_fft_low_high_multiple_files(
  dirpath = dirpath,
  pattern = my_pattern,
  nseq = nseq,
  spectrum_span = spectrum_span,
  show_legend = FALSE
)

final_plot_low_high$final_plot

SamplingPointsSpectralAnalysis <- final_plot_low_high$final_plot


ggsave(filename = "SI_6.SamplingPointsSpectralAnalysis.jpg", SamplingPointsSpectralAnalysis, path = "../OutputFigures.dir/SupplementalFigures.dir", width = 20, height = 10, units = "in", dpi = 300, limitsize = FALSE)

# ###############################################################################
# ########################## Save plot ###########################################
# ###############################################################################
# 
# out_dir <- "../OutputFigures.dir"
# 
# if (!dir.exists(out_dir)) {
#   dir.create(out_dir, recursive = TRUE)
# }
# 
# ggsave(
#   filename = file.path(
#     out_dir,
#     "SpectralDensity_End_vs_MidEnd_FirstGeneration_First10Samples_ExactLowHigh_ByReplicate.pdf"
#   ),
#   plot = final_plot_low_high,
#   width = 24,
#   height = 12,
#   units = "in",
#   device = "pdf",
#   limitsize = FALSE
# )
# 
# ggsave(
#   filename = file.path(
#     out_dir,
#     "SpectralDensity_End_vs_MidEnd_FirstGeneration_First10Samples_ExactLowHigh_ByReplicate.jpg"
#   ),
#   plot = final_plot_low_high,
#   width = 24,
#   height = 12,
#   units = "in",
#   dpi = 300,
#   device = "jpeg",
#   limitsize = FALSE
# )
```



# 7. Simple Gradual Model

## 7.1. Allele frequency all parameters

```{r, warning=FALSE, echo=FALSE, message=FALSE}
rm(list = ls())
source("AlleleFrequencyPlotCode.R")
dirpath <- "../../Output.dir/SinFS.dir/"
pattern <- "^genome1_n(10|70|300)(?:\\D|$)"  #"^genome1\\D"
result <- process_files(dirpath, pattern, "loci_gen")

gradIplots_AF <- result$plots
```

### 7.1.1. Monogenic

```{r, warning=FALSE, fig.width = 40, fig.height = 55, echo=FALSE, message=FALSE}
#| label: GradI_Single_Locus_AllReplicates
#| fig-cap: "SI 7.1.1. Single locus 30 replicates allele frequency dynamics for gradual two equal seasons selection model, showing all parameter interactions. The highlighted line indicates the mean allele frequency for each generation."
#| fig-pos: "H"

library(dplyr)
library(ggplot2)


#####################################################
######### data processing function ##################
#####################################################

process_files <- function(dirpath, pattern) {
  
  files <- list.files(dirpath, pattern = pattern, full.names = TRUE)
  
  dataframes <- list()
  
  # Extracting parameters
  
  for (file in files) {
    fname <- basename(file) 
    H <- as.numeric(sub(".*_H(0\\.\\d+).*", "\\1", fname))
    loci <- as.numeric( sub(".*_n(\\d+)_.*", "\\1", fname))
    SD <- as.numeric(sub(".*SD(\\d+).*", "\\1", fname))
    Gen <- as.numeric(sub(".*Gen(\\d+).*", "\\1", fname))
    replicate <- as.numeric(sub(".*genome(\\d+)_.*", "\\1", fname))
    
    data <- read.csv(file, header = TRUE) %>% 
      mutate(
        H         = H,
        loci      = loci,
        SD        = SD,
        Gen       = Gen,
        replicate = as.factor(replicate),
        h2_sd     = paste0("h2 = ", H, " sd = ", SD),
        loci_gen  = paste0("loci = ", loci, " gen = ", Gen)
      )
    
    dataframes[[fname]] <- data
  }
  
  # Combine all dataframes into one 
  
  combined_data <- bind_rows(dataframes)
  
  return(combined_data)
}

########################################################################
######### Process the files to get combined data and make a plot ######
#######################################################################

dirpath <- "../../Output.dir/SinFS.dir/"
pattern <- "^genome\\d+_n(1)_H0\\.(1|5|8)(SD(1|2|4))?(Gen(10|20|30))?\\.csv$"

combined_data <- process_files(dirpath, pattern)

SimpleGradSingleLocusAF <- combined_data %>%
  mutate(
    H_SD_Gen = paste0("h\u00B2 = ", H, "\u0394\ = ", SD, " Gen = ", Gen)
  ) %>% 
  ggplot(aes(x = Generation, y = Frequency)) +
  geom_line(aes(group = replicate),
            color = "gray50", 
            alpha = 0.8, 
            size = 0.5) +
  # geom_hline(yintercept = 0.5, 
  #            color = "red4", 
  #            alpha = 0.5, 
  #            size = 3) +
  stat_summary(fun = mean,
               aes(group = 1), 
               geom = "line", 
               color = "red3", 
               alpha = 1, 
               size = 2) +
  facet_wrap(~ H_SD_Gen, ncol = 3) +
  labs(
    x = "Generation",
    y = "Frequency"
  ) +
  theme_bw() +
  theme(
    text = element_text(family = "sans"),
    legend.position = "none",
    axis.text.x = element_text(face = "bold", size = 40, angle = 35,
                               hjust = 1, margin = margin(t = 10)),
    axis.text.y = element_text(face = "bold", size = 40, angle = 15,
                               margin = margin(r = 10)),
    axis.line   = element_line(size = 2),
    plot.title  = element_text(hjust = 0.01, face = "bold", size = 40),
    axis.title.x = element_text(size = 40, face = "bold",
                                margin = margin(t = 10)),
    axis.title.y = element_text(size = 40, face = "bold",
                                margin = margin(r = 10)),
    strip.text = element_text(size = 40, face = "bold"),
    panel.spacing = unit(5, "lines"),
    panel.grid = element_blank()
  )

SimpleGradSingleLocusAF

ggsave(filename = "SI_7.1.1.SimpleGradSingleLocusAF.jpg", SimpleGradSingleLocusAF, path = "../OutputFigures.dir/SupplementalFigures.dir", width = 40, height = 55, units = "in", dpi = 300, limitsize = FALSE)
```

### 7.1.2. Oligogenic

```{r, fig.height = 40, fig.width = 50, echo=FALSE}
#| label: GradualI_AF_Loci10Gen10
#| fig-cap: "SI 7.1.2.1. Allele frequency dynamics for all parameter combinations with selection length of 10 generations from a single replicate, gradual two equal seasons selection model. Each line  represents the frequency trajectory for a locus from oligogenic trait (10 loci)."
#| fig-pos: "H"

GradualI_AF_Loci10Gen10 <- gradIplots_AF$`loci = 10 gen = 10` +
  ggtitle("Season Length (Gen) = 10") +
  theme(
    plot.title = element_text(
      hjust = 0.5,         
      size = 70, 
      color = "firebrick4",
      margin = margin(b = 40) 
    )
  )

print(GradualI_AF_Loci10Gen10)

ggsave(filename = "SI_7.1.2.1.GradualI_AF_Loci10Gen10.jpg", GradualI_AF_Loci10Gen10, path = "../OutputFigures.dir/SupplementalFigures.dir", width = 50, height = 40, units = "in", dpi = 300, limitsize = FALSE)
```

```{r, fig.height = 40, fig.width = 50, echo=FALSE}
#| label: GradualI_AF_Loci10Gen20
#| fig-cap: "SI 7.1.2.2. Allele frequency dynamics for all parameter combinations with selection length of 20 generations from a single replicate, gradual two equal seasons selection model. Each line  represents the frequency trajectory for a locus from oligogenic trait (10 loci)."
#| fig-pos: "H"
GradualI_AF_Loci10Gen20 <- gradIplots_AF$`loci = 10 gen = 20` +
  ggtitle("Season Length (Gen) = 20") +
  theme(
    plot.title = element_text(
      hjust = 0.5,         
      size = 70, 
      color = "firebrick4",
      margin = margin(b = 40) 
    )
  )

print(GradualI_AF_Loci10Gen20)

ggsave(filename = "SI_7.1.2.2.GradualI_AF_Loci10Gen20.jpg", GradualI_AF_Loci10Gen20, path = "../OutputFigures.dir/SupplementalFigures.dir", width = 50, height = 40, units = "in", dpi = 300, limitsize = FALSE)
```

```{r, fig.height = 40, fig.width = 50, echo=FALSE}
#| label: GradualI_AF_Loci10Gen30
#| fig-cap: "SI 7.1.2.3. Allele frequency dynamics for all parameter combinations with selection length of 30 generations from a single replicate, gradual two equal seasons selection model. Each line  represents the frequency trajectory for a locus from oligogenic trait (10 loci)."
#| fig-pos: "H"
GradualI_AF_Loci10Gen30 <- gradIplots_AF$`loci = 10 gen = 30` +
  ggtitle("Season Length (Gen) = 30") +
  theme(
    plot.title = element_text(
      hjust = 0.5,         
      size = 70, 
      color = "firebrick4",
      margin = margin(b = 40) 
    )
  )

print(GradualI_AF_Loci10Gen30)


ggsave(filename = "SI_7.1.2.3.GradualI_AF_Loci10Gen30.jpg", GradualI_AF_Loci10Gen30, path = "../OutputFigures.dir/SupplementalFigures.dir", width = 50, height = 40, units = "in", dpi = 300, limitsize = FALSE)
```

### 7.1.3. Polygenic 70 loci

```{r, fig.height = 40, fig.width = 50, echo=FALSE}
#| label: GradualI_AF_Loci70Gen10
#| fig-cap: "SI 7.1.3.1. Allele frequency dynamics for all parameter combinations with selection length of 10 generations from a single replicate, gradual two equal seasons selection model. Each line  represents the frequency trajectory for a locus from polygenic trait (70 loci)."
#| fig-pos: "H"
GradualI_AF_Loci70Gen10 <- gradIplots_AF$`loci = 70 gen = 10` +
  ggtitle("Season Length (Gen) = 10") +
  theme(
    plot.title = element_text(
      hjust = 0.5,         
      size = 70, 
      color = "firebrick4",
      margin = margin(b = 40) 
    )
  )

print(GradualI_AF_Loci70Gen10)


ggsave(filename = "SI_7.1.3.1.GradualI_AF_Loci70Gen10.jpg", GradualI_AF_Loci70Gen10, path = "../OutputFigures.dir/SupplementalFigures.dir", width = 50, height = 40, units = "in", dpi = 300, limitsize = FALSE)
```

```{r, fig.height = 40, fig.width = 50, echo=FALSE}
#| label: GradualI_AF_Loci70Gen20
#| fig-cap: "SI 7.1.3.2. Allele frequency dynamics for all parameter combinations with selection length of 20 generations from a single replicate, gradual two equal seasons selection model. Each line  represents the frequency trajectory for a locus from polygenic trait (70 loci)."
#| fig-pos: "H"
GradualI_AF_Loci70Gen20 <- gradIplots_AF$`loci = 70 gen = 20` +
  ggtitle("Season Length (Gen) = 20") +
  theme(
    plot.title = element_text(
      hjust = 0.5,         
      size = 70, 
      color = "firebrick4",
      margin = margin(b = 40) 
    )
  )

print(GradualI_AF_Loci70Gen20)

ggsave(filename = "SI_7.1.3.2.GradualI_AF_Loci70Gen20.jpg", GradualI_AF_Loci70Gen20, path = "../OutputFigures.dir/SupplementalFigures.dir", width = 50, height = 40, units = "in", dpi = 300, limitsize = FALSE)
```

```{r, fig.height = 40, fig.width = 50, echo=FALSE}
#| label: GradualI_AF_Loci70Gen30
#| fig-cap: "SI 7.1.3.3. Allele frequency dynamics for all parameter combinations with selection length of 30 generations from a single replicate, gradual two equal seasons selection model. Each line  represents the frequency trajectory for a locus from polygenic trait (70 loci)."
#| fig-pos: "H"
GradualI_AF_Loci70Gen30 <- gradIplots_AF$`loci = 70 gen = 30` +
  ggtitle("Season Length (Gen) = 30") +
  theme(
    plot.title = element_text(
      hjust = 0.5,         
      size = 70, 
      color = "firebrick4",
      margin = margin(b = 40) 
    )
  )

print(GradualI_AF_Loci70Gen30)

ggsave(filename = "SI_7.1.3.3.GradualI_AF_Loci70Gen30.jpg", GradualI_AF_Loci70Gen30, path = "../OutputFigures.dir/SupplementalFigures.dir", width = 50, height = 40, units = "in", dpi = 300, limitsize = FALSE)
```

### 7.1.4. Polygenic 300 loci

```{r, fig.height = 40, fig.width = 50, echo=FALSE}
#| label: GradualI_AF_Loci300Gen10
#| fig-cap: "SI 7.1.4.1. Allele frequency dynamics for all parameter combinations with selection length of 10 generations from a single replicate, gradual two equal seasons selection model. Each line  represents the frequency trajectory for a locus from polygenic trait (300 loci)."
#| fig-pos: "H"

GradualI_AF_Loci300Gen10 <- gradIplots_AF$`loci = 300 gen = 10` +
  ggtitle("Season Length (Gen) = 10") +
  theme(
    plot.title = element_text(
      hjust = 0.5,         
      size = 70, 
      color = "firebrick4",
      margin = margin(b = 40) 
    )
  )

print(GradualI_AF_Loci300Gen10)


ggsave(filename = "SI_7.1.4.1.GradualI_AF_Loci300Gen10.jpg", GradualI_AF_Loci300Gen10, path = "../OutputFigures.dir/SupplementalFigures.dir", width = 50, height = 40, units = "in", dpi = 300, limitsize = FALSE)
```

```{r, fig.height = 40, fig.width = 50, echo=FALSE}
#| label: GradualI_AF_Loci300Gen20
#| fig-cap: "SI 7.1.4.2. Allele frequency dynamics for all parameter combinations with selection length of 20 generations from a single replicate, gradual two equal seasons selection model. Each line  represents the frequency trajectory for a locus from polygenic trait (300 loci)."
#| fig-pos: "H"

GradualI_AF_Loci300Gen20 <- gradIplots_AF$`loci = 300 gen = 20` +
  ggtitle("Season Length (Gen) = 20") +
  theme(
    plot.title = element_text(
      hjust = 0.5,         
      size = 70, 
      color = "firebrick4",
      margin = margin(b = 40) 
    )
  )

print(GradualI_AF_Loci300Gen20)


ggsave(filename = "SI_7.1.4.2.GradualI_AF_Loci300Gen20.jpg", GradualI_AF_Loci300Gen20, path = "../OutputFigures.dir/SupplementalFigures.dir", width = 50, height = 40, units = "in", dpi = 300, limitsize = FALSE)
```

```{r, fig.height = 40, fig.width = 50, echo=FALSE}
#| label: GradualI_AF_Loci300Gen30
#| fig-cap: "SI 7.1.4.3. Allele frequency dynamics for all parameter combinations with selection length of 30 generations from a single replicate, gradual two equal seasons selection model. Each line  represents the frequency trajectory for a locus from polygenic trait (300 loci)."
#| fig-pos: "H"

GradualI_AF_Loci300Gen30 <- gradIplots_AF$`loci = 300 gen = 30` +
  ggtitle("Season Length (Gen) = 30") +
  theme(
    plot.title = element_text(
      hjust = 0.5,         
      size = 70, 
      color = "firebrick4",
      margin = margin(b = 40) 
    )
  )

print(GradualI_AF_Loci300Gen30)


ggsave(filename = "SI_7.1.4.3.GradualI_AF_Loci300Gen30.jpg", GradualI_AF_Loci300Gen30, path = "../OutputFigures.dir/SupplementalFigures.dir", width = 50, height = 40, units = "in", dpi = 300, limitsize = FALSE)
```

## 7.2. Spectral analysis for all parameters

```{r, echo=FALSE}
run_fft_analysis <- function(folder_path, pattern, spectrum_span = 2) {
  library(parallel)
  library(doParallel)
  library(foreach)
  library(dplyr)
  library(ggplot2)
  library(cowplot)
  
  
  theme_set(theme_classic())
  
  mythemes <- theme_bw() +
    theme(
      text            = element_text(family = "sans"), 
      legend.position = "none",
      axis.text.x     = element_text(face = "bold", size = 40, angle = 25, 
                                       margin = margin(t = 20), hjust = 1),
      axis.text.y     = element_text(face = "bold", size = 40, angle = 15, 
                                       margin = margin(r = 10)),
      axis.line       = element_line(size = 3),
      plot.title      = element_text(hjust = 0.01, face = "bold", size = 80, 
                                       margin = margin(b = 1, unit = "lines")),
      plot.margin     = unit(c(5, 1, 1, 1), "lines"),
      axis.title.x    = element_text(size = 40, face = "bold", margin = margin(t = 30)),
      axis.title.y    = element_text(size = 40, face = "bold", margin = margin(r = 35)),
      strip.text      = element_text(size = 40, face = "bold"),
      panel.spacing   = unit(5, "lines"),
      panel.grid      = element_blank()
    )
  
  # File list
  
  file_list <- list.files(path = folder_path, pattern = pattern, full.names = TRUE)
  
  if (length(file_list) == 0) {
    stop("No files found with the given pattern.")
  }
  
  # Create a data frame with filenames and extract parameters
  
  files_df <- data.frame(file_name = file_list) %>%
    mutate(
      base_name = basename(file_name),  
      n = ifelse(
         grepl("_n\\d+", base_name),
         as.numeric(sub(".*_n(\\d+).*", "\\1", base_name)),
         NA_real_
           ),
      replct <- as.numeric(sub(".*genome(\\d+)_.*", "\\1", base_name)),
      H = ifelse(
         grepl("_H[0-9]+\\.?[0-9]*", base_name),
         as.numeric(sub(".*_H([0-9]+\\.?[0-9]*).*", "\\1", base_name)),
         NA_real_
        ),
      SD = ifelse(
        grepl("SD[0-9]+(\\.[0-9]+)?", base_name),
        as.numeric(sub(".*SD([0-9]+(?:\\.[0-9]+)?).*", "\\1", base_name)),
        NA_real_
        ),
      Gen = ifelse(
        grepl("Gen\\d+", base_name),
        as.numeric(sub(".*Gen(\\d+).*", "\\1", base_name)),
        NA_real_
        ),
      Genome = case_when(
        n == "1" ~ "Monogenic",
        n == "10" ~ "Oligogenic",
        n == "70" ~ "Polygenic 70",
        n == "100" ~ "Polygenic 100",
        n == "300" ~ "Polygenic 300",
        TRUE ~ "Unknown"
      )
    ) %>%
    mutate(
      n = as.numeric(n),
      H = as.numeric(H),
      SD = as.numeric(SD),
      Gen = as.numeric(Gen),
      param_combination = paste0("n_", n, "_H", H, 
                                 ifelse(!is.na(SD), paste0("_SD", SD), ""), 
                                 ifelse(!is.na(Gen), paste0("_Gen", Gen), ""))
    )
  
  # Set up parallel backend
  
  num_cores <- detectCores()
  cl <- makeCluster(64)
  registerDoParallel(cl)
  
  # Read and combine data from all replicate files in parallel
  combined_data_list <- foreach(i = seq_along(files_df$file_name), .packages = c("dplyr")) %dopar% {
    file <- files_df$file_name[i]
    params <- files_df[i, ]
    df <- read.csv(file)
    data <- df %>%
      mutate(
        allele_id = as.factor(Position),
        generation = as.numeric(Generation),
        allele_frequency = Frequency,
        file = params$base_name,
        replct = params$replct,
        n = params$n,
        H = params$H,
        SD = params$SD,
        Gen = params$Gen,
        Genome = params$Genome,
        param_combination = params$param_combination
      ) %>%
      dplyr::select(allele_id, generation, allele_frequency, replct, n, H, SD, Gen, Genome, param_combination)
    data
  }
  combined_data <- bind_rows(combined_data_list)

  filtered_data <- combined_data 
  
  # Calculating the mean allele frequency for each grouping
  mean_allele_data <- filtered_data %>%
    group_by(generation, n, replct, H, SD, Gen, Genome, param_combination) %>%
    summarize(mean_allele_frequency = mean(allele_frequency), .groups = "drop")
  
  # Creating time series objects
  ts_data_list <- mean_allele_data %>%
    group_by(n, replct, H, SD, Gen, Genome, param_combination) %>%
    summarize(ts_data = list(ts(mean_allele_frequency, start = min(generation), frequency = 1)), .groups = 'drop')
  
  # Computing spectral density estimates in parallel
  spec_results_list <- foreach(i = 1:nrow(ts_data_list), .packages = c("stats")) %dopar% {
    ts_data <- ts_data_list$ts_data[[i]]
    spectrum(ts_data, spans = spectrum_span, plot = FALSE)
  }
  
  # Preparing data for plotting
  plot_data_list <- foreach(i = seq_along(spec_results_list), .packages = c("dplyr")) %dopar% {
    spec_result <- spec_results_list[[i]]
    params <- ts_data_list[i, ]
    period <- 1 / spec_result$freq
    data.frame(
      Period = period,
      Spectrum = spec_result$spec,
      n = params$n,
      replct = params$replct,
      H = params$H,
      SD = params$SD,
      Gen = params$Gen,
      Genome = params$Genome,
      param_combination = params$param_combination
    )
  }
  
  stopCluster(cl)
  

  plot_data <- bind_rows(plot_data_list)
  

  plot_data <- plot_data %>%
    group_by(param_combination) %>%
    mutate(threshold = case_when(
      Gen == 10 ~ 40,
      Gen == 20 ~ 50,
      Gen == 30 ~ 80,
      TRUE ~ 80
    )) %>%
    filter(Period < threshold) %>%
    ungroup() %>%
    mutate(
      Genome_Gen = paste0("Genome = ", Genome, " Gen = ", Gen),
      h2_sd = paste("H = ", H," ", "\u0394\ = ", SD, sep = ""), 
      #H_label = paste0("H = ", H),
      #SD_label = ifelse(!is.na(SD), paste0("SD = ", SD), "No SD"),
      Gen_label = ifelse(!is.na(Gen), paste0("Gen = ", Gen), "No Gen"),
      n_label = paste0("n_", n)
    )
  
  fft_plots <- list()
  
  uni_genomegen <- unique(plot_data$Genome_Gen)
  
  for(genomegen in uni_genomegen){
    myplot_data <- plot_data %>% filter(Genome_Gen == genomegen)

  fft_plots[[genomegen]] <- ggplot(myplot_data, aes(x = Period, y = Spectrum, color = factor(replct), group = factor(replct))) +
    geom_line(size = 1.1) +
    facet_wrap( ~ h2_sd, scales = "free") +
    labs(x = "Period (Generations)", y = "Spectral Density") +
    mythemes
  }
  
  return(fft_plots)
}

```

```{r, fig.height = 12, fig.width = 8, echo=FALSE}
dirpath <- "../../Output.dir/SinFS.dir/"
pattern <- "^genome"
gradIplots_SPA <- run_fft_analysis(dirpath, pattern, spectrum_span = 2)

```

### 7.2.1. Monogenic

```{r, fig.height = 40, fig.width = 50, echo=FALSE}
#| label: GradualI_Spect_Loci1Gen10
#| fig-cap: "SI 7.2.1.1. Spectral density across 30 replicates for monogenic trait (1 locus) with gradual optima change two equal seasons, all parameter combinations with selection length of 10 generations. Each peak represents a full cycle of selection period."
#| fig-pos: "H"

GradualI_Spect_Loci1Gen10 <- gradIplots_SPA[[1]] +
  ggtitle("Season Length (Gen) = 10") +
  theme(
    plot.title = element_text(
      hjust = 0.5,         
      size = 70, 
      color = "firebrick4",
      margin = margin(b = 40) 
    )
  )

print(GradualI_Spect_Loci1Gen10)


ggsave(filename = "SI_7.2.1.1.GradualI_Spect_Loci1Gen10.jpg", GradualI_Spect_Loci1Gen10, path = "../OutputFigures.dir/SupplementalFigures.dir", width = 50, height = 40, units = "in", dpi = 300, limitsize = FALSE)
```

```{r, fig.height = 40, fig.width = 50, echo=FALSE}
#| label: GradualI_Spect_Loci1Gen20
#| fig-cap: "SI 7.2.1.2. Spectral density across 30 replicates for monogenic trait (1 locus) with gradual optima change two equal seasons, all parameter combinations with selection length of 20 generations. Each peak represents a full cycle of selection period."
#| fig-pos: "H"

GradualI_Spect_Loci1Gen20 <- gradIplots_SPA[[2]] +
  ggtitle("Season Length (Gen) = 20") +
  theme(
    plot.title = element_text(
      hjust = 0.5,         
      size = 70, 
      color = "firebrick4",
      margin = margin(b = 40) 
    )
  )

print(GradualI_Spect_Loci1Gen20)


ggsave(filename = "SI_7.2.1.2.GradualI_Spect_Loci1Gen20.jpg", GradualI_Spect_Loci1Gen20, path = "../OutputFigures.dir/SupplementalFigures.dir", width = 50, height = 40, units = "in", dpi = 300, limitsize = FALSE)
```

```{r, fig.height = 40, fig.width = 50, echo=FALSE}
#| label: GradualI_Spect_Loci1Gen30
#| fig-cap: "SI 7.2.1.3. Spectral density across 30 replicates for monogenic trait (1 locus) with gradual optima change two equal seasons, all parameter combinations with selection length of 30 generations. Each peak represents a full cycle of selection period."
#| fig-pos: "H"

GradualI_Spect_Loci1Gen30 <- gradIplots_SPA[[3]] +
  ggtitle("Season Length (Gen) = 30") +
  theme(
    plot.title = element_text(
      hjust = 0.5,         
      size = 70, 
      color = "firebrick4",
      margin = margin(b = 40) 
    )
  )

print(GradualI_Spect_Loci1Gen30)


ggsave(filename = "SI_7.2.1.3.GradualI_Spect_Loci1Gen30.jpg", GradualI_Spect_Loci1Gen30, path = "../OutputFigures.dir/SupplementalFigures.dir", width = 50, height = 40, units = "in", dpi = 300, limitsize = FALSE)
```

### 7.2.2. Oligogenic

```{r, fig.height = 40, fig.width = 50, echo=FALSE}
#| label: GradualI_Spect_Loci10Gen10
#| fig-cap: "SI 7.2.2.1. Spectral density across 30 replicates for oligogenic trait (10 loci) with gradual optima change two equal seasons, all parameter combinations with selection length of 10 generations. Each peak represents a full cycle of selection period."
#| fig-pos: "H"

GradualI_Spect_Loci10Gen10 <- gradIplots_SPA[[4]] +
  ggtitle("Season Length (Gen) = 10") +
  theme(
    plot.title = element_text(
      hjust = 0.5,         
      size = 70, 
      color = "firebrick4",
      margin = margin(b = 40) 
    )
  )

print(GradualI_Spect_Loci10Gen10)


ggsave(filename = "SI_7.2.2.1.GradualI_Spect_Loci10Gen10.jpg", GradualI_Spect_Loci10Gen10, path = "../OutputFigures.dir/SupplementalFigures.dir", width = 50, height = 40, units = "in", dpi = 300, limitsize = FALSE)
```

```{r, fig.height = 40, fig.width = 50, echo=FALSE}
#| label: GradualI_Spect_Loci10Gen20
#| fig-cap: "SI 7.2.2.2. Spectral density across 30 replicates for oligogenic trait (10 loci) with gradual optima change two equal seasons, all parameter combinations with selection length of 20 generations. Each peak represents a full cycle of selection period."
#| fig-pos: "H"

GradualI_Spect_Loci10Gen20 <- gradIplots_SPA[[5]] +
  ggtitle("Season Length (Gen) = 20") +
  theme(
    plot.title = element_text(
      hjust = 0.5,         
      size = 70, 
      color = "firebrick4",
      margin = margin(b = 40) 
    )
  )

print(GradualI_Spect_Loci10Gen20)


ggsave(filename = "SI_7.2.2.2.GradualI_Spect_Loci10Gen20.jpg", GradualI_Spect_Loci10Gen20, path = "../OutputFigures.dir/SupplementalFigures.dir", width = 50, height = 40, units = "in", dpi = 300, limitsize = FALSE)
```

```{r, fig.height = 40, fig.width = 50, echo=FALSE}
#| label: GradualI_Spect_Loci10Gen30
#| fig-cap: "SI 7.2.2.3. Spectral density across 30 replicates for oligogenic trait (10 loci) with gradual optima change two equal seasons, all parameter combinations with selection length of 30 generations. Each peak represents a full cycle of selection period."
#| fig-pos: "H"

GradualI_Spect_Loci10Gen30 <- gradIplots_SPA[[6]] +
  ggtitle("Season Length (Gen) = 30") +
  theme(
    plot.title = element_text(
      hjust = 0.5,         
      size = 70, 
      color = "firebrick4",
      margin = margin(b = 40) 
    )
  )

print(GradualI_Spect_Loci10Gen30)


ggsave(filename = "SI_7.2.2.3.GradualI_Spect_Loci10Gen30.jpg", GradualI_Spect_Loci10Gen30, path = "../OutputFigures.dir/SupplementalFigures.dir", width = 50, height = 40, units = "in", dpi = 300, limitsize = FALSE)
```

### 7.2.3. Polygenic 70

```{r, fig.height = 40, fig.width = 50, echo=FALSE}
#| label: GradualI_Spect_Loci70Gen10
#| fig-cap: "SI 7.2.3.1. Spectral density across 30 replicates for polygenic trait (70 loci) with gradual optima change two equal seasons, all parameter combinations with selection length of 10 generations. Each peak represents a full cycle of selection period."
#| fig-pos: "H"

GradualI_Spect_Loci70Gen10 <- gradIplots_SPA[[7]] +
  ggtitle("Season Length (Gen) = 10") +
  theme(
    plot.title = element_text(
      hjust = 0.5,         
      size = 70, 
      color = "firebrick4",
      margin = margin(b = 40) 
    )
  )

print(GradualI_Spect_Loci70Gen10)


ggsave(filename = "SI_7.2.3.1.GradualI_Spect_Loci70Gen10.jpg", GradualI_Spect_Loci70Gen10, path = "../OutputFigures.dir/SupplementalFigures.dir", width = 50, height = 40, units = "in", dpi = 300, limitsize = FALSE)
```

```{r, fig.height = 40, fig.width = 50, echo=FALSE}
#| label: GradualI_Spect_Loci70Gen20
#| fig-cap: "SI 7.2.3.2. Spectral density across 30 replicates for polygenic trait (70 loci) with gradual optima change two equal seasons, all parameter combinations with selection length of 20 generations. Each peak represents a full cycle of selection period."
#| fig-pos: "H"

GradualI_Spect_Loci70Gen20 <- gradIplots_SPA[[8]] +
  ggtitle("Season Length (Gen) = 20") +
  theme(
    plot.title = element_text(
      hjust = 0.5,         
      size = 70, 
      color = "firebrick4",
      margin = margin(b = 40) 
    )
  )

print(GradualI_Spect_Loci70Gen20)


ggsave(filename = "SI_7.2.3.2.GradualI_Spect_Loci70Gen20.jpg", GradualI_Spect_Loci70Gen20, path = "../OutputFigures.dir/SupplementalFigures.dir", width = 50, height = 40, units = "in", dpi = 300, limitsize = FALSE)
```

```{r, fig.height = 40, fig.width = 50, echo=FALSE}
#| label: GradualI_Spect_Loci70Gen30
#| fig-cap: "SI 7.2.3.3. Spectral density across 30 replicates for polygenic trait (70 loci) with gradual optima change two equal seasons, all parameter combinations with selection length of 30 generations. Each peak represents a full cycle of selection period."
#| fig-pos: "H"

GradualI_Spect_Loci70Gen30 <- gradIplots_SPA[[9]] +
  ggtitle("Season Length (Gen) = 30") +
  theme(
    plot.title = element_text(
      hjust = 0.5,         
      size = 70, 
      color = "firebrick4",
      margin = margin(b = 40) 
    )
  )

print(GradualI_Spect_Loci70Gen30)


ggsave(filename = "SI_7.2.3.3.GradualI_Spect_Loci70Gen30.jpg", GradualI_Spect_Loci70Gen30, path = "../OutputFigures.dir/SupplementalFigures.dir", width = 50, height = 40, units = "in", dpi = 300, limitsize = FALSE)
```

### 7.2.4. Polygenic 300

```{r, fig.height = 40, fig.width = 50, echo=FALSE}
#| label: GradualI_Spect_Loci300Gen10
#| fig-cap: "SI 7.2.4.1. Spectral density across 30 replicates for polygenic trait (300 loci) with gradual optima change two equal seasons, all parameter combinations with selection length of 10 generations. Each peak represents a full cycle of selection period."
#| fig-pos: "H"

GradualI_Spect_Loci300Gen10 <- gradIplots_SPA[[13]] +
  ggtitle("Season Length (Gen) = 10") +
  theme(
    plot.title = element_text(
      hjust = 0.5,         
      size = 70, 
      color = "firebrick4",
      margin = margin(b = 40) 
    )
  )

print(GradualI_Spect_Loci300Gen10)


ggsave(filename = "SI_7.2.4.1.GradualI_Spect_Loci300Gen10.jpg", GradualI_Spect_Loci300Gen10, path = "../OutputFigures.dir/SupplementalFigures.dir", width = 50, height = 40, units = "in", dpi = 300, limitsize = FALSE)
```

```{r, fig.height = 40, fig.width = 50, echo=FALSE}
#| label: GradualI_Spect_Loci300Gen20
#| fig-cap: "SI 2.2.4.2. Spectral density across 30 replicates for polygenic trait (300 loci) with gradual optima change two equal seasons, all parameter combinations with selection length of 20 generations. Each peak represents a full cycle of selection period."
#| fig-pos: "H"

GradualI_Spect_Loci300Gen20 <- gradIplots_SPA[[14]] +
  ggtitle("Season Length (Gen) = 20") +
  theme(
    plot.title = element_text(
      hjust = 0.5,         
      size = 70, 
      color = "firebrick4",
      margin = margin(b = 40) 
    )
  )

print(GradualI_Spect_Loci300Gen20)

ggsave(filename = "SI_7.2.4.2.GradualI_Spect_Loci300Gen20.jpg", GradualI_Spect_Loci300Gen20, path = "../OutputFigures.dir/SupplementalFigures.dir", width = 50, height = 40, units = "in", dpi = 300, limitsize = FALSE)
```

```{r, fig.height = 40, fig.width = 50, echo=FALSE}
#| label: GradualI_Spect_Loci300Gen30
#| fig-cap: "SI 7.2.4.3. Spectral density across 30 replicates for polygenic trait (300 loci) with gradual optima change two equal seasons, all parameter combinations with selection length of 30 generations. Each peak represents a full cycle of selection period."
#| fig-pos: "H"

GradualI_Spect_Loci300Gen30 <- gradIplots_SPA[[15]] +
  ggtitle("Season Length (Gen) = 30") +
  theme(
    plot.title = element_text(
      hjust = 0.5,         
      size = 70, 
      color = "firebrick4",
      margin = margin(b = 40) 
    )
  )

print(GradualI_Spect_Loci300Gen30)

ggsave(filename = "SI_7.2.4.3.GradualI_Spect_Loci300Gen30.jpg", GradualI_Spect_Loci300Gen30, path = "../OutputFigures.dir/SupplementalFigures.dir", width = 50, height = 40, units = "in", dpi = 300, limitsize = FALSE)
```

# 8. Complex model I

## 8.1. Allele frequency all parameters for a single replicate

```{r, warning=FALSE, echo=FALSE, message=FALSE}
rm(list = ls())
source("AlleleFrequencyPlotCode.R")
dirpath <- "../../Output.dir/SinFSGen.dir/"
pattern <- pattern <- "^genome1_n(10|70|300)(?:\\D|$)"  #"^genome1\\D" 
result <- process_files(dirpath, pattern, "loci")
#
gradIIeQualDplots_AF <- result$plots
```

### 8.1.1. Monogenic

```{r, warning=FALSE, fig.width = 30, fig.height = 20, echo=FALSE, message=FALSE}
#| label: GradII_Single_Locus_AllReplicates
#| fig-cap: "SI 8.1.1. Single locus 30 replicates allele frequency dynamics for gradual optima change with even optima and uneven season length, showing all parameter interactions. The highlighted line indicates the mean allele frequency for each generation."
#| fig-pos: "H"
#| 
#####################################################
######### data processing function ##################
#####################################################

process_files <- function(dirpath, pattern) {
  
  files <- list.files(dirpath, pattern = pattern, full.names = TRUE)
  

  dataframes <- list()
  
  # Extracting parameters
  
  for (file in files) {
    fname <- basename(file) 
    H <- as.numeric(sub(".*_H(0\\.\\d+).*", "\\1", fname))
    loci <- as.numeric( sub(".*_n(\\d+)_.*", "\\1", fname))
    SD <- as.numeric(sub(".*SD(\\d+).*", "\\1", fname))
    replicate <- as.numeric(sub(".*genome(\\d+)_.*", "\\1", fname))
    
    
    data <- read.csv(file, header = TRUE) %>% 
      mutate(
        H  = H,
        loci = loci,
        SD = SD,
        replicate = as.factor(replicate))

    dataframes[[fname]] <- data
  }
  
  # Combine all dataframes into one 
  
  combined_data <- bind_rows(dataframes)
  
  return(combined_data)
}

########################################################################
######### Process the files to get combined data and make a plot ######
#######################################################################

dirpath <- "../../Output.dir/SinFSGen.dir/"
pattern <- "^genome\\d+_n(1)_H0\\.(1|5|8)(SD(1|2|4))?(Gen(10|20|30))?\\.csv$"

combined_data <- process_files(dirpath, pattern)

GradII_SingleLocusAF <- combined_data %>%
  mutate(
    h2_sd = paste0("SD = ", SD, ": ",  "h\u00B2 = ", H)
  ) %>% 
  ggplot(aes(x = Generation, y = Frequency)) +
  geom_line(aes(group = replicate),
            color = "gray50", 
            alpha = 0.8, 
            size = 0.5) +
  stat_summary(fun = mean,
               aes(group = 1), 
               geom = "line", 
               color = "red3", 
               alpha = 1, 
               size = 2) +
  facet_wrap(~ h2_sd, ncol = 3) +
  labs(
    x = "Generation",
    y = "Frequency"
  ) +
  theme_bw() +
  theme(
    text = element_text(family = "sans"),
    legend.position = "none",
    axis.text.x = element_text(face = "bold", size = 40, angle = 35,
                               hjust = 1, margin = margin(t = 10)),
    axis.text.y = element_text(face = "bold", size = 40, angle = 15,
                               margin = margin(r = 10)),
    axis.line   = element_line(size = 2),
    plot.title  = element_text(hjust = 0.01, face = "bold", size = 40),
    axis.title.x = element_text(size = 40, face = "bold",
                                margin = margin(t = 10)),
    axis.title.y = element_text(size = 40, face = "bold",
                                margin = margin(r = 10)),
    strip.text = element_text(size = 40, face = "bold"),
    panel.spacing = unit(5, "lines"),
    panel.grid = element_blank()
  )

GradII_SingleLocusAF


ggsave(filename = "SI_8.1.1.GradII_SingleLocusAF.jpg", GradII_SingleLocusAF, path = "../OutputFigures.dir/SupplementalFigures.dir", width = 30, height = 20, units = "in", dpi = 300, limitsize = FALSE)
```

### 8.1.2. Oligogenic

```{r, fig.height = 40, fig.width = 50, echo=FALSE}
#| label: GradII_Olig_AF
#| fig-cap: "SI 8.1.2. Allele frequency dynamics for all parameter combinations from a single replicate, gradual optima change with even optima and uneven season length. Each line  represents the frequency trajectory for a locus from oligogenic trait (10 loci)."
#| fig-pos: "H"

GradII_Olig_AF <- gradIIeQualDplots_AF[[10]] +
  ggtitle("Complex Model I Oligogenic") +
  theme(
    plot.title = element_text(
      hjust = 0.5,         
      size = 70, 
      color = "firebrick4",
      margin = margin(b = 40) 
    )
  )

print(GradII_Olig_AF)


ggsave(filename = "SI_8.1.2.GradII_Olig_AF.jpg", GradII_Olig_AF, path = "../OutputFigures.dir/SupplementalFigures.dir", width = 50, height = 40, units = "in", dpi = 300, limitsize = FALSE)
```

### 8.1.3. Polygenic 70 loci

```{r, fig.height = 40, fig.width = 50, echo=FALSE}
#| label: GradII_Poly_70_AF
#| fig-cap: "SI 8.1.3. Allele frequency dynamics for all parameter combinations from a single replicate, gradual optima change with even optima and uneven season length. Each line  represents the frequency trajectory for a locus from polygenic trait (70 loci)."
#| fig-pos: "H"

GradII_Poly_70_AF <- gradIIeQualDplots_AF[[70]] +
  ggtitle("Complex Model I Poligenic (70 loci)") +
  theme(
    plot.title = element_text(
      hjust = 0.5,         
      size = 70, 
      color = "firebrick4",
      margin = margin(b = 40) 
    )
  )

print(GradII_Poly_70_AF)


ggsave(filename = "SI_8.1.3.GradII_Poly_70_AF.jpg", GradII_Poly_70_AF, path = "../OutputFigures.dir/SupplementalFigures.dir", width = 50, height = 40, units = "in", dpi = 300, limitsize = FALSE)
```

### 8.1.4. Polygenic 300 loci

```{r, fig.height = 40, fig.width = 50, echo=FALSE}
#| label: GradII_Poly_300_AF
#| fig-cap: "SI 8.1.4. Allele frequency dynamics for all parameter combinations from a single replicate, gradual optima change with even optima and uneven season length. Each line  represents the frequency trajectory for a locus from polygenic trait (300 loci)."
#| fig-pos: "H"

GradII_Poly_300_AF <- gradIIeQualDplots_AF[[300]] +
  ggtitle("Complex Model I Poligenic (300 loci)") +
  theme(
    plot.title = element_text(
      hjust = 0.5,         
      size = 70, 
      color = "firebrick4",
      margin = margin(b = 40) 
    )
  )

print(GradII_Poly_300_AF)


ggsave(filename = "SI_8.1.4.GradII_Poly_300_AF.jpg", GradII_Poly_300_AF, path = "../OutputFigures.dir/SupplementalFigures.dir", width = 50, height = 40, units = "in", dpi = 300, limitsize = FALSE)
```


## 8.2. Spectral analysis for all parameters

```{r, echo=FALSE}
run_fft_analysis <- function(folder_path, pattern, spectrum_span = 2) {
  library(parallel)
  library(doParallel)
  library(foreach)
  library(dplyr)
  library(ggplot2)
  library(cowplot)
  
  
  theme_set(theme_classic())
  
  mythemes <- theme_bw() +
    theme(
      text            = element_text(family = "sans"), 
      legend.position = "none",
      axis.text.x     = element_text(face = "bold", size = 40, angle = 25, 
                                       margin = margin(t = 20), hjust = 1),
      axis.text.y     = element_text(face = "bold", size = 40, angle = 15, 
                                       margin = margin(r = 10)),
      axis.line       = element_line(size = 3),
      plot.title      = element_text(hjust = 0.01, face = "bold", size = 80, 
                                       margin = margin(b = 1, unit = "lines")),
      plot.margin     = unit(c(5, 1, 1, 1), "lines"),
      axis.title.x    = element_text(size = 40, face = "bold", margin = margin(t = 30)),
      axis.title.y    = element_text(size = 40, face = "bold", margin = margin(r = 35)),
      strip.text      = element_text(size = 40, face = "bold"),
      panel.spacing   = unit(5, "lines"),
      panel.grid      = element_blank()
    )
  
  # File list
  
  file_list <- list.files(path = folder_path, pattern = pattern, full.names = TRUE)
  
  if (length(file_list) == 0) {
    stop("No files found with the given pattern.")
  }
  
  # Create a data frame with filenames and extract parameters
  
  files_df <- data.frame(file_name = file_list) %>%
    mutate(
      base_name = basename(file_name),  
      n = ifelse(
         grepl("_n\\d+", base_name),
         as.numeric(sub(".*_n(\\d+).*", "\\1", base_name)),
         NA_real_
           ),
      replct <- as.numeric(sub(".*genome(\\d+)_.*", "\\1", base_name)),
      H = ifelse(
         grepl("_H[0-9]+\\.?[0-9]*", base_name),
         as.numeric(sub(".*_H([0-9]+\\.?[0-9]*).*", "\\1", base_name)),
         NA_real_
        ),
      SD = ifelse(
        grepl("SD[0-9]+(\\.[0-9]+)?", base_name),
        as.numeric(sub(".*SD([0-9]+(?:\\.[0-9]+)?).*", "\\1", base_name)),
        NA_real_
        ),
      Gen = ifelse(
        grepl("Gen\\d+", base_name),
        as.numeric(sub(".*Gen(\\d+).*", "\\1", base_name)),
        NA_real_
        ),
      Genome = case_when(
        n == "1" ~ "Monogenic",
        n == "10" ~ "Oligogenic",
        n == "70" ~ "Polygenic 70",
        n == "100" ~ "Polygenic 100",
        n == "300" ~ "Polygenic 300",
        TRUE ~ "Unknown"
      )
    ) %>%
    mutate(
      n = as.numeric(n),
      H = as.numeric(H),
      SD = as.numeric(SD),
      Gen = as.numeric(Gen),
      param_combination = paste0("n_", n, "_H", H, 
                                 ifelse(!is.na(SD), paste0("_SD", SD), ""), 
                                 ifelse(!is.na(Gen), paste0("_Gen", Gen), ""))
    )
  
  # Set up parallel backend
  
  num_cores <- detectCores()
  cl <- makeCluster(64)
  registerDoParallel(cl)
  
  # Read and combine data from all replicate files in parallel
  combined_data_list <- foreach(i = seq_along(files_df$file_name), .packages = c("dplyr")) %dopar% {
    file <- files_df$file_name[i]
    params <- files_df[i, ]
    df <- read.csv(file)
    data <- df %>%
      mutate(
        allele_id = as.factor(Position),
        generation = as.numeric(Generation),
        allele_frequency = Frequency,
        file = params$base_name,
        replct = params$replct,
        n = params$n,
        H = params$H,
        SD = params$SD,
        Gen = params$Gen,
        Genome = params$Genome,
        param_combination = params$param_combination
      ) %>%
      dplyr::select(allele_id, generation, allele_frequency, replct, n, H, SD, Gen, Genome, param_combination)
    data
  }
  combined_data <- bind_rows(combined_data_list) %>% filter(generation <=1802)

  filtered_data <- combined_data 
  
  # Calculating the mean allele frequency for each grouping
  mean_allele_data <- filtered_data %>%
    group_by(generation, n, replct, H, SD, Gen, Genome, param_combination) %>%
    summarize(mean_allele_frequency = mean(allele_frequency), .groups = "drop")
  
  # Creating time series objects
  ts_data_list <- mean_allele_data %>%
    group_by(n, replct, H, SD, Gen, Genome, param_combination) %>%
    summarize(ts_data = list(ts(mean_allele_frequency, start = min(generation), frequency = 1)), .groups = 'drop')
  
  # Computing spectral density estimates in parallel
  spec_results_list <- foreach(i = 1:nrow(ts_data_list), .packages = c("stats")) %dopar% {
    ts_data <- ts_data_list$ts_data[[i]]
    spectrum(ts_data, spans = spectrum_span, plot = FALSE)
  }
  
  # Preparing data for plotting
  plot_data_list <- foreach(i = seq_along(spec_results_list), .packages = c("dplyr")) %dopar% {
    spec_result <- spec_results_list[[i]]
    params <- ts_data_list[i, ]
    period <- 1 / spec_result$freq
    data.frame(
      Period = period,
      Spectrum = spec_result$spec,
      n = params$n,
      replct = params$replct,
      H = params$H,
      SD = params$SD,
      Gen = params$Gen,
      Genome = params$Genome,
      param_combination = params$param_combination
    )
  }
  
  stopCluster(cl)
  

  plot_data <- bind_rows(plot_data_list)
  

  plot_data <- plot_data %>%
    group_by(param_combination) %>%
    mutate(threshold = case_when(
      Gen == 10 ~ 40,
      Gen == 20 ~ 50,
      Gen == 30 ~ 80,
      TRUE ~ 80
    )) %>%
    filter(Period < threshold) %>%
    ungroup() %>%
    mutate(
      Genome_Gen = paste0("Genome = ", Genome, " Gen = ", Gen),
      h2_sd = paste("H = ", H," ", "\u0394\ = ", SD, sep = ""), 
      #H_label = paste0("H = ", H),
      #SD_label = ifelse(!is.na(SD), paste0("SD = ", SD), "No SD"),
      Gen_label = ifelse(!is.na(Gen), paste0("Gen = ", Gen), "No Gen"),
      n_label = paste0("n_", n)
    )
  
  fft_plots <- list()
  
  uni_genomegen <- unique(plot_data$Genome_Gen)
  
  for(genomegen in uni_genomegen){
    myplot_data <- plot_data %>% filter(Genome_Gen == genomegen)

  fft_plots[[genomegen]] <- ggplot(myplot_data, aes(x = Period, y = Spectrum, color = factor(replct), group = factor(replct))) +
    geom_line(size = 1.1) +
    facet_wrap( ~ h2_sd, scales = "free") +
    labs(x = "Period (Generations)", y = "Spectral Density") +
    mythemes
  }
  
  return(fft_plots)
}

```

```{r, fig.height = 8, fig.width = 12, echo=FALSE}
dirpath <- "../../Output.dir/SinFSGen.dir/"
pattern <- "^genome"
result <- run_fft_analysis(dirpath, pattern, spectrum_span = 2)
```

### 8.2.1. Polygenic 70

```{r, fig.height = 40, fig.width = 50, echo=FALSE}
#| label: GradII_Poly_70_SA
#| fig-cap: "SI 8.2.1. Spectral density across 30 replicates for polygenic trait (70 loci) with gradual optima change with even optima and uneven season length, all parameter combinations. For high parameters, Each peak represents one of the four full cycle of selection periods while the peaks are murky under low heritability and selection pressure (first column)."
#| fig-pos: "H"

GradII_Poly_70_SA <- result[[3]] +
  ggtitle("Spectral Density: Complex Model I Polygenic (70 loci)") +
  theme(
    plot.title = element_text(
      hjust = 0.5,         
      size = 70, 
      color = "firebrick4",
      margin = margin(b = 40) 
    )
  )

print(GradII_Poly_70_SA)


ggsave(filename = "SI_8.2.1.GradII_Poly_70_SA.jpg", GradII_Poly_70_SA, path = "../OutputFigures.dir/SupplementalFigures.dir", width = 50, height = 40, units = "in", dpi = 300, limitsize = FALSE)
```

### 8.2.2. Polygenic 300

```{r, fig.height = 40, fig.width = 50, echo=FALSE}
#| label: GradII_GradII_Poly_300_SA
#| fig-cap: "SI 8.2.2. Spectral density across 30 replicates for polygenic trait (300 loci) with gradual optima change with even optima and uneven season length, all parameter combinations. For high parameters, Each peak represents one of the four full cycle of selection periods while the peaks are murky under low heritability and selection pressure (first column)."
#| fig-pos: "H"
GradII_GradII_Poly_300_SA <- result[[5]] +
  ggtitle("Spectral Density: Complex Model I Polygenic (300 loci)") +
  theme(
    plot.title = element_text(
      hjust = 0.5,         
      size = 70, 
      color = "firebrick4",
      margin = margin(b = 40) 
    )
  )

print(GradII_GradII_Poly_300_SA)


ggsave(filename = "SI_8.2.2.GradII_Poly_300_SA.jpg", GradII_Poly_300_SA, path = "../OutputFigures.dir/SupplementalFigures.dir", width = 50, height = 40, units = "in", dpi = 300, limitsize = FALSE)
```

# 9. Complex model II

## 9.1. Allele frequency all parameters for a single replicate

```{r, warning=FALSE, echo=FALSE, message=FALSE}
rm(list = ls())
source("AlleleFrequencyPlotCode.R")
dirpath <- "../../Output.dir/FourSeasFourAmp.dir/"
pattern <- pattern <- "^genome1_n(10|70|300)(?:\\D|$)"  #"^genome1\\D" 
result <- process_files(dirpath, pattern, "loci")
#
gradIIplots_AF <- result$plots
```

### 9.1.1. Monogenic

```{r, warning=FALSE, fig.width = 40, fig.height = 15, echo=FALSE, message=FALSE}
#| label: GradII_Uneq_Single_Locus_AllReplicates
#| fig-cap: "SI 9.1.1. Single locus 30 replicates allele frequency dynamics for gradual optima change with uneven optima and uneven season length, showing all parameter interactions. The highlighted line indicates the mean allele frequency for each generation."
#| fig-pos: "H"
#| 
#####################################################
######### data processing function ##################
#####################################################

process_files <- function(dirpath, pattern) {
  
  files <- list.files(dirpath, pattern = pattern, full.names = TRUE)
  

  dataframes <- list()
  
  # Extracting parameters
  
  for (file in files) {
    fname <- basename(file) 
    H <- as.numeric(sub(".*_H(0\\.\\d+).*", "\\1", fname))
    loci <- as.numeric( sub(".*_n(\\d+)_.*", "\\1", fname))
    SD <- as.numeric(sub(".*SD(\\d+).*", "\\1", fname))
    replicate <- as.numeric(sub(".*genome(\\d+)_.*", "\\1", fname))
    
    
    data <- read.csv(file, header = TRUE) %>% 
      mutate(
        H = H,
        loci = loci,
        SD = SD,
        replicate = as.factor(replicate))

    dataframes[[fname]] <- data
  }
  
  # Combine all dataframes into one 
  
  combined_data <- bind_rows(dataframes)
  
  return(combined_data)
}

########################################################################
######### Process the files to get combined data and make a plot ######
#######################################################################

dirpath <- "../../Output.dir/FourSeasFourAmp.dir/"
pattern <- "^genome\\d+_n(1)_H0\\.(1|5|8)(SD(1|2|4))?(Gen(10|20|30))?\\.csv$"

combined_data <- process_files(dirpath, pattern)

GradII_SingleLocusAF <- combined_data %>%
  mutate(
    h2_sd = paste0("h\u00B2 = ", H)
  ) %>% 
  ggplot(aes(x = Generation, y = Frequency)) +
  geom_line(aes(group = replicate),
            color = "gray50", 
            alpha = 0.8, 
            size = 0.5) +
  stat_summary(fun = mean,
               aes(group = 1), 
               geom = "line", 
               color = "red3", 
               alpha = 1, 
               size = 1) +
  facet_wrap(~ h2_sd, ncol = 3) +
  labs(
    x = "Generation",
    y = "Frequency"
  ) +
  theme_bw() +
  theme(
    text = element_text(family = "sans"),
    legend.position = "none",
    axis.text.x = element_text(face = "bold", size = 40, angle = 35,
                               hjust = 1, margin = margin(t = 10)),
    axis.text.y = element_text(face = "bold", size = 40, angle = 15,
                               margin = margin(r = 10)),
    axis.line   = element_line(size = 2),
    plot.title  = element_text(hjust = 0.01, face = "bold", size = 40),
    axis.title.x = element_text(size = 40, face = "bold",
                                margin = margin(t = 10)),
    axis.title.y = element_text(size = 40, face = "bold",
                                margin = margin(r = 10)),
    strip.text = element_text(size = 40, face = "bold"),
    panel.spacing = unit(5, "lines"),
    panel.grid = element_blank()
  )

GradII_SingleLocusAF


ggsave(filename = "SI_9.1.1.GradII_SingleLocusAF.jpg", GradII_SingleLocusAF, path = "../OutputFigures.dir/SupplementalFigures.dir", width = 50, height = 40, units = "in", dpi = 300, limitsize = FALSE)
```

### 9.1.2. Oligogenic

```{r, fig.width = 40, fig.height = 15, echo=FALSE}
#| label: GradII_Uneq_Olig_AF
#| fig-cap: "SI 4.1.2. Allele frequency dynamics for all parameter combinations from a single replicate, gradual optima change with uneven optima and uneven season length. Each line  represents the frequency trajectory for a locus from oligogenic trait (10 loci)."
#| fig-pos: "H"

GradII_Olig_AF <- gradIIplots_AF[[10]] +
  ggtitle("Complex Model II") +
  theme(
    plot.title = element_text(
      hjust = 0.5,         
      size = 70, 
      color = "firebrick4",
      margin = margin(b = 40) 
    )
  )

print(GradII_Olig_AF)


ggsave(filename = "SI_9.1.2.GradII_Olig_AF.jpg", GradII_Olig_AF, path = "../OutputFigures.dir/SupplementalFigures.dir", width = 40, height = 15, units = "in", dpi = 300, limitsize = FALSE)
```

### 9.1.3. Polygenic 70 loci

```{r, fig.width = 40, fig.height = 15, echo=FALSE}
#| label: GradII_UnequalD_Poly_70_AF
#| fig-cap: "SI 4.1.3. Allele frequency dynamics for all parameter combinations from a single replicate, gradual optima change with uneven optima and uneven season length. Each line  represents the frequency trajectory for a locus from polygenic trait (70 loci)."
#| fig-pos: "H"

GradII_UnequalD_Poly_70_AF <- gradIIplots_AF[[70]] +
  ggtitle("Complex Model II Poligenic (70 loci)") +
  theme(
    plot.title = element_text(
      hjust = 0.5,         
      size = 70, 
      color = "firebrick4",
      margin = margin(b = 40) 
    )
  )

print(GradII_UnequalD_Poly_70_AF)


ggsave(filename = "SI_9.1.3.GradII_UnequalD_Poly_70_AF.jpg", GradII_UnequalD_Poly_70_AF, path = "../OutputFigures.dir/SupplementalFigures.dir", width = 40, height = 15, units = "in", dpi = 300, limitsize = FALSE)
```

### 9.1.4. Polygenic 300 loci

```{r, fig.width = 40, fig.height = 15, echo=FALSE}
#| label: GradII_UnequalD_Poly_300_AF
#| fig-cap: "SI 9.1.4. Allele frequency dynamics for all parameter combinations from a single replicate, gradual optima change with uneven optima and uneven season length. Each line  represents the frequency trajectory for a locus from polygenic trait (300 loci)."
#| fig-pos: "H"

GradII_UnequalD_Poly_300_AF <- gradIIplots_AF[[300]] +
  ggtitle("Complex Model II Poligenic (300 loci)") +
  theme(
    plot.title = element_text(
      hjust = 0.5,         
      size = 70, 
      color = "firebrick4",
      margin = margin(b = 40) 
    )
  )

print(GradII_UnequalD_Poly_300_AF)


ggsave(filename = "SI_9.1.4.GradII_UnequalD_Poly_300_AF.jpg", GradII_UnequalD_Poly_300_AF, path = "../OutputFigures.dir/SupplementalFigures.dir", width = 40, height = 15, units = "in", dpi = 300, limitsize = FALSE)
```

## 9.2. Spectral analysis for all parameters

```{r, echo=FALSE}
run_fft_analysis <- function(folder_path, pattern, spectrum_span = 2) {
  library(parallel)
  library(doParallel)
  library(foreach)
  library(dplyr)
  library(ggplot2)
  library(cowplot)
  
  
  theme_set(theme_classic())
  
  mythemes <- theme_bw() +
    theme(
      text = element_text(family = "sans"), 
      legend.position = "none",
      axis.text.x = element_text(face = "bold", size = 40, angle = 25, 
                                       margin = margin(t = 20), hjust = 1),
      axis.text.y = element_text(face = "bold", size = 40, angle = 15, 
                                       margin = margin(r = 10)),
      axis.line = element_line(size = 3),
      plot.title = element_text(hjust = 0.01, face = "bold", size = 80, 
                                       margin = margin(b = 1, unit = "lines")),
      plot.margin = unit(c(5, 1, 1, 1), "lines"),
      axis.title.x = element_text(size = 40, face = "bold", margin = margin(t = 30)),
      axis.title.y = element_text(size = 40, face = "bold", margin = margin(r = 35)),
      strip.text = element_text(size = 40, face = "bold"),
      panel.spacing = unit(5, "lines"),
      panel.grid = element_blank()
    )
  
  # File list
  
  file_list <- list.files(path = folder_path, pattern = pattern, full.names = TRUE)
  
  if (length(file_list) == 0) {
    stop("No files found with the given pattern.")
  }
  
  # Create a data frame with filenames and extract parameters
  
  files_df <- data.frame(file_name = file_list) %>%
    mutate(
      base_name = basename(file_name),  
      n = ifelse(
         grepl("_n\\d+", base_name),
         as.numeric(sub(".*_n(\\d+).*", "\\1", base_name)),
         NA_real_
           ),
      replct <- as.numeric(sub(".*genome(\\d+)_.*", "\\1", base_name)),
      H = ifelse(
         grepl("_H[0-9]+\\.?[0-9]*", base_name),
         as.numeric(sub(".*_H([0-9]+\\.?[0-9]*).*", "\\1", base_name)),
         NA_real_
        ),
      SD = ifelse(
        grepl("SD[0-9]+(\\.[0-9]+)?", base_name),
        as.numeric(sub(".*SD([0-9]+(?:\\.[0-9]+)?).*", "\\1", base_name)),
        NA_real_
        ),
      Gen = ifelse(
        grepl("Gen\\d+", base_name),
        as.numeric(sub(".*Gen(\\d+).*", "\\1", base_name)),
        NA_real_
        ),
      Genome = case_when(
        n == "1" ~ "Monogenic",
        n == "10" ~ "Oligogenic",
        n == "70" ~ "Polygenic 70",
        n == "100" ~ "Polygenic 100",
        n == "300" ~ "Polygenic 300",
        TRUE ~ "Unknown"
      )
    ) %>%
    mutate(
      n = as.numeric(n),
      H = as.numeric(H),
      SD = as.numeric(SD),
      Gen = as.numeric(Gen),
      param_combination = paste0("n_", n, "_H", H, 
                                 ifelse(!is.na(SD), paste0("_SD", SD), ""), 
                                 ifelse(!is.na(Gen), paste0("_Gen", Gen), ""))
    )
  
  # Set up parallel backend
  
  num_cores <- detectCores()
  cl <- makeCluster(64)
  registerDoParallel(cl)
  
  # Read and combine data from all replicate files in parallel
  combined_data_list <- foreach(i = seq_along(files_df$file_name), .packages = c("dplyr")) %dopar% {
    file <- files_df$file_name[i]
    params <- files_df[i, ]
    df <- read.csv(file)
    data <- df %>%
      mutate(
        allele_id = as.factor(Position),
        generation = as.numeric(Generation),
        allele_frequency = Frequency,
        file = params$base_name,
        replct = params$replct,
        n = params$n,
        H = params$H,
        SD = params$SD,
        Gen = params$Gen,
        Genome = params$Genome,
        param_combination = params$param_combination
      ) %>%
      dplyr::select(allele_id, generation, allele_frequency, replct, n, H, SD, Gen, Genome, param_combination)
    data
  }
  combined_data <- bind_rows(combined_data_list) %>% filter(generation <=1802)

  filtered_data <- combined_data 
  
  # Calculating the mean allele frequency for each grouping
  mean_allele_data <- filtered_data %>%
    group_by(generation, n, replct, H, SD, Gen, Genome, param_combination) %>%
    summarize(mean_allele_frequency = mean(allele_frequency), .groups = "drop")
  
  # Creating time series objects
  ts_data_list <- mean_allele_data %>%
    group_by(n, replct, H, SD, Gen, Genome, param_combination) %>%
    summarize(ts_data = list(ts(mean_allele_frequency, start = min(generation), frequency = 1)), .groups = 'drop')
  
  # Computing spectral density estimates in parallel
  spec_results_list <- foreach(i = 1:nrow(ts_data_list), .packages = c("stats")) %dopar% {
    ts_data <- ts_data_list$ts_data[[i]]
    spectrum(ts_data, spans = spectrum_span, plot = FALSE)
  }
  
  # Preparing data for plotting
  plot_data_list <- foreach(i = seq_along(spec_results_list), .packages = c("dplyr")) %dopar% {
    spec_result <- spec_results_list[[i]]
    params <- ts_data_list[i, ]
    period <- 1 / spec_result$freq
    data.frame(
      Period = period,
      Spectrum = spec_result$spec,
      n = params$n,
      replct = params$replct,
      H = params$H,
      SD = params$SD,
      Gen = params$Gen,
      Genome = params$Genome,
      param_combination = params$param_combination
    )
  }
  
  stopCluster(cl)
  

  plot_data <- bind_rows(plot_data_list)
  

  plot_data <- plot_data %>%
    group_by(param_combination) %>%
    mutate(threshold = case_when(
      Gen == 10 ~ 40,
      Gen == 20 ~ 50,
      Gen == 30 ~ 80,
      TRUE ~ 80
    )) %>%
    filter(Period < threshold) %>%
    ungroup() %>%
    mutate(
      Genome_Gen = paste0("Genome = ", Genome, " Gen = ", Gen),
      h2_sd = paste("H = ", H," ", "\u0394\ = ", SD, sep = ""), 
      #H_label = paste0("H = ", H),
      #SD_label = ifelse(!is.na(SD), paste0("SD = ", SD), "No SD"),
      Gen_label = ifelse(!is.na(Gen), paste0("Gen = ", Gen), "No Gen"),
      n_label = paste0("n_", n)
    )
  
  fft_plots <- list()
  
  uni_genomegen <- unique(plot_data$Genome_Gen)
  
  for(genomegen in uni_genomegen){
    myplot_data <- plot_data %>% filter(Genome_Gen == genomegen)

  fft_plots[[genomegen]] <- ggplot(myplot_data, aes(x = Period, y = Spectrum, color = factor(replct), group = factor(replct))) +
    geom_line(size = 1.1) +
    facet_wrap( ~ h2_sd, scales = "free") +
    labs(x = "Period (Generations)", y = "Spectral Density") +
    mythemes
  }
  
  return(fft_plots)
}

```

```{r, fig.width = 40, fig.height = 15, echo=FALSE}
dirpath <- "../../Output.dir/SinFSGen.dir/"
pattern <- "^genome"
result <- run_fft_analysis(dirpath, pattern, spectrum_span = 2)
```

### 9.2.1. Polygenic 70

```{r, fig.width = 40, fig.height = 25, echo=FALSE}
#| label: GradII_UnequalD_Poly_70_SA
#| fig-cap: "SI 9.2.1. Spectral density across 30 replicates for polygenic trait (70 loci) with gradual optima change with uneven optima and uneven season length, all parameter combinations. For high parameters, Each peak represents one of the four full cycle of selection periods while the peaks are murky under low heritability and selection pressure (first column)."
#| fig-pos: "H"

GradII_UnequalD_Poly_70_SA <- result[[3]] +
  ggtitle("Spectral Density: Complex Model II Polygenic (70 loci)") +
  theme(
    plot.title = element_text(
      hjust = 0.5,         
      size = 70, 
      color = "firebrick4",
      margin = margin(b = 40) 
    )
  )

print(GradII_UnequalD_Poly_70_SA)


ggsave(filename = "SI_9.2.1.GradII_UnequalD_Poly_70_SA.jpg", GradII_UnequalD_Poly_70_SA, path = "../OutputFigures.dir/SupplementalFigures.dir", width = 40, height = 25, units = "in", dpi = 300, limitsize = FALSE)
```

### 9.2.2. Polygenic 300

```{r, fig.width = 40, fig.height = 25, echo=FALSE}
#| label: GradII_GradII_UnequalD_Poly_300_SA
#| fig-cap: "SI 9.2.2. Spectral density across 30 replicates for polygenic trait (300 loci) with gradual optima change with uneven optima and uneven season length, all parameter combinations. For high parameters, Each peak represents one of the four full cycle of selection periods while the peaks are murky under low heritability and selection pressure (first column)."
#| fig-pos: "H"
GradII_GradII_UnequalD_Poly_300_SA <- result[[5]] +
  ggtitle("Spectral Density: Complex Model II Polygenic (300 loci)") +
  theme(
    plot.title = element_text(
      hjust = 0.5,         
      size = 70, 
      color = "firebrick4",
      margin = margin(b = 40) 
    )
  )

print(GradII_GradII_UnequalD_Poly_300_SA)


ggsave(filename = "SI_9.2.2.GradII_UnequalD_Poly_300_SA.jpg", GradII_UnequalD_Poly_300_SA, path = "../OutputFigures.dir/SupplementalFigures.dir", width = 40, height = 25, units = "in", dpi = 300, limitsize = FALSE)
```


## 10. Spectral All models comparisons


```{r,  warning=FALSE, fig.width = 50, fig.height = 30, dpi=300, echo=FALSE, message=FALSE}
#| label: All_models_Spec
#| fig-cap: "SI 10. Spectral analysis across 30 replicates for monogenic(left), oligogenic(middle), and polygenic(right) traits, with each colored is one replicate. For the simple gradual model, the parameters are h2 = 0.5, Δ = 2, and Gen = 20. Thus, the dominant spectral peaks occur at 40, consistent with a full seasonal cycle. Although the oligogenic model has more noise, the complex gradual model I (uneven season lengths and even distance to optima Δ) exhibit four distinct peaks aligned with the four-season lengths, plus a faded long period peak at 60 which signal the recurrence across multiple cycles. In complex gradual II (uneven season lengths and uneven Δ), the spectrum is noisier than other selection regimes, and it is challenging to observe all peaks corresponding to the number of considered seasons mainly because some seasons have a small selection pressure and the dynamics in those seasons are masked by the presence of seasons experiencing stronger selections."
#| fig-pos: "H"
n_values <- c(1, 10,100)#1, 
gene_number_labels <- c("1" = "1 Locus", "10" = "10 Loci", "100" = "100 Loci", "300" = "300 Loci")

selections <- list(
#"LinFS.dir" = "Instantaneous",
"SinFS.dir" = "Simple Gradual",
"SinFSGen.dir" = "Complex Gradual I", 
"FourSeasFourAmp.dir" = "Complex Gradual II"
)

allele_freq_list <- list()
for (n in n_values) {
  for (dir_name in names(selections)) {
    selection_label <- selections[[dir_name]]
    if (dir_name == "SinFSGen.dir") {
      file_pattern <- paste0("genome\\d+_n", n, "_H0\\.5SD2\\.csv$")
      file_path <- paste0("../../Output.dir/", dir_name)
    }else if (dir_name == "FourSeasFourAmp.dir") {
      file_pattern <- paste0("genome\\d+_n", n, "_H0\\.5\\.csv$")
      file_path <- paste0("../../Output.dir/", dir_name)
    } else {
      file_pattern <- paste0("genome\\d+_n", n, "_H0\\.5SD2Gen20\\.csv$")
      file_path <- paste0("../../Output.dir/", dir_name)
    }
    
    file_list <- list.files(
      path = file_path,
      pattern = file_pattern,
      full.names = TRUE
    )
    
    for (file in file_list) {
      data <- read.csv(file) #%>% filter(Generation >=1800)
      replicate_value <- as.numeric( sub(".*genome(\\d+)_.*", "\\1", basename(file)))
      
      data <- data %>%
        mutate(
          Selection = selection_label,
          Gene_Number = gene_number_labels[as.character(n)],
          Replicate = factor(replicate_value)
        )
      
      allele_freq_list[[length(allele_freq_list) + 1]] <- data
    }
  }
}

AlleleFreq_dataset <- bind_rows(allele_freq_list) %>%
  mutate(
    Selection = fct_relevel(Selection, "Instantaneous", "Simple Gradual", "Complex Gradual I", "Complex Gradual II"),
    Gene_Number = fct_relevel(Gene_Number, "1 Locus", "10 Loci", "100 Loci", "300 Loci")
  )

  num_cores_to_use <- min(detectCores() - 16, 8) # check the cores before
  cluster_type   <- if (.Platform$OS.type == "windows") "PSOCK" else "FORK"
  cl <- makeCluster(num_cores_to_use, type = cluster_type)
  registerDoParallel(cl)

grouped_data <- AlleleFreq_dataset %>%
  group_by(Selection, Gene_Number, Replicate)

unique_combinations <- grouped_data %>%
  summarize() %>%
  ungroup()

spectral_results <- foreach(i = 1:nrow(unique_combinations), .packages = c("dplyr", "stats")) %dopar% {
  sel <- unique_combinations$Selection[i]
  gene_num <- unique_combinations$Gene_Number[i]
  rep <- unique_combinations$Replicate[i]
  
  df <- AlleleFreq_dataset %>%
    filter(Selection == sel, Gene_Number == gene_num, Replicate == rep) %>%
    arrange(Generation)
  
  mean_freq_df <- df %>%
    group_by(Generation) %>%
    summarize(Mean_Frequency = mean(Frequency, na.rm = TRUE)) %>%
    arrange(Generation)
  
ts_data <- ts(mean_freq_df$Mean_Frequency, 
              start = min(mean_freq_df$Generation), frequency = 1)
  
spec_result <- spectrum(ts_data, spans = 2, plot = FALSE)
period <- 1 / spec_result$freq
  
  data.frame(
    Period = period,
    Spectrum = spec_result$spec,
    Selection = sel,
    Gene_Number = gene_num,
    Replicate = rep
  )
}

# Stop cluster
stopCluster(cl)

spectral_data <- bind_rows(spectral_results)

spectral_data <- spectral_data %>%
  filter(Period < 80)

All_models_Spec <- spectral_data %>%
  mutate(
    Facet_formula = factor(
      paste0(Gene_Number, " ", Selection),
      levels = c(
        "1 Locus Instantaneous", "10 Loci Instantaneous", "100 Loci Instantaneous",  "300 Loci Instantaneous",
        "1 Locus Simple Gradual", "10 Loci Simple Gradual", "100 Loci Simple Gradual",  "300 Loci Simple Gradual",
        "1 Locus Complex Gradual I", "10 Loci Complex Gradual I", "100 Loci Complex Gradual I" , "300 Loci Complex Gradual I" ,
        "1 Locus Complex Gradual II", "10 Loci Complex Gradual II", "100 Loci Complex Gradual II", "300 Loci Complex Gradual II"
      )
    )
  ) %>% 
  ggplot(aes(x = Period, y = Spectrum, group = Replicate, color = Replicate)) +
  geom_line(alpha = 1, size = 2) +
  scale_y_continuous(labels = scales::label_number())+
  #facet_wrap( ~ Selection + Gene_Number, scales = "free", ncol = 3) +
  facet_wrap( ~ Facet_formula, scales = "free", ncol = 3, dir = "h") +
  #scale_color_viridis_d() +  # Use a discrete color palette
  labs(
    x = "Period (Generations)",
    y = "Spectral Density",
    color = "Replicate"
  ) +
  labs(title = "Spectral Density", x = "Period (Generations)",
       y = "Spectral Density")+
  theme_bw()+
  mythemes
    
# 
# ggsave("All_models_Spec.jpg", plot = All_models_Spec, dpi = 600, width = 49, height = 30, units = "in", path = "../OutputFigures.dir")

ggsave("SI_10.All_models_Spec.jpg",  plot = All_models_Spec, width = 50, height = 30, units = "in", path = "../OutputFigures.dir/SupplementalFigures.dir", limitsize = FALSE)

print(All_models_Spec)
```


## 11. Fluctuating population fixation

```{r, fig.width=30, fig.height=20, echo=FALSE, message=FALSE}
#| label: FixationRate_comparison
#| fig-cap: "SI 11. Allele-frequency dynamics and initial QTL fixation across models with fluctuating selection and/or fluctuating population size for a polygenic model of 100 loci. The top panel shows allele-frequency dynamics for 30 randomly selected initial QTL alleles across five replicates in the high-parameter regime, while the bottom panel shows the mean ± SE percentage of initial QTL alleles fixed across 30 replicates."
#| fig-pos: "H"

rm(list = ls())

library(dplyr)
library(tidyr)
library(ggplot2)
library(stringr)
library(purrr)
library(future)
library(furrr)

plot_dir <- "/home/etb68/Mylab/evogen-sims/FluctSelectionModels.dir/WritingFigures.dir/OutputFigures.dir/Amplitudes_plt.dir/PopModels"
dir.create(plot_dir, recursive = TRUE, showWarnings = FALSE)

target_n <- 300
target_replicates <- 1:30
target_H <- c(0.1, 0.8)
target_SD <- c(1, 4)
target_Gen <- c(10, 30)

target_replicates_for_dynamics <- 1:5
dynamics_H <- 0.8
dynamics_SD <- 4
dynamics_Gen <- 30
n_alleles_for_dynamics <- 30
max_generation_to_plot <- 2000

default_Gen_if_missing <- 30
fixation_tol <- 1e-9

n_workers <- min(32, future::availableCores())
future::plan(multisession, workers = n_workers)

model_sources <- tibble(
  Model = c(
    "Constant_Selection Instantaneous_Population",
    "Null_Selection Instantaneous_Population",
    "Instantaneous_Selection Constant_Population",
    "Instantaneous_Selection Instantaneous_Population"
  ),
  folder_path = c(
    "~/Mylab/EvoGenFP.sims/FluctPopulationModels.dir/Output.dir/ConstSelInstatPop",
    "~/Mylab/EvoGenFP.sims/FluctPopulationModels.dir/Output.dir/NeutrSelInstatPop",
    "~/Mylab/evogen-sims/FluctSelectionModels.dir/Output.dir/LinFS.dir",
    "~/Mylab/EvoGenFP.sims/FluctPopulationModels.dir/Output.dir/InstSelInstatPop"
  )
) %>%
  mutate(folder_path = path.expand(folder_path))

safe_num <- function(x) {
  suppressWarnings(as.numeric(x))
}

clean_model_label <- function(x) {
  x %>%
    str_replace_all("_", " ") %>%
    str_replace(" Constant Population", "\nConstant Population") %>%
    str_replace(" Instantaneous Population", "\nInstantaneous Population")
}

make_allele_id <- function(df) {
  if (all(c("Position", "Effect", "Origin") %in% names(df))) {
    df %>%
      mutate(allele_id = paste(Position, Effect, Origin, sep = "_"))
  } else if (all(c("Position", "Effect") %in% names(df))) {
    df %>%
      mutate(allele_id = paste(Position, Effect, sep = "_"))
  } else {
    df %>%
      mutate(allele_id = as.character(Position))
  }
}

format_factors <- function(df) {
  df %>%
    mutate(
      Model = factor(Model, levels = model_sources$Model),
      Model_Label = factor(
        clean_model_label(as.character(Model)),
        levels = clean_model_label(model_sources$Model)
      ),
      H_factor = factor(H, levels = target_H),
      SD_factor = factor(SD, levels = target_SD),
      Gen_factor = factor(Gen, levels = target_Gen)
    )
}

extract_params <- function(file, Model) {
  file_name <- basename(file)
  
  tibble(
    Model = Model,
    file = file,
    file_name = file_name,
    replicate = coalesce(
      safe_num(str_match(file_name, "^genome([0-9]+)_")[, 2]),
      safe_num(str_match(file_name, "genome_repl([0-9]+)_")[, 2]),
      safe_num(str_match(file_name, "^repl([0-9]+)_")[, 2])
    ),
    n = coalesce(
      safe_num(str_match(file_name, "_n([0-9]+)_")[, 2]),
      safe_num(str_match(file_name, "_loci([0-9]+)_")[, 2])
    ),
    H = coalesce(
      safe_num(str_match(file_name, "H([0-9]+(?:\\.[0-9]+)?)SD")[, 2]),
      safe_num(str_match(file_name, "_h([0-9]+(?:\\.[0-9]+)?)")[, 2])
    ),
    SD = coalesce(
      safe_num(str_match(file_name, "SD([0-9]+(?:\\.[0-9]+)?)(?:Gen|\\.csv)")[, 2]),
      safe_num(str_match(file_name, "_SD([0-9]+(?:\\.[0-9]+)?)")[, 2])
    ),
    Gen = coalesce(
      safe_num(str_match(file_name, "Gen([0-9]+)")[, 2]),
      safe_num(str_match(file_name, "_Gen([0-9]+)")[, 2])
    )
  )
}

files_by_model <- model_sources %>%
  mutate(
    file = map(
      folder_path,
      ~ list.files(.x, pattern = "\\.csv$", full.names = TRUE)
    )
  ) %>%
  unnest(file)

if (nrow(files_by_model) == 0) {
  stop("No files found. Check model_sources$folder_path.")
}

param_table_raw <- pmap_dfr(
  files_by_model %>% select(file, Model),
  extract_params
) %>%
  filter(
    !is.na(replicate),
    !is.na(n),
    n == target_n,
    replicate %in% target_replicates
  )

if (nrow(param_table_raw) == 0) {
  stop("No files remain after n and replicate filtering.")
}

param_table <- param_table_raw %>%
  mutate(
    is_null = str_detect(Model, "^Null_Selection"),
    Gen = if_else(is_null & is.na(Gen), default_Gen_if_missing, Gen)
  ) %>%
  split(seq_len(nrow(.))) %>%
  map_dfr(function(row_df) {
    
    row_df <- as_tibble(row_df)
    
    if (row_df$is_null) {
      
      expand_grid(
        H = if (is.na(row_df$H)) target_H else row_df$H,
        SD = if (is.na(row_df$SD)) target_SD else row_df$SD,
        Gen = row_df$Gen
      ) %>%
        mutate(
          Model = row_df$Model,
          file = row_df$file,
          file_name = row_df$file_name,
          replicate = row_df$replicate,
          n = row_df$n
        )
      
    } else {
      
      tibble(
        Model = row_df$Model,
        file = row_df$file,
        file_name = row_df$file_name,
        replicate = row_df$replicate,
        n = row_df$n,
        H = row_df$H,
        SD = row_df$SD,
        Gen = row_df$Gen
      )
    }
  }) %>%
  filter(
    !is.na(H),
    !is.na(SD),
    !is.na(Gen),
    H %in% target_H,
    SD %in% target_SD,
    Gen %in% target_Gen
  ) %>%
  distinct(Model, file, file_name, replicate, n, H, SD, Gen, .keep_all = TRUE) %>%
  format_factors()

if (nrow(param_table) == 0) {
  stop("No files remain after parameter expansion and filtering.")
}

replicate_check <- param_table %>%
  count(Model, H, SD, Gen, name = "n_replicates") %>%
  filter(n_replicates != length(target_replicates))

if (nrow(replicate_check) > 0) {
  print(replicate_check)
  stop("Some model/parameter combinations do not have all target replicates.")
}

read_clean_allele_file <- function(file, file_name) {
  fl <- read.csv(file)
  
  if (!all(c("Generation", "Frequency", "Position") %in% names(fl))) {
    warning("Skipping file missing required columns: ", file_name)
    return(NULL)
  }
  
  fl %>%
    make_allele_id() %>%
    mutate(
      Generation = safe_num(Generation),
      Frequency = safe_num(Frequency),
      allele_id = as.character(allele_id)
    ) %>%
    filter(
      !is.na(Generation),
      !is.na(Frequency),
      !is.na(allele_id),
      is.finite(Generation),
      is.finite(Frequency)
    )
}

calculate_fixation <- function(Model, file, file_name, replicate, n, H, SD, Gen, ...) {
  fl <- read_clean_allele_file(file, file_name)
  if (is.null(fl) || nrow(fl) == 0) return(NULL)
  
  first_generation <- min(fl$Generation)
  
  initial_alleles <- fl %>%
    filter(Generation == first_generation) %>%
    distinct(allele_id)
  
  fixed_alleles <- fl %>%
    semi_join(initial_alleles, by = "allele_id") %>%
    filter(Frequency >= 1 - fixation_tol) %>%
    distinct(allele_id)
  
  tibble(
    Model = Model,
    file_name = file_name,
    replicate = replicate,
    n = n,
    H = H,
    SD = SD,
    Gen = Gen,
    fixed_count = nrow(fixed_alleles),
    total_initial_alleles = nrow(initial_alleles),
    fixation_percent = 100 * fixed_count / total_initial_alleles
  )
}

sample_allele_dynamics <- function(Model, file, file_name, replicate, n, H, SD, Gen, ...) {
  fl <- read_clean_allele_file(file, file_name)
  if (is.null(fl) || nrow(fl) == 0) return(NULL)
  
  first_generation <- min(fl$Generation)
  
  initial_alleles <- fl %>%
    filter(Generation == first_generation) %>%
    distinct(allele_id)
  
  fl <- fl %>%
    semi_join(initial_alleles, by = "allele_id") %>%
    filter(Generation <= max_generation_to_plot)
  
  if (nrow(fl) == 0) return(NULL)
  
  set.seed(
    768678 +
      as.integer(replicate) * 1000 +
      as.integer(n) +
      as.integer(SD) +
      as.integer(Gen) +
      as.integer(H * 100)
  )
  
  sampled_alleles <- sample(
    unique(fl$allele_id),
    min(n_alleles_for_dynamics, n_distinct(fl$allele_id)),
    replace = FALSE
  )
  
  fl %>%
    filter(allele_id %in% sampled_alleles) %>%
    mutate(
      Model = Model,
      file_name = file_name,
      replicate = replicate,
      n = n,
      H = H,
      SD = SD,
      Gen = Gen
    )
}

param_table_dynamics <- param_table %>%
  filter(
    replicate %in% target_replicates_for_dynamics,
    H == dynamics_H,
    SD == dynamics_SD,
    Gen == dynamics_Gen
  )

allele_dynamics_by_replicate <- future_pmap_dfr(
  param_table_dynamics,
  sample_allele_dynamics,
  .options = furrr_options(
    seed = TRUE,
    packages = c("dplyr", "stringr")
  )
) %>%
  format_factors()

Allele_Frequency_Dynamics_By_Replicate <- ggplot(
  allele_dynamics_by_replicate,
  aes(
    x = Generation,
    y = Frequency,
    group = interaction(Model, replicate, allele_id)
  )
) +
  geom_line(alpha = 0.35, linewidth = 0.45) +
  facet_grid(
    Model_Label ~ replicate,
    scales = "free_y",
    labeller = labeller(
      replicate = function(x) paste0("Replicate ", x)
    )
  ) +
  labs(
    x = "Generation",
    y = "Allele Frequency"
  ) +
  theme_bw() +
  theme(
    text = element_text(family = "sans"),
    axis.text.x = element_text(face = "bold", size = 10, angle = 45, hjust = 1),
    axis.text.y = element_text(face = "bold", size = 10),
    axis.line = element_line(linewidth = 0.8),
    axis.title.x = element_text(size = 16, face = "bold", margin = margin(t = 15)),
    axis.title.y = element_text(size = 16, face = "bold", margin = margin(r = 15)),
    strip.text.x = element_text(size = 12, face = "bold"),
    strip.text.y = element_text(size = 11, face = "bold"),
    panel.spacing = unit(0.8, "lines"),
    panel.grid = element_blank(),
    legend.position = "none"
  )

print(Allele_Frequency_Dynamics_By_Replicate)

fixation_by_replicate <- future_pmap_dfr(
  param_table,
  calculate_fixation,
  .options = furrr_options(
    seed = TRUE,
    packages = c("dplyr", "stringr")
  )
) %>%
  format_factors()

fixation_summary <- fixation_by_replicate %>%
  group_by(Model, Model_Label, H, SD, Gen, H_factor, SD_factor, Gen_factor) %>%
  summarize(
    mean_fixation_percent = mean(fixation_percent, na.rm = TRUE),
    se_fixation_percent = sd(fixation_percent, na.rm = TRUE) / sqrt(n()),
    .groups = "drop"
  ) %>%
  format_factors()

Fixation_Percentages_Model <- ggplot(
  fixation_summary,
  aes(
    x = Model_Label,
    y = mean_fixation_percent,
    color = H_factor,
    shape = SD_factor,
    linetype = Gen_factor,
    group = interaction(H_factor, SD_factor, Gen_factor)
  )
) +
  geom_line(linewidth = 3) +
  geom_point(size = 7, stroke = 1.1) +
  geom_errorbar(
    aes(
      ymin = pmax(mean_fixation_percent - se_fixation_percent, 0),
      ymax = pmin(mean_fixation_percent + se_fixation_percent, 100)
    ),
    width = 0.12,
    linewidth = 0.9,
    alpha = 0.8
  ) +
  labs(
    x = "Model",
    y = "Percentage of Initial QTL Alleles Fixed (%)",
    color = "Heritability (h\u00B2)",
    linetype = "Season Length (Gen)",
    shape = "Distance to Optimum (\u0394)"
  ) +
  scale_color_manual(values = c("0.1" = "darkblue", "0.8" = "firebrick")) +
  scale_linetype_manual(values = c("10" = "solid", "30" = "dashed")) +
  theme_bw() +
  theme(
    text = element_text(family = "sans"),
    axis.text.x = element_text(face = "bold", size = 26, angle = 20, hjust = 1),
    axis.text.y = element_text(face = "bold", size = 30),
    axis.line = element_line(linewidth = 1.2),
    axis.title.x = element_text(size = 30, face = "bold", margin = margin(t = 30)),
    axis.title.y = element_text(size = 30, face = "bold", margin = margin(r = 35)),
    panel.grid = element_blank(),
    legend.position = c(0.95, 0.95),
    legend.justification = c("right", "top"),
    legend.text = element_text(size = 32, face = "bold"),
    legend.title = element_text(size = 34, face = "bold"),
    legend.key.width = unit(2.5, "cm")
  ) +
  guides(
    color = guide_legend(override.aes = list(shape = 16, size = 6), byrow = TRUE),
    linetype = guide_legend(override.aes = list(linewidth = 2, color = "black"))
  )

print(Fixation_Percentages_Model)


ggsave(filename = "SI_11.Fixation_Percentages_Model_WithPop.jpg", Fixation_Percentages_Model, path = "../OutputFigures.dir/SupplementalFigures.dir", width = 40, height = 20, units = "in", dpi = 300, limitsize = FALSE)

# ggsave(
#   filename = "allele_frequency_dynamics_by_replicate.jpg",
#   plot = Allele_Frequency_Dynamics_By_Replicate,
#   path = plot_dir,
#   dpi = 600,
#   width = 26,
#   height = 18,
#   units = "in"
# )

# ggsave(
#   filename = "fixation_by_model_selection_population.jpg",
#   plot = Fixation_Percentages_Model,
#   path = plot_dir,
#   dpi = 600,
#   width = 40,
#   height = 20,
#   units = "in"
# )
```

