---
title: "Genome_Modeling_Yeast"
author: "Esdras T."
date: '2023-01-16'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(paletteer)
library(cowplot)
ggplot2::theme_set(theme_cowplot())
```

## Effect of selection pressure and population size on yeast phenotype and genotype over generations

The following document entails the path followed while designing the yeast model while considering the:
1) Constant selection (Optimum) vs Constant Population
2) Fluctuating selection vs Constant Population
3) Constant Selection vs Fluctuating Population
4) Fluctuating Selection vs Fluctuating Population

### 1) Constant selection (Optimum) vs Constant Population
 This model is straight forward as everything is constant. There are 100 QTL positions that affect the phenotype of interest (for example, change in temperature), and we also used a dummy population to start with some allele frequencies and effect of those QTL in our population. The optimum was considered to be the sum of mean phenotypes and 2 standard deviations. 

```{r echo=FALSE}
CSCP_Genom = read.csv("/Users/etb68/OneDrive - University of Missouri/Academics Mizzou (etb68@umsystem.edu)/Biologycal_Sciences/Research_Projects/Yeast_GitHub/evogen-sims/ET_Yeast/output.dir/DummyPop/WF_models/genome_CSCP_WF.csv")

CSCP_Pheno = read.csv("/Users/etb68/OneDrive - University of Missouri/Academics Mizzou (etb68@umsystem.edu)/Biologycal_Sciences/Research_Projects/Yeast_GitHub/evogen-sims/ET_Yeast/output.dir/DummyPop/WF_models/MeanPhenotypes_CSCP_WF.csv")

CSCP_Pheno %>% ggplot(aes(Generation, Phenotype)) + geom_point() +  theme_cowplot(12)
CSCP_Pheno %>% ggplot(aes(Phenotype)) + geom_histogram(bins = 150) +  theme_cowplot(12)

CSCP_Genom %>%  ggplot(aes(Generation, Frequency, col = as.character(Effect)))+
  geom_point()+
  theme_cowplot(12)+
  theme(legend.position = "none")

```

### 2) Fluctuating selection vs Constant Population

Different functions were used to set a fluctuating selection. 1) The first was to use two different optima where some generations were give an optimum of mean phenotype plus 2 sd and  other generations were given an optimum of mean phenotype minus 2 sd.  2) The next used a uniform distribution with a minimum optimum of mean phenotype minus 2sd and the maximum of mean phenotype plus 2sd. 3) The third used a normal distribution with mean = mean(phenotypes)+ sd(phenotypes) times 2 and  standard deviation = sd(phenotypes) times 2. 4) the fourth fluctuating selection was based of the increase of mean phenotype for every 25 generations for 1, 2, 3, and 4 standard deviations then the cycle starts over again until we reach the genration 1000. 5) The last fluctuation in selection was not based on the change in optimum, but the slection coefficient and dominance.
All the output results are read below, the graphs are combined together for easy comparison.

```{r echo=FALSE}
FSCP1_Genom = read.csv("/Users/etb68/OneDrive - University of Missouri/Academics Mizzou (etb68@umsystem.edu)/Biologycal_Sciences/Research_Projects/Yeast_GitHub/evogen-sims/ET_Yeast/output.dir/DummyPop/WF_models/genome_FSCP_WF.v1.csv")

FSCP1_Pheno = read.csv("/Users/etb68/OneDrive - University of Missouri/Academics Mizzou (etb68@umsystem.edu)/Biologycal_Sciences/Research_Projects/Yeast_GitHub/evogen-sims/ET_Yeast/output.dir/DummyPop/WF_models/MeanPhenotypes_FSCP_WF.v1.csv")

plot1_phenoGen = FSCP1_Pheno %>% ggplot(aes(Generation, Phenotype)) + geom_point() +  theme_cowplot(12)+ ggtitle("FSCP1 Pheno vs Generation")
plot1_pheno = FSCP1_Pheno %>% ggplot(aes(Phenotype)) + geom_histogram(bins = 150) +  theme_cowplot(12) + ggtitle("FSCP1 Pheno")

plot1_Genom = FSCP1_Genom %>%  ggplot(aes(Generation, Frequency, col = as.character(Effect)))+
  geom_point()+
  theme_cowplot(12)+
  theme(legend.position = "none")+
  ggtitle("FSCP1 Genome")

######################## FSCP2  #####################

FSCP2_Genom = read.csv("/Users/etb68/OneDrive - University of Missouri/Academics Mizzou (etb68@umsystem.edu)/Biologycal_Sciences/Research_Projects/Yeast_GitHub/evogen-sims/ET_Yeast/output.dir/DummyPop/WF_models/genome_FSCP_WF.v2.1.csv")

FSCP2_Pheno = read.csv("/Users/etb68/OneDrive - University of Missouri/Academics Mizzou (etb68@umsystem.edu)/Biologycal_Sciences/Research_Projects/Yeast_GitHub/evogen-sims/ET_Yeast/output.dir/DummyPop/WF_models/MeanPhenotypes_FSCP_WF.v2.1.csv")

plot2_phenoGen = FSCP2_Pheno %>% ggplot(aes(Generation, Phenotype)) + geom_point() +  theme_cowplot(12) + ggtitle("FSCP2 Pheno vs Generation")
plot2_pheno = FSCP2_Pheno %>% ggplot(aes(Phenotype)) + geom_histogram(bins = 150) +  theme_cowplot(12) + ggtitle("FSCP2 Pheno")

plot2_Genom = FSCP2_Genom %>%  ggplot(aes(Generation, Frequency, col = as.character(Effect)))+
  geom_point()+
  theme_cowplot(12)+
  theme(legend.position = "none")+
  ggtitle("FSCP2 Genome")

############## FSCP3  #################

FSCP3_Genom = read.csv("/Users/etb68/OneDrive - University of Missouri/Academics Mizzou (etb68@umsystem.edu)/Biologycal_Sciences/Research_Projects/Yeast_GitHub/evogen-sims/ET_Yeast/output.dir/DummyPop/WF_models/genome_FSCP_WF.v2.2.csv")

FSCP3_Pheno = read.csv("/Users/etb68/OneDrive - University of Missouri/Academics Mizzou (etb68@umsystem.edu)/Biologycal_Sciences/Research_Projects/Yeast_GitHub/evogen-sims/ET_Yeast/output.dir/DummyPop/WF_models/MeanPhenotypes_FSCP_WF.v2.2.csv")

plot3_phenoGen = FSCP3_Pheno %>% ggplot(aes(Generation, Phenotype)) + geom_point() +  theme_cowplot(12) + ggtitle("FSCP3 Pheno vs Generation")
plot3_pheno = FSCP3_Pheno %>% ggplot(aes(Phenotype)) + geom_histogram(bins = 150) +  theme_cowplot(12) + ggtitle("FSCP3 Pheno")

plot3_Genom = FSCP3_Genom %>%  ggplot(aes(Generation, Frequency, col = as.character(Effect)))+
  geom_point()+
  theme_cowplot(12)+
  theme(legend.position = "none")+
  ggtitle("FSCP3 Genome")

################### FSCP4  ################

FSCP4_Genom = read.csv("/Users/etb68/OneDrive - University of Missouri/Academics Mizzou (etb68@umsystem.edu)/Biologycal_Sciences/Research_Projects/Yeast_GitHub/evogen-sims/ET_Yeast/output.dir/DummyPop/WF_models/genome_FSCP_WF.v3.csv")

FSCP4_Pheno = read.csv("/Users/etb68/OneDrive - University of Missouri/Academics Mizzou (etb68@umsystem.edu)/Biologycal_Sciences/Research_Projects/Yeast_GitHub/evogen-sims/ET_Yeast/output.dir/DummyPop/WF_models/MeanPhenotypes_FSCP_WF.v3.csv")

plot4_phenoGen = FSCP4_Pheno %>% ggplot(aes(Generation, Phenotype)) + geom_point() +  theme_cowplot(12) + ggtitle("FSCP4 Pheno vs Generation")
plot4_pheno = FSCP4_Pheno %>% ggplot(aes(Phenotype)) + geom_histogram(bins = 150) +  theme_cowplot(12) + ggtitle("FSCP4 Pheno")

plot4_Genom = FSCP4_Genom %>%  ggplot(aes(Generation, Frequency, col = as.character(Effect)))+
  geom_point()+
  theme_cowplot(12)+
  theme(legend.position = "none")+
  ggtitle("FSCP4 Genome")

################## FSCP5  ######################

FSCP5_Genom = read.csv("/Users/etb68/OneDrive - University of Missouri/Academics Mizzou (etb68@umsystem.edu)/Biologycal_Sciences/Research_Projects/Yeast_GitHub/evogen-sims/ET_Yeast/output.dir/DummyPop/WF_models/genome_FSCP_WF.v4.csv")

FSCP5_Pheno = read.csv("/Users/etb68/OneDrive - University of Missouri/Academics Mizzou (etb68@umsystem.edu)/Biologycal_Sciences/Research_Projects/Yeast_GitHub/evogen-sims/ET_Yeast/output.dir/DummyPop/WF_models/MeanPhenotypes_FSCP_WF.v4.csv")

plot5_phenoGen = FSCP5_Pheno %>% ggplot(aes(Generation, Phenotype)) + geom_point() +  theme_cowplot(12) + ggtitle("FSCP5 Pheno vs Generation")

plot5_pheno = FSCP5_Pheno %>% ggplot(aes(Phenotype)) + geom_histogram(bins = 150) +  theme_cowplot(12) + ggtitle("FSCP5 Pheno")

plot5_Genom = FSCP5_Genom %>%  ggplot(aes(Generation, Frequency, col = as.character(Effect)))+
  geom_point()+
  theme_cowplot(12)+
  theme(legend.position = "none")+
  ggtitle("FSCP5 Genome")

plot_grid(plot1_phenoGen, plot2_phenoGen, plot3_phenoGen, plot4_phenoGen, plot5_phenoGen, ncol = 2)


```


```{r}
plot_grid(plot1_pheno, plot2_pheno, plot3_pheno, plot4_pheno, plot5_pheno, ncol = 2)
```


```{r}
plot_grid(plot1_Genom, plot2_Genom, plot3_Genom, plot4_Genom, plot5_Genom, ncol = 2)
```


### 3) Constant Selection vs Fluctuating Population

There are many ways of modeling a fluctuating population while considering a given generation interval. For this study, the chosen generation interval is mostly 25.The first model considered a population fluctuating between 10,000 and 1,000 for every 25 generations. In reality, such kind of pop might be hard to find it in normal world. Another possibility was to model a population that follows a uniform distribution (Check the code to know generation interval. Also, the pop size was integer, of course) with a minimum of 100 and max of 10,000. Also, Poisson distribution has been used while considering a mean (alpha parameter) of 10,000.
<<<<<<< HEAD

```{r}

### Constant Selection & fluctuating pop between 10000 and 1000

CSFPo_Genom = read.csv("/Users/etb68/OneDrive - University of Missouri/Academics Mizzou (etb68@umsystem.edu)/Biologycal_Sciences/Research_Projects/Yeast_GitHub/evogen-sims/ET_Yeast/output.dir/DummyPop/WF_models/genome_CSFP_WF.csv")

CSFPo_Pheno = read.csv("/Users/etb68/OneDrive - University of Missouri/Academics Mizzou (etb68@umsystem.edu)/Biologycal_Sciences/Research_Projects/Yeast_GitHub/evogen-sims/ET_Yeast/output.dir/DummyPop/WF_models/MeanPhenotypes_CSFP_WF.csv")

CSFPo_PhGen_plot = CSFPo_Pheno %>% ggplot(aes(Generation, Phenotype)) + geom_point() +  theme_cowplot(12) + ggtitle("Initial CSFP Pheno vs Generation")
CSFPo_Ph_plot = CSFPo_Pheno %>% ggplot(aes(Phenotype)) + geom_histogram(bins = 150) +  theme_cowplot(12) + ggtitle("Initial CSFP Pheno")

CSFPo_Geno_plot = CSFPo_Genom %>%  ggplot(aes(Generation, Frequency, col = as.character(Effect)))+
  geom_point()+
  theme_cowplot(12)+
  theme(legend.position = "none") + 
  ggtitle("Initial CSFP Allele Freq")

### Constant Selection & fluctuating pop following uniform distribution


CSFPu_Genom = read.csv("/Users/etb68/OneDrive - University of Missouri/Academics Mizzou (etb68@umsystem.edu)/Biologycal_Sciences/Research_Projects/Yeast_GitHub/evogen-sims/ET_Yeast/output.dir/DummyPop/WF_models/Uniform_Pop/genome_CSFPu_WF.csv")

CSFPu_Pheno = read.csv("/Users/etb68/OneDrive - University of Missouri/Academics Mizzou (etb68@umsystem.edu)/Biologycal_Sciences/Research_Projects/Yeast_GitHub/evogen-sims/ET_Yeast/output.dir/DummyPop/WF_models/Uniform_Pop/MeanPhenotypes_CSFPu_WF.csv")

CSFPu_PhGen_plot = CSFPu_Pheno %>% ggplot(aes(Generation, Phenotype)) + geom_point() +  theme_cowplot(12) + ggtitle("Unif CSFP Pheno vs Generation")
CSFPu_Ph_plot = CSFPu_Pheno %>% ggplot(aes(Phenotype)) + geom_histogram(bins = 150) +  theme_cowplot(12) + ggtitle("Unif CSFP Pheno")

CSFPu_Geno_plot = CSFPu_Genom %>%  ggplot(aes(Generation, Frequency, col = as.character(Effect)))+
  geom_point()+
  theme_cowplot(12)+
  theme(legend.position = "none") + 
  ggtitle("Unif CSFP Allele Freq")

### Constant Selection & fluctuating pop following Poisson distribution


CSFPp_Genom = read.csv("/Users/etb68/OneDrive - University of Missouri/Academics Mizzou (etb68@umsystem.edu)/Biologycal_Sciences/Research_Projects/Yeast_GitHub/evogen-sims/ET_Yeast/output.dir/DummyPop/WF_models/Pois_Pop/genome_CSFPp_WF.csv")

CSFPp_Pheno = read.csv("/Users/etb68/OneDrive - University of Missouri/Academics Mizzou (etb68@umsystem.edu)/Biologycal_Sciences/Research_Projects/Yeast_GitHub/evogen-sims/ET_Yeast/output.dir/DummyPop/WF_models/Pois_Pop/MeanPhenotypes_CSFPp_WF.csv")

CSFPp_PhGen_plot = CSFPp_Pheno %>% ggplot(aes(Generation, Phenotype)) + geom_point() +  theme_cowplot(12) + ggtitle("Pois CSFP Pheno vs Generation ")
CSFPp_Ph_plot = CSFPp_Pheno %>% ggplot(aes(Phenotype)) + geom_histogram(bins = 150) +  theme_cowplot(12) + ggtitle("Pois CSFP Pheno")

CSFPp_Geno_plot = CSFPp_Genom %>%  ggplot(aes(Generation, Frequency, col = as.character(Effect)))+
  geom_point()+
  theme_cowplot(12)+
  theme(legend.position = "none") + 
  ggtitle("Pois CSFP Allele Freq")

```


```{r}
plot_grid(CSFPo_PhGen_plot, CSFPu_PhGen_plot, CSFPp_PhGen_plot)

```


```{r}

plot_grid(CSFPo_Ph_plot, CSFPu_Ph_plot, CSFPp_Ph_plot)

```


```{r}
plot_grid(CSFPo_Geno_plot, CSFPu_Geno_plot, CSFPp_Geno_plot)
```


### 4) Fluctuating Selection vs Fluctuating Population

These models are the combinations of previously seen fluctuating models.That is, every stated fluctuation in selection combined with the initial, uniform, or poisson changes in population.

#### a) Optimum for some generations equals to mean phenotype plus 2 sd while others have mean phenotype minus 2 sd

```{r}
######Initial Pop (10000 and 1000) ###### 

FSFPo1_Genom = read.csv("/Users/etb68/OneDrive - University of Missouri/Academics Mizzou (etb68@umsystem.edu)/Biologycal_Sciences/Research_Projects/Yeast_GitHub/evogen-sims/ET_Yeast/output.dir/DummyPop/WF_models/genome_FSFP_WF.v1.csv")

FSFPo1_pheno = read.csv("/Users/etb68/OneDrive - University of Missouri/Academics Mizzou (etb68@umsystem.edu)/Biologycal_Sciences/Research_Projects/Yeast_GitHub/evogen-sims/ET_Yeast/output.dir/DummyPop/WF_models/MeanPhenotypes_FSFP_WF.v1.csv")

FSFPo1_PhGen_plot = FSFPo1_pheno %>% ggplot(aes(Generation, Phenotype)) + geom_point() +  theme_cowplot(12)+ ggtitle("FSFPo1 Pheno vs Generation")
FSFPo1_Ph_plot = FSFPo1_pheno %>% ggplot(aes(Phenotype)) + geom_histogram(bins = 150) +  theme_cowplot(12) + ggtitle("FSFPo1 Pheno")

FSFPo1_Geno_plot = FSFPo1_Genom %>%  ggplot(aes(Generation, Frequency, col = as.character(Effect)))+
  geom_point()+
  theme_cowplot(12)+
  theme(legend.position = "none")+
  ggtitle("FSFPo1 Genome")

###### Uniform Pop (with mean = 10,000) ###### 


FSFPu1_Genom = read.csv("/Users/etb68/OneDrive - University of Missouri/Academics Mizzou (etb68@umsystem.edu)/Biologycal_Sciences/Research_Projects/Yeast_GitHub/evogen-sims/ET_Yeast/output.dir/DummyPop/WF_models/Uniform_Pop/genome_FSFPu_WF.v1.csv")

FSFPu1_pheno = read.csv("/Users/etb68/OneDrive - University of Missouri/Academics Mizzou (etb68@umsystem.edu)/Biologycal_Sciences/Research_Projects/Yeast_GitHub/evogen-sims/ET_Yeast/output.dir/DummyPop/WF_models/Uniform_Pop/MeanPhenotypes_FSFPu_WF.v1.csv")

FSFPu1_PhGen_plot = FSFPu1_pheno %>% ggplot(aes(Generation, Phenotype)) + geom_point() +  theme_cowplot(12)+ ggtitle("FSFPu1 Pheno vs Generation")
FSFPu1_Ph_plot = FSFPu1_pheno %>% ggplot(aes(Phenotype)) + geom_histogram(bins = 150) +  theme_cowplot(12) + ggtitle("FSFPu1 Pheno")

FSFPu1_Geno_plot = FSFPu1_Genom %>%  ggplot(aes(Generation, Frequency, col = as.character(Effect)))+
  geom_point()+
  theme_cowplot(12)+
  theme(legend.position = "none")+
  ggtitle("FSFPu1 Genome")

###### Poisson Pop (with mean = 10,000) ###### 


FSFPp1_Genom = read.csv("/Users/etb68/OneDrive - University of Missouri/Academics Mizzou (etb68@umsystem.edu)/Biologycal_Sciences/Research_Projects/Yeast_GitHub/evogen-sims/ET_Yeast/output.dir/DummyPop/WF_models/Pois_Pop/genome_FSFPp_WF.v1.csv")

FSFPp1_pheno = read.csv("/Users/etb68/OneDrive - University of Missouri/Academics Mizzou (etb68@umsystem.edu)/Biologycal_Sciences/Research_Projects/Yeast_GitHub/evogen-sims/ET_Yeast/output.dir/DummyPop/WF_models/Pois_Pop/MeanPhenotypes_FSFPp_WF.v1.csv")

FSFPp1_PhGen_plot = FSFPp1_pheno %>% ggplot(aes(Generation, Phenotype)) + geom_point() +  theme_cowplot(12)+ ggtitle("FSFPp1 Pheno vs Generation")
FSFPp1_Ph_plot = FSFPp1_pheno %>% ggplot(aes(Phenotype)) + geom_histogram(bins = 150) +  theme_cowplot(12) + ggtitle("FSFPp1 Pheno")

FSFPp1_Geno_plot = FSFPp1_Genom %>%  ggplot(aes(Generation, Frequency, col = as.character(Effect)))+
  geom_point()+
  theme_cowplot(12)+
  theme(legend.position = "none")+
  ggtitle("FSFPp1 Genome")

```


```{r}
plot_grid(FSFPo1_PhGen_plot, FSFPu1_PhGen_plot, FSFPp1_PhGen_plot)

```


```{r}
plot_grid(FSFPo1_Ph_plot, FSFPu1_Ph_plot, FSFPp1_Ph_plot)
```


```{r}
plot_grid(FSFPo1_Geno_plot, FSFPu1_Geno_plot, FSFPp1_Geno_plot)

```

#### b) Optimum following uniform distribution

```{r}
######Initial Pop (10000 and 1000) ###### 

FSFPo2_Genom = read.csv("/Users/etb68/OneDrive - University of Missouri/Academics Mizzou (etb68@umsystem.edu)/Biologycal_Sciences/Research_Projects/Yeast_GitHub/evogen-sims/ET_Yeast/output.dir/DummyPop/WF_models/genome_FSFP_WF.v2.1.csv")

FSFPo2_pheno = read.csv("/Users/etb68/OneDrive - University of Missouri/Academics Mizzou (etb68@umsystem.edu)/Biologycal_Sciences/Research_Projects/Yeast_GitHub/evogen-sims/ET_Yeast/output.dir/DummyPop/WF_models/MeanPhenotypes_FSFP_WF.v2.1.csv")

FSFPo2_PhGen_plot = FSFPo2_pheno %>% ggplot(aes(Generation, Phenotype)) + geom_point() +  theme_cowplot(12)+ ggtitle("FSFPo2 Pheno vs Generation")
FSFPo2_Ph_plot = FSFPo2_pheno %>% ggplot(aes(Phenotype)) + geom_histogram(bins = 150) +  theme_cowplot(12) + ggtitle("FSFPo2 Pheno")

FSFPo2_Geno_plot = FSFPo2_Genom %>%  ggplot(aes(Generation, Frequency, col = as.character(Effect)))+
  geom_point()+
  theme_cowplot(12)+
  theme(legend.position = "none")+
  ggtitle("FSFPo2 Genome")

###### Uniform Pop (with mean = 10,000) ###### 


FSFPu2_Genom = read.csv("/Users/etb68/OneDrive - University of Missouri/Academics Mizzou (etb68@umsystem.edu)/Biologycal_Sciences/Research_Projects/Yeast_GitHub/evogen-sims/ET_Yeast/output.dir/DummyPop/WF_models/Uniform_Pop/genome_FSFPu_WF.v2.1.csv")

FSFPu2_pheno = read.csv("/Users/etb68/OneDrive - University of Missouri/Academics Mizzou (etb68@umsystem.edu)/Biologycal_Sciences/Research_Projects/Yeast_GitHub/evogen-sims/ET_Yeast/output.dir/DummyPop/WF_models/Uniform_Pop/MeanPhenotypes_FSFPu_WF.v2.1.csv")

FSFPu2_PhGen_plot = FSFPu2_pheno %>% ggplot(aes(Generation, Phenotype)) + geom_point() +  theme_cowplot(12)+ ggtitle("FSFPu2 Pheno vs Generation")
FSFPu2_Ph_plot = FSFPu2_pheno %>% ggplot(aes(Phenotype)) + geom_histogram(bins = 150) +  theme_cowplot(12) + ggtitle("FSFPu2 Pheno")

FSFPu2_Geno_plot = FSFPu2_Genom %>%  ggplot(aes(Generation, Frequency, col = as.character(Effect)))+
  geom_point()+
  theme_cowplot(12)+
  theme(legend.position = "none")+
  ggtitle("FSFPu2 Genome")

###### Poisson Pop (with mean = 10,000) ###### 


FSFPp2_Genom = read.csv("/Users/etb68/OneDrive - University of Missouri/Academics Mizzou (etb68@umsystem.edu)/Biologycal_Sciences/Research_Projects/Yeast_GitHub/evogen-sims/ET_Yeast/output.dir/DummyPop/WF_models/Pois_Pop/genome_FSFPp_WF.v2.1.csv")

FSFPp2_pheno = read.csv("/Users/etb68/OneDrive - University of Missouri/Academics Mizzou (etb68@umsystem.edu)/Biologycal_Sciences/Research_Projects/Yeast_GitHub/evogen-sims/ET_Yeast/output.dir/DummyPop/WF_models/Pois_Pop/MeanPhenotypes_FSFPp_WF.v2.1.csv")

FSFPp2_PhGen_plot = FSFPp1_pheno %>% ggplot(aes(Generation, Phenotype)) + geom_point() +  theme_cowplot(12)+ ggtitle("FSFPp2 Pheno vs Generation")
FSFPp2_Ph_plot = FSFPp2_pheno %>% ggplot(aes(Phenotype)) + geom_histogram(bins = 150) +  theme_cowplot(12) + ggtitle("FSFPp2 Pheno")

FSFPp2_Geno_plot = FSFPp2_Genom %>%  ggplot(aes(Generation, Frequency, col = as.character(Effect)))+
  geom_point()+
  theme_cowplot(12)+
  theme(legend.position = "none")+
  ggtitle("FSFPp2 Genome")

```


```{r}
plot_grid(FSFPo2_PhGen_plot, FSFPu2_PhGen_plot, FSFPp2_PhGen_plot)
```


```{r}
plot_grid(FSFPo2_Ph_plot, FSFPu2_Ph_plot, FSFPp2_Ph_plot)
```


```{r}
plot_grid(FSFPo2_Geno_plot, FSFPu2_Geno_plot, FSFPp2_Geno_plot)
```


#### c) Optimum following normal distribution

```{r}
######Initial Pop (10000 and 1000) ###### 

FSFPo3_Genom = read.csv("/Users/etb68/OneDrive - University of Missouri/Academics Mizzou (etb68@umsystem.edu)/Biologycal_Sciences/Research_Projects/Yeast_GitHub/evogen-sims/ET_Yeast/output.dir/DummyPop/WF_models/genome_FSFP_WF.v2.2.csv")

FSFPo3_pheno = read.csv("/Users/etb68/OneDrive - University of Missouri/Academics Mizzou (etb68@umsystem.edu)/Biologycal_Sciences/Research_Projects/Yeast_GitHub/evogen-sims/ET_Yeast/output.dir/DummyPop/WF_models/MeanPhenotypes_FSFP_WF.v2.2.csv")

FSFPo3_PhGen_plot = FSFPo3_pheno %>% ggplot(aes(Generation, Phenotype)) + geom_point() +  theme_cowplot(12)+ ggtitle("FSFPo3 Pheno vs Generation")
FSFPo3_Ph_plot = FSFPo3_pheno %>% ggplot(aes(Phenotype)) + geom_histogram(bins = 150) +  theme_cowplot(12) + ggtitle("FSFPo3 Pheno")

FSFPo3_Geno_plot = FSFPo3_Genom %>%  ggplot(aes(Generation, Frequency, col = as.character(Effect)))+
  geom_point()+
  theme_cowplot(12)+
  theme(legend.position = "none")+
  ggtitle("FSFPo3 Genome")

###### Uniform Pop (with mean = 10,000) ###### 


FSFPu3_Genom = read.csv("/Users/etb68/OneDrive - University of Missouri/Academics Mizzou (etb68@umsystem.edu)/Biologycal_Sciences/Research_Projects/Yeast_GitHub/evogen-sims/ET_Yeast/output.dir/DummyPop/WF_models/Uniform_Pop/genome_FSFPu_WF.v2.2.csv")

FSFPu3_pheno = read.csv("/Users/etb68/OneDrive - University of Missouri/Academics Mizzou (etb68@umsystem.edu)/Biologycal_Sciences/Research_Projects/Yeast_GitHub/evogen-sims/ET_Yeast/output.dir/DummyPop/WF_models/Uniform_Pop/MeanPhenotypes_FSFPu_WF.v2.2.csv")

FSFPu3_PhGen_plot = FSFPu3_pheno %>% ggplot(aes(Generation, Phenotype)) + geom_point() +  theme_cowplot(12)+ ggtitle("FSFPu3 Pheno vs Generation")
FSFPu3_Ph_plot = FSFPu3_pheno %>% ggplot(aes(Phenotype)) + geom_histogram(bins = 150) +  theme_cowplot(12) + ggtitle("FSFPu3 Pheno")

FSFPu3_Geno_plot = FSFPu3_Genom %>%  ggplot(aes(Generation, Frequency, col = as.character(Effect)))+
  geom_point()+
  theme_cowplot(12)+
  theme(legend.position = "none")+
  ggtitle("FSFPu3 Genome")

###### Poisson Pop (with mean = 10,000) ###### 


FSFPp3_Genom = read.csv("/Users/etb68/OneDrive - University of Missouri/Academics Mizzou (etb68@umsystem.edu)/Biologycal_Sciences/Research_Projects/Yeast_GitHub/evogen-sims/ET_Yeast/output.dir/DummyPop/WF_models/Pois_Pop/genome_FSFPp_WF.v2.2.csv")

FSFPp3_pheno = read.csv("/Users/etb68/OneDrive - University of Missouri/Academics Mizzou (etb68@umsystem.edu)/Biologycal_Sciences/Research_Projects/Yeast_GitHub/evogen-sims/ET_Yeast/output.dir/DummyPop/WF_models/Pois_Pop/MeanPhenotypes_FSFPp_WF.v2.2.csv")

FSFPp3_PhGen_plot = FSFPp1_pheno %>% ggplot(aes(Generation, Phenotype)) + geom_point() +  theme_cowplot(12)+ ggtitle("FSFPp3 Pheno vs Generation")
FSFPp3_Ph_plot = FSFPp3_pheno %>% ggplot(aes(Phenotype)) + geom_histogram(bins = 150) +  theme_cowplot(12) + ggtitle("FSFPp3 Pheno")

FSFPp3_Geno_plot = FSFPp3_Genom %>%  ggplot(aes(Generation, Frequency, col = as.character(Effect)))+
  geom_point()+
  theme_cowplot(12)+
  theme(legend.position = "none")+
  ggtitle("FSFPp3 Genome")

```


```{r}
plot_grid(FSFPo3_PhGen_plot, FSFPu3_PhGen_plot, FSFPp3_PhGen_plot)
```


```{r}
plot_grid(FSFPo3_Ph_plot, FSFPu3_Ph_plot, FSFPp3_Ph_plot)
```


```{r}
plot_grid(FSFPo3_Geno_plot, FSFPu3_Geno_plot, FSFPp3_Geno_plot)
```


#### d) Optimum adding 1 to 4 standard deviation for an interval of 25 

```{r echo=FALSE}
######Initial Pop (10000 and 1000) ###### 

FSFPo4_Genom = read.csv("/Users/etb68/OneDrive - University of Missouri/Academics Mizzou (etb68@umsystem.edu)/Biologycal_Sciences/Research_Projects/Yeast_GitHub/evogen-sims/ET_Yeast/output.dir/DummyPop/WF_models/genome_FSFP_WF.v3.csv")

FSFPo4_pheno = read.csv("/Users/etb68/OneDrive - University of Missouri/Academics Mizzou (etb68@umsystem.edu)/Biologycal_Sciences/Research_Projects/Yeast_GitHub/evogen-sims/ET_Yeast/output.dir/DummyPop/WF_models/MeanPhenotypes_FSFP_WF.v3.csv")

FSFPo4_PhGen_plot = FSFPo4_pheno %>% ggplot(aes(Generation, Phenotype)) + geom_point() +  theme_cowplot(12)+ ggtitle("FSFPo4 Pheno vs Generation")
FSFPo4_Ph_plot = FSFPo4_pheno %>% ggplot(aes(Phenotype)) + geom_histogram(bins = 150) +  theme_cowplot(12) + ggtitle("FSFPo4 Pheno")

FSFPo4_Geno_plot = FSFPo4_Genom %>%  ggplot(aes(Generation, Frequency, col = as.character(Effect)))+
  geom_point()+
  theme_cowplot(12)+
  theme(legend.position = "none")+
  ggtitle("FSFPo4 Genome")

###### Uniform Pop (with mean = 10,000) ###### 


FSFPu4_Genom = read.csv("/Users/etb68/OneDrive - University of Missouri/Academics Mizzou (etb68@umsystem.edu)/Biologycal_Sciences/Research_Projects/Yeast_GitHub/evogen-sims/ET_Yeast/output.dir/DummyPop/WF_models/Uniform_Pop/genome_FSFPu_WF.v3.csv")

FSFPu4_pheno = read.csv("/Users/etb68/OneDrive - University of Missouri/Academics Mizzou (etb68@umsystem.edu)/Biologycal_Sciences/Research_Projects/Yeast_GitHub/evogen-sims/ET_Yeast/output.dir/DummyPop/WF_models/Uniform_Pop/MeanPhenotypes_FSFPu_WF.V3.csv")

FSFPu4_PhGen_plot = FSFPu4_pheno %>% ggplot(aes(Generation, Phenotype)) + geom_point() +  theme_cowplot(12)+ ggtitle("FSFPu4 Pheno vs Generation")
FSFPu4_Ph_plot = FSFPu4_pheno %>% ggplot(aes(Phenotype)) + geom_histogram(bins = 150) +  theme_cowplot(12) + ggtitle("FSFPu4 Pheno")

FSFPu4_Geno_plot = FSFPu4_Genom %>%  ggplot(aes(Generation, Frequency, col = as.character(Effect)))+
  geom_point()+
  theme_cowplot(12)+
  theme(legend.position = "none")+
  ggtitle("FSFPu4 Genome")

###### Poisson Pop (with mean = 10,000) ###### 


FSFPp4_Genom = read.csv("/Users/etb68/OneDrive - University of Missouri/Academics Mizzou (etb68@umsystem.edu)/Biologycal_Sciences/Research_Projects/Yeast_GitHub/evogen-sims/ET_Yeast/output.dir/DummyPop/WF_models/Pois_Pop/genome_FSFPp_WF.v3.csv")

FSFPp4_pheno = read.csv("/Users/etb68/OneDrive - University of Missouri/Academics Mizzou (etb68@umsystem.edu)/Biologycal_Sciences/Research_Projects/Yeast_GitHub/evogen-sims/ET_Yeast/output.dir/DummyPop/WF_models/Pois_Pop/MeanPhenotypes_FSFPp_WF.v3.csv")

FSFPp4_PhGen_plot = FSFPp4_pheno %>% ggplot(aes(Generation, Phenotype)) + geom_point() +  theme_cowplot(12)+ ggtitle("FSFPp4 Pheno vs Generation")
FSFPp4_Ph_plot = FSFPp4_pheno %>% ggplot(aes(Phenotype)) + geom_histogram(bins = 150) +  theme_cowplot(12) + ggtitle("FSFPp4 Pheno")

FSFPp4_Geno_plot = FSFPp4_Genom %>%  ggplot(aes(Generation, Frequency, col = as.character(Effect)))+
  geom_point()+
  theme_cowplot(12)+
  theme(legend.position = "none")+
  ggtitle("FSFPp4 Genome")

```


```{r}
plot_grid(FSFPo4_PhGen_plot, FSFPu4_PhGen_plot, FSFPp4_PhGen_plot)

```


```{r}
plot_grid(FSFPo4_Ph_plot, FSFPu4_Ph_plot, FSFPp4_Ph_plot)
```


```{r}
plot_grid(FSFPo4_Geno_plot, FSFPu4_Geno_plot, FSFPp4_Geno_plot)
```


#### e) No optimum for fitness, instead, selection coef and dominance

```{r}
######Initial Pop (10000 and 1000) ###### 

FSFPo5_Genom = read.csv("/Users/etb68/OneDrive - University of Missouri/Academics Mizzou (etb68@umsystem.edu)/Biologycal_Sciences/Research_Projects/Yeast_GitHub/evogen-sims/ET_Yeast/output.dir/DummyPop/WF_models/genome_FSFP_WF.v4.csv")

FSFPo5_pheno = read.csv("/Users/etb68/OneDrive - University of Missouri/Academics Mizzou (etb68@umsystem.edu)/Biologycal_Sciences/Research_Projects/Yeast_GitHub/evogen-sims/ET_Yeast/output.dir/DummyPop/WF_models/MeanPhenotypes_FSFP_WF.v4.csv")

FSFPo5_PhGen_plot = FSFPo5_pheno %>% ggplot(aes(Generation, Phenotype)) + geom_point() +  theme_cowplot(12)+ ggtitle("FSFPo5 Pheno vs Generation")
FSFPo5_Ph_plot = FSFPo5_pheno %>% ggplot(aes(Phenotype)) + geom_histogram(bins = 150) +  theme_cowplot(12) + ggtitle("FSFPo5 Pheno")

FSFPo5_Geno_plot = FSFPo5_Genom %>%  ggplot(aes(Generation, Frequency, col = as.character(Effect)))+
  geom_point()+
  theme_cowplot(12)+
  theme(legend.position = "none")+
  ggtitle("FSFPo5 Genome")

###### Uniform Pop (with mean = 10,000) ###### 


FSFPu5_Genom = read.csv("/Users/etb68/OneDrive - University of Missouri/Academics Mizzou (etb68@umsystem.edu)/Biologycal_Sciences/Research_Projects/Yeast_GitHub/evogen-sims/ET_Yeast/output.dir/DummyPop/WF_models/Uniform_Pop/genome_FSFPu_WF.v4.csv")

FSFPu5_pheno = read.csv("/Users/etb68/OneDrive - University of Missouri/Academics Mizzou (etb68@umsystem.edu)/Biologycal_Sciences/Research_Projects/Yeast_GitHub/evogen-sims/ET_Yeast/output.dir/DummyPop/WF_models/Uniform_Pop/MeanPhenotypes_FSFPu_WF.v4.csv")

FSFPu5_PhGen_plot = FSFPu5_pheno %>% ggplot(aes(Generation, Phenotype)) + geom_point() +  theme_cowplot(12)+ ggtitle("FSFPu5 Pheno vs Generation")
FSFPu5_Ph_plot = FSFPu5_pheno %>% ggplot(aes(Phenotype)) + geom_histogram(bins = 150) +  theme_cowplot(12) + ggtitle("FSFPu5 Pheno")

FSFPu5_Geno_plot = FSFPu5_Genom %>%  ggplot(aes(Generation, Frequency, col = as.character(Effect)))+
  geom_point()+
  theme_cowplot(12)+
  theme(legend.position = "none")+
  ggtitle("FSFPu5 Genome")

###### Poisson Pop (with mean = 10,000) ###### 


FSFPp5_Genom = read.csv("/Users/etb68/OneDrive - University of Missouri/Academics Mizzou (etb68@umsystem.edu)/Biologycal_Sciences/Research_Projects/Yeast_GitHub/evogen-sims/ET_Yeast/output.dir/DummyPop/WF_models/Pois_Pop/genome_FSFPp_WF.v4.csv")

FSFPp5_pheno = read.csv("/Users/etb68/OneDrive - University of Missouri/Academics Mizzou (etb68@umsystem.edu)/Biologycal_Sciences/Research_Projects/Yeast_GitHub/evogen-sims/ET_Yeast/output.dir/DummyPop/WF_models/Pois_Pop/MeanPhenotypes_FSFPp_WF.v4.csv")

FSFPp5_PhGen_plot = FSFPp5_pheno %>% ggplot(aes(Generation, Phenotype)) + geom_point() +  theme_cowplot(12)+ ggtitle("FSFPp5 Pheno vs Generation")
FSFPp5_Ph_plot = FSFPp5_pheno %>% ggplot(aes(Phenotype)) + geom_histogram(bins = 150) +  theme_cowplot(12) + ggtitle("FSFPp5 Pheno")

FSFPp5_Geno_plot = FSFPp5_Genom %>%  ggplot(aes(Generation, Frequency, col = as.character(Effect)))+
  geom_point()+
  theme_cowplot(12)+
  theme(legend.position = "none")+
  ggtitle("FSFPp5 Genome")

```


```{r}
plot_grid(FSFPo5_PhGen_plot, FSFPu5_PhGen_plot, FSFPp5_PhGen_plot)
```


```{r}
plot_grid(FSFPo5_Ph_plot, FSFPu5_Ph_plot, FSFPp5_Ph_plot)
```


```{r}
plot_grid(FSFPo5_Geno_plot, FSFPu5_Geno_plot, FSFPp5_Geno_plot)
```
=======
>>>>>>> 4053e85d2cdbf6198cd36527325ccf73d3acda93

```{r}

### Constant Selection & fluctuating pop between 10000 and 1000

CSFPo_Genom = read.csv("/Users/etb68/OneDrive - University of Missouri/Academics Mizzou (etb68@umsystem.edu)/Biologycal_Sciences/Research_Projects/Yeast_GitHub/evogen-sims/ET_Yeast/output.dir/DummyPop/WF_models/genome_CSFP_WF.csv")

CSFPo_Pheno = read.csv("/Users/etb68/OneDrive - University of Missouri/Academics Mizzou (etb68@umsystem.edu)/Biologycal_Sciences/Research_Projects/Yeast_GitHub/evogen-sims/ET_Yeast/output.dir/DummyPop/WF_models/MeanPhenotypes_CSFP_WF.csv")

CSFPo_PhGen_plot = CSFPo_Pheno %>% ggplot(aes(Generation, Phenotype)) + geom_point() +  theme_cowplot(12) + ggtitle("Initial CSFP Pheno vs Generation")
CSFPo_Ph_plot = CSFPo_Pheno %>% ggplot(aes(Phenotype)) + geom_histogram(bins = 150) +  theme_cowplot(12) + ggtitle("Initial CSFP Pheno")

CSFPo_Geno_plot = CSFPo_Genom %>%  ggplot(aes(Generation, Frequency, col = as.character(Effect)))+
  geom_point()+
  theme_cowplot(12)+
  theme(legend.position = "none") + 
  ggtitle("Initial CSFP Allele Freq")

### Constant Selection & fluctuating pop following uniform distribution


CSFPu_Genom = read.csv("/Users/etb68/OneDrive - University of Missouri/Academics Mizzou (etb68@umsystem.edu)/Biologycal_Sciences/Research_Projects/Yeast_GitHub/evogen-sims/ET_Yeast/output.dir/DummyPop/WF_models/Uniform_Pop/genome_CSFPu_WF.csv")

CSFPu_Pheno = read.csv("/Users/etb68/OneDrive - University of Missouri/Academics Mizzou (etb68@umsystem.edu)/Biologycal_Sciences/Research_Projects/Yeast_GitHub/evogen-sims/ET_Yeast/output.dir/DummyPop/WF_models/Uniform_Pop/MeanPhenotypes_CSFPu_WF.csv")

CSFPu_PhGen_plot = CSFPu_Pheno %>% ggplot(aes(Generation, Phenotype)) + geom_point() +  theme_cowplot(12) + ggtitle("Unif CSFP Pheno vs Generation")
CSFPu_Ph_plot = CSFPu_Pheno %>% ggplot(aes(Phenotype)) + geom_histogram(bins = 150) +  theme_cowplot(12) + ggtitle("Unif CSFP Pheno")

CSFPu_Geno_plot = CSFPu_Genom %>%  ggplot(aes(Generation, Frequency, col = as.character(Effect)))+
  geom_point()+
  theme_cowplot(12)+
  theme(legend.position = "none") + 
  ggtitle("Unif CSFP Allele Freq")

### Constant Selection & fluctuating pop following Poisson distribution


CSFPp_Genom = read.csv("/Users/etb68/OneDrive - University of Missouri/Academics Mizzou (etb68@umsystem.edu)/Biologycal_Sciences/Research_Projects/Yeast_GitHub/evogen-sims/ET_Yeast/output.dir/DummyPop/WF_models/Pois_Pop/genome_CSFPp_WF.csv")

CSFPp_Pheno = read.csv("/Users/etb68/OneDrive - University of Missouri/Academics Mizzou (etb68@umsystem.edu)/Biologycal_Sciences/Research_Projects/Yeast_GitHub/evogen-sims/ET_Yeast/output.dir/DummyPop/WF_models/Pois_Pop/MeanPhenotypes_CSFPp_WF.csv")

CSFPp_PhGen_plot = CSFPp_Pheno %>% ggplot(aes(Generation, Phenotype)) + geom_point() +  theme_cowplot(12) + ggtitle("Pois CSFP Pheno vs Generation ")
CSFPp_Ph_plot = CSFPp_Pheno %>% ggplot(aes(Phenotype)) + geom_histogram(bins = 150) +  theme_cowplot(12) + ggtitle("Pois CSFP Pheno")

CSFPp_Geno_plot = CSFPp_Genom %>%  ggplot(aes(Generation, Frequency, col = as.character(Effect)))+
  geom_point()+
  theme_cowplot(12)+
  theme(legend.position = "none") + 
  ggtitle("Pois CSFP Allele Freq")

plot_grid(CSFPo_PhGen_plot, CSFPu_PhGen_plot, CSFPp_PhGen_plot)

plot_grid(CSFPo_Ph_plot, CSFPu_Ph_plot, CSFPp_Ph_plot)

plot_grid(CSFPo_Geno_plot, CSFPu_Geno_plot, CSFPp_Geno_plot)

```

### 4) Fluctuating Selection vs Fluctuating Population

These models are the combinations of previously seen fluctuating models.That is, every stated fluctuation in selection combined with the initial, uniform, or poisson changes in population.
