---
title: "Project_Proposal"
author: "ET"
format: html
editor: visual
---

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(tidyr)
library(ggplot2)
library(tidyselect)
library(dplyr)
library(stringr)
library(cowplot)
library(ggridges)
theme_set(theme_cowplot())
```

```{r, echo=FALSE, message=FALSE}
mytheme <- function(){
  theme_set(theme_cowplot())+
    theme(axis.title = element_text(face = "bold"),
          axis.text = element_text(face = "italic", size = 12),
          axis.line = element_line(size = 1),
          plot.title = element_text(hjust = 0.5),
          legend.position = "none")
}
```

```{r, echo=FALSE}
########### Infinitisimal Model #################
a = 5
b = 25
x = seq(1:100)
y <- function(x){
  Y = a*exp(-x/b)
}
Y <- y(x)
z = data.frame(Y, x)

z %>% ggplot(aes(x,Y))+
  geom_line(size = 2)+
  annotate("text", x = 55, y = max(Y)/1.5, label = "Exponential Effects", fontface = "bold", size = 10) +  #  Add this line
  labs(x = "Loci", y = "Effect", size = 17)+
  theme_set(theme_cowplot())+
  theme(legend.position = "none",
        axis.text = element_text(size = 17, face = "bold"),
        axis.line = element_line(size = 2),
        axis.title = element_text(size = 17, face = "bold"),
        strip.text = element_text(size = 17, face = "bold"))
```

## Selection Pressure

```{r, echo=FALSE}
Opti_Gen <- tibble(Generation = seq(1:100),
                   Optimum1 = rep(c(rep(110, 10), rep(90, 10)), 5),
                   Optimum2 = rep(c(rep(105, 10), rep(95, 10)), 5))

mu_pheno = mean(Opti_Gen$Optimum1)

Opt_Data <- Opti_Gen %>% 
  filter(Generation == 0 | Generation %% 25 != 0)

p2 <- ggplot()+
  geom_line(data = Opt_Data, aes(x = Generation, y = (Optimum1 - 100)/2.5), size = 1)+
  #geom_line(data = Opt_Data, aes(x = Generation, y = Optimum2), size = 1, color = "blue", linetype = "dotted")+
  #geom_hline(yintercept = mu_pheno, col = "darkred", size = 1)+
 # annotate("text", x = 55, y = mu_pheno + 0.5, 
    #       label = "Mean Phenotype", 
    #       size = 5, vjust = 0.1, hjust = 0., 
    #       col = "darkred", angle = 85)+
  #labs(x = NULL, y = NULL)+
  labs(x = "Generation", y = "Optimum")+
  theme_set(theme_cowplot())

p2

```

```{r, echo=FALSE}
Generation <- seq(1, 100, length.out = 400) 
phenotypes <- rnorm(10000, 0, 1)
Optimum <- 10 *sin( pi* Generation / 25) /2.5
df <- data.frame(Generation, Optimum) 

p3 <- ggplot(df) + 
  geom_line(aes(Generation, Optimum), size = 1) + 
  #geom_hline(yintercept = mean(Optimum), 
 #            color = "darkred", size = 1)+ 
 # annotate("text", x = 40, y = 100.5, 
  #         label = "Mean Phenotype", 
 #          size = 5, vjust = 0.1, hjust = 0, 
  #         col = "darkred", angle = 85)+ 
  #labs(x = NULL, y = NULL) + #  x = "Generation", y = "Phenotype"
  labs(x = "Generation", y = "Optimum")+
  theme_set(theme_cowplot())+
  theme(legend.position = "none",
        axis.text = element_text(size = 17, face = "bold"),
        axis.line = element_line(size = 2),
        axis.title = element_text(size = 17, face = "bold"),
        strip.text = element_text(size = 17, face = "bold"))

p3

```

```{r, echo=FALSE}
# Generation sequence from 1 to 2000
Generation <- c(1:100)
phenotypes <- rnorm(10000, 0, 1)
# Signals vector
signals = c(12, 22, 10, 16) # 5, 10, 20, 30

# Initialize Optimum vector
Optimum = rep(0, length(Generation))

# Loop over each signal to calculate the Optimum
for (i in signals) {
    #Optimum = Optimum + 4 * sin((pi) * Generation / i)
  Optimum = Optimum + (mean(phenotypes) + sd(phenotypes)*4) * sin((22/7) * Generation / i)
}
Optimum = Optimum / 4

# Create data frame for plotting
df <- data.frame(Generation, Optimum)

# Load necessary libraries
library(ggplot2)
library(cowplot)
library(dplyr)

# Plot the Optimum over the first 501 generations
p4 <- ggplot(df %>% filter(Generation < 502)) + 
    geom_line(aes(Generation, Optimum), size = 1) +
    #geom_hline(yintercept = mean(phenotypes), color = "darkred", size = 5) +
    #annotate("text", x = 75, y = 0.1, label = "Mean Phenotype", size = 10, vjust = 0.1, hjust = 0, col = "darkred", angle = 70) + 
    
    ylim(-4, 4) +  # Set y-axis limits
    labs(x = "Generation", y = "Optimum")+
  theme_set(theme_cowplot())+
  theme(legend.position = "none",
        axis.text = element_text(size = 17, face = "bold"),
        axis.line = element_line(size = 2),
        axis.title = element_text(size = 17, face = "bold"),
        strip.text = element_text(size = 17, face = "bold"))

print(p4)

```

```{r, echo=FALSE, fig.width = 8, fig.height = 4}
mygrid <- plot_grid(p1, p2, p3, p4, labels = "AUTO", label_size = 10,label_colour = NULL, label_x = 0.15, label_y = 1.02, hjust = -0.5, vjust = 1.5, scale = 1,ncol = 2, align = "hv") +
  theme(plot.margin = margin(t = 10, r = 10, b = 10, l = 10)) +
  draw_label("Generation", size = 17, x = 0.5, y = -0.0105, hjust = .3, fontface = "bold")+
  draw_label("Phenotype", size = 17, x = -0.007, y = 0.5, vjust = 0.5, angle = 90, fontface = "bold")

mygrid

```

## Population Size

```{r, warning = FALSE, echo = FALSE}
library(ggplot2)
library(cowplot)
library(gganimate)
library(gifski)

mytheme <- theme(
  axis.text = element_text(size = 20, face = "bold"),
  axis.line = element_line(size = 2),
  axis.title = element_text(size = 20, face = "bold"),
  strip.text = element_text(size = 20, face = "bold"),
  legend.title = element_text(size = 20, face = "bold"),
  legend.text =  element_text(size = 20, face = "bold")
)

a <- 10000
b <- 3000
x <- seq(1, 100, length.out = 100)
yi <- 3000 + 7000 / (1 + exp(-0.1 * (x - 50)))
yii <- rep(c(rep(a, 25), rep(b, 25)), 2)
yiii <- 3500 * sin(x / 10) + 6500
data <- data.frame(x = x, yi = yi, yii = yii, yiii = yiii)

p <- ggplot(data) +
  geom_line(aes(x = x, y = 6500, color = "Pop A"), size = 2) +
  geom_line(aes(x = x, y = yi, color = "Pop B"), size = 2) +
  geom_line(aes(x = x, y = yii, color = "Pop C"), size = 2, linetype = "dotdash") +
  geom_line(aes(x = x, y = yiii, color = "Pop D"), size = 2, linetype = "dashed") +
  labs(x = "Generation", y = "Population", color = "Functions: ") +
  scale_color_manual(values = c("Pop A" = "aquamarine4", "Pop B" = "blue", "Pop C" = "lightpink4", "Pop D" = "hotpink")) +
  theme_cowplot() +
  theme(legend.position = "bottom") +
  mytheme +
  transition_reveal(x)

# Create the animation with gifski_renderer
anim <- animate(p, nframes = 60, fps = 10, width = 800, height = 400, renderer = gifski_renderer())

# # Save the animation
# anim_save("~/Desktop/animated_plot.gif", animation = anim)
anim
```

## Population size and Selection Pressure

### Different time

```{r, warning = FALSE, echo = FALSE}
library(ggplot2)
library(cowplot)
library(gganimate)
library(gifski)


x1 <- seq(0, 8 * pi, length.out = 400)   # 4 cycles
x2 <- seq(0, 8 * pi, length.out = 400) 
y1 <- sin(x1)
y2 <- sin(x2 + 2)
data1 <- data.frame(x1, x2 , y1 = y1, y2 = y2, frame = 1:400)

# Plot
p1 <- ggplot(data1) +
  geom_line(aes(x = x1, y = y1, color = "Selection"), size = 2) +
  geom_line(aes(x = x2, y = y2, color = "Population"), size = 2) +
  labs(x = NULL, y = NULL, color = "Factors: ") +
  scale_color_manual(values = c("Selection" = "steelblue", "Population" = "darkorchid1")) +
  theme_cowplot() +
  theme(
    legend.position = "bottom",
    axis.text = element_blank(),
    axis.ticks = element_blank(),
    axis.title = element_blank()
  ) +
  transition_reveal(frame)

# Create and save the animation
anim1 <- animate(p1, nframes = 200, fps = 10, width = 800, height = 400, renderer = gifski_renderer())

#anim_save("~/Desktop/animated_Pop_Select1.gif", animation = anim1)

anim1
```

### Same time

```{r}
library(ggplot2)
library(cowplot)
library(gganimate)
library(gifski)

# Data for two sinusoidal signals with the same wavelength but different phase and amplitude
x <- seq(0, 8 * pi, length.out = 400)  # 4 cycles
y1 <- sin(x)                # First signal
y2 <- 2 * sin(x + pi)       # Second signal, shifted by π (opposite phase)

# Create a data frame
data1 <- data.frame(x = x, y1 = y1, y2 = y2, frame = 1:400)

# Plot the signals
p2 <- ggplot(data1) +
  geom_line(aes(x = x, y = y1, color = "Selection"), size = 2) +
  geom_line(aes(x = x, y = y2, color = "Population"), size = 2) +
  labs(x = NULL, y = NULL, color = "Factors: ") +
  scale_color_manual(values = c("Selection" = "steelblue", "Population" = "darkorchid1")) +
  theme_cowplot() +
  theme(
    legend.position = "bottom",
    axis.text = element_blank(),
    axis.ticks = element_blank(),
    axis.title = element_blank()
  ) +
  transition_reveal(frame)

# Create and save the animation
anim2 <- animate(p2, nframes = 200, fps = 10, width = 800, height = 400, renderer = gifski_renderer())

# anim_save("~/Desktop/animated_Pop_Select2.gif", animation = anim2)

anim2
```

## Spectral Analysis

```{r, warning = FALSE, echo = FALSE}

  mytheme <- theme(
    legend.position = "none",
    axis.text.x = element_text(angle = 45, hjust = 1, size = 15, face = "bold"),
    axis.text.y = element_text(size = 15, face = "bold"),
    axis.line = element_line(linewidth = 1),
    axis.title = element_text(size = 15, face = "bold"),
    strip.text = element_text(size = 15, face = "bold"),
    plot.title = element_text(hjust = 0.5, size = 15, face = "bold"),  # Centered title
    panel.spacing = unit(1, "lines")
  ) +
    theme(panel.grid = element_blank())


set.seed(123)

time <- seq(0, 8 * pi, length.out = 400)  
signal1 <- sin(time)                
signal2 <- 2 * sin(time * pi)       
signal3 <- 3 * sin(time * pi*2)   

combined_signal <- signal1 + signal2 + signal3


data <- data.frame(time = time, amplitude = combined_signal)


sp1 <- ggplot(data, aes(x = time, y = combined_signal)) +
  geom_line(color = "darkred") +
  labs(title = "Combined Signal", x = "Time (s)", y = "Amplitude") +
  theme_bw()+
  mytheme

sp2 <-  ggplot(data, aes(x = time, y = signal1)) +
  geom_line(color = "magenta") +
  labs(title = "Signals", x = NULL, y = NULL) +
  theme_bw()+
  mytheme

sp3 <-  ggplot(data, aes(x = time, y = signal2)) +
  geom_line(color = "darkmagenta") +
  labs(x = NULL, y = "Amplitude") +
  theme_bw()+
  mytheme

sp4 <- ggplot(data, aes(x = time, y = signal3)) +
  geom_line(color = "magenta4") +
  labs(x = "Time", y = NULL) +
  theme_bw()+
  mytheme

sp1


spec_result <- spectrum(combined_signal, plot = FALSE)

# Extract the frequency and spectral density (amplitude)
frequency <- spec_result$freq
amplitude <- spec_result$spec


fft_data <- data.frame(frequency = frequency, amplitude = amplitude) 


ggplot(fft_data, aes(x = frequency, y = amplitude)) +
  geom_line(color = "red") +
  labs(title = "Decomposed Frequency", 
       x = "Frequency (Hz)", 
       y = "Amplitude") +
  theme_bw()+
  mytheme
```

```{r, fig.width=6, fig.height = 3}

# Assuming sp2, sp3, and sp4 are your ggplot objects
library(cowplot)

# Combine plots using plot_grid
combined_plot <- plot_grid(sp2, sp3, sp4, ncol = 1, align = "v", axis = "lr")


combined_plot+ theme(
    legend.position = "none",
    axis.text.x = element_text(angle = 45, hjust = 1, size = 15, face = "bold"),
    axis.text.y = element_text(size = 15, face = "bold"),
    axis.line = element_line(linewidth = 1),
    axis.title = element_text(size = 15, face = "bold"),
    strip.text = element_text(size = 15, face = "bold"),
    plot.title = element_text(hjust = 0.5, size = 15, face = "bold"),  # Centered title
    panel.spacing = unit(1, "lines")
  ) +
    theme(panel.grid = element_blank())
```

```{r}
a <- 7
b <- 5
c <- 3

d <- c(c,b,a)

barplot(d,500)
```

```{r, echo=FALSE}
# Load necessary library
library(ggplot2)

mytheme <- function(){
  theme_set(theme_cowplot())+
    theme(axis.title = element_text(face = "bold"),
          axis.text = element_text(face = "italic", size = 12),
          axis.line = element_line(size = 1),
          plot.title = element_text(hjust = 0.5),
          legend.position = "none")
}

# Sample data
set.seed(123)
data <- data.frame(
  Year = 2000:2020,
  Population = cumsum(runif(21, min = 0, max = 100))
)

# Fit a linear model
model <- lm(Population ~ Year, data = data)

# Predict future values
future_years <- data.frame(Year = 2021:2030)
future_predictions <- predict(model, newdata = future_years)

# Combine data
future_data <- data.frame(Year = 2021:2030, Population = future_predictions)
combined_data <- rbind(data, future_data)

# Plot
ggplot(combined_data, aes(x = Year, y = Population)) +
  geom_line(color = "blue") +
  geom_point(data = data, aes(x = Year, y = Population), color = "red") +
  geom_line(data = future_data, aes(x = Year, y = Population), color = "darkmagenta", linetype = "dashed", size = 2) +
  theme_classic() +
  labs(x = "Year", y = "Population") +
  theme(legend.position = "none",
        axis.text = element_text(size = 17, face = "bold"),
        axis.line = element_line(size = 2),
        axis.title = element_text(size = 17, face = "bold"),
        strip.text = element_text(size = 17, face = "bold"))

```

## Simulated GWAS

```{r, echo=FALSE}
# Load necessary libraries
if (!requireNamespace("qqman", quietly = TRUE)) install.packages("qqman")
library(qqman)

set.seed(123)

# Generate a random dataset of SNPs for budding yeast
n_snps <- 10000  # Total number of SNPs
chromosomes <- rep(1:16, length.out = n_snps)  #  Yeast's 16 chromosomes
positions <- cumsum(sample(1000:2000, n_snps, replace = TRUE))  # Random positions on chromosomes

# Simulate mostly random p-values but ensure some are significant and near non-significant SNPs
p_values <- runif(n_snps, min = 0, max = 1)  # Random p-values

# Force significant p-values in specific regions close to non-significant SNPs
significant_snps <- sample(1:(n_snps-2), 100)  # Pick 10 SNPs at random to be significant, ensuring no edge cases
p_values[significant_snps] <- runif(100, min = 0, max = 1e-3)  # Assign low p-values to make them significant

# Adjust the positions of significant SNPs to be close to non-significant SNPs
for (i in significant_snps) {
  p_values[i + 1] <- runif(1, min = 0.05, max = 0.5)  # Assign non-significant values right next to significant SNPs
  p_values[i - 1] <- runif(1, min = 0.05, max = 0.5)  # Assign non-significant values right next to significant SNPs
}

# SNPs dataframe
snp_data <- data.frame(SNP = paste0("rs", 1:n_snps),
                       CHR = chromosomes,
                       BP = positions,
                       P = p_values)

# Use a of pvalue = 0.01 which is 2 in negative log
threshold <- 0.01

# Generate the Manhattan plot with a -log10(p) threshold of 2

manhattan(snp_data, chr = "CHR", bp = "BP", p = "P", snp = "SNP", 
          genomewideline = -log10(threshold), 
          suggestiveline = -log10(1e-3), 
          highlight = snp_data$SNP[snp_data$P < threshold],
          col = c("magenta4", "orange3"),
          main = "Simulated Manhattan Plot")
```

## Spectral analysis for preliminary

```{r}
run_fft_analysis <- function(folder_path, pattern, spectrum_span = 2) {
  # Load necessary libraries
  library(parallel)
  library(doParallel)
  library(foreach)
  library(dplyr)
  library(ggplot2)
  library(cowplot)
  library(stringr)
  
  theme_set(theme_cowplot())
  
  # Define a custom theme function with bold facet labels and centered plot title
  mytheme <- theme_cowplot() +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 90, hjust = 1, size = 12, face = "bold"),
        axis.text.y = element_text(size = 12, face = "bold"),
        axis.line = element_line(linewidth = 2),
        axis.title.x = element_text(size = 12, face = "bold", margin = margin(t = 10)),
        axis.title.y = element_text(size = 12, face = "bold", margin = margin(r = 15)),
        strip.text = element_text(size = 12, face = "bold"),
        panel.spacing = unit(3, "lines"),
        panel.grid = element_blank())
  
  # Create the directory to save images if it doesn't exist
  last_dir <- basename(normalizePath(folder_path))
  save_dir <- file.path("myimages", last_dir)
  if (!dir.exists(save_dir)) {
    dir.create(save_dir, recursive = TRUE)
  }
  
  # Get a list of all replicate files matching the pattern
  file_list <- list.files(
    path = folder_path,
    pattern = pattern,
    full.names = TRUE
  )
  
  # Check if files are found
  if (length(file_list) == 0) {
    stop("No files found with the given pattern.")
  }
  
  # Create a data frame with filenames and extract parameter information
  files_df <- data.frame(file_name = file_list) %>%
    mutate(
      base_name = basename(file_name),
      genome = str_extract(base_name, "genome\\d+") %>% str_remove("genome"),
      n = str_extract(base_name, "_n\\d+") %>% str_remove("_n"),
      H = str_extract(base_name, "_H\\d+\\.\\d*") %>% str_remove("_H"),
      SD = str_extract(base_name, "SD\\d+(\\.\\d+)?"),  # Adjusted regex
      SD = ifelse(is.na(SD), NA, str_remove(SD, "SD")),
      Gen = str_extract(base_name, "Gen\\d+"),
      Gen = ifelse(is.na(Gen), NA, str_remove(Gen, "Gen"))
    ) %>%
    mutate(
      n = as.numeric(n),
      H = as.numeric(H),
      SD = as.numeric(SD),
      Gen = as.numeric(Gen),
      param_combination = paste0(
        "n_", n, "_H", H,
        ifelse(!is.na(SD), paste0("_SD", SD), ""),
        ifelse(!is.na(Gen), paste0("_Gen", Gen), "")
      )
    )
  
  # Set up parallel backend
  num_cores <- detectCores()
  num_cores_to_use <- max(1, num_cores - 16)  # Leave at least 16 cores unused
  
  cl <- makeCluster(num_cores_to_use)
  registerDoParallel(cl)
  
  # Read and combine data from all replicate files in parallel
  combined_data_list <- foreach(i = seq_along(files_df$file_name), .packages = c("dplyr", "stringr")) %dopar% {
    file <- files_df$file_name[i]
    params <- files_df[i, ]
    df <- read.csv(file)
    data <- df %>%
      mutate(
        allele_id = as.factor(Position),
        generation = as.numeric(Generation),
        allele_frequency = Frequency,
        sample_size = 10000,
        file = params$base_name,
        genome = params$genome,
        n = params$n,
        H = params$H,
        SD = params$SD,
        Gen = params$Gen,
        param_combination = params$param_combination
      ) %>%
      dplyr::select(
        allele_id, generation, allele_frequency, sample_size, file,
        genome, n, H, SD, Gen, param_combination
      )
    data
  }
  combined_data <- bind_rows(combined_data_list)
  
  # Calculate the mean allele frequency for each grouping
  mean_allele_data <- combined_data %>%
    group_by(generation, n, genome, H, SD, Gen, param_combination) %>%
    summarize(mean_allele_frequency = mean(allele_frequency), .groups = "drop")
  
  # Create time series objects
  ts_data_list <- mean_allele_data %>%
    group_by(n, genome, H, SD, Gen, param_combination) %>%
    summarize(ts_data = list(ts(mean_allele_frequency, start = min(generation), frequency = 1)), .groups = 'drop')
  
  # Compute spectral density estimates in parallel
  spec_results_list <- foreach(i = 1:nrow(ts_data_list), .packages = c("stats")) %dopar% {
    ts_data <- ts_data_list$ts_data[[i]]
    spectrum(ts_data, spans = spectrum_span, plot = FALSE)
  }
  
  # Prepare data for plotting in parallel
  plot_data_list <- foreach(i = seq_along(spec_results_list), .packages = c("dplyr", "stringr")) %dopar% {
    spec_result <- spec_results_list[[i]]
    params <- ts_data_list[i, ]
    # Compute period
    period <- 1 / spec_result$freq
    data.frame(
      Period = period,
      Spectrum = spec_result$spec,
      n = params$n,
      genome = params$genome,
      H = params$H,
      SD = params$SD,
      Gen = params$Gen,
      param_combination = params$param_combination
    )
  }
  
  # Stop cluster
  stopCluster(cl)
  
  # Combine all plot data
  plot_data <- bind_rows(plot_data_list)
  
  # Filter Period after grouping by param_combination
  plot_data <- plot_data %>%
    group_by(param_combination) %>%
    mutate(
      # Set threshold based on Gen value
      threshold = case_when(
        Gen == 10 ~ 40,
        Gen == 20 ~ 50,
        Gen == 30 ~ 80,
        TRUE ~ max(Period)  # Default threshold if Gen is not 10, 20, or 30
      )
    ) %>%
    filter(Period < threshold) %>%
    ungroup()
  
  # Prepare data for faceting
  plot_data <- plot_data %>%
    mutate(
      H_label = paste0("H = ", H),
      SD_label = ifelse(!is.na(SD), paste0("SD = ", SD), "No SD"),
      Gen_label = ifelse(!is.na(Gen), paste0("Gen = ", Gen), "No Gen"),
      n_label = paste0("n_", n)
    ) %>%
  filter((H == 0.1 & SD == 1 & Gen == 10) |
         (H == 0.8 & SD == 4 & Gen == 30))
  
  # Generate plots for each unique combination of n and Gen
  unique_n_Gen_values <- unique(paste0("n_", plot_data$n))
  
  fft_plots <- list()
  
  for (n_Gen_value in unique_n_Gen_values) {
    # Split n_Gen_value back into n and Gen
    n_value <- as.numeric(str_extract(n_Gen_value, "(?<=n_)[^_]+"))
    Gen_value <- as.numeric(str_extract(n_Gen_value, "(?<=Gen)[^_]+"))
    
    plot_df <- plot_data %>%
      filter(n == n_value)
    
    # Determine the faceting variables
    if (all(plot_df$SD_label == "No SD")) {
      # If SD is missing, facet only by H_label
      facet_formula <- ~ H_label
    } else {
      # Facet by SD_label and H_label
      facet_formula <- H_label ~ SD_label + Gen_label
    }
    
    p <- ggplot(plot_df, aes(x = Period, y = Spectrum, color = genome, group = genome)) +
      geom_line(linewidth = 1.1) +
      facet_wrap(facet_formula, scales = "free", ncol = 4) +  # Set scales to "free"
      labs(
        #title = paste("Spectral Analysis for", n_Gen_value),
        x = "Period (Generations)",
        y = "Spectral Density"
      ) +
      mytheme
    
    fft_plots[[n_Gen_value]] <- p
    
    # # Save the plot with n and Gen in filename
    # filename <- paste0("Spectral_", n_Gen_value, ".png")
    # ggsave(filename = file.path(save_dir, filename), plot = p)
  }
  
  return(fft_plots)
}
```

##### Instant

```{r, fig.height=14, fig.width=26}
dirpath <- "~/YeastProj.dir/evogen-sims/ET_Yeast/output.dir/Selection_Models/WF.dir/LinFS.dir/"
#source('~/YeastProj.dir/evogen-sims/ET_Yeast/Writing1.dir/Code.dir/ComboSpec.R')
pattern = "^genome\\d+_n100_H0\\.(1|8)(SD(1|4))?(Gen(10|30))?\\.csv$"
run_fft_analysis(dirpath, pattern)
```

##### gradual II
```{r}
dirpath <- "~/YeastProj.dir/evogen-sims/ET_Yeast/output.dir/Selection_Models/WF.dir/SinFSGen.dir/"
#source('~/YeastProj.dir/evogen-sims/ET_Yeast/Writing1.dir/Code.dir/ComboSpec.R')
pattern = "^genome\\d+_n100_H0\\.(1|8)(SD(1|4))?(Gen(10|30))?\\.csv$"
run_fft_analysis(dirpath, pattern)
```

##### Neutral

```{r}
run_fft_analysis <- function(folder_path, pattern, spectrum_span = 2) {
  # Load necessary libraries
  library(parallel)
  library(doParallel)
  library(foreach)
  library(dplyr)
  library(ggplot2)
  library(cowplot)
  library(stringr)
  
  theme_set(theme_cowplot())
  
  # Define a custom theme function with bold facet labels and centered plot title
  mytheme <- theme_cowplot() +
    theme(legend.position = "none",
          axis.text.x = element_text(angle = 90, hjust = 1, size = 12, face = "bold"),
          axis.text.y = element_text(size = 12, face = "bold"),
          axis.line = element_line(linewidth = 2),
          axis.title.x = element_text(size = 12, face = "bold", margin = margin(t = 10)),
          axis.title.y = element_text(size = 12, face = "bold", margin = margin(r = 15)),
          strip.text = element_text(size = 12, face = "bold"),
          panel.spacing = unit(3, "lines"),
          panel.grid = element_blank())
  
  # Create the directory to save images if it doesn't exist
  last_dir <- basename(normalizePath(folder_path))
  save_dir <- file.path("myimages", last_dir)
  if (!dir.exists(save_dir)) {
    dir.create(save_dir, recursive = TRUE)
  }
  
  # Get a list of all replicate files matching the pattern
  file_list <- list.files(
    path = folder_path,
    pattern = pattern,
    full.names = TRUE
  )
  
  # Check if files are found
  if (length(file_list) == 0) {
    stop("No files found with the given pattern.")
  }
  
  # Create a data frame with filenames and extract parameter information
  files_df <- data.frame(file_name = file_list) %>%
    mutate(
      base_name = basename(file_name),
      genome = str_extract(base_name, "genome\\d+") %>% str_remove("genome"),
      n = str_extract(base_name, "_n\\d+") %>% str_remove("_n"),
      H = str_extract(base_name, "_H\\d+\\.\\d*") %>% str_remove("_H"),
      SD = str_extract(base_name, "SD\\d+(\\.\\d+)?") %>% str_remove("SD"),
      Gen = str_extract(base_name, "Gen\\d+") %>% str_remove("Gen")
    ) %>%
    mutate(
      n = as.numeric(n),
      H = as.numeric(H),
      SD = as.numeric(SD),
      Gen = as.numeric(Gen),
      param_combination = paste0(
        "n_", n, "_H", H,
        ifelse(!is.na(SD), paste0("_SD", SD), ""),
        ifelse(!is.na(Gen), paste0("_Gen", Gen), "")
      )
    )
  
  # Set up parallel backend
  num_cores <- detectCores()
  num_cores_to_use <- max(1, num_cores - 16)  # Leave at least 16 cores unused
  
  cl <- makeCluster(num_cores_to_use)
  registerDoParallel(cl)
  
  # Read and combine data from all replicate files in parallel
  combined_data_list <- foreach(i = seq_along(files_df$file_name), .packages = c("dplyr", "stringr")) %dopar% {
    file <- files_df$file_name[i]
    params <- files_df[i, ]
    df <- read.csv(file)
    data <- df %>%
      mutate(
        allele_id = as.factor(Position),
        generation = as.numeric(Generation),
        allele_frequency = Frequency,
        sample_size = 10000,
        file = params$base_name,
        genome = params$genome,
        n = params$n,
        H = params$H,
        SD = params$SD,
        Gen = params$Gen,
        param_combination = params$param_combination
      ) %>%
      dplyr::select(
        allele_id, generation, allele_frequency, sample_size, file,
        genome, n, H, SD, Gen, param_combination
      )
    data
  }
  combined_data <- bind_rows(combined_data_list)
  
  # Calculate the mean allele frequency for each grouping
  mean_allele_data <- combined_data %>%
    group_by(generation, n, genome, H, SD, Gen, param_combination) %>%
    summarize(mean_allele_frequency = mean(allele_frequency), .groups = "drop")
  
  # Create time series objects
  ts_data_list <- mean_allele_data %>%
    group_by(n, genome, H, SD, Gen, param_combination) %>%
    summarize(ts_data = list(ts(mean_allele_frequency, start = min(generation), frequency = 1)), .groups = 'drop')
  
  # Compute spectral density estimates in parallel
  spec_results_list <- foreach(i = 1:nrow(ts_data_list), .packages = c("stats")) %dopar% {
    ts_data <- ts_data_list$ts_data[[i]]
    spectrum(ts_data, spans = spectrum_span, plot = FALSE)
  }
  
  # Prepare data for plotting in parallel
  plot_data_list <- foreach(i = seq_along(spec_results_list), .packages = c("dplyr", "stringr")) %dopar% {
    spec_result <- spec_results_list[[i]]
    params <- ts_data_list[i, ]
    # Compute period
    period <- 1 / spec_result$freq
    data.frame(
      Period = period,
      Spectrum = spec_result$spec,
      n = params$n,
      genome = params$genome,
      H = params$H,
      SD = params$SD,
      Gen = params$Gen,
      param_combination = params$param_combination
    )
  }
  
  # Stop cluster
  stopCluster(cl)
  
  # Combine all plot data
  plot_data <- bind_rows(plot_data_list)
  
  # Filter Period after grouping by param_combination
  plot_data <- plot_data %>%
    group_by(param_combination) %>%
    mutate(
      # Set threshold based on Gen value
      threshold = case_when(
        !is.na(Gen) & Gen == 10 ~ 40,
        !is.na(Gen) & Gen == 20 ~ 50,
        !is.na(Gen) & Gen == 30 ~ 80,
        TRUE ~ 60  # Default threshold if Gen is missing or not 10, 20, 30
      )
    ) %>%
    filter(Period < threshold) %>%
    ungroup()
  
  # Prepare data for faceting
  plot_data <- plot_data %>%
    mutate(
      H_label = paste0("H = ", H),
      SD_label = ifelse(!is.na(SD), paste0("SD = ", SD), "No SD"),
      Gen_label = ifelse(!is.na(Gen), paste0("Gen = ", Gen), "No Gen"),
      n_label = paste0("n_", n),
      facet_label = paste0(
        H_label,
        ifelse(SD_label != "No SD", paste0(", ", SD_label), ""),
        ifelse(Gen_label != "No Gen", paste0(", ", Gen_label), "")
      )
    )
  
  # Remove any filters that exclude data when SD or Gen is missing
  # You can add filters here if needed, but ensure they handle NA values appropriately
  
  # Generate plots for each unique n value
  unique_n_values <- unique(plot_data$n)
  
  fft_plots <- list()
  
  for (n_value in unique_n_values) {
    plot_df <- plot_data %>%
      filter(n == n_value)
    
    p <- ggplot(plot_df, aes(x = Period, y = Spectrum, color = genome, group = genome)) +
      geom_line(linewidth = 1.1) +
      facet_wrap(~ facet_label, scales = "free", ncol = 4) +  # Set scales to "free"
      labs(
        x = "Period (Generations)",
        y = "Spectral Density"
      ) +
      mytheme
    
    fft_plots[[paste0("n_", n_value)]] <- p
    
    # Uncomment the following lines if you wish to save the plots
    # filename <- paste0("Spectral_n_", n_value, ".png")
    # ggsave(filename = file.path(save_dir, filename), plot = p)
  }
  
  return(fft_plots)
}


dirpath <- "~/YeastProj.dir/evogen-sims/ET_Yeast/output.dir/Selection_Models/WF.dir/NS.dir/"
#source('~/YeastProj.dir/evogen-sims/ET_Yeast/Writing1.dir/Code.dir/ComboSpec.R')
pattern = "^genome\\d+_n100_H0\\.(1|8)(SD(1|4))?(Gen(10|30))?\\.csv$"
run_fft_analysis(dirpath, pattern)
```


## Allele frequency and Phenotypes

### Phenotypes

```{r, fig.height=14, fig.width=26}
library(dplyr)
library(ggplot2)
library(forcats)
library(cowplot)
library(stringr)
library(plotly)
library(patchwork)
library(purrr)
library(doParallel)

# Custom theme for plots
mytheme <- function(){
  theme(axis.text = element_text(size = 17, face = "bold"),
        axis.line = element_line(size = 2),
        axis.title = element_text(size = 17, face = "bold"),
        strip.text = element_text(size = 17, face = "bold"), 
        plot.title = element_text(hjust = 0.5))
}

# Function to process phenotype files
process_files <- function(dirpath, pattern) {
  files <- list.files(dirpath, pattern, full.names = TRUE)
  
  dataframes <- list()
  for(file in files){
    replicate <- as.numeric(str_extract(file, "(?<=MeanPhenotypes)\\d+"))
    H <- as.numeric(str_extract(file, "(?<=H)0\\.\\d+"))
    loci <- as.numeric(str_extract(file, "(?<=_n)\\d+"))
    SD <- as.numeric(str_extract(file, "(?<=SD)\\d+"))
    Gen <- as.numeric(str_extract(file, "(?<=Gen)\\d+"))
    
    selection_label <- ifelse(loci == 1, "Monogenic",
                              ifelse(loci == 10, "Oligogenic", "Polygenic"))
    
    data <- read.csv(file, header = TRUE) %>% 
      mutate(H = H, loci = loci, SD = SD, Gen = Gen,
             replicate = as.factor(replicate),
             Selection = selection_label,
             h2_sd = paste("h2 = ", H," ", "sd = ", SD, sep = ""),
             loci_gen = paste("loci = ", loci," ", "gen = ", Gen, sep = ""),
             Fitness = exp(-(1/125) * (Phenotype - Optimum)^2),
             Optimum = ifelse(Optimum == max(Optimum, na.rm = TRUE), "High", "Low"))
    
    dataframes[[file]] <- data
  }
  combined_data <- bind_rows(dataframes) %>%
    filter(Generation == 0 | Generation %% 30 == 0 & Generation <=500)
  
  return(combined_data)
}

# Directory path and pattern for files
dirpath <- "~/YeastProj.dir/evogen-sims/ET_Yeast/output.dir/Selection_Models/WF.dir/LinFS.dir/"
pattern <- "^MeanPhenotypes\\d+_n(1|10|300)_H0\\.(1|5|8)(SD(1|2|4))?(Gen(10|20|30))?\\.csv$"

# Process the files and get combined data
combined_data <- process_files(dirpath, pattern)

# Filter data to include only specific combinations of H, SD, and Gen
filtered_data <- combined_data %>%
  filter((H == 0.1 & SD == 1 & Gen == 10) |
          (H == 0.5 & SD == 2 & Gen == 20)|
         (H == 0.8 & SD == 4 & Gen == 30))

# Ensure the gen variable is included in the data and facets
filtered_data <- filtered_data %>%
  mutate(Gen = factor(Gen, levels = unique(Gen)))

# Plotting phenotypes

phenotype_plots <- filtered_data %>%
  ggplot(aes(x = Generation, y = Phenotype)) +
  geom_boxplot(aes(group = Generation, color = Optimum), size = 1, varwidth = TRUE, alpha = 0.5) +
  facet_grid(Selection ~ H + SD + Gen, labeller = labeller(
    Selection = function(x) x,
    H = label_both,
    SD = label_both,
    Gen = label_both)) +
  theme_cowplot() +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 45, hjust = 1, size = 20, face = "bold"),
        axis.text.y = element_text(size = 20, face = "bold"),
        axis.line = element_line(linewidth = 5),
        axis.title.x = element_text(size = 20, face = "bold", margin = margin(t = 25)),
        axis.title.y = element_text(size = 20, face = "bold", margin = margin(r = 5)),
        strip.text = element_text(size = 20, face = "bold"),
        panel.spacing = unit(3, "lines"),
        panel.grid = element_blank())

phenotype_plots
```

### Allele Freq

```{r, fig.height=14, fig.width=26}
library(dplyr)
library(ggplot2)
library(forcats)
library(cowplot)
library(stringr)

rm(list = ls())

# Function to read in the files based on the specified parameters and extract Selection, H, SD, and Gen values using regex
read_files <- function() {
  file_list <- list.files(path = "~/YeastProj.dir/evogen-sims/ET_Yeast/output.dir/Selection_Models/WF.dir/LinFS.dir/", pattern = "genome10_n(10|70)_H0\\.(1|8)(SD(1|4))?Gen(10|30)\\.csv$", full.names = TRUE)
  
  datasets <- lapply(file_list, function(file) {
    data <- read.csv(file)
    matches <- str_match(file, "genome10_n([0-9]+)_H([0-9\\.]+)SD([0-9]+)Gen([0-9]+)")
    selection_type <- as.numeric(matches[2])
    selection_label <- ifelse(selection_type == 1, "Monogenic",
                              ifelse(selection_type == 10, "Oligogenic", "Polygenic"))
    
    data <- data %>% 
      mutate(Selection = selection_label,
             H = as.numeric(matches[3]),
             SD = as.numeric(matches[4]),
             Gen = as.numeric(matches[5]))
    return(data)
  })
  
  return(bind_rows(datasets))
}

# Read in the data
Genome_dataset <- read_files() %>% 
  filter(Generation <= 500) %>% 
  mutate(Selection = fct_relevel(Selection, 
                                 "Monogenic",  
                                 "Oligogenic", 
                                 "Polygenic"))

# Set seed for reproducibility
set.seed(8450)

# Group by Selection and select up to 30 unique positions for each group
selected_positions <- Genome_dataset %>%
  group_by(Selection) %>%
  group_map(~ {
    positions <- unique(.x$Position)
    if (length(positions) > 10) {
      sample(positions, 10)
    } else {
      positions
    }
  }) %>%
  unlist()

# Filter dataset to include only selected positions
filtered_dataset <- Genome_dataset %>%
  filter(Position %in% selected_positions)

# filtered_dataset <- filtered_dataset %>%
#   filter((H == 0.1 & SD == 1 & Gen == 10) |
#          (H == 0.5 & SD == 2 & Gen == 20) |
#           (H == 0.8 & SD == 4 & Gen == 30))

# Assign specific positions to be highlighted
highlighted_positions <- c("915217", "644619")
filtered_dataset <- filtered_dataset %>%
  mutate(Color = case_when(
    Selection == "Monogenic" ~ "red",
    Selection == "Oligogenic" & Position == "915217" ~ "red",
    Selection == "Polygenic" & Position == "1054696" ~ "red",
    TRUE ~ "black"
  ),
  LineSize = case_when(
    Color == "darkred" ~ 1.5,
    TRUE ~ 0.5
  ))

# Create the plot
freqplot <- filtered_dataset %>%
  filter(Generation <= 500) %>%
  ggplot(aes(x = Generation, y = Frequency, group = factor(Position), color = Color, linewidth = LineSize)) +
  geom_line(alpha = 1) +
  scale_color_identity() +
  scale_linewidth_identity() +
  facet_grid(Selection ~ H + SD + Gen, labeller = labeller(
    Selection = function(x) x,
    H = label_both,
    SD = label_both,
    Gen = label_both
  )) +
  theme_cowplot() +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 45, hjust = 1, size = 20, face = "bold"),
        axis.text.y = element_text(size = 20, face = "bold"),
        axis.line = element_line(linewidth = 5),
        axis.title.x = element_text(size = 20, face = "bold", margin = margin(t = 25)),
        axis.title.y = element_text(size = 20, face = "bold", margin = margin(r = 25)),
        strip.text = element_text(size = 20, face = "bold"),
        panel.spacing = unit(3, "lines"),
        panel.grid = element_blank())

# Print the plot
print(freqplot)
```

### Three in One

#### Freq

```{r, warning=FALSE, fig.width = 26, fig.height = 14, echo=FALSE}
# Function to extract H, SD, and Gen values from filename
extract_params <- function(filename) {
  # Extract the values using regular expressions
  h_value <- str_extract(filename, "(?<=H)\\d\\.\\d")
  sd_value <- str_extract(filename, "(?<=SD)\\d")
  gen_value <- str_extract(filename, "(?<=Gen)\\d+")
  
  # Convert to numeric
  h_value <- as.numeric(h_value)
  sd_value <- as.numeric(sd_value)
  gen_value <- as.numeric(gen_value)
  
  return(list(H = h_value, SD = sd_value, Gen = gen_value))
}

# Function to create the plot
create_plot <- function(path, pattern) {
  # List all relevant files using the provided path and pattern
  file_list <- list.files(path = path, pattern = pattern, full.names = TRUE)
  
  # Read and combine datasets with extracted parameters
  combined_dataset <- map_df(file_list, function(file) {
    data <- read.csv(file)
    params <- extract_params(file)
    data <- data %>%
      mutate(H = params$H, SD = params$SD, Gen = params$Gen) %>%
  filter((H == 0.1 & SD == 1 & Gen == 10) |
         (H == 0.8 & SD == 4 & Gen == 30))
    
    return(data)
  })
  
  # Set seed for reproducibility and randomly select at most 30 positions
  set.seed(123)
  unique_positions <- unique(combined_dataset$Position)
  selected_positions <- sample(unique_positions, size = min(30, length(unique_positions)))
  
  # Filter dataset to include only selected positions
  filtered_dataset <- combined_dataset %>% 
    filter(Position %in% selected_positions)
  
  # Create the plot with faceting by H, SD, and Gen
  freqplot <- filtered_dataset %>% 
    filter(Generation <= 600) %>% 
    ggplot(aes(x = Generation, y = Frequency, group = factor(Position))) +
    geom_line(aes(color = ifelse(factor(Position) == "644619", "highlighted", "other")), size = 0.5) +
    scale_color_manual(values = c("highlighted" = "red", "other" = "grey")) +
    facet_wrap(H ~ SD + Gen, labeller = label_both, scales = "free") +
    theme_cowplot() +
    theme(
      legend.position = "none",
      axis.text.x = element_text(angle = 90, hjust = 1, size = 12, face = "bold"),
      axis.text.y = element_text(size = 12, face = "bold"),
      axis.line = element_line(size = 2),
      axis.title = element_text(size = 12, face = "bold"),
      strip.text = element_text(size = 12, face = "bold"),
      panel.spacing = unit(3, "lines"),
      panel.grid = element_blank()
    )
  
  return(freqplot)
}

# Example usage
path <- "~/YeastProj.dir/evogen-sims/ET_Yeast/output.dir/Selection_Models/WF.dir/LinFS.dir"
pattern <- "genome1_n300_H(0\\.1|0\\.8)SD(1|4)Gen(10|30)\\.csv"
freqplot <- create_plot(path, pattern)

print(freqplot)

```

#### Pheno

```{r, warning=FALSE, fig.width = 26, fig.height = 14, echo=FALSE}
library(dplyr)
library(ggplot2)
library(cowplot)
library(stringr)
library(purrr)

# Function to extract H, SD, Gen, and Replicate values from filename
extract_params <- function(filename) {
  # Extract the values using regular expressions
  h_value <- str_extract(filename, "(?<=H)\\d\\.\\d")
  sd_value <- str_extract(filename, "(?<=SD)\\d+")
  gen_value <- str_extract(filename, "(?<=Gen)\\d+")
  replicate_value <- str_extract(filename, "(?<=MeanPhenotypes)\\d+")

  # Convert to numeric
  h_value <- as.numeric(h_value)
  sd_value <- as.numeric(sd_value)
  gen_value <- as.numeric(gen_value)
  replicate_value <- as.numeric(replicate_value)

  return(list(H = h_value, SD = sd_value, Gen = gen_value, Replicate = replicate_value))
}

# List all relevant files using a pattern that captures any number of replicates
file_list <- list.files(
  path = "~/YeastProj.dir/evogen-sims/ET_Yeast/output.dir/Selection_Models/WF.dir/LinFS.dir",
  pattern = "MeanPhenotypes\\d+_n300_H(0\\.1|0\\.8)SD(1|4)Gen(10|30)\\.csv",
  full.names = TRUE
)

# Read and combine datasets with extracted parameters
combined_dataset <- map_df(file_list, function(file) {
  data <- read.csv(file)
  params <- extract_params(file)
  data <- data %>%
    mutate(
      H = params$H,
      SD = params$SD,
      Gen = params$Gen,
      Replicate = params$Replicate,
      Optimum = ifelse(Optimum == max(Optimum, na.rm = TRUE), "High", "Low")
    ) %>%
  filter((H == 0.1 & SD == 1 & Gen == 10) |
         (H == 0.8 & SD == 4 & Gen == 30))
  return(data)
})

# Filter the data to include Generation 1 and every generation divisible by 30, up to Generation 500
filtered_data <- combined_dataset %>%
  filter(
    (Generation == 1 | (Generation %% 30 == 0)) & Generation <= 600
  )

# Create the boxplot with faceting by H, SD, and Gen
phenoplot <- filtered_data %>% 
  ggplot(aes(x = factor(Generation), y = Phenotype, color = Optimum)) +
  geom_boxplot() +
  facet_wrap(H ~ SD + Gen, labeller = label_both, scales = "free", ncol = 4) +
  theme_cowplot() +
  theme(
    legend.position = "none",
    axis.text.x = element_text(angle = 90, hjust = 1, size = 12, face = "bold"),
    axis.text.y = element_text(size = 12, face = "bold"),
    axis.line = element_line(size = 2),
    axis.title = element_text(size = 12, face = "bold"),
    strip.text = element_text(size = 12, face = "bold"),
    panel.spacing = unit(3, "lines"),
    panel.grid = element_blank()
  ) +
  xlab("Generation") +
  ylab("Phenotype")

# Print the plot
print(phenoplot)

```

#### Spec

```{r, warning=FALSE, fig.width = 26, fig.height = 14, echo=FALSE}
dirpath <- "~/YeastProj.dir/evogen-sims/ET_Yeast/output.dir/Selection_Models/WF.dir/LinFS.dir/"
#source('~/YeastProj.dir/evogen-sims/ET_Yeast/Writing1.dir/Code.dir/ComboSpec.R')
pattern = "^genome\\d+_n300_H0\\.(1|8)(SD(1|4))?(Gen(10|30))?\\.csv$"

spec_plots <- run_fft_analysis(dirpath, pattern)
spec_plots[1]
```

#### All

```{r, warning=FALSE, fig.width = 18, fig.height = 8, echo=FALSE}

freqplot <- freqplot + 
  labs(title = "A", x = "Generation", y = "Frequency") +
  theme(
    plot.title = element_text(hjust = 0.01, face = "bold", size = 15, color = "red"),
    axis.title.x = element_text(margin = margin(t = 10), color = "red"),
    axis.title.y = element_text(margin = margin(r = 20), color = "red"),
    panel.spacing = unit(4, "lines")
  )

phenoplot <- phenoplot + 
  labs(title = "B", x = "Generation", y = "Frequency") +
  theme(
    plot.title = element_text(hjust = 0.01, face = "bold", size = 15, color = "red"),
    axis.title.x = element_text(margin = margin(t = 10), color = "red"),
    axis.title.y = element_text(margin = margin(r = 20), color = "red"),
    panel.spacing = unit(4, "lines")
  )
spec_plot1 <- spec_plots[1] 
#spec_plot2 <- spec_plots[2]

spec_plot1 <- spec_plot1$n_300 + 
  labs(title = "C", x = "Periodicity", y = "Spectral Density") +
  theme(
    plot.title = element_text(hjust = 0.01, face = "bold", size = 15, color = "red"),
    axis.title.x = element_text(margin = margin(t = 10), color = "red"),
    axis.title.y = element_text(margin = margin(r = 20), color = "red"),
    panel.spacing = unit(4, "lines")
  )

# spec_plot2 <- spec_plot2$n_300_Gen_30 + 
#   labs(title = "Spectral Analysis 30 Gen", x = "Periodicity", y = "Spectral Density") +
#   theme(
#     plot.title = element_text(hjust = 0.5, face = "bold", size = 30, color = "red"),
#     axis.title.x = element_text(margin = margin(t = 10), color = "red"),
#     axis.title.y = element_text(margin = margin(r = 10), color = "red")
#   )
#
#plot_grid(freqplot, phenoplot)
```

```{r, warning=FALSE, fig.width = 6, fig.height = 6, echo=FALSE}
plot_grid(freqplot, phenoplot,spec_plot1, ncol = 1)
```

```{r, warning=FALSE, fig.width = 6, fig.height = 4, echo=FALSE}
plot_grid(freqplot, phenoplot, ncol = 1)
```

```{r, warning=FALSE, fig.width = 6, fig.height = 2, echo=FALSE}
spec_plots
```

### Proper Orthogonal Decomposition

```{r}
data <- read.csv("~/YeastProj.dir/evogen-sims/ET_Yeast/output.dir/Selection_Models/WF.dir/LinFS.dir/genome30_n10_H0.8SD4Gen30.csv") %>% dplyr::select(c(-Effect, -Origin))
```

```{r}
data_t <- data %>% pivot_wider(names_from = Position, values_from = Frequency) %>% 
  dplyr::select(-Generation) 

data_t <- as.data.frame(data_t) %>%
  mutate_all(~ ifelse(is.na(.), 0, .))


mynames <- colnames(data_t)

colnames(data_t) <- NULL

tail(data_t)
```

```{r}
svd_reslt <- svd(data_t)
```

```{r}
U <- svd_reslt$u
S <- diag(svd_reslt$d)
V <- svd_reslt$v

print(dim(S))
```

```{r}
# Number of singular values to use
k <- 2

# Reconstruct the image using the first k singular values
U_k <- U[, 1:k]
S_k <- S[1:k, 1:k]
V_k <- V[, 1:k]

# Reconstructed image matrix
datarec <- U_k %*% S_k %*% t(V_k)

colnames(datarec) <- mynames

new_datarec <- as.data.frame(datarec) %>% mutate(Generation = rep(1:2000))
```

```{r}
new_datarec <- new_datarec %>% pivot_longer(-Generation, names_to = "Position", values_to = "Frequency")
```

```{r}
p1 <- new_datarec %>% ggplot(aes(Generation, Frequency, color = Position))+
  geom_line(linewidth = 0.5)+
  theme_bw()+
  theme(legend.position = "none")

p2 <- data%>% ggplot(aes(Generation, Frequency, color = as.factor(Position), group = Position))+
  geom_line(linewidth = 0.5)+
  theme_bw()+
  theme(legend.position = "none")

library(cowplot)

plot_grid(p1,p2, ncol = 1)
```



###### 30 sample
```{r}
# Read and preprocess your data
data <- read.csv("~/YeastProj.dir/evogen-sims/ET_Yeast/output.dir/Selection_Models/WF.dir/LinFS.dir/genome30_n100_H0.8SD4Gen30.csv") %>% 
  dplyr::select(-Effect, -Origin)

data_t <- data %>%
  pivot_wider(names_from = Position, values_from = Frequency) %>%
  dplyr::select(-Generation) %>%
  mutate_all(~ ifelse(is.na(.), 0, .))

mynames <- colnames(data_t)
colnames(data_t) <- NULL

# Perform SVD
svd_reslt <- svd(data_t)
U <- svd_reslt$u
S <- diag(svd_reslt$d)
V <- svd_reslt$v

# Reconstruct the data using the first k singular values
k <- 2
U_k <- U[, 1:k]
S_k <- S[1:k, 1:k]
V_k <- V[, 1:k]
datarec <- U_k %*% S_k %*% t(V_k)
colnames(datarec) <- mynames

new_datarec <- as.data.frame(datarec) %>%
  mutate(Generation = rep(1:2000)) %>%
  pivot_longer(-Generation, names_to = "Position", values_to = "Frequency")

# Sample 30 positions
positions_sample <- sample(unique(data$Position), 10)

# Filter datasets for the sampled positions
data_sample <- data %>% filter(Position %in% positions_sample)
new_datarec_sample <- new_datarec %>% filter(Position %in% positions_sample)

# Create plots
p1 <- new_datarec_sample %>%
  ggplot(aes(Generation, Frequency, color = Position)) +
  geom_line(linewidth = 0.5) +
  theme_bw() +
  theme(legend.position = "none")

p2 <- data_sample %>%
  ggplot(aes(Generation, Frequency, color = as.factor(Position), group = Position)) +
  geom_line(linewidth = 0.5) +
  theme_bw() +
  theme(legend.position = "none")

# Display the plots
library(cowplot)
plot_grid(p1, p2, ncol = 1)

```


#### All replicates

```{r}
# Generate file paths for all replicates
file_paths <- paste0(
  "~/YeastProj.dir/evogen-sims/ET_Yeast/output.dir/Selection_Models/WF.dir/SinFSGen.dir//genome",
  1:30,
  "_n100_H0.5SD4.csv"
)

# Read and combine data from all replicates
data_list <- lapply(1:30, function(i) {
  file_path <- file_paths[i]
  data <- read.csv(file_path) %>% 
    dplyr::select(-Effect, -Origin) %>%
    mutate(Replicate = i)  # Add replicate number
  return(data)
})

# Combine all data into one dataframe
data_all <- bind_rows(data_list)

```

```{r}
# Compute mean frequency across replicates
data_mean <- data_all %>%
  group_by(Generation, Position) %>%
  summarise(Frequency = mean(Frequency, na.rm = TRUE)) %>%
  ungroup()

```

```{r}
# Pivot data to wide format
data_t <- data_mean %>%
  pivot_wider(names_from = Position, values_from = Frequency) %>%
  dplyr::select(-Generation) %>%
  mutate_all(~ ifelse(is.na(.), 0, .))

# Store column names and remove them from data_t
mynames <- colnames(data_t)
colnames(data_t) <- NULL

# Perform SVD
svd_reslt <- svd(data_t)
U <- svd_reslt$u
S <- diag(svd_reslt$d)
V <- svd_reslt$v

# Number of singular values to use
k <- 3

# Reconstruct the data using the first k singular values
U_k <- U[, 1:k]
S_k <- S[1:k, 1:k]
V_k <- V[, 1:k]

# Reconstructed data matrix
datarec <- U_k %*% S_k %*% t(V_k)
colnames(datarec) <- mynames

# Add Generation back to the reconstructed data
new_datarec <- as.data.frame(datarec) %>%
  mutate(Generation = unique(data_mean$Generation))

```

```{r}
# Convert reconstructed data to long format
new_datarec <- new_datarec %>%
  pivot_longer(-Generation, names_to = "Position", values_to = "Frequency")

```

```{r}
# Sample 30 positions
set.seed(123)  # For reproducibility
positions_sample <- sample(unique(data_mean$Position), 30)

# Filter datasets for the sampled positions
data_sample <- data_mean %>% filter(Position %in% positions_sample)
new_datarec_sample <- new_datarec %>% filter(Position %in% positions_sample)

```


```{r}
# Plot the reconstructed data for the sampled positions
p1 <- new_datarec_sample %>%
  ggplot(aes(Generation, Frequency, color = Position)) +
  geom_line(linewidth = 0.5) +
  theme_bw() +
  theme(legend.position = "none")

# Plot the mean data for the sampled positions
p2 <- data_sample %>%
  ggplot(aes(Generation, Frequency, color = Position, group = Position)) +
  geom_line(linewidth = 0.5) +
  theme_bw() +
  theme(legend.position = "none")

```


```{r}
library(cowplot)

# Combine and display the plots
plot_grid(p1, p2, ncol = 1)

```
### Averaging out and applying mixed models

```{r}
# Load necessary libraries
library(dplyr)
library(tidyr)
library(ggplot2)
library(cowplot)

# 1. Read and combine data from all replicates
file_paths <- paste0(
  "~/YeastProj.dir/evogen-sims/ET_Yeast/output.dir/Selection_Models/WF.dir/LinFS.dir/genome",
  1,
  "_n100_H0.1SD3Gen10.csv"
)

data_list <- lapply(1, function(i) {
  file_path <- file_paths[i]
  data <- read.csv(file_path) %>% 
    dplyr::select(-Effect, -Origin) %>%
    mutate(Replicate = i)
  return(data)
})

data_all <- bind_rows(data_list)

# 2. Compute mean frequency across replicates
data_mean <- data_all %>%
  group_by(Generation, Position) %>%
  summarise(Frequency = mean(Frequency, na.rm = TRUE)) %>%
  ungroup()

# 3. Prepare data for SVD without removing column names
data_wide <- data_mean %>%
  pivot_wider(names_from = Position, values_from = Frequency) %>%
  arrange(Generation)  # Ensure consistent ordering

# Store Generation separately
generations <- data_wide$Generation

# Remove Generation column for SVD
data_t <- data_wide %>%
  dplyr::select(-Generation) %>%
  mutate_all(~ ifelse(is.na(.), 0, .))

# Convert to matrix while retaining column names
data_t_matrix <- as.matrix(data_t)

# 4. Perform SVD on the matrix with column names intact
svd_reslt <- svd(data_t_matrix)

U <- svd_reslt$u
S <- diag(svd_reslt$d)
V <- svd_reslt$v

# 5. Reconstruct the data using the first k singular values
k <- 2
U_k <- U[, 1:k]
S_k <- S[1:k, 1:k]
V_k <- V[, 1:k]

# Reconstructed data matrix
datarec <- U_k %*% S_k %*% t(V_k)

# Assign original column names and row names
colnames(datarec) <- colnames(data_t_matrix)
rownames(datarec) <- rownames(data_t_matrix)

# 6. Convert reconstructed data back to a data frame
new_datarec <- as.data.frame(datarec)

# Add Generation back to the data frame
new_datarec$Generation <- generations

# 7. Convert data to long format
new_datarec_long <- new_datarec %>%
  pivot_longer(-Generation, names_to = "Position", values_to = "Frequency")

# 8. Sample 30 positions for plotting
set.seed(123)
positions_sample <- sample(unique(data_mean$Position), 30)

data_sample <- data_mean %>% filter(Position %in% positions_sample)
new_datarec_sample <- new_datarec_long %>% filter(Position %in% positions_sample)

# 9. Update and create plots
p1 <- new_datarec_sample %>%
  ggplot(aes(Generation, Frequency, color = Position)) +
  geom_line(linewidth = 0.5) +
  theme_bw() +
  theme(legend.position = "none")

p2 <- data_sample %>% mutate(Position = as.factor(Position)) %>% 
  ggplot(aes(Generation, Frequency, color = Position, group = Position)) +
  geom_line(linewidth = 0.5) +
  theme_bw() +
  theme(legend.position = "none")

# 10. Display the plots
plot_grid(p1, p2, ncol = 1)

```
### Ribbon

```{r}
# 1. Compute summary statistics across replicates
data_summary <- data_all %>%
  group_by(Generation, Position) %>%
  summarise(
    MeanFrequency = mean(Frequency, na.rm = TRUE),
    MedianFrequency = median(Frequency, na.rm = TRUE),
    SD = sd(Frequency, na.rm = TRUE),
    LowerQuantile = quantile(Frequency, 0.25, na.rm = TRUE),
    UpperQuantile = quantile(Frequency, 0.75, na.rm = TRUE)
  ) %>%
  ungroup()

# 2. Sample positions for plotting
set.seed(123)
positions_sample <- sample(unique(data_summary$Position), 30)

# 3. Plot median frequency with interquartile range
p <- data_summary %>%
  filter(Position %in% positions_sample) %>%
  ggplot(aes(x = Generation, y = MedianFrequency, color = factor(Position), group = factor(Position))) +
  geom_line() +
  geom_ribbon(aes(ymin = LowerQuantile, ymax = UpperQuantile, fill = Position), alpha = 0.2, color = NA) +
  theme_bw() +
  theme(legend.position = "none")

# 4. Display the plot
print(p)

```

#### Mixed models using residuals

```{r}
# Load necessary libraries
library(dplyr)
library(lme4)
library(ggplot2)
library(dplyr)
library(tidyr)
library(ggplot2)
library(cowplot)

# 1. Read and combine data from all replicates
file_paths <- paste0(
  "~/YeastProj.dir/evogen-sims/ET_Yeast/output.dir/Selection_Models/WF.dir/SinFSGen.dir/genome",
  1,
  "_n100_H0.5SD1.csv"
)

data_list <- lapply(1, function(i) {
  file_path <- file_paths[i]
  data <- read.csv(file_path) %>% 
    dplyr::select(-Effect, -Origin) %>%
    mutate(Replicate = i)
  return(data)
})

data_all <- bind_rows(data_list)

# Convert Position to a factor if it's not already
data_all$Position <- as.factor(data_all$Position)

# Center Generation to improve numerical stability
data_all$Generation_centered <- scale(data_all$Generation, center = TRUE, scale = FALSE)

# Fit the mixed-effects model
model <- lmer(
  Frequency ~ Generation_centered +  (1 | Position),
  data = data_all,
  REML = FALSE
)

```

##### Extract residulas

```{r}
# Add residuals to the data frame
data_all$Residuals <- resid(model)
```

##### Residual variance for each Position
```{r}
# Calculate residual variance within each position
residual_variance <- data_all %>%
  group_by(Position) %>%
  summarise(
    ResidualVariance = var(Residuals, na.rm = TRUE),
    ResidualSD = sd(Residuals, na.rm = TRUE)
  )

```
##### Positions with high residual variance

```{r}
# Rank positions by residual variance
residual_variance_ranked <- residual_variance %>%
  arrange(desc(ResidualVariance))

# View top positions with highest residual variance
top_fluctuating_positions <- residual_variance_ranked %>%
  head(10)  # Adjust the number as needed

print(top_fluctuating_positions)

```

##### Freq Trajectories

```{r}
# Get the list of positions to plot
positions_to_plot <- top_fluctuating_positions$Position

# Filter data for these positions
data_top_positions <- data_all %>%
  filter(Position %in% positions_to_plot)

# Compute mean frequency over replicates
data_plot <- data_top_positions %>%
  group_by(Generation, Position) %>%
  summarise(MeanFrequency = mean(Frequency, na.rm = TRUE)) %>%
  ungroup()

# Plot frequency trajectories
ggplot(data_plot, aes(x = Generation, y = MeanFrequency, color = Position)) +
  geom_line(size = 0.2) +
  theme_bw() +
  #theme(legend.position = "none") +
  labs(title = "Frequency Trajectories of Positions with High Residual Variance",
       x = "Generation",
       y = "Mean Frequency")

```


##### Residuals over time

```{r}
# Plot residuals for top positions
ggplot(data_top_positions, aes(x = Generation, y = Residuals, color = Position)) +
  geom_line(size = 0.2) +
  theme_bw() +
#  theme(legend.position = "none") +
  labs(title = "Residuals Over Time for Positions with High Residual Variance",
       x = "Generation",
       y = "Residuals")

```




### Mixed Models with random effect

```{r}
# Convert Position to a factor if it's not already
data_all$Position <- as.factor(data_all$Position)

# Fit the mixed-effects model
model <- lmer(
  Frequency ~ Generation + (1 | Position),
  data = data_all,
  REML = FALSE
)

```

```{r}
# Plot residuals vs fitted values
plot(model)

# QQ plot of residuals
qqnorm(residuals(model))
qqline(residuals(model))

```

```{r}
# model <- lmer(
#   Frequency ~ Generation + (1 | Replicate) + (1 | Position),
#   data = data_all,
#   REML = FALSE
# )

```


```{r}
# Extract random effects for positions
ranef_positions <- ranef(model)$Position

# Convert to a data frame
ranef_positions_df <- as.data.frame(ranef_positions)
ranef_positions_df$Position <- rownames(ranef_positions_df)
colnames(ranef_positions_df) <- c("RandomEffect", "Position")

```

```{r}
# Calculate the variance of random effects for positions
variance_positions <- VarCorr(model)$Position[1]

# Print the variance
print(paste("Variance of random effects for positions:", variance_positions))


```


```{r}
# Add absolute value of random effects
ranef_positions_df <- ranef_positions_df %>%
  mutate(AbsRandomEffect = abs(RandomEffect))

# Rank positions by absolute random effect
ranef_positions_ranked <- ranef_positions_df %>%
  arrange(desc(AbsRandomEffect))

# View the top positions with the largest random effects
top_fluctuating_positions <- ranef_positions_ranked %>%
  head(30)  # Adjust the number as needed

print(top_fluctuating_positions)

```


```{r}
# Histogram of random effects
ggplot(ranef_positions_df, aes(x = abs(RandomEffect))) +
  geom_histogram(binwidth = 0.01, fill = "blue", color = "black") +
  theme_bw() +
  labs(title = "Distribution of Random Effects for Positions",
       x = "Random Effect (Position Intercept)",
       y = "Count")

```


```{r}
# Get the list of top fluctuating positions
tyu <- ranef_positions_df %>% 
  filter(abs(RandomEffect) <= 0.15)

positions_to_plot <- tyu$Position
# Filter data for these positions
data_top_positions <- data_all %>%
  filter(Position %in% positions_to_plot)

# Compute mean frequency over replicates
data_plot <- data_top_positions %>%
  mutate(Position = factor(Position)) %>% 
  group_by(Generation, Position) %>%
  summarise(MeanFrequency = mean(Frequency, na.rm = TRUE)) %>%
  ungroup()

# Plot frequency trajectories
ggplot(data_plot, aes(x = Generation, y = MeanFrequency, color = Position)) +
  geom_line(size = .1) +
  theme_bw() +
  theme(legend.position = "none")+
  labs(title = "Frequency Trajectories of Positions with Largest Random Effects",
       x = "Generation",
       y = "Mean Frequency")

```
```{r}
# Identify the position with the maximum random effect
max_random_effect_position <- tyu %>% 
  filter(RandomEffect == min(RandomEffect)) %>% 
  pull(Position)

# Plot frequency trajectories with custom colors
ggplot(data_plot, aes(x = Generation, y = MeanFrequency, color = Position)) +
  geom_line(size = .2) +
  scale_color_manual(values = ifelse(levels(data_plot$Position) == max_random_effect_position, "red", "grey")) +
  theme_bw() +
  theme(legend.position = "none") +
  labs(title = "Frequency Trajectories of Positions with Largest Random Effects",
       x = "Generation",
       y = "Mean Frequency")

```
#### Applying SVD and check for Oscillations

```{r}
#trans_data_plot <- data_plot %>% pivot_longer()
# Store Generation separately
generations <- data_plot$Generation

# Remove Generation column for SVD
data_t <- data_plot %>%
  pivot_wider(names_from = Position, values_from = MeanFrequency) %>%
  dplyr::select(-Generation) %>% 
  mutate_all(~ ifelse(is.na(.), 0, .))

# Convert to matrix while retaining column names
data_t_matrix <- as.matrix(data_t)

# 4. Perform SVD on the matrix with column names intact
svd_reslt <- svd(data_t_matrix)

U <- svd_reslt$u
S <- diag(svd_reslt$d)
V <- svd_reslt$v

# 5. Reconstruct the data using the first k singular values
k <- 2
U_k <- U[, 1:k]
S_k <- S[1:k, 1:k]
V_k <- V[, 1:k]

# Reconstructed data matrix
datarec <- U_k %*% S_k %*% t(V_k)

# Assign original column names and row names
colnames(datarec) <- colnames(data_t_matrix)
rownames(datarec) <- rownames(data_t_matrix)

# 6. Convert reconstructed data back to a data frame
new_datarec <- as.data.frame(datarec)

# Add Generation back to the data frame
new_datarec$Generation <- seq(1:2000)

# 7. Convert data to long format
new_datarec_long <- new_datarec %>%
  pivot_longer(-Generation, names_to = "Position", values_to = "Frequency")

# # 8. Sample 30 positions for plotting
# #set.seed(123)
# #positions_sample <- sample(unique(data_mean$Position), 30)
# 
# data_sample <- data_mean %>% filter(Position %in% positions_sample)
# new_datarec_sample <- new_datarec_long %>% filter(Position %in% positions_sample)

# 9. Update and create plots
p1 <- new_datarec_long %>%
  filter(Generation <= 1500) %>% 
  ggplot(aes(Generation, Frequency, color = Position)) +
  geom_line(linewidth = 0.5) +
  theme_bw() +
  theme(legend.position = "none")

# p2 <- data_sample %>% mutate(Position = as.factor(Position)) %>% 
#   ggplot(aes(Generation, Frequency, color = Position, group = Position)) +
#   geom_line(linewidth = 0.5) +
#   theme_bw() +
#   theme(legend.position = "none")
# 
# # 10. Display the plots
# plot_grid(p1, p2, ncol = 1)
p1
```


```{r}
# Calculate variance of random effects for positions
ranef_positions_df$Variance <- apply(ranef_positions_df[, -ncol(ranef_positions_df)], 1, var)

# Identify positions with high variance
high_variance_positions <- ranef_positions_df %>%
  arrange(desc(Variance)) %>%
  head(10)  # Top 10 positions with highest variance

```


```{r}
# Positions with highest variance
positions_to_plot <- high_variance_positions$Position

# Filter data for these positions
data_high_var <- data_all %>%
  filter(Position %in% positions_to_plot)

# Plot frequencies over time
ggplot(data_high_var, aes(x = Generation, y = Frequency, color = Replicate)) +
  geom_line() +
  facet_wrap(~ Position) +
  theme_bw()

```

### High FLU

```{r}
# Load necessary libraries
library(dplyr)
library(ggplot2)

# Assuming 'data_all' is your combined dataset with columns:
# Generation, Position, Frequency, Replicate

# Compute mean frequency and standard deviation over time for each position
fluctuation_metrics <- data_all %>%
  group_by(Position, Generation) %>%
  summarise(MeanFrequency = mean(Frequency, na.rm = TRUE)) %>%
  ungroup() %>%
  group_by(Position) %>%
  summarise(
    MeanFreq = mean(MeanFrequency, na.rm = TRUE),
    StdDevFreq = sd(MeanFrequency, na.rm = TRUE)
  ) %>%
  mutate(
    CoefficientOfVariation = StdDevFreq / MeanFreq
  )

```

#### Calculate Mean Absolute Change (MAC

```{r}
# Compute Mean Absolute Change for each position
mac_metrics <- data_all %>%
  group_by(Position, Generation) %>%
  summarise(MeanFrequency = mean(Frequency, na.rm = TRUE)) %>%
  arrange(Position, Generation) %>%
  group_by(Position) %>%
  mutate(
    FrequencyChange = abs(MeanFrequency - lag(MeanFrequency))
  ) %>%
  summarise(
    MeanAbsoluteChange = mean(FrequencyChange, na.rm = TRUE)
  )

```


```{r}
# Combine fluctuation metrics
fluctuation_metrics <- fluctuation_metrics %>%
  left_join(mac_metrics, by = "Position")

```

```{r}
# Rank positions by Coefficient of Variation
fluctuation_metrics <- fluctuation_metrics %>%
  arrange(desc(CoefficientOfVariation))

# View top positions with highest fluctuation
top_fluctuating_positions <- fluctuation_metrics %>%
  top_n(10, CoefficientOfVariation)  # Adjust 'n' as needed

print(top_fluctuating_positions)

```


```{r}
# Define a threshold for Coefficient of Variation
cv_threshold <- 0.1  # Adjust as appropriate

positions_above_threshold <- fluctuation_metrics %>%
  filter(CoefficientOfVariation > cv_threshold)

print(positions_above_threshold)

```


```{r}
# Get the list of positions to plot
positions_to_plot <- top_fluctuating_positions$Position

# Filter data for these positions
data_fluctuating <- data_all %>%
  filter(Position %in% positions_to_plot)

# Compute mean frequency over replicates
data_plot <- data_fluctuating %>%
  group_by(Generation, Position) %>%
  summarise(MeanFrequency = mean(Frequency, na.rm = TRUE)) %>%
  ungroup()

```

```{r}
# Plot frequency trajectories
ggplot(data_plot, aes(x = Generation, y = MeanFrequency, color = Position)) +
  geom_line(size = 1) +
  facet_wrap(~ Position, scales = "free_y") +
  theme_bw() +
  theme(legend.position = "none") +
  labs(title = "Frequency Trajectories of Top Fluctuating Positions",
       x = "Generation",
       y = "Mean Frequency")

```


### Hierarchical Modeling with brms

```{r}
# Install brms if not already installed
install.packages("brms")

library(brms)

```


```{r}
# Define the model formula
formula <- bf(
  Frequency ~ Generation * Position + (Generation | Replicate)
)

```

```{r}
# Fit the hierarchical model
bayesian_model <- brm(
  formula = formula,
  data = data_all,
  family = gaussian(),
  chains = 4,
  cores = 4,
  iter = 1000,
  control = list(adapt_delta = 0.95)
)

```


```{r}
# View the summary
summary(bayesian_model)

# Plot posterior distributions
plot(bayesian_model)

```

```{r}
# Check trace plots
plot(bayesian_model, pars = "^b_")

# Posterior predictive checks
pp_check(bayesian_model)

```


### Visualize Model Predictions

```{r}
# For mixed-effects model
data_all$Predicted_Frequency <- predict(model)

# For hierarchical model (posterior predictions)
posterior_preds <- posterior_predict(bayesian_model)
data_all$Bayesian_Predicted_Frequency <- colMeans(posterior_preds)

```


```{r}
# Sample 30 positions for plotting
set.seed(123)
positions_sample <- sample(unique(data_all$Position), 30)

# Filter data for sampled positions
data_sample <- data_all %>% filter(Position %in% positions_sample)

# Plot mixed-effects model predictions
ggplot(data_sample, aes(x = Generation, y = Frequency, color = Position)) +
  geom_point(alpha = 0.5) +
  geom_line(aes(y = Predicted_Frequency), size = 1) +
  facet_wrap(~ Position) +
  theme_bw() +
  theme(legend.position = "none")

# Plot Bayesian model predictions
ggplot(data_sample, aes(x = Generation, y = Frequency, color = Position)) +
  geom_point(alpha = 0.5) +
  geom_line(aes(y = Bayesian_Predicted_Frequency), size = 1) +
  facet_wrap(~ Position) +
  theme_bw() +
  theme(legend.position = "none")

```


#### Ignore
```{r}
# Load necessary library
library(stats)

# Assuming your data frame is named data_t
# Convert data frame to matrix
data_matrix <- as.matrix(data_t)

# Compute the covariance matrix
cov_matrix <- cov(data_matrix)

# Perform eigen decomposition
eigen_decomp <- eigen(cov_matrix)

# Extract eigenvalues and eigenvectors
eigenvalues <- eigen_decomp$values
eigenvectors <- eigen_decomp$vectors

# Project data onto the principal components
projected_data <- data_matrix %*% eigenvectors

# Plot the first few principal components to observe periodicity/oscillation
plot(projected_data[, 1], type = "l", main = "First Principal Component")
plot(projected_data[, 2], type = "l", main = "Second Principal Component")
plot(projected_data[, 3], type = "l", main = "Third Principal Component")
plot(projected_data[, 50], type = "l", main = "4th Principal Component")

```

```{r}
# Load necessary libraries
library(ggplot2)
library(reshape2)

# Assuming you have already projected the data onto the principal components
# and the result is stored in projected_data

# Select the first 50 principal components
pc_data <- projected_data[, 1:50]

# Convert to data frame and add an observation index
pc_df <- data.frame(pc_data)
pc_df$Observation <- 1:nrow(pc_df)

# Melt the data frame for ggplot
pc_melted <- melt(pc_df, id.vars = "Observation")

# Plot the first 50 principal components
ggplot(pc_melted, aes(x = Observation, y = value, color = variable)) +
  geom_line() +
  labs(title = "First 50 Principal Components",
       x = "Observation",
       y = "Principal Component Value") +
  theme_minimal()

```

```{r}
svd_result <- svd(data_matrix)
U <- svd_result$u
S <- diag(svd_result$d)
V <- svd_result$v
```

```{r}
# Center the data by subtracting the mean across generations for each genomic position
data_centered <- scale(data_t, center = TRUE, scale = FALSE)

# Perform Singular Value Decomposition (SVD)
svd_result <- svd(data_centered, "economy")

# Singular values
singular_values <- svd_result$d

# Left singular vectors (generations)
U <- svd_result$u

# Right singular vectors (positions)
V <- svd_result$v

# Plot the singular values to check which modes are dominant
plot(singular_values, type = 'b', main = "Singular Values", xlab = "Mode", ylab = "Value")

# Inspect the first few modes
# For example, plot the first mode across generations to see when selection might occur
plot(U[,1], type = 'l', main = "First Mode Across Generations", xlab = "Generation", ylab = "Mode Amplitude")

# Reconstruct the data using the first few modes (to capture selection signature)
reconstructed_data <- U[,1:2] %*% diag(singular_values[1:2]) %*% t(V[,1:2])

# Analyze reconstructed data to identify patterns of allele frequency changes over generations


```

```{r}
# Calculate the difference between original and reconstructed data
difference <- data_t - reconstructed_data

# Summary of the differences
summary(difference)

# Plot the difference for a particular genomic position across generations
plot(1:nrow(difference), difference[,1], type = 'l', main = "Difference for Genomic Position 1", 
     xlab = "Generation", ylab = "Difference in Allele Frequency")


```

```{r}
# Create the initial plot
plot(mode_1, type = 'l', main = 'First Temporal Mode', xlab = 'Generation', ylab = 'Mode 1 Value')

# Example: Highlighting significant changes in the first mode
threshold <- 0.1  # Define a threshold for significant change
significant_generations <- which(abs(diff(mode_1)) > threshold)
points(significant_generations, mode_1[significant_generations], col = 'red', pch = 19)

```
